### 2021-07-02 paper/paper.tex
add paper

\documentclass[RNAAS]{aastex631}
\usepackage{hyperref}
\let\tablenum\relax
\usepackage[output-exponent-marker = \text{e}]{siunitx}

%% Define new commands here
\newcommand\latex{La\TeX}

\graphicspath{{./}{figures/}}
\shortauthors{Lucas et al.}

\begin{document}

\title{A Search for Circumstellar Companions Around Nearby White Dwarf Sirius b}

\correspondingauthor{Miles Lucas}
\email{mdlucas@hawaii.edu}

\author[0000-0001-6341-310X]{Miles Lucas}
\affiliation{Institute for Astronomy, University of Hawai'i, USA}

\author[0000-0003-1341-5531]{Michael Bottom}
\affiliation{Institute for Astronomy, University of Hawai'i, USA}

\author{Garreth Ruane}
\author{Sam Ragland}

\begin{abstract}

\end{abstract}

\section{}

% \acknowledgments

% \software{
% astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},
% numpy \citep{harris2020array},
% scikit-image \citep{2014arXiv1407.6245V},
% }

\bibliography{references}{}
\bibliographystyle{aasjournal}

\end{document}

### 2021-07-02 src/SiriusB.jl
get environment setup

@@ -1,0 +1,13 @@
+module SiriusB
+
+export rootdir, datadir, srcdir, notebookdir
+
+# path configuration
+rootdir(args...) = joinpath(@__DIR__(), "..", args...)
+datadir(args...) = rootdir("data", args...)
+srcdir(args...) = rootdir("src", args...)
+notebookdir(args...) = rootdir("notebooks", args...)
+
+
+
+end

### 2021-07-19 paper/paper.tex
add dertection_limits notebook

@@
-\documentclass[RNAAS]{aastex631}
+\documentclass[twocolumn]{aastex631}
 \usepackage{hyperref}
@@
 
-\author{Garreth Ruane}
-\author{Sam Ragland}
+\author[0000-0003-4769-1665]{Garreth Ruane}
+\affiliation{Jet Propulsion Laboratory, California Institute of Technology, USA}
+
+\author[0000-0002-0696-1780]{Sam Ragland}
+\affiliation{W.M. Keck Observatory, USA}
 
@@
 
-\section{}
+\section{Introduction}
+
+Directly imaging exoplanets is a powerful method in exoplanet science which explores a parameter space very complementary to the popular transit photometry and radial velocity methods.
+Two of the key parameters that limit direct imaging are \textit{contrast}, the relative brightness between the host star and the companion, and \textit{separation}, due to the diffraction and seeing limited nature of astronomy, especially the effects of Earth's atmosphere above ground-based telescopes.
+Sirius B is an enticing prospect for a direct imaging search because it is very close, only \SI{2.7}{pc} away, which allows probing very close-in orbital separations, down to a few AU.
+Also, due to the strong cooling of white dwarfs, the luminosity will be 3-4 orders of magnitude less than its main sequence progenitor.
+This means current ground-based instrumetns can probe 3-4 orders of magnitude deeper into the planetary mass space.
+
+Any potential companion around an evolved star must have survived multiple stages of stellar evolution, notably the red giant phase and the asymptotic giant phase.
+In the red giant phase, the main sequence star inflates in a shell around the collapsing inert core.
+Any planet within the Roche limit of the expanding star will be engulfed, polluting the stellar atmosphere.
+In the asymptotic giant phase, the star will be blowing off mass in shells which can become highly ionized by strong ultraviolet and X-ray emission from the star, which has consequences for planetary atmospheres.
+By the end of the star's evolution, as it enters the white dwarf cooling sequence, it is expected that a planet beyond a critical separation (to escape engulfment during the red giant phase) will typically migrate outward as a function of the mass loss of the star.
+
+\section{Observations}
+
+Sirius is the closest star system to the Sun at \SI{2.7}{pc} away.
+The host, Sirius a is infamously one of the brightest stars in the sky, with a K-band magnitude of -1.35.
+Sirius b has a well-studied orbit
+
+\section{Analysis}
+
+For each epoch
 

### 2021-07-19 src/mass_models/__init__.py

@@ -1,0 +1,1 @@
+from .read_model import *

### 2021-07-19 src/mass_models/read_model.py

@@ -1,0 +1,202 @@
+# code from Mike that interpolates over tables of photometric models
+# such as AMES-COND, BT-SETTI, SONORA, and the like, allowing us to
+# estimate planetary masses from a given contrast
+
+import re
+
+import numpy as np
+from astropy.io import fits
+from astropy.table import Table
+from scipy.interpolate import interp2d
+
+__all__ = ["MassModel"]
+
+def Mj_to_solar(mass_MJ):
+    return mass_MJ / 1047.9
+
+
+def solar_to_Mj(mass_ms):
+    return mass_ms * 1047.9
+
+
+def distance_modulus(dist_pc):
+    return 5.0 * np.log10(dist_pc) - 5
+
+
+def extract_first_number_from_string(stringy):
+    allnums = re.findall(r"-?\d+\.?\d*", stringy)
+    firstnum = float(allnums[0])
+    return firstnum
+
+
+def get_headers(headerline):
+    # return the line column labels
+    # unfucking the M/MsTeff thing
+    return list(filter(None, headerline.replace("Teff", " Teff").split(" ")))
+
+
+def split_row(row):
+    bb = filter(None, row.split(" "))
+    return bb
+
+
+def parse_allard_file(fname):
+    with open(fname) as f:
+        content = f.readlines()
+        content = [x.strip() for x in content]
+
+    output = []
+    age = None
+    for line in content:
+        if "Gyr" in line:
+            age = extract_first_number_from_string(line)
+            continue
+        if "M/Ms" in line:
+            headers = get_headers(line)
+        else:
+            # split the row by spaces
+            row = split_row(line)
+            try:
+                numrow = [float(x) for x in row]
+                # if not empty
+                if numrow:
+                    output.append([1000 * age] + numrow)
+            except:
+                pass
+    tab = Table(np.array(output), names=["Age(Myr)"] + headers)
+    return tab.to_pandas()
+
+
+class MassModel:
+    def __init__(self, filename):
+        self.table = parse_allard_file(filename)
+
+    def get_below(self, item, amt, subtable=None):
+        # returns a subtable
+        # eg get_below('Age(Myr)', 1000) will return
+        # a subtable of the closest age at or below 1000 Myrs
+        if subtable is None:
+            subtable = self.table
[…]

### 2021-07-20 paper/paper.tex
update paper

--- 2021-07-02 paper/paper.tex
@@
 \usepackage[output-exponent-marker = \text{e}]{siunitx}
+
+\DeclareSIUnit\parsec{pc}
+\DeclareSIUnit\au{AU}
+\DeclareSIUnit\mj{M_J}
+\DeclareSIUnit\year{yr}
 
@@
 
+\shorttitle{A Search for Circumstellar Companions around Sirius b}
+\shortauthors{Lucas et al.}
+
 \correspondingauthor{Miles Lucas}
@@
 
-\section{}
+\section{Introduction} \label{sec:intro}
 
-% \acknowledgments
+Very little is known about the evolution of planetary systems beyond the main-sequence lifetime of their host stars.
+Theoretical calculations show that planets can survive the red giant and asymptotic giant stages \citep{burleigh_imaging_2002,jura_pollution_2008,nordhaus_orbits_2013}, and results from radial velocity and transit surveys suggest extrasolar planets are prevalent throughout the Milky Way \citep{cumming_keck_2008}.
+However, only one planetary mass object has been detected around a white dwarf (WD) with imaging \citep[WD 0806-661;][]{luhman_discovery_2011}.
 
-% \software{
-% astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},
-% numpy \citep{harris2020array},
-% scikit-image \citep{2014arXiv1407.6245V},
-% }
+Directly imaging exoplanets is a powerful method in exoplanet science which explores a parameter space very complementary to the popular transit photometry and radial velocity methods.
+The red giant stage has cleared planets within a few \si{au} greatly lowering the transit probability.
+White dwarfs have very few spectral lines to make high-precision radial velocity measurements from spectral lines.
+Imaging, though, benefits from the orbital expansion of the planet, and the cooling of the white dwarf greatly reduces the contrast between them \citep{burleigh_imaging_2002,gould_finding_2008}.
+The Degenerate Objects around Degenerate Objects (DODO) survey observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC and provided upper limits around $\sim$\SI{8}{\mj} beyond \SI{35}{\au} \citep{hogan_dodo_2009}.
+
+In this work we study the closest white dwarf to the Sun, Sirius b, and provide upper mass limits based on our observations in the near-infrared.
+\autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.
+
+\section{Observations} \label{sec:obs}
+
+Sirius is the closest star system to the Sun at \SI{2.7}{\parsec} away, consisting of an A1Vm star (a) and a WD with an age around \SI{225}{\mega\year} \citep{bond_sirius_2017,collaboration_gaia_2018}.
+There are no known planets around either star, and using constrained 3-body numerical simulations a potential companion around Sirius b would only be stable with a \SI{1.79}{\year} orbit, which corresponds to a circular orbit with \SI{1.5}{\au} separation.
+Sirius b has been studied in the \SI{10}{\micro\meter} regime recently by \cite{pathak_high_2021}, who achieve \SIrange[]{1.8}{3.5}{\mj} upper limits within 2 arcseconds.
+
+We targeted Sirius b directly using Keck/NIRC2 in Lp-band across three epochs in 2020 \autoref{tbl:obs}.
+Due to the high proper motion and reasonable orbital motion, we started by calculating the projected offset and position angle from Sirius a based on the orbital parameters from \cite{bond_sirius_2017}.
+We first slewed to Sirius a, which is easy to lock onto due to its brightness \citep[-1.35 K-band magnitude;][]{bonnet-bidaud_adonis_2008}.
+We found that Sirius b is too dim \citep[9.01 K-band magnitude;][]{bonnet-bidaud_adonis_2008} for the adaptive optics (AO) performance necessary for coronagraphy and that the scattered light from Sirius a was detrimental to closing the AO loop when using Sirius b as a natural guide star (NGS) anyways.
+Therefore, we employed a unique off-axis solution, using a narrow laser-line filter for the wavefront sensor using Sirius a as the NGS and offsetting to Sirius b manually.
+
+The scattered light from Sirius a is so strong, in fact, that radial diffraction spikes from the Keck II secondary mirror support structure are still present in the Sirius b frames, which reduced our overall observing efficiency due to discarding these frames.
+An example of such a diffraction spike is shown in \autoref{fig:spike}.
+
+\begin{figure}
+    \centering
+    \epsscale{1}
+    \plotone{spike}
+    \caption{Calibrated science frame of Sirius b from 2020-02-04 epoch showing the strong scattered light effects from Sirius a.}
+    \label{fig:spike}
+\end{figure}
+
+\begin{deluxetable*}{ccccc}
+    % \tabletypesize{\scriptsize}
+    \tablecaption{Observing parameters for the three epochs of data.
+All observations were carried out using the NIRC2 Lp-band filter.
+Observation time is based on the frames that were selected for processing.
+    \label{tbl:obs}}
+    \tablehead{
+        \colhead{Date observed} & 
+        \colhead{Observation time (hr)} & 
+        \colhead{Seeing (arcsec)} & 
+        \colhead{Temp (\textdegree C)} & 
+        \colhead{PWV (mm)}
+    }
+    \startdata
+    2020-02-04 & 1.44 &  &  &  \\
+    2020-11-21 & 2.91 &  &  &  \\
+    2020-11-28 & 2.44 &  &  &  \\
+    \enddata
+\end{deluxetable*}
+
+\section{Analysis} \label{sec:analysis}
+
+\section{Results} \label{sec:results}
+
+\section{Conclusions} \label{sec:conclusion}
+
+\begin{acknowledgments}
+
+\end{acknowledgments}
+
+\software{
+ADI.jl \citep{lucas_adijl_2020},
+astropy \citep{collaboration_astropy_2013,astropy_collaboration_astropy_2018},
+Julia \citep{bezanson_julia_2017},
+numpy \citep{harris_array_2020},
+scikit-image \citep{walt_scikit-image_2014},
+}
 

### 2021-07-20 paper/figures/spike.jl

@@ -1,0 +1,20 @@
+using PlotUtils: zscale
+using PyCall
+using SiriusB
+
+fits = pyimport("astropy.io.fits")
+pro = pyimport("proplot")
+
+# rcParams
+pro.rc["image.origin"] = "lower"
+pro.rc["image.cmap"] = "inferno"
+
+data_cube = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_cube_calib.fits"))
+frame = data_cube[88, :, :]
+
+fig, axs = pro.subplots(figwidth="3.5in")
+ax = first(axs)
+vmin, vmax = zscale(frame)
+ax.imshow(frame; vmin, vmax)
+ax.format(xlabel="x", ylabel="y", grid=false)
+fig.save(joinpath(@__DIR__, "spike.pdf"))

### 2021-07-20 paper/paper.tex
update offset code and add to paper

@@
 
-\begin{deluxetable*}{ccccc}
+\begin{deluxetable*}{ccccccc}
     % \tabletypesize{\scriptsize}
@@
         \colhead{Date observed} &
+        \colhead{Sirius a offset (")} &
+        \colhead{Sirius a PA (\textdegree)} &
         \colhead{Observation time (hr)} & 
@@
     \startdata
-    2020-02-04 & 1.44 &  &  &  \\
-    2020-11-21 & 2.91 &  &  &  \\
-    2020-11-28 & 2.44 &  &  &  \\
+    2020-02-04 & 11.20 & 67.90 & 1.44 &  &  &  \\
+    2020-11-21 & 11.27 & 66.42 & 2.91 &  &  &  \\
+    2020-11-28 & 11.27 & 66.38 & 2.44 &  &  &  \\
     \enddata
@@
 \section{Analysis} \label{sec:analysis}
+
+For each epoch we applied a flat correction using calibration frames captured during observing.
+We also removed bad pixels using a combination of L.A.Cosmic \citep{dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
+We finally remove sky background using a high-pass median filter.
+Each frame is co-registered and aligned with the center of the FOV and lastly cropped to the inner 200 pixels.
+With the pixel scale of \SI{10}{mas\per px} the crop corresponds to a maximum separation of \SI{2.7}{\au}.
+We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.
+
+We apply the technique of angular differential imaging \citep[ADI;][]{marois_angular_2006} where we disable the field rotator and allow the FOV to rotate throughout the night as Earth rotates.
+This apparent rotation isolates systematic noise from the telescope, which includes the point-spread function (PSF).
+By modeling and subtracting the PSF before derotating the frames to a common direction, potential companion signal is preserved since it does not appear stationary in the
 

### 2021-07-20 src/position.jl

@@ -5,13 +5,15 @@ in addition to the fact we were using Sirius A as the AO NGS and targeting
 Sirius B in an off-axis manner.
 =#
 
+using AstroAngles
 using AstroLib
+using Dates
 using Measurements
 using SkyCoords
 using Unitful, UnitfulAstro
 
 # http://simbad.u-strasbg.fr/simbad/sim-basic?Ident=sirius+a&submit=SIMBAD+search
-sirius = ICRSCoords("06:45:08.91728", "-16:42:48.0171")
+sirius = ICRSCoords(hms"06:45:08.91728", dms"-16:42:48.0171")
 parallax = 379.21e-3 #mas
 distance = 1 / parallax # pc
 
@@ -41,17 +43,29 @@ r(t) = a * (1 - e^2) / (1 + e * cos(ν(t)))
 pa(t) = Ω + atan(tan(ν(t) + ω) * cos(i))
 sep(t) = r(t) * cos(ν(t) + ω) / cos(pa(t) - Ω)
 
-t = 2020.8876712328767123u"yr" # time for 11/20/2020
-t = 2020.9094227697923797u"yr" # time for 11/27/2020
-ρ_arcsec = sep(t)
-θ = pa(t)
+year_val(epoch) = year_val(Date(epoch))
+year_val(epoch::TimeType) = year(epoch) + (dayofyear(epoch) - 1) / daysinyear(epoch)
 
-ρ = deg2rad(ρ_arcsec / 3600)
-θ_deg = rad2deg(θ)
+for epoch in ["2020-02-04", "2020-11-21", "2020-11-28"]
+    t = year_val(epoch)u"yr"
+    ρ = sep(t)
+    θ = pa(t) |> rad2deg
 
 
-println("ρ= $ρ_arcsec\", θ= $(θ_deg)°")
-println("offset: $(ρ_arcsec .* sincosd(θ_deg))")
+    @info epoch=epoch t ρ θ
+end
+
+# t = 2020.8876712328767123u"yr" # time for 11/20/2020
+# t = 2020.9094227697923797u"yr" # time for 11/27/2020
+# ρ_arcsec = sep(t)
+# θ = pa(t)
+
+# ρ = deg2rad(ρ_arcsec / 3600)
+# θ_deg = rad2deg(θ)
+
+
+# println("ρ= $ρ_arcsec\", θ= $(θ_deg)°")
+# println("offset: $(ρ_arcsec .* sincosd(θ_deg))")
 
 
[…]

### 2021-07-20 paper/paper.tex
update paper

@@
 We finally remove sky background using a high-pass median filter.
-Each frame is co-registered and aligned with the center of the FOV and lastly cropped to the inner 200 pixels.
+At this point frames were manually filtered to remove bad frames, especially those with diffraction spikes like in \autoref{fig:spike}.
+Then, each good frame is co-registered using cross-correlations \citep{guizar-sicairos_efficient_2008} and aligned with the center of the FOV.
+Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch.
 With the pixel scale of \SI{10}{mas\per px} the crop corresponds to a maximum separation of \SI{2.7}{\au}.
@@
 
-We apply the technique of angular differential imaging \citep[ADI;][]{marois_angular_2006} where we disable the field rotator and allow the FOV to rotate throughout the night as Earth rotates.
-This apparent rotation isolates systematic noise from the telescope, which includes the point-spread function (PSF).
-By modeling and subtracting the PSF before derotating the frames to a common direction, potential companion signal is preserved since it does not appear stationary in the
+During observing we applied the technique of angular differential imaging \citep[ADI;][]{marois_angular_2006} where we disable the field rotator and allow the FOV to rotate throughout the night along with Earth.
+The point-spread function (PSF), which is an instrumental effect, will not appear to rotate while any potential companion will appear to rotate.
+This allows modeling and subtracting the PSF with less probability for subtracting companion signal.
+After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
+
+For this analysis we used three statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we model the PSF in annuli of increasing separation, since each annulus has similar statistcal properties under the framework of ADI \citep{marois_angular_2006}.
+
+We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) detection map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}.
+These metrics assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
+The SLIM map is an ensemble statistic which calculates the average STIM map from many residual cubes, such as many variations of PCA with differing number of components.
+
+Another metric we calculate for some of the algorithms is the contrast curve, which determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
+We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
 
 \section{Results} \label{sec:results}
+
+The flat residual images from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian S/N maps and STIM maps.
+The best performing algorithms for each epoch in terms of sensitivity were median subtraction median subtraction, and PCA subtraction with 2 principal components.
+For each epoch we determined there was not significant evidence for a companion around Sirius b.
 

### 2021-07-21 paper/paper.tex
add mroe figures and update paper

@@
 We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.
+For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (an example of one is shown in \autoref{fig:psf}).
+
+\begin{figure}
+    \centering
+    \epsscale{1}
+    \plotone{psf}
+    \caption{The median frame from the 2020-11-21 epoch showing the instrumental PSF.
+The inner core has a FWHM of $\sim$\SI{76}{mas}.
+The speckle pattern can be seen in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shapes of the segmented mirrors.}
+    \label{fig:psf}
+\end{figure}
 
@@
 
-The flat residual images from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian S/N maps and STIM maps.
+\begin{figure*}
+    \centering
+    \epsscale{1.1}
+    \plotone{residuals}
+    \caption{The flat residuals of each epoch after PSF subtraction, derotating, and collapsing. The inner full-width at half-maximum (FWHM) is masked out for each frame.}
+    \label{fig:residuals}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \epsscale{1.1}
+    \plotone{snr}
+    \caption{The S/N maps for each epoch calculated with Gaussian noise assumptions. The inner full-width at half-maximum (FWHM) is masked out for each map.}
+    \label{fig:snr}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \epsscale{1.1}
+    \plotone{stim}
+    \caption{The STIM maps for each epoch calculated from the residual cube.
+Note that the STIM probability has a typical cutoff threshold of 0.5 for significant detections.
+The inner full-width at half-maximum (FWHM) is masked out for each map.}
+    \label{fig:stim}
+\end{figure*}
+
 The best performing algorithms for each epoch in terms of sensitivity were median subtraction median subtraction, and PCA subtraction with 2 principal components.
+The flat residual images from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian S/N maps (\autoref{fig:snr}) and STIM maps (\autoref{fig:stim}).
 For each epoch we determined there was not significant evidence for a companion around Sirius b.

### 2021-07-21 paper/figures/psf.jl

@@ -1,0 +1,46 @@
+using HCIToolbox
+using PlotUtils: zscale
+using PyCall
+using SiriusB
+
+
+fits = pyimport("astropy.io.fits")
+pro = pyimport("proplot")
+
+# rcParams
+pro.rc["image.origin"] = "lower"
+pro.rc["image.cmap"] = "inferno"
+pro.rc["grid"] = false
+
+cube= fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_cube_calib_registered_crop.fits"))
+
+flat = collapse(cube)
+
+function norm_psf(frame)
+    tmp = frame .- minimum(frame)
+    return tmp ./ maximum(tmp)
+    # return log10.(tmp ./ maximum(tmp))
+end
+psf = norm_psf(flat)
+
+tick_locs = range(20, 179, length=5)
+tick_labs = @. string(round(0.01 * (tick_locs - 99.5), digits=1))
+
+py"""
+import proplot as pro
+from matplotlib.colors import LogNorm
+
+fig, axs = pro.subplots(figwidth="3.5in")
+
+axs[0].imshow($psf, norm=LogNorm(vmin=3e-3, vmax=5e-2))
+axs[0].format(title="Epoch 2020-11-21")
+axs.format(
+    xticks=$tick_locs,
+    xticklabels=$tick_labs,
+    yticks=$tick_locs,
+    yticklabels=$tick_labs,
+    xlabel="x [arcsec]",
+    ylabel="y [arcsec]",
+)
+fig.save($(joinpath(@__DIR__, "psf.pdf")))
+"""

### 2021-07-21 paper/figures/residuals.jl

@@ -1,0 +1,190 @@
+using ADI
+using PyCall
+using SiriusB
+
+
+fits = pyimport("astropy.io.fits")
+pro = pyimport("proplot")
+
+# rcParams
+pro.rc["image.origin"] = "lower"
+pro.rc["image.cmap"] = "inferno"
+pro.rc["grid"] = false
+
+cube1 = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_cube_calib_registered_crop.fits"))
+angles1 = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_pa.fits"))
+
+cube2 = fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_cube_calib_registered_crop.fits"))
+angles2 = fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_pa.fits"))
+
+cube3 = fits.getdata(datadir("epoch_2020nov28", "processed", "2020nov28_sirius-b_cube_calib_registered_crop.fits"))
+angles3 = fits.getdata(datadir("epoch_2020nov28", "processed", "2020nov28_sirius-b_pa.fits"))
+
+
+res1 = subtract(Classic(), mask_circle(cube1, 7.985399074538929))
+res2 = subtract(Classic(), mask_circle(cube2, 7.644946278252633))
+res3 = subtract(PCA(2), mask_circle(cube3, 8.216162087416189))
+
+flat_res1 = collapse(res1, angles1)
+flat_res2 = collapse(res2, angles2)
+flat_res3 = collapse(res3, angles3)
+
+sn_1 = detectionmap(flat_res1, 7.985399074538929)
+sn_2 = detectionmap(flat_res2, 7.644946278252633)
+sn_3 = detectionmap(flat_res3, 8.216162087416189)
+
+stim_1 = stimmap(res1, angles1)
+stim_2 = stimmap(res2, angles2)
+stim_3 = stimmap(res3, angles3)
+
+
+tick_locs = range(20, 179, length=5)
+tick_labs = @. string(round(0.01 * (tick_locs - 99.5), digits=1))
+
+py"""
+import proplot as pro
+fig, axs = pro.subplots(ncols=3, wspace="1em", figwidth="7in")
+
[…]

### 2021-07-23 paper/paper.tex
update paper

@@
 
-For this analysis we used three statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
+For this analysis we used four statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, non-negative matrix factorization\citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
 The median subtraction and PCA methods were also applied in an annular method, where we model the PSF in annuli of increasing separation, since each annulus has similar statistcal properties under the framework of ADI \citep{marois_angular_2006}.
@@
 
+\appendix
+
+\section{ADI Processing Results}
+
+\include{sections/adi_results}
+
+\begin{figure*}
+    \plotone{2020feb04_contrast_curves}
+    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-02-04 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
+\end{figure*}
+
+\begin{figure*}
+    \plotone{2020nov21_contrast_curves}
+    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-21 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
+\end{figure*}
+
+\begin{figure*}
+    \plotone{2020nov28_contrast_curves}
+    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-28 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
+\end{figure*}
+
 \end{document}

### 2021-07-23 paper/sections/adi_results.tex
update paper

\figsetstart
\figsetnum{6}
\figsettitle{ADI processing results}

\figsetgrpstart
\figsetgrpnum{6.1}
\figsetgrptitle{2020-02-04 median}
\figsetplot{reports/2020feb04_median}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.2}
\figsetgrptitle{2020-02-04 PCA(2)}
\figsetplot{reports/2020feb04_pca-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.3}
\figsetgrptitle{2020-02-04 NMF(2))}
\figsetplot{reports/2020feb04_nmf-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.4}
\figsetgrptitle{2020-02-04 GreeDS(2)}
\figsetplot{reports/2020feb04_greeds-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.5}
\figsetgrptitle{2020-02-04 annular median}
\figsetplot{reports/2020feb04_annular_median}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.6}
\figsetgrptitle{2020-02-04 annular PCA(2))}
\figsetplot{reports/2020feb04_annular_pca-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.7}
\figsetgrptitle{2020-02-04 annular NMF(2)}
\figsetplot{reports/2020feb04_annular_nmf-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.8}
\figsetgrptitle{2020-11-21 median subtraction.}
\figsetplot{reports/2020nov21_median}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.9}
\figsetgrptitle{2020-11-21 PCA subtraction with 2 components.}
\figsetplot{reports/2020nov21_pca-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.10}
\figsetgrptitle{2020-11-21 NMF subtraction with 2 components.}
\figsetplot{reports/2020nov21_nmf-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.11}
\figsetgrptitle{2020-11-21 GreeDS with 2 components.}
\figsetplot{reports/2020nov21_greeds-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.12}
\figsetgrptitle{2020-11-21 annular median subtraction with a rotation threshold of 0.5.}
\figsetplot{reports/2020nov21_annular_median}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.13}
\figsetgrptitle{2020-11-21 annular PCA subtraction with 2 components and a rotation threshold ofnov21 0.5.}
\figsetplot{reports/2020nov21_annular_pca-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.14}
\figsetgrptitle{2020-11-21 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
\figsetplot{reports/2020nov21_annular_nmf-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.15}
\figsetgrptitle{2020-11-28 median subtraction.}
\figsetplot{reports/2020nov28_median}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.16}
\figsetgrptitle{2020-11-28 PCA subtraction with 2 components.}
\figsetplot{reports/2020nov28_pca-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.17}
\figsetgrptitle{2020-11-28 NMF subtraction with 2 components.}
\figsetplot{reports/2020nov28_nmf-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.18}
\figsetgrptitle{2020-11-28 GreeDS with 2 components.}
\figsetplot{reports/2020nov28_greeds-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.19}
\figsetgrptitle{2020-11-28 annular median subtraction with a rotation threshold of 0.5.}
\figsetplot{reports/2020nov28_annular_median}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.20}
\figsetgrptitle{2020-11-28 annular PCA subtraction with 2 components and a rotation threshold ofnov28 0.5.}
\figsetplot{reports/2020nov28_annular_pca-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{6.21}
\figsetgrptitle{2020-11-28 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
\figsetplot{reports/2020nov28_annular_nmf-2}
\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\figsetgrpend

\figsetend

\begin{figure*}
\figurenum{6}
\plotone{reports/2020feb04_median}
\caption{Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
\end{figure*}

### 2021-07-23 paper/figures/pca_nmf_greeds.jl

@@ -1,0 +1,137 @@
+using ADI
+using ProgressLogging
+using PSFModels: Gaussian
+using PyCall
+using SiriusB
+
+fits = pyimport("astropy.io.fits")
+pro = pyimport("proplot")
+
+pro.use_style("ggplot")
+pro.rc["image.cmap"] = "inferno"
+pro.rc["image.origin"] = "lower"
+pro.rc["grid"] = false
+
+parallax = 376.6801e-3 # arcseconds
+pxscale = 0.01 # arcsec / px
+auscale = pxscale / parallax # AU / px
+
+
+function plot_mosaic(res_cubes, angles; epoch, label, ncomps)
+    py"""
+    import proplot as pro
+    fig, axs = pro.subplots(nrows=6, ncols=5, share=3, width="7.5in", space=0)
+    """
+    i = 0
+    for (n, res) in zip(res_cubes, ncomps)
+        lab = "ncomp=$n"
+        flat = collapse(res, angles)
+        py"""
+        axs[$i].imshow($flat)
+        axs[$i].text(6, 6, $lab, color="w")
+        """
+        i += 1
+    end
+
+    ticks = range(40, 159, length=3)
+    tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
+
+    py"""
+    axs.format(
+        yticks=$ticks,
+        yticklabels=$tick_labs,
+        ylabel="y [arcsec]"
+        xticks=$ticks,
+        xticklabels=$tick_labs,
+        xlabel="x [arcsec]",
+    )
+    fig.savefig($(figuredir(make_filename_friendly("$(epoch)_$(label)_mosaic") * ".pdf")))
+    """
+end
+
+function plot_results(contrast_curves; epoch, label)
+    py"""
+    import proplot as pro
+    fig, axs = pro.subplots(width="7.5in", height="4in")
+    cycle = pro.Cycle("viridis", $(length(res_cubes)))
+    lines = []
+    """
+    i = 0
+    for (label, curve) in contrast_curves
+        dist = curve.distance .* auscale
+        color = "C$i"
+        py"""
+        l = axs.plot($dist, $(curve.contrast), cycle=cycle, color=$color)
+        lines.append(l)
+        """
+        i += 1
+    end
+    py"""
+    axs.text(0.25, 5e-4, $(_epochs[epoch]), fontsize=14)
+    fig.colorbar(lines, label="ncomp")
[…]

### 2021-07-23 paper/figures/reports.jl

@@ -1,0 +1,179 @@
+using ADI
+using ProgressLogging
+using PSFModels: Gaussian
+using PyCall
+using SiriusB
+
+fits = pyimport("astropy.io.fits")
+pro = pyimport("proplot")
+
+pro.use_style("ggplot")
+pro.rc["image.cmap"] = "inferno"
+pro.rc["image.origin"] = "lower"
+pro.rc["grid"] = false
+
+parallax = 376.6801e-3 # arcseconds
+pxscale = 0.01 # arcsec / px
+auscale = pxscale / parallax # AU / px
+
+function plot_results(res_cube, angles, curve; fwhm, epoch, label)
+    # produce images
+    flat_res = collapse(res_cube, angles)
+    snr_map = detectionmap(flat_res, fwhm)
+    sig_map = detectionmap(significance, flat_res, fwhm)
+    stim_map = stimmap(res_cube, angles)
+
+    arcsec = curve.distance .* pxscale
+
+    ticks = range(20, 179, length=5)
+    tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
+    # start plotting
+    # NB: proplot does tricky things with the Axes class that doesn't play nicely
+    # with PyCall.jl because it's treated as a Vector in Julia, so use Python
+    # syntax instead
+    py"""
+    import proplot as pro
+
+    layout = [[1, 2, 5, 5],
+              [3, 4, 5, 5]]
+    fig, axs = pro.subplots(
+        layout,
+        width="7.5in",
+        wspace=("3.25em", "2.5em", "0"),
+        hspace="1.25em",
+        share=0
+    )
+    axs[0].imshow($flat_res, colorbar="r", colorbar_kw=dict(space=0))
+    axs[0].text(6, 6, "flat residual", color="w")
+    axs[2].imshow($stim_map, vmin=0, vmax=1, colorbar="r", colorbar_kw=dict(space=0))
+    axs[2].text(6, 6, "STIM prob.", color="w")
+    axs[1].imshow($snr_map, vmin=0, vmax=5, colorbar="r", colorbar_kw=dict(space=0))
+    axs[1].text(6, 6, "S/N", color="w")
+    axs[3].imshow($sig_map, vmin=0, vmax=5, colorbar="r", colorbar_kw=dict(space=0))
+    axs[3].text(6, 6, "significance", color="w")
+
+    axs[0].format(xticks="null")
+    axs[1].format(xticks="null", yticks="null")
[…]

### 2021-07-23 src/SiriusB.jl

@@ -4,13 +4,16 @@ using Dates
 using FITSIO
 using SkyCoords
 
-export rootdir, datadir, srcdir, notebookdir, parallactic_angles, gaussian_fit, gaussian_fit_offset
+export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir,
+       parallactic_angles, gaussian_fit, gaussian_fit_offset
 
 # path configuration
 rootdir(args...) = joinpath(@__DIR__(), "..", args...)
 datadir(args...) = rootdir("data", args...)
 srcdir(args...) = rootdir("src", args...)
 notebookdir(args...) = rootdir("notebooks", args...)
+paperdir(args...) = rootdir("paper", args...)
+figuredir(args...) = paperdir("figures", args...)
 
 
 """

### 2021-07-24 paper/paper.tex
update paper

@@
 \DeclareSIUnit\mj{M_J}
+\DeclareSIUnit\ms{M_\odot}
 \DeclareSIUnit\year{yr}
@@
 
-Very little is known about the evolution of planetary systems beyond the main-sequence lifetime of their host stars.
+High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets.
+Being able to probe the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory.
+The process required to image a planet is daunting, however.
+The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim10^{-8}$, and for a Sun-Earth system are $\sim10^{-10}$ \citep{traub_direct_2010}.
+In addition, the close angular separation of planets makes it difficult to distinguish them from the diffraction pattern of the star and other noise sources.
+In order to make such a difficult detection it is imperative to minimize diffraction, scattering, and systematic noise.
+
+Nearby white dwarfs (within $\sim$\qty{100}{\parsec}) are compelling targets for direct imaging searches, despite the limited knowledge of planetary systems around evolved stars.
+\cite{burleigh_imaging_2002} suggests planets on initially wide (>\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\ms}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf.
+During the asymptotic giant (AGB) phase, strong ionizing soft X-ray and UV emission will likely photoevaporate planetary atmospheres.
+In addition,  the mass loss of the star will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{WD}}/M_{*,\mathrm{MS}}$ \citep{jeans_cosmogonic_1924}.
+
 Theoretical calculations show that planets can survive the red giant and asymptotic giant stages \citep{burleigh_imaging_2002,jura_pollution_2008,nordhaus_orbits_2013}, and results from radial velocity and transit surveys suggest extrasolar planets are prevalent throughout the Milky Way \citep{cumming_keck_2008}.
+
 However, only one planetary mass object has been detected around a white dwarf (WD) with imaging \citep[WD 0806-661;][]{luhman_discovery_2011}.
@@
 Directly imaging exoplanets is a powerful method in exoplanet science which explores a parameter space very complementary to the popular transit photometry and radial velocity methods.
-The red giant stage has cleared planets within a few \si{au} greatly lowering the transit probability.
+The red giant stage has cleared planets within a few \unit{au} greatly lowering the transit probability.
 White dwarfs have very few spectral lines to make high-precision radial velocity measurements from spectral lines.
 Imaging, though, benefits from the orbital expansion of the planet, and the cooling of the white dwarf greatly reduces the contrast between them \citep{burleigh_imaging_2002,gould_finding_2008}.
-The Degenerate Objects around Degenerate Objects (DODO) survey observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC and provided upper limits around $\sim$\SI{8}{\mj} beyond \SI{35}{\au} \citep{hogan_dodo_2009}.
+The Degenerate Objects around Degenerate Objects (DODO) survey observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC and provided upper limits around $\sim$\qty{8}{\mj} beyond \qty{35}{\au} \citep{hogan_dodo_2009}.
 
@@
 
+Sirius is one of the closest star system to the Sun at \qty{2.7}{\parsec} away, consisting of an A1Vm star (a) and a WD with an age around \qty{225}{\mega\year} \citep{bond_sirius_2017,collaboration_gaia_2018}.
+There are no known planets around either star, and using constrained 3-body numerical simulations a potential companion around Sirius b would only be stable with a \qty{1.79}{\year} orbit, which corresponds to a circular orbit with \qty{1.5}{\au} separation.
+Sirius b has been studied in the \qty{10}{\micro\meter} regime recently by \cite{pathak_high_2021}, who achieve \qtyrange[]{1.8}{3.5}{\mj} upper limits within 2 arcseconds.
+
 \section{Observations} \label{sec:obs}
 
-Sirius is the closest star system to the Sun at \SI{2.7}{\parsec} away, consisting of an A1Vm star (a) and a WD with an age around \SI{225}{\mega\year} \citep{bond_sirius_2017,collaboration_gaia_2018}.
-There are no known planets around either star, and using constrained 3-body numerical simulations a potential companion around Sirius b would only be stable with a \SI{1.79}{\year} orbit, which corresponds to a circular orbit with \SI{1.5}{\au} separation.
-Sirius b has been studied in the \SI{10}{\micro\meter} regime recently by \cite{pathak_high_2021}, who achieve \SIrange[]{1.8}{3.5}{\mj} upper limits within 2 arcseconds.
+We targeted Sirius B directly using Keck/NIRC2 in Lp-band across three epochs in 2020 (\autoref{tbl:obs}).
+Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
+The adaptive optics (AO) calibration routinely failed when the extremely bright (-1.35 K-band magnitude) diffraction patterns would sweep into the field of view (FoV) of Sirius B (shown in \autoref{fig:spike}).
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the low-order wavefront correction algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
+In order to overcome these issues, we decided to try using Sirius A as the NGS and off-axis guiding to Sirius B.
 
-We targeted Sirius b directly using Keck/NIRC2 in Lp-band across three epochs in 2020 \autoref{tbl:obs}.
-Due to the high proper motion and reasonable orbital motion, we started by calculating the projected offset and position angle from Sirius a based on the orbital parameters from \cite{bond_sirius_2017}.
-We first slewed to Sirius a, which is easy to lock onto due to its brightness \citep[-1.35 K-band magnitude;][]{bonnet-bidaud_adonis_2008}.
-We found that Sirius b is too dim \citep[9.01 K-band magnitude;][]{bonnet-bidaud_adonis_2008} for the adaptive optics (AO) performance necessary for coronagraphy and that the scattered light from Sirius a was detrimental to closing the AO loop when using Sirius b as a natural guide star (NGS) anyways.
-Therefore, we employed a unique off-axis solution, using a narrow laser-line filter for the wavefront sensor using Sirius a as the NGS and offsetting to Sirius b manually.
+The Keck AO system \citep{wizinowich_performance_2000} was not designed to accomadate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the wavefront sensor (WFS).
+We accomplished this using a narrow laser-line filter in front of the WFS, which brought Sirius A from $\sim$ -1.35 mag down to $\sim$ 5 mag.
+While still extremely bright, this was enough attenuation to close the AO loop.
+From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \cite{bond_sirius_2017}.
+In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
+For both the November epochs we tried exploiting this by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter method we used in \autoref{sec:analysis}.
+We tried deploying the vortex coronagraph along with QACITS, but again the scattered light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
 
-The scattered light from Sirius a is so strong, in fact, that radial diffraction spikes from the Keck II secondary mirror support structure are still present in the Sirius b frames, which reduced our overall observing efficiency due to discarding these frames.
-An example of such a diffraction spike is shown in \autoref{fig:spike}.
+During each observation, calibration frames were taken in the form of dark frames and sky flat frames.
+We also disabled the field rotator, which caused the FoV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
 
@@
 
-\begin{deluxetable*}{ccccccc}
-    % \tabletypesize{\scriptsize}
+\begin{deluxetable*}{ccccccccc}
+    \tabletypesize{\scriptsize}
     \tablecaption{Observing parameters for the three epochs of data.
@@
         \colhead{Date observed} &
-        \colhead{Sirius a offset (")} &
-        \colhead{Sirius a PA (\textdegree)} &
+        \colhead{Sirius A offset (arcsec)} &
+        \colhead{Sirius A PA (\textdegree)} &
         \colhead{Observation time (hr)} & 
+        \colhead{FoV rotation (\textdegree)} &
+        \colhead{FWHM (mas)} &
         \colhead{Seeing (arcsec)} & 
@@
     \startdata
-    2020-02-04 & 11.20 & 67.90 & 1.44 &  &  &  \\
-    2020-11-21 & 11.27 & 66.42 & 2.91 &  &  &  \\
-    2020-11-28 & 11.27 & 66.38 & 2.44 &  &  &  \\
+    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & &  &  \\
+    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & &  &  \\
+    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & &  &  \\
     \enddata
@@
 We also removed bad pixels using a combination of L.A.Cosmic \citep{dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
-We finally remove sky background using a high-pass median filter.
-At this point frames were manually filtered to remove bad frames, especially those with diffraction spikes like in \autoref{fig:spike}.
-Then, each good frame is co-registered using cross-correlations \citep{guizar-sicairos_efficient_2008} and aligned with the center of the FOV.
+We removed sky background using a high-pass median filter with a box size of 31 pixels.
+At this point frames were manually filtered to remove bad frames, especially those with diffraction spikes within a few hundred pixels, like in \autoref{fig:spike}.
+Then, each good frame is co-registered using cross-correlations \citep{guizar-sicairos_efficient_2008} as a first-order correction and then fitting each frame with a Gaussian PSF.
+The co-registered frames are then shifted to the center of the FoV.
 Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch.
-With the pixel scale of \SI{10}{mas\per px} the crop corresponds to a maximum separation of \SI{2.7}{\au}.
+With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \qty{1}{"} or a projected separation of \qty{2.7}{\au}.
 We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.
 For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (an example of one is shown in \autoref{fig:psf}).
+All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the reduced data cubes and parallactic angles have been made available on Zenodo \citep{lucas_nirc2_2021}.
 
@@
     \caption{The median frame from the 2020-11-21 epoch showing the instrumental PSF.
-The inner core has a FWHM of $\sim$\SI{76}{mas}.
+The inner core has a FWHM of $\sim$\qty{76}{mas}.
 The speckle pattern can be seen in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shapes of the segmented mirrors.}
@@
 
-During observing we applied the technique of angular differential imaging \citep[ADI;][]{marois_angular_2006} where we disable the field rotator and allow the FOV to rotate throughout the night along with Earth.
-The point-spread function (PSF), which is an instrumental effect, will not appear to rotate while any potential companion will appear to rotate.
+By taking data with the field rotator disabled (ADI), the point-spread function (PSF), which is an instrumental effect, will not appear to rotate while any potential companion will appear to rotate.
 This allows modeling and subtracting the PSF with less probability for subtracting companion signal.
@@
 
-For this analysis we used four statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, non-negative matrix factorization\citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we model the PSF in annuli of increasing separation, since each annulus has similar statistcal properties under the framework of ADI \citep{marois_angular_2006}.
+For this analysis we used four statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we model the PSF in annuli of increasing separation frame-by-frame, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
 
-We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) detection map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}.
-These metrics assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
-The SLIM map is an ensemble statistic which calculates the average STIM map from many residual cubes, such as many variations of PCA with differing number of components.
+We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve.
+The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
+The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
+We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
+The collapsed residual frames along with the above metrics for each algorithm for each epoch can be found in \autoref{sec:adi-results}.
 
-Another metric we calculate for some of the algorithms is the contrast curve, which determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
-We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
+Another metric we explored was the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}.
+The SLIM map is an ensemble statistic which calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
+We use the SLIM map with the PCA, NMF, and GreeDS algorithms because they all depend on choosing the number of basis components, which is hard to determine \textit{a priori}.
+For each algorithm, we create residual cubes for increasing number of components, from 1 to 10.
+The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms can be found in \autoref{sec:adi-results}.
+All of the code for these reductions can be found at the GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}}.
 
@@
     \centering
-    \epsscale{1.1}
+    \epsscale{1}
     \plotone{residuals}
@@
     \centering
-    \epsscale{1.1}
-    \plotone{snr}
-    \caption{The S/N maps for each epoch calculated with Gaussian noise assumptions. The inner full-width at half-maximum (FWHM) is masked out for each map.}
-    \label{fig:snr}
+    \epsscale{1}
+    \plotone{sig}
+    \caption{The \textit{significance} maps for each epoch accounting for small sample statistics \citep{mawet_fundamental_2014}.
+Typically a critical value for detection is 5.
+The inner full-width at half-maximum (FWHM) is masked out for each map.}
+    \label{fig:sig}
 \end{figure*}
@@
     \centering
-    \epsscale{1.1}
+    \epsscale{1}
     \plotone{stim}
@@
 
-The best performing algorithms for each epoch in terms of sensitivity were median subtraction median subtraction, and PCA subtraction with 2 principal components.
-The flat residual images from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian S/N maps (\autoref{fig:snr}) and STIM maps (\autoref{fig:stim}).
-For each epoch we determined there was not significant evidence for a companion around Sirius b.
+We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
+For the 2020-02-04 and 2020-11-21 epochs full-frame median subtraction had the best contrast at all separations.
+For the 2020-11-28 epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.5}{1}{"}) and had similar performance to other algorithms beyond \qty{1}{"}.
+The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).
+
+In these images there is not \textit{consistent} or overwhelming evidence for a substellar companion.
+The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\qty{0.13}{"} from the center.
+The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star ($\sim$2 FWHM) all discredit the probability of these blobs being companions.
+Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient" algorithm \citep[OFTI;][]{blunt_orbits_2017}.
+We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}).
+We take this as direct evidence against the blobs being substellar companions of any kind.
+
+The contrast maps from the best performing algorithm for each reduction are shown in \autoref{fig:contrast}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
+Then we use an age of \qty{225}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
+The best performing epoch was the 2020-11-21 night, which managed to reach an exceptional sensitivity of \qtylist[list-units=single]{3.5;1.9;1.1;0.72;0.63}{\mj} at projected separations of \qtylist[list-units=single]{0.25;0.5;0.75;1;2}{\au} (\qtylist[list-units=single]{0.09;0.19;0.28;0.38;0.75}{"}) respectively.
+
+\begin{figure*}[t]
+    \centering
+    \epsscale{1}
+    \plotone{contrast_curves}
+    \caption{The contrast curves for the best performing algorithm from each epoch.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected cuves \citep{mawet_fundamental_2014}.
+In addition, the expected upper limit for orbital separation of a stable orbit \citep{bond_sirius_2017} of \qty{1.5}{\au} are plotted in a vertical dashed line.
+The companion mass values are interpolated from the AMES-Cond grid \citep{allard_models_2012}.
+The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.}
+    \label{fig:contrast}
+\end{figure*}
 
 \section{Conclusions} \label{sec:conclusion}
+
+It is interesting to note that there is a symmetric shape in the residual frames from GreeDS and NMF for the November epochs.
+Both these algorithms were designed for imaging disks, so it is natural to consider this structure to be some kind of circumstellar debris disk.
 
@@
 
-\section{ADI Processing Results}
+\section{ADI Processing Results} \label{sec:adi-results}
 
@@
 
+\section{Provisional Orbit Fitting} \label{sec:orbits}
+
+\begin{deluxetable*}{ccc}
+    \tablecaption{Provisional astrometry for blobs of interesest from each epoch. The uncertainties are represented in parantheses and are derived from the FWHM of the PSF from each epoch.
+    \label{tbl:astrometry}}
+    \tablehead{
+        \colhead{Date observed} &
+        \colhead{offset (mas)} &
+        \colhead{PA (\textdegree)}
+    }
+    \startdata
+    2020-02-04 & 193(38) & -99(11)  \\
+    2020-11-21 & 125(38) & 75(17)  \\
+    2020-11-28 & 215(40) & 23(11)  \\
+    \enddata
+\end{deluxetable*}
+
+\begin{figure*}
+    \plotone{orbit}
+    \caption{Provisional orbits fit using OFTI with $10^4$ orbits. None of the orbits contain all three points within their uncertainties.}
+\end{figure*}
+
 \end{document}

### 2021-07-24 paper/figures/contrast.jl

@@ -1,0 +1,90 @@
+using CSV
+using DataFrames
+using PyCall
+using SiriusB
+
+pro = pyimport("proplot")
+# rcParams
+pro.use_style("ggplot")
+pro.rc["image.origin"] = "lower"
+pro.rc["image.cmap"] = "inferno"
+pro.rc["grid"] = false
+
+py"""
+import sys
+sys.path.append($(srcdir()))
+"""
+models = pyimport("mass_models")
+model = models.MassModel(srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt"))
+
+parallax = 376.6801e-3 # arcseconds
+pxscale = 0.01 # arcseconds/px
+auscale = pxscale / parallax # AU/px
+age = 225; # Myr
+
+contrast_curves = [
+    DataFrame(CSV.File(datadir("epoch_2020feb04", "processed", "2020feb04_contrast-curve_median.csv"))),
+    DataFrame(CSV.File(datadir("epoch_2020nov21", "processed", "2020nov21_contrast-curve_median.csv"))),
+    DataFrame(CSV.File(datadir("epoch_2020nov28", "processed", "2020nov28_contrast-curve_annular-PCA-2.csv"))),
+]
+
+contrast_to_dmag(contrast) = -2.5 * log10(contrast)
+
+function dmag_to_mass(dmag)
+    model.contrast_to_mass(
+        deltaMag=dmag,
+        age_Myr=age,
+        band="Lp",
+        dist_pc=1/parallax,
+        stellar_apparent_mag=9.1
+    )
+end
+
+distances = [curve.distance .* auscale for curve in contrast_curves]
+
+masses = map(contrast_curves) do curve
+    dmag = contrast_to_dmag.(curve.contrast)
+    dmag_to_mass.(dmag)
+end
+
+masses_corr = map(contrast_curves) do curve
+    dmag = contrast_to_dmag.(curve.contrast_corr)
+    dmag_to_mass.(dmag)
+end
+
+py"""
+import proplot as pro
+fig, axs = pro.subplots(width="7.5in", height="4in")
+
+axs.plot($(distances[1]), $(masses[1]), c="C0", label="  2020-02-04\n     median")
+axs.plot($(distances[1]), $(masses_corr[1]), c="C0", ls="--")
+
[…]

### 2021-07-24 paper/figures/pca_nmf_greeds.jl

@@ -20,7 +20,7 @@ auscale = pxscale / parallax # AU / px
 function plot_mosaic(res_cubes, angles; epoch, label, ncomps)
     py"""
     import proplot as pro
-    fig, axs = pro.subplots(nrows=6, ncols=5, share=3, width="7.5in", space=0)
+    fig, axs = pro.subplots(nrows=2, ncols=5, share=3, width="7.5in", space=0)
     """
     i = 0
     for (n, res) in zip(res_cubes, ncomps)
@@ -49,26 +49,55 @@ function plot_mosaic(res_cubes, angles; epoch, label, ncomps)
     """
 end
 
-function plot_results(contrast_curves; epoch, label)
+function plot_results(res_cubes, angles, contrast_curves; epoch, label, fwhm)
     py"""
     import proplot as pro
-    fig, axs = pro.subplots(width="7.5in", height="4in")
+    fig, axs = pro.subplots([[1, 3], [2, 3]], share=0, width="7.5in")
     cycle = pro.Cycle("viridis", $(length(res_cubes)))
     lines = []
     """
+    # plot the average STIM map and SLIM probability map
+    ticks = range(20, 179, length=5)
+    tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
+
+    stimmap, slimmask = slimmap(res_cubes, angles; N=cil(Int, π/4 * fwhm^2))
+    slimprob = stimmap .* slimmask
+    py"""
+    axs[0].imshow($stimmap, vmin=0, vmax=1)
+    axs[0].text(6, 6, "mean STIM", color="w")
+    m = axs[1].imshow($slimprob, vmin=0, vmax=1)
+    axs[1].text(6, 6, "SLIM map", color="w")
+    fig.colorbar(m, loc="l")
+
+    axs[0].format(
+        ylabel="y [arcsec]"
+        yticks=$ticks
+        yticklabels=$tick_labs
+        xticks="null"
+    )
+    axs[1].format(
+        ylabel="y [arcsec]"
+        xlabel="x [arcsec]"
+        yticks=$ticks
+        yticklabels=$tick_labs
+        xticks=$ticks
+        yticklabels=$tick_labs
+    )
+    """
+    # now plot contrast curves
     i = 0
     for (label, curve) in contrast_curves
         dist = curve.distance .* auscale
         color = "C$i"
         py"""
[…]

### 2021-07-24 paper/figures/reports.jl

@@ -147,7 +147,7 @@ end
     @info "FWHM for epoch $epoch is $fwhm px"
     starphot = Metrics.estimate_starphot(cube, fwhm)
     psfphot = Metrics.estimate_starphot(psf_model, fwhm) * exp(res[4])
-    @info "star photometry is ≈ $starphot (PSF amp was $psfphot)"
+    @info "star photometry is ≈ $starphot (PSF photometry was $psfphot)"
     
     # naturally mask out inner FWHM
     av_cube = AnnulusView(cube .- minimum(cube); inner=fwhm)

### 2021-07-24 paper/figures/residuals.jl

@@ -11,45 +11,49 @@ pro.rc["image.origin"] = "lower"
 pro.rc["image.cmap"] = "inferno"
 pro.rc["grid"] = false
 
-cube1 = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_cube_calib_registered_crop.fits"))
-angles1 = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_pa.fits"))
+epochs = [
+    "2020feb04",
+    "2020nov21",
+    "2020nov28"
+]
+cubes = [
+    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_cube_calib_registered_crop.fits"))
+    for epoch in epochs
+]
+angles = [
+    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_pa.fits"))
+    for epoch in epochs
+]
+fwhms = [
+    7.985399074538929,
+    7.644946278252633,
+    8.216162087416189
+]
 
-cube2 = fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_cube_calib_registered_crop.fits"))
-angles2 = fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_pa.fits"))
-
-cube3 = fits.getdata(datadir("epoch_2020nov28", "processed", "2020nov28_sirius-b_cube_calib_registered_crop.fits"))
-angles3 = fits.getdata(datadir("epoch_2020nov28", "processed", "2020nov28_sirius-b_pa.fits"))
-
-
-res1 = subtract(Classic(), mask_circle(cube1, 7.985399074538929))
-res2 = subtract(Classic(), mask_circle(cube2, 7.644946278252633))
-res3 = subtract(PCA(2), mask_circle(cube3, 8.216162087416189))
-
-flat_res1 = collapse(res1, angles1)
-flat_res2 = collapse(res2, angles2)
-flat_res3 = collapse(res3, angles3)
-
-sn_1 = detectionmap(flat_res1, 7.985399074538929)
-sn_2 = detectionmap(flat_res2, 7.644946278252633)
-sn_3 = detectionmap(flat_res3, 8.216162087416189)
-
[…]

### 2021-07-26 src/SiriusB.jl
update angles

@@ -15,45 +15,10 @@ notebookdir(args...) = rootdir("notebooks", args...)
 paperdir(args...) = rootdir("paper", args...)
 figuredir(args...) = paperdir("figures", args...)
 
+function load_or_produce(func, filename; force=false)
 
-"""
-    parallactic_angles(filelist; latitude=19.82636)
 
-Calculate the parallactic angless(in degrees) for the given FITS files in the middle of the exposure. Uses the given 
-`latitude` which defaults to the Keck II site.
-"""
-function parallactic_angles(filelist; latitude=19.82636)
-    map(filelist) do filename
-        # get header
-        header = read_header(filename)
-
-        # compute the hour angle at the middle of the frame
-        exp_start = Time(header["EXPSTART"])
-        exp_stop = Time(header["EXPSTOP"])
-        exp_mid = Dates.value((exp_stop - exp_start) / 2)
-        # convert exp_mid from nanoseconds of time to degrees
-        Δha = exp_mid / 1e9 / 24 / 10
-        ha_mid = header["HA"] + Δha
-
-        # precess the star coordinates to the appropriate epoch
-        ra = deg2rad(header["RA"])
-        dec = deg2rad(header["DEC"])
-        coord = FK5Coords{2000}(ra, dec)
-        obs_epoch = Date(header["DATE-OBS"])
-        yr = year(obs_epoch) + (dayofyear(obs_epoch) - 1) / daysinyear(obs_epoch)
-        coord_curr = convert(FK5Coords{yr}, coord)
-
-        # derive true PA at the middle of the frame
-        ra = coord_curr.ra
-        dec = coord_curr.dec
-        PA = -rad2deg(atan(-sind(ha_mid), cos(dec) * tand(latitude) - sin(dec) * cosd(ha_mid)))
-        # apply instrumental effects
-        PA += header["ROTPOSN"] - header["INSTANGL"] + (header["PARANG"] - header["PARANTEL"])
-
-        return PA
-    end
-end
-
+include("angles.jl")
 include("fitting.jl")
 include("badpix.jl")
 

### 2021-07-26 src/angles.jl

@@ -1,0 +1,38 @@
+
+
+"""
+    parallactic_angles(filelist; latitude=19.82636)
+
+Calculate the parallactic angles (in degrees) for the given FITS files in the middle of the exposure. Uses the given 
+`latitude` which defaults to the Keck II site.
+"""
+parallactic_angles(filelist; kwargs...) = map(f -> parallactic_angle(read_header(f); kwargs...), filelist)
+
+parallactic_angles(filelist::DataFrame; kwargs...) = map(r -> parallactic_angle(r; kwargs...), eachrow(filelist))
+
+function parallactic_angle(row; latitude=19.82636)
+    # compute the hour angle at the middle of the frame
+    exp_start = Time(row["EXPSTART"])
+    exp_stop = Time(row["EXPSTOP"])
+    exp_mid = Dates.value((exp_stop - exp_start) / 2)
+    # convert exp_mid from nanoseconds of time to degrees
+    Δha = exp_mid / 1e9 / 24 / 10
+    ha_mid = row["HA"] + Δha
+
+    # precess the star coordinates to the appropriate epoch
+    ra = deg2rad(row["RA"])
+    dec = deg2rad(row["DEC"])
+    coord = FK5Coords{2000}(ra, dec)
+    obs_epoch = Date(row["DATE-OBS"])
+    yr = year(obs_epoch) + (dayofyear(obs_epoch) - 1) / daysinyear(obs_epoch)
+    coord_curr = convert(FK5Coords{yr}, coord)
+
+    # derive true PA at the middle of the frame
+    ra = coord_curr.ra
+    dec = coord_curr.dec
+    PA = -rad2deg(atan(-sind(ha_mid), cos(dec) * tand(latitude) - sin(dec) * cosd(ha_mid)))
+    # apply instrumental effects
+    PA += row["ROTPOSN"] - row["INSTANGL"] + (row["PARANG"] - row["PARANTEL"])
+
+    return PA
+end

### 2021-07-26 src/SiriusB.jl
add more functionality to module

@@ -1,11 +1,17 @@
 module SiriusB
 
+using CSV
+using DataFrames
 using Dates
 using FITSIO
+import ImageTransformations: center
 using SkyCoords
+using PyCall
 
-export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir,
-       parallactic_angles, gaussian_fit, gaussian_fit_offset
+export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir, load_or_produce,
+       parallactic_angles, gaussian_fit, gaussian_fit_offset, center
+
+fits = pyimport("astropy.io.fits")
 
 # path configuration
 rootdir(args...) = joinpath(@__DIR__(), "..", args...)
@@ -15,7 +21,48 @@ notebookdir(args...) = rootdir("notebooks", args...)
 paperdir(args...) = rootdir("paper", args...)
 figuredir(args...) = paperdir("figures", args...)
 
+"""
+    load_or_produce(f, filename; force=false)
+
+Load the data from `filename` if it exists, otherwise (or if `force` is true) produce the data using the function `f`. This is a simplified version of the system DrWatson.jl uses for organization and reproducibility. To facilitate loading and saving, only ".fits" and ".csv" files are supported.
+
+# Examples
+
+```julia
+using ADI
+load_or_produce("flat_res_pca-2.csv") do
+    PCA(2)(cube, angles)
+end
+```
+"""
 function load_or_produce(func, filename; force=false)
+    ext = last(splitext(filename))
+
+    if !isfile(filename) || force
+        @info "$filename not found, producing..."
+        res = func()
+        SAVER[ext](filename, res)
+        @info "file saved to $filename"
+        return res
+    else
+        @info "file loaded from $filename"
+        return LOADER[ext](filename)
+    end        
+end
+
+const LOADER = Dict(
+    ".csv" => load_csv,
+    ".fits" => load_fits
+)
+load_fits(filename; kwargs...) = Array(fits.getdata(filename; kwargs...))
+load_csv(filename; kwargs...) = DataFrame(CSV.File(filename; kwargs...))
+
+const SAVER = Dict(
+    ".csv" => save_csv,
+    ".fits" => save_fits
+)
+save_fits(filename, data; kwargs...) = fits.writeto(filename, Array(data); overwrite=true, kwargs...)
+save_csv(filename, data; kwargs...) = CSV.write(data, filename; kwargs...)
 
 
 include("angles.jl")

### 2021-07-26 src/fitting.jl

@@ -23,11 +23,11 @@ function loss(X::AbstractVector{T}, target::SubArray) where T
 end
 
 """
-    gaussian_fit(frame, guess=(256.5, 256.5))
+    gaussian_fit(frame, guess=center(frame))
 
 Fit a 2D Gaussian PSF profile to `frame` centered around `guess` and return the best fitting parameters `[x, y, FWHM, log(Amp)]`.
 """
-function gaussian_fit(frame::AbstractMatrix{T}, guess=(256.5, 256.5); sub_size=100) where T
+function gaussian_fit(frame::AbstractMatrix{T}, guess=center(frame); sub_size=100) where T
     # crop target view for speed
     half_size = sub_size ÷ 2
     indsx = round(Int, guess[1]-half_size):round(Int, guess[1]+half_size)
@@ -40,13 +40,14 @@ function gaussian_fit(frame::AbstractMatrix{T}, guess=(256.5, 256.5); sub_size=1
 end
 
 """
-    gaussian_fit_offset(frame, guess=(256.5, 256.5))
+    gaussian_fit_offset(frame, guess=center(frame))
 
 Fit a 2D Gaussian PSF profile to `frame` centered around `guess` and return the offset from the center. Combine this with `HCIToolbox.shift_frame` for registering frames.
 """
 function gaussian_fit_offset(frame::AbstractMatrix{T}, args...; kwargs...) where T
     Xbest = gaussian_fit(frame, args...; kwargs...)
-    dx = 256.5 - Xbest[1]
-    dy = 256.5 - Xbest[2]
+    cy, cx = center(frame)
+    dx = cx - Xbest[1]
+    dy = cy - Xbest[2]
     return dx, dy
 end

### 2021-07-27 paper/paper.tex
update paper

@@
 \DeclareSIUnit\year{yr}
+\sisetup{
+    list-units=single
+}
 
@@
 
+We present the deepest study of planetary companions around Sirius B, the closest and brightest white dwarf in the night sky.
+We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 to take direct images of Sirius B.
+Each epoch was prepared and processed using the technique of angular differential imaging, which allowed us to reach exceptional sensitivity limits.
+The best-performing contrast from each epochs reached sensitivities of \qtylist{3.5;1.9;1.1;0.72;0.63}{\mj} at projected separations of \qtylist{0.25;0.5;0.75;1;2}{\au} (\qtylist{0.09;0.19;0.28;0.38;0.75}{\arcsecond}) respectively.
+These sensitivites are the best yet around Sirius B and are better than any limits reached around other evolved star.
+Despite the exceptional sensitivity of our observations, we do not report any additional companions around Sirius B.
+
 \end{abstract}
@@
 Nearby white dwarfs (within $\sim$\qty{100}{\parsec}) are compelling targets for direct imaging searches, despite the limited knowledge of planetary systems around evolved stars.
-\cite{burleigh_imaging_2002} suggests planets on initially wide (>\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\ms}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf.
+\cite{burleigh_imaging_2002} suggests planets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\ms}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf.
+Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, however the tidal forces on planets that readily escape engulfment are negligible.
 During the asymptotic giant (AGB) phase, strong ionizing soft X-ray and UV emission will likely photoevaporate planetary atmospheres.
-In addition,  the mass loss of the star will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{WD}}/M_{*,\mathrm{MS}}$ \citep{jeans_cosmogonic_1924}.
+In addition, the mass loss of the star will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
 
-Theoretical calculations show that planets can survive the red giant and asymptotic giant stages \citep{burleigh_imaging_2002,jura_pollution_2008,nordhaus_orbits_2013}, and results from radial velocity and transit surveys suggest extrasolar planets are prevalent throughout the Milky Way \citep{cumming_keck_2008}.
+If the planet has managed to survive through the RGB and AGB phases, stars below \qty{8}{\ms} will enter the white dwarf cooling sequence, which will lead to a reduction in luminosity by $10^3-10^4$.
+This means the contrast between a white dwarf and a companion will be 3-4 orders of magnitude lower than the equivalent main sequence system.
+The combination of expanded orbits and lower contrast are beneficial for imaging, due to the limited inner working angles and sensitivities of ground-based instrumentation.
+The transit photometry method is very insensitive to planets around white dwarfs because the probability of a transit decreases with increasing separation.
+Similarly, the radial velocity method is limited to very massive planets on larger separations in addition to the extremely broad spectral features of a white dwarf which greatly limit the precision of radial velocity measurements.
 
-However, only one planetary mass object has been detected around a white dwarf (WD) with imaging \citep[WD 0806-661;][]{luhman_discovery_2011}.
+The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by looking for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
+This excess could likely be attributed to circumstellar dust or gas discs, which are indicators of the planetary formation history.
+Of the $\sim$ 100 white dwarfs they studied, no companions were found.
+The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38.
+Eventually this excess was determined to be from a dust disc \citep{telesco_observations_1990}, with the current interpretation associating the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.
 
-Directly imaging exoplanets is a powerful method in exoplanet science which explores a parameter space very complementary to the popular transit photometry and radial velocity methods.
-The red giant stage has cleared planets within a few \unit{au} greatly lowering the transit probability.
-White dwarfs have very few spectral lines to make high-precision radial velocity measurements from spectral lines.
-Imaging, though, benefits from the orbital expansion of the planet, and the cooling of the white dwarf greatly reduces the contrast between them \citep{burleigh_imaging_2002,gould_finding_2008}.
-The Degenerate Objects around Degenerate Objects (DODO) survey observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC and provided upper limits around $\sim$\qty{8}{\mj} beyond \qty{35}{\au} \citep{hogan_dodo_2009}.
+The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\mj} on a very wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}.
+The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\mj} beyond \qty{35}{\au}.
+The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\mj} at \qty{6.2}{\au}.
+Sirius B has also been imaged, which will be discussed later.
+To date, there has been no direct images of an exoplanet around a white dwarf.
 
-In this work we study the closest white dwarf to the Sun, Sirius b, and provide upper mass limits based on our observations in the near-infrared.
+The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, an A1Vm star known for being the brightest in the night sky, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,collaboration_gaia_2018}.
+The proximity and brightness of the Sirius system make it one of the most well-studied systems throughout history \citep[see][]{wesemael_sirius_1982}.
+
+The orbit of Sirius B was first studied by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
+\citet{bond_companion_1862} reported and confirmed visual evidence of Sirius B by Alvan G.
+Clark and his father.
+\citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be very similar to a main-sequence early A-type star despite the faintness, which we know know to be typical of white dwarf specra.
+
+Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864}, with the first orbital solution including dynamic masses published by \citet{van_den_bos_orbit_1960}.
+\citet{gatewood_study_1978} improve upone the van den Bos orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary.
+\citet{bond_sirius_2017} greatly refine the orbit using a compilation of historical data and HST data, which gives dynamical masses of \qty{2.063+-0.023}{\ms} and \qty{1.018+-0.011}{\ms} for A and B, respectively.
+
+The precise dynamical masses are key for finding the age of Sirius; \citet{bond_sirius_2017} report a cooling age for Sirius B of \qty{126}{\mega\year} using isochrones.
+Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\ms}, which when combined with stellar evolution codes yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}.
+
+A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holman_long-term_1999}.
+\citet{bond_sirius_2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
+
+Some of the first modern studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\mj} at \ang{;;2} (\qty{5.3}{\au}).
+\citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\mj} at \ang{;;3} (\qty{7.9}{\au}).
+\citet{skemer_sirius_2011} used mid-IR (out to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
+\citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\mj} at \ang{;;1}.
+Very recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
+Because of the simultaneous observation, their contrast is split depending on which half of the FoV is being considered.
+Their average sensitivity is $\sim$\qty{2.5}{\mj} at $\sim$\qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\mj} at \qty{1}{\au}.
+
+In this work we report our study of Sirius B using direct images from Keck/NIRC2.
 \autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.
-
-Sirius is one of the closest star system to the Sun at \qty{2.7}{\parsec} away, consisting of an A1Vm star (a) and a WD with an age around \qty{225}{\mega\year} \citep{bond_sirius_2017,collaboration_gaia_2018}.
-There are no known planets around either star, and using constrained 3-body numerical simulations a potential companion around Sirius b would only be stable with a \qty{1.79}{\year} orbit, which corresponds to a circular orbit with \qty{1.5}{\au} separation.
-Sirius b has been studied in the \qty{10}{\micro\meter} regime recently by \cite{pathak_high_2021}, who achieve \qtyrange[]{1.8}{3.5}{\mj} upper limits within 2 arcseconds.
 
@@
 
-We targeted Sirius B directly using Keck/NIRC2 in Lp-band across three epochs in 2020 (\autoref{tbl:obs}).
+Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes dimmer than Sirius A, which makes it it a very technically challenging target, especially on ground-based telescopes which have to deal with extra scaterring and diffraction from the atmosphere.
+
+We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
@@
 Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the low-order wavefront correction algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
+This is very similar to the issues reported by \citet[\S2]{vigan_high-contrast_2015}  in their attempts to image Sirius B.
 In order to overcome these issues, we decided to try using Sirius A as the NGS and off-axis guiding to Sirius B.
@@
 
-Another metric we explored was the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}.
+Another metric used was the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}.
 The SLIM map is an ensemble statistic which calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
@@
 
+\begin{figure*}[t]
+    \centering
+    \epsscale{1}
+    \plotone{contrast_curves}
+    \caption{The contrast curves for the best performing algorithm from each epoch.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected cuves \citep{mawet_fundamental_2014}.
+In addition, the expected upper limit for orbital separation of a stable orbit \citep{bond_sirius_2017} of \qty{1.5}{\au} are plotted in a vertical dashed line.
+The companion mass values are interpolated from the AMES-Cond grid \citep{allard_models_2012}.
+The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.}
+    \label{fig:contrast}
+\end{figure*}
+
 We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
@@
 We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
-Then we use an age of \qty{225}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
-The best performing epoch was the 2020-11-21 night, which managed to reach an exceptional sensitivity of \qtylist[list-units=single]{3.5;1.9;1.1;0.72;0.63}{\mj} at projected separations of \qtylist[list-units=single]{0.25;0.5;0.75;1;2}{\au} (\qtylist[list-units=single]{0.09;0.19;0.28;0.38;0.75}{"}) respectively.
-
-\begin{figure*}[t]
-    \centering
-    \epsscale{1}
-    \plotone{contrast_curves}
-    \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected cuves \citep{mawet_fundamental_2014}.
-In addition, the expected upper limit for orbital separation of a stable orbit \citep{bond_sirius_2017} of \qty{1.5}{\au} are plotted in a vertical dashed line.
-The companion mass values are interpolated from the AMES-Cond grid \citep{allard_models_2012}.
-The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.}
-    \label{fig:contrast}
-\end{figure*}
+Then we use an age of \qty{226}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
+It is important to note how the precision of the system age (see \autoref{sec:intro}) leads to quite accurate interpolation on the evolutionary grids.
+The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qtylist[list-units=single]{3.5;1.9;1.1;0.72;0.63}{\mj} at projected separations of \qtylist[list-units=single]{0.25;0.5;0.75;1;2}{\au} (\qtylist[list-units=single]{0.09;0.19;0.28;0.38;0.75}{\arcsecond}) respectively.
 
@@
 
-It is interesting to note that there is a symmetric shape in the residual frames from GreeDS and NMF for the November epochs.
-Both these algorithms were designed for imaging disks, so it is natural to consider this structure to be some kind of circumstellar debris disk.
+In this work we demonstrate the results of high-contrast images of Sirius B in the near-IR.
+Our sensitivy limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\mj} at \qty{0.25}{\au}.
+In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\mj}.
+Despite the exceptional sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
+
+We have published alongside this work the entire codebase used for pre-processing the data, doing the ADI reductions, and for generating every figure in this manuscript.
+We have also published our reduced datasets under an open license.
+We hope that this improves the reproducibility of the work as well as providing data for exploring new and different ADI algorithms.
+
+This study also shows the capability for near-IR non-coronagraphic imaging for faint white dwarfs.
+Our sensitivity limits are deeper and closer than any other WD imaging results, even those using coronagraphs, thanks in no small part to the proximity of Sirius B.
+
+It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
+Both of these algorithms have been shown to outperform traditional median and PCA subtraction for disc imaging.
+In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen.
+Due to the nature of high-contrast imaging, it is extremely difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no evidence for IR excess from a circumstellar disc.
+Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disc.
+
+As this study and others have probed deeper and closer to Sirius B, we must consider, too, the astrophysics of post-main-sequence evolution.
+As mentioned in \autoref{sec:intro}, the expansion of the star during the RGB phase places a limit on the innermost orbital separation that would escape engulfment or strong tidal forces.
+A study into the evolution of the Sirius B progenitor through the RGB phase could provide these limits; it is possible we have reached those limits observationally and could provide some definitive answer to whether Sirius B has a companion.
 
@@
 \begin{figure*}
-    \plotone{orbit}
-    \caption{Provisional orbits fit using OFTI with $10^4$ orbits. None of the orbits contain all three points within their uncertainties.}
+    \plotone{orbit_frames}
+    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components.
+Each frame was been cropped to the inner \ang{;;0.25}.
+The inner FWHM has been masked out in each frame.}
+\end{figure*}
+
+\begin{figure*}
+    \plotone{orbit_corner}
+    \caption{Corner plot of the marginal posteriors from the OFTI samples.}
 \end{figure*}

### 2021-07-27 paper/figures/contrast.jl

@@ -20,12 +20,12 @@ model = models.MassModel(srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0
 parallax = 376.6801e-3 # arcseconds
 pxscale = 0.01 # arcseconds/px
 auscale = pxscale / parallax # AU/px
-age = 225; # Myr
+age = 226; # Myr
 
 contrast_curves = [
-    DataFrame(CSV.File(datadir("epoch_2020feb04", "processed", "2020feb04_contrast-curve_median.csv"))),
-    DataFrame(CSV.File(datadir("epoch_2020nov21", "processed", "2020nov21_contrast-curve_median.csv"))),
-    DataFrame(CSV.File(datadir("epoch_2020nov28", "processed", "2020nov28_contrast-curve_annular-PCA-2.csv"))),
+    DataFrame(CSV.File(datadir("epoch_2020feb04", "residuals", "2020feb04_contrast-curve_median.csv"))),
+    DataFrame(CSV.File(datadir("epoch_2020nov21", "residuals", "2020nov21_contrast-curve_median.csv"))),
+    DataFrame(CSV.File(datadir("epoch_2020nov28", "residuals", "2020nov28_contrast-curve_annular-pca-2.csv"))),
 ]
 
 contrast_to_dmag(contrast) = -2.5 * log10(contrast)

### 2021-07-27 paper/figures/orbits.jl

@@ -1,0 +1,153 @@
+using ADI
+using AstroTime
+using CSV
+using DataFrames
+using LinearAlgebra
+using Measurements
+using PyCall
+using PyPlot
+using SiriusB
+
+fits = pyimport("astropy.io.fits")
+driver = pyimport("orbitize.driver")
+pro = pyimport("proplot")
+
+# rcParams
+pro.rc["image.origin"] = "lower"
+pro.rc["image.cmap"] = "inferno"
+pro.rc["grid"] = false
+
+epochs = [
+    "2020feb04",
+    "2020nov21",
+    "2020nov28"
+]
+cubes = [
+    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_cube_calib_registered_crop.fits"))
+    for epoch in epochs
+]
+angles = [
+    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_pa.fits"))
+    for epoch in epochs
+]
+fwhms = [
+    7.985399074538929,
+    7.644946278252633,
+    8.216162087416189
+]
+av_cubes = [AnnulusView(cube; inner=fwhm) for (cube, fwhm) in zip(cubes, fwhms)]
+res_cubes = [subtract(GreeDS(2), av_cube; angles=angle) for (av_cube, angle) in zip(av_cubes, angles)]
+stims = [stimmap(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
+flat_res = [collapse(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
+
+parallax = 376.36801 # mas
+pxscale = 10 # mas/px
+
+
+errs = fwhms ./ 2
+
+# guesses from GreeDS outputs of three epochs
+pos = [
+    110.821 ± errs[1]  95.6414 ± errs[1];
+    111.024 ± errs[2]  94.5881 ± errs[2];
+    110.98 ± errs[3]  95.9881 ± errs[3];
+] # px coordinates
+
+ctr = hcat(center(flat_res[1])...)
+
+delta_px = pos .- ctr
+delta = delta_px .* pxscale
+
+###
+# plot the epochs
+# first, zoom in
+crop_res = @. crop(stims, 50)
+
+tick_locs = range(5, 43, length=3)
+tick_labs = @. string(round(0.01 * (tick_locs - 24.5), digits=1))
+
+
[…]

### 2021-07-27 paper/figures/reports.jl

@@ -169,8 +169,14 @@ end
 
     @progress "algorithm" for (alg, target, label) in targets
         @info label
-        res_cube = subtract(alg, target; angles, fwhm)
-        cc = contrast_curve(alg, target, angles, psf_model; fwhm, angles, starphot, nbranch=6)
+        filename = make_filename_friendly(datadir("epoch_$epoch", "residuals", "$(epoch)_sirius-b_residual_$label.fits"))
+        res_cube = load_or_produce(filename) do
+            subtract(alg, target; angles, fwhm)
+        end
+        filename = make_filename_friendly(datadir("epoch_$epoch", "residuals", "$(epoch)_sirius-b_contrast-curve_$label.csv"))
+        cc = load_or_produce(filename) do
+            contrast_curve(alg, target, angles, psf_model; fwhm, angles, starphot, nbranch=6)
+        end
         push!(contrast_curves, label => cc)
         plot_results(res_cube, angles, cc; fwhm, label, epoch)
     end

### 2021-07-27 src/SiriusB.jl

@@ -11,7 +11,7 @@ using PyCall
 export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir, load_or_produce,
        parallactic_angles, gaussian_fit, gaussian_fit_offset, center
 
-fits = pyimport("astropy.io.fits")
+const PYFITS = pyimport("astropy.io.fits")
 
 # path configuration
 rootdir(args...) = joinpath(@__DIR__(), "..", args...)
@@ -36,10 +36,11 @@ end
 ```
 """
 function load_or_produce(func, filename; force=false)
+    filename = normpath(filename)
     ext = last(splitext(filename))
 
     if !isfile(filename) || force
-        @info "$filename not found, producing..."
+        @info "$(normpath(filename)) not found, producing..."
         res = func()
         SAVER[ext](filename, res)
         @info "file saved to $filename"
@@ -50,20 +51,26 @@ function load_or_produce(func, filename; force=false)
     end        
 end
 
+
+load_fits(filename; kwargs...) = Array(PYFITS.getdata(filename; kwargs...))
+load_csv(filename; kwargs...) = DataFrame(CSV.File(filename; kwargs...))
 const LOADER = Dict(
     ".csv" => load_csv,
     ".fits" => load_fits
 )
-load_fits(filename; kwargs...) = Array(fits.getdata(filename; kwargs...))
-load_csv(filename; kwargs...) = DataFrame(CSV.File(filename; kwargs...))
 
+function save_fits(filename, data; kwargs...)
+    mkpath(dirname(filename))
+    PYFITS.writeto(filename, Array(data); overwrite=true, kwargs...)
+end
+function save_csv(filename, data; kwargs...)
+    mkpath(dirname(filename))
+    CSV.write(filename, data; kwargs...)
+end
 const SAVER = Dict(
     ".csv" => save_csv,
     ".fits" => save_fits
 )
-save_fits(filename, data; kwargs...) = fits.writeto(filename, Array(data); overwrite=true, kwargs...)
-save_csv(filename, data; kwargs...) = CSV.write(data, filename; kwargs...)
-
 
 include("angles.jl")
 include("fitting.jl")

### 2021-07-29 paper/paper.tex
update paper

@@
 \let\tablenum\relax
-\usepackage[output-exponent-marker = \text{e}]{siunitx}
+\usepackage{siunitx}
+\usepackage{makecell}
 
@@
 \DeclareSIUnit\au{AU}
-\DeclareSIUnit\mj{M_J}
-\DeclareSIUnit\ms{M_\odot}
+\DeclareSIUnit\jupitermass{M_J}
+\DeclareSIUnit\milliarcsecond{mas}
+\DeclareSIUnit\solarmass{M_\odot}
 \DeclareSIUnit\year{yr}
 \sisetup{
-    list-units=single
+    list-units=single,
+    separate-uncertainty
 }
@@
 
-\title{A Search for Circumstellar Companions Around Nearby White Dwarf Sirius b}
+\title{A Search for Circumstellar Companions of Sirius B}
 
-\shorttitle{A Search for Circumstellar Companions around Sirius b}
 \shortauthors{Lucas et al.}
@@
 \begin{abstract}
-
-We present the deepest study of planetary companions around Sirius B, the closest and brightest white dwarf in the night sky.
-We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 to take direct images of Sirius B.
-Each epoch was prepared and processed using the technique of angular differential imaging, which allowed us to reach exceptional sensitivity limits.
-The best-performing contrast from each epochs reached sensitivities of \qtylist{3.5;1.9;1.1;0.72;0.63}{\mj} at projected separations of \qtylist{0.25;0.5;0.75;1;2}{\au} (\qtylist{0.09;0.19;0.28;0.38;0.75}{\arcsecond}) respectively.
-These sensitivites are the best yet around Sirius B and are better than any limits reached around other evolved star.
-Despite the exceptional sensitivity of our observations, we do not report any additional companions around Sirius B.
-
+We present deep imaging of Sirius B, the closest and brightest white dwarf.
+We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging.
+We reach sub-Jupiter sensitivities at sub-AU separations, down to an ultimate sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}.
+Despite the high sensitivity of our observations, we do not detect any companions around Sirius B.
+These observations showcase that for nearby faint targets direct imaging is limited more by background noise than absolute contrast.
 \end{abstract}
@@
 Nearby white dwarfs (within $\sim$\qty{100}{\parsec}) are compelling targets for direct imaging searches, despite the limited knowledge of planetary systems around evolved stars.
-\cite{burleigh_imaging_2002} suggests planets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\ms}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf.
+\cite{burleigh_imaging_2002} suggests planets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\solarmass}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf.
 Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, however the tidal forces on planets that readily escape engulfment are negligible.
@@
 
-If the planet has managed to survive through the RGB and AGB phases, stars below \qty{8}{\ms} will enter the white dwarf cooling sequence, which will lead to a reduction in luminosity by $10^3-10^4$.
+If the planet has managed to survive through the RGB and AGB phases, stars below \qty{8}{\solarmass} will enter the white dwarf cooling sequence, which will lead to a reduction in luminosity by $10^3-10^4$.
 This means the contrast between a white dwarf and a companion will be 3-4 orders of magnitude lower than the equivalent main sequence system.
@@
 
-The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\mj} on a very wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}.
-The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\mj} beyond \qty{35}{\au}.
-The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\mj} at \qty{6.2}{\au}.
+The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a very wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}.
+The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
+The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.
 Sirius B has also been imaged, which will be discussed later.
@@
 Clark and his father.
-\citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be very similar to a main-sequence early A-type star despite the faintness, which we know know to be typical of white dwarf specra.
+\citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be very similar to a main-sequence early A-type star despite the faintness, which we know know to be typical of white dwarf spectra.
 
 Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864}, with the first orbital solution including dynamic masses published by \citet{van_den_bos_orbit_1960}.
-\citet{gatewood_study_1978} improve upone the van den Bos orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary.
-\citet{bond_sirius_2017} greatly refine the orbit using a compilation of historical data and HST data, which gives dynamical masses of \qty{2.063+-0.023}{\ms} and \qty{1.018+-0.011}{\ms} for A and B, respectively.
+\citet{gatewood_study_1978} improved upon the van den Bos orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary.
+\citet{bond_sirius_2017} greatly refine the orbit using a compilation of historical data and HST data, which gives dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 
 The precise dynamical masses are key for finding the age of Sirius; \citet{bond_sirius_2017} report a cooling age for Sirius B of \qty{126}{\mega\year} using isochrones.
-Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\ms}, which when combined with stellar evolution codes yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}.
+Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\solarmass}, which when combined with stellar evolution codes yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}.
+The precision of the system age is useful for constraining the mass of potential companions.
 
@@
 
-Some of the first modern studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\mj} at \ang{;;2} (\qty{5.3}{\au}).
-\citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\mj} at \ang{;;3} (\qty{7.9}{\au}).
+Some of the first modern studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}).
+\citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\jupitermass} at \ang{;;3} (\qty{7.9}{\au}).
 \citet{skemer_sirius_2011} used mid-IR (out to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
-\citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\mj} at \ang{;;1}.
+\citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
 Very recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
-Because of the simultaneous observation, their contrast is split depending on which half of the FoV is being considered.
-Their average sensitivity is $\sim$\qty{2.5}{\mj} at $\sim$\qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\mj} at \qty{1}{\au}.
+Because of the simultaneous observation, their contrast is split depending on which half of the FOV is being considered.
+Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.
 
@@
 
-Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes dimmer than Sirius A, which makes it it a very technically challenging target, especially on ground-based telescopes which have to deal with extra scaterring and diffraction from the atmosphere.
+Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes which have to deal with extra scattering and diffraction from the atmosphere.
 
@@
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
-The adaptive optics (AO) calibration routinely failed when the extremely bright (-1.35 K-band magnitude) diffraction patterns would sweep into the field of view (FoV) of Sirius B (shown in \autoref{fig:spike}).
-Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the low-order wavefront correction algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
+The adaptive optics (AO) calibration failed when the extremely bright (-1.35 K-band magnitude) diffraction patterns would sweep into the field of view (FOV) of the wavefront sensor (WFS).
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
 This is very similar to the issues reported by \citet[\S2]{vigan_high-contrast_2015} in their attempts to image Sirius B.
-In order to overcome these issues, we decided to try using Sirius A as the NGS and off-axis guiding to Sirius B.
+In order to overcome these issues, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
 
-The Keck AO system \citep{wizinowich_performance_2000} was not designed to accomadate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the wavefront sensor (WFS).
-We accomplished this using a narrow laser-line filter in front of the WFS, which brought Sirius A from $\sim$ -1.35 mag down to $\sim$ 5 mag.
-While still extremely bright, this was enough attenuation to close the AO loop.
+The Keck AO system \citep{wizinowich_performance_2000} was not designed to accommodate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the WFS.
+We experimented with different filters in front of the WFS, settling on a narrow laser-line filter which attenuated Sirius B by $\sim$6 magnitudes.
+While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
 From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \cite{bond_sirius_2017}.
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
-For both the November epochs we tried exploiting this by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter method we used in \autoref{sec:analysis}.
 We tried deploying the vortex coronagraph along with QACITS, but again the scattered light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
@@
 During each observation, calibration frames were taken in the form of dark frames and sky flat frames.
-We also disabled the field rotator, which caused the FoV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
+We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
 
@@
     \centering
-    \epsscale{1}
+    \epsscale{1.1}
     \plotone{spike}
@@
 \begin{deluxetable*}{ccccccccc}
-    \tabletypesize{\scriptsize}
+    \tabletypesize{\small}
     \tablecaption{Observing parameters for the three epochs of data.
@@
     \tablehead{
-        \colhead{Date observed} &
-        \colhead{Sirius A offset (arcsec)} &
-        \colhead{Sirius A PA (\textdegree)} &
-        \colhead{Observation time (hr)} & 
-        \colhead{FoV rotation (\textdegree)} &
-        \colhead{FWHM (mas)} &
-        \colhead{Seeing (arcsec)} & 
-        \colhead{Temp (\textdegree C)} & 
-        \colhead{PWV (mm)}
+        \colhead{\makecell{Date\\observed}} &
+        \colhead{\makecell{Sirius B\\offset} (\unit{\arcsecond})} &
+        \colhead{\makecell{Sirius B\\PA} (\unit{\degree})} &
+        \colhead{\makecell{Obs.\\time} (hr)} & 
+        \colhead{\makecell{FOV\\rotation} (\unit{\degree})} &
+        \colhead{FWHM (\unit{\milliarcsecond})} &
+        \colhead{Seeing (\unit{\arcsecond})} & 
+        \colhead{Temp (\unit{\celsius})} & 
+        \colhead{PWV (\unit{\milli\meter})}
     }
@@
 We removed sky background using a high-pass median filter with a box size of 31 pixels.
-At this point frames were manually filtered to remove bad frames, especially those with diffraction spikes within a few hundred pixels, like in \autoref{fig:spike}.
-Then, each good frame is co-registered using cross-correlations \citep{guizar-sicairos_efficient_2008} as a first-order correction and then fitting each frame with a Gaussian PSF.
-The co-registered frames are then shifted to the center of the FoV.
+For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter.
+At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}.
+Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF.
+The co-registered frames are then shifted to the center of the FOV.
 Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch.
-With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \qty{1}{"} or a projected separation of \qty{2.7}{\au}.
+With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
 We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.
-For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (an example of one is shown in \autoref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the reduced data cubes and parallactic angles have been made available on Zenodo \citep{lucas_nirc2_2021}.
+For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
+All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles have been made available on Zenodo \citep{lucas_nirc2_2021}.
 
@@
     \centering
-    \epsscale{1}
+    \epsscale{1.1}
     \plotone{psf}
     \caption{The median frame from the 2020-11-21 epoch showing the instrumental PSF.
-The inner core has a FWHM of $\sim$\qty{76}{mas}.
-The speckle pattern can be seen in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shapes of the segmented mirrors.}
+The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}.
+The speckle pattern can be seen in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
     \label{fig:psf}
@@
 
-By taking data with the field rotator disabled (ADI), the point-spread function (PSF), which is an instrumental effect, will not appear to rotate while any potential companion will appear to rotate.
-This allows modeling and subtracting the PSF with less probability for subtracting companion signal.
+By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate.
+This reduces the probability of subtracting companion signal when we subtract the stellar PSF model.
 After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
 
-For this analysis we used four statistical models for modeling the stellar PSF, classic median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we model the PSF in annuli of increasing separation frame-by-frame, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
+For this analysis we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation frame-by-frame, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
 
@@
 
-Another metric used was the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020}.
-The SLIM map is an ensemble statistic which calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
-We use the SLIM map with the PCA, NMF, and GreeDS algorithms because they all depend on choosing the number of basis components, which is hard to determine \textit{a priori}.
-For each algorithm, we create residual cubes for increasing number of components, from 1 to 10.
+A common problem when using subspace-driven ADI algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
+In our analysis we employ the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
+The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
+A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without having to settle on the number of components ahead of time.
+For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
+We chose 10 as the max number of components because we saw a dramatic dropoff in contrast sensitivity after the first few components.
 The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms can be found in \autoref{sec:adi-results}.
-All of the code for these reductions can be found at the GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}}.
+
+All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}.
+All of the code for the ADI processing in this paper, including the scripts for each figure produced can be found at the GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} in Jupyter notebooks and Julia scripts.
 
@@
     \centering
-    \epsscale{1}
+    \epsscale{0.95}
     \plotone{residuals}
@@
     \centering
-    \epsscale{1}
+    \epsscale{0.95}
     \plotone{sig}
@@
     \centering
-    \epsscale{1}
+    \epsscale{0.95}
     \plotone{stim}
@@
     \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected cuves \citep{mawet_fundamental_2014}.
-In addition, the expected upper limit for orbital separation of a stable orbit \citep{bond_sirius_2017} of \qty{1.5}{\au} are plotted in a vertical dashed line.
-The companion mass values are interpolated from the AMES-Cond grid \citep{allard_models_2012}.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
+The companion mass values are interpolated from the AMES-Cond grid.
 The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.}
@@
 We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
-For the 2020-02-04 and 2020-11-21 epochs full-frame median subtraction had the best contrast at all separations.
-For the 2020-11-28 epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.5}{1}{"}) and had similar performance to other algorithms beyond \qty{1}{"}.
+For the first two epochs full-frame median subtraction had the best contrast at all separations.
+For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
 The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).
@@
 In these images there is not \textit{consistent} or overwhelming evidence for a substellar companion.
-The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\qty{0.13}{"} from the center.
-The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star ($\sim$2 FWHM) all discredit the probability of these blobs being companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient" algorithm \citep[OFTI;][]{blunt_orbits_2017}.
+The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} from the center.
+The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star ($\sim$2 FWHM) all reduce the probability of these blobs being true companions.
+Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
 We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}).
 We take this as direct evidence against the blobs being substellar companions of any kind.
+
+It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
+Both of these algorithms have been shown to outperform traditional median and PCA subtraction for disk imaging.
+In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen.
+Due to the nature of high-contrast imaging, it is extremely difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no evidence for IR excess from a circumstellar disk.
+Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.
 
@@
 It is important to note how the precision of the system age (see \autoref{sec:intro}) leads to quite accurate interpolation on the evolutionary grids.
-The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qtylist[list-units=single]{3.5;1.9;1.1;0.72;0.63}{\mj} at projected separations of \qtylist[list-units=single]{0.25;0.5;0.75;1;2}{\au} (\qtylist[list-units=single]{0.09;0.19;0.28;0.38;0.75}{\arcsecond}) respectively.
+The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the sky-background limited regime.
 
@@
 In this work we demonstrate the results of high-contrast images of Sirius B in the near-IR.
-Our sensitivy limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\mj} at \qty{0.25}{\au}.
-In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\mj}.
-Despite the exceptional sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
+Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au}.
+In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}.
+Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
 
-We have published alongside this work the entire codebase used for pre-processing the data, doing the ADI reductions, and for generating every figure in this manuscript.
+We have published alongside this work the entire codebase used for pre-processing and reducing the data, and for generating every figure in this manuscript.
 We have also published our reduced datasets under an open license.
@@
 
-This study also shows the capability for near-IR non-coronagraphic imaging for faint white dwarfs.
-Our sensitivity limits are deeper and closer than any other WD imaging results, even those using coronagraphs, thanks in no small part to the proximity of Sirius B.
+In recent years improving contrast and inner working angle were the dominant parameters of interest.
+Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the background noise than the speckle noise.
+Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}.
+This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.
 
-It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
-Both of these algorithms have been shown to outperform traditional median and PCA subtraction for disc imaging.
-In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen.
-Due to the nature of high-contrast imaging, it is extremely difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no evidence for IR excess from a circumstellar disc.
-Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disc.
-
-As this study and others have probed deeper and closer to Sirius B, we must consider, too, the astrophysics of post-main-sequence evolution.
-As mentioned in \autoref{sec:intro}, the expansion of the star during the RGB phase places a limit on the innermost orbital separation that would escape engulfment or strong tidal forces.
-A study into the evolution of the Sirius B progenitor through the RGB phase could provide these limits; it is possible we have reached those limits observationally and could provide some definitive answer to whether Sirius B has a companion.
+In closing,
 
@@
 
-\include{sections/adi_results}
+\input{sections/adi_results_full}
 
-\begin{figure*}
-    \plotone{2020feb04_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-02-04 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
-\end{figure*}
-
-\begin{figure*}
-    \plotone{2020nov21_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-21 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
-\end{figure*}
-
-\begin{figure*}
-    \plotone{2020nov28_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-28 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
-\end{figure*}
-
+\clearpage
 \section{Provisional Orbit Fitting} \label{sec:orbits}
 
-\begin{deluxetable*}{ccc}
+\begin{deluxetable}{ccc}[h!]
     \tablecaption{Provisional astrometry for blobs of interesest from each epoch. The uncertainties are represented in parantheses and are derived from the FWHM of the PSF from each epoch.
@@
         \colhead{Date observed} &
-        \colhead{offset (mas)} &
-        \colhead{PA (\textdegree)}
+        \colhead{offset (\unit{\milliarcsecond})} &
+        \colhead{PA (\unit{\degree})}
     }
     \startdata
-    2020-02-04 & 193(38) & -99(11)  \\
-    2020-11-21 & 125(38) & 75(17)  \\
-    2020-11-28 & 215(40) & 23(11)  \\
+    2020-02-04 & $114\pm 40$ & $-115\pm 20$  \\
+    2020-11-21 & $121\pm 38$ & $-119\pm 18$  \\
+    2020-11-28 & $114\pm 41$ & $-113\pm 21$  \\
     \enddata
-\end{deluxetable*}
+\end{deluxetable}
 
-\begin{figure*}
+\begin{figure}[h!]
+    \centering
     \plotone{orbit_frames}
@@
 Each frame was been cropped to the inner \ang{;;0.25}.
-The inner FWHM has been masked out in each frame.}
-\end{figure*}
+The inner FWHM has been masked out in each frame.
+The width of the circles represent the uncertainty.}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}[h!]
+    \centering
     \plotone{orbit_corner}
     \caption{Corner plot of the marginal posteriors from the OFTI samples.}
-\end{figure*}
+\end{figure}
 

### 2021-07-29 paper/sections/adi_results_full.tex
update paper

Results from processing each epoch of Sirius B data with various ADI algorithms. The top-left image is the subtracted, derotated, and collapsed image. The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection. The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_median}
    \caption{2020-02-04 median}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_pca-2}
    \caption{2020-02-04 PCA(2)}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_nmf-2}
    \caption{2020-02-04 NMF(2))}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_greeds-2}
    \caption{2020-02-04 GreeDS(2)}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_annular_median}
    \caption{2020-02-04 annular median}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_annular_pca-2}
    \caption{2020-02-04 annular PCA(2))}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020feb04_annular_nmf-2}
    \caption{2020-02-04 annular NMF(2)}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{2020feb04_contrast_curves}
    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-02-04 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
\end{figure}

%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_median}
    \caption{2020-11-21 median subtraction.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_pca-2}
    \caption{2020-11-21 PCA subtraction with 2 components.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_nmf-2}
    \caption{2020-11-21 NMF subtraction with 2 components.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_greeds-2}    
    \caption{2020-11-21 GreeDS with 2 components.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_annular_median}
    \caption{2020-11-21 annular median subtraction with a rotation threshold of 0.5.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_annular_pca-2}
    \caption{2020-11-21 annular PCA subtraction with 2 components and a rotation threshold ofnov21 0.5.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov21_annular_nmf-2}
    \caption{2020-11-21 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{2020nov21_contrast_curves}
    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-21 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
\end{figure}

%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_median}
    \caption{2020-11-28 median subtraction.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_pca-2}
    \caption{2020-11-28 PCA subtraction with 2 components.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_nmf-2}
    \caption{2020-11-28 NMF subtraction with 2 components.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_greeds-2}
    \caption{2020-11-28 GreeDS with 2 components.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_annular_median}
    \caption{2020-11-28 annular median subtraction with a rotation threshold of 0.5.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_annular_pca-2}
    \caption{2020-11-28 annular PCA subtraction with 2 components and a rotation threshold ofnov28 0.5.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{reports/2020nov28_annular_nmf-2}
    \caption{2020-11-28 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
\end{figure}

\begin{figure}[h!]
    \centering
    \epsscale{0.9}
    \plotone{2020nov28_contrast_curves}
    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-28 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
\end{figure}

### 2021-07-29 paper/figures/psf.jl

@@ -32,8 +32,11 @@ from matplotlib.colors import LogNorm
 
 fig, axs = pro.subplots(figwidth="3.5in")
 
-axs[0].imshow($psf, norm=LogNorm(vmin=3e-3, vmax=5e-2))
-axs[0].format(title="Epoch 2020-11-21")
+axs.imshow($psf, 
+    norm=LogNorm(vmin=3e-3, vmax=5e-2),
+    colorbar="r",
+)
+axs.format(title="Epoch 2020-11-21")
 axs.format(
     xticks=$tick_locs,
     xticklabels=$tick_labs,
@@ -42,5 +45,5 @@ axs.format(
     xlabel="x [arcsec]",
     ylabel="y [arcsec]",
 )
-fig.save($(joinpath(@__DIR__, "psf.pdf")))
+fig.save($(figuredir("psf.pdf")))
 """

### 2021-07-29 paper/figures/spike.jl

@@ -8,6 +8,7 @@ pro = pyimport("proplot")
 # rcParams
 pro.rc["image.origin"] = "lower"
 pro.rc["image.cmap"] = "inferno"
+pro.rc["grid"] = false
 
 data_cube = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_cube_calib.fits"))
 frame = data_cube[88, :, :]
@@ -15,6 +16,6 @@ frame = data_cube[88, :, :]
 fig, axs = pro.subplots(figwidth="3.5in")
 ax = first(axs)
 vmin, vmax = zscale(frame)
-ax.imshow(frame; vmin, vmax)
-ax.format(xlabel="x", ylabel="y", grid=false)
-fig.save(joinpath(@__DIR__, "spike.pdf"))
+ax.imshow(frame; vmin, vmax, colorbar="r")
+ax.format(xlabel="x", ylabel="y")
+fig.save(figuredir("spike.pdf"))

### 2021-07-30 paper/paper.tex
update paper

@@
 We reach sub-Jupiter sensitivities at sub-AU separations, down to an ultimate sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}.
-Despite the high sensitivity of our observations, we do not detect any companions around Sirius B.
-These observations showcase that for nearby faint targets direct imaging is limited more by background noise than absolute contrast.
+Despite the high sensitivity of our observations, we do not detect any companions around Sirius B, which is consistent with previous studies.
+These observations showcase that for nearby faint targets direct imaging is ultimately limited by background noise more than contrast.
 \end{abstract}
@@
 The process required to image a planet is daunting, however.
-The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim10^{-8}$, and for a Sun-Earth system are $\sim10^{-10}$ \citep{traub_direct_2010}.
-In addition, the close angular separation of planets makes it difficult to distinguish them from the diffraction pattern of the star and other noise sources.
+The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{-8}$, and for a Sun-Earth system are $\sim$$10^{-10}$ \citep{traub_direct_2010}.
+In addition, the close angular separation of planets makes it difficult to detect them over the diffraction pattern of the star and other noise sources.
 In order to make such a difficult detection it is imperative to minimize diffraction, scattering, and systematic noise.
 
-Nearby white dwarfs (within $\sim$\qty{100}{\parsec}) are compelling targets for direct imaging searches, despite the limited knowledge of planetary systems around evolved stars.
-\cite{burleigh_imaging_2002} suggests planets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars (\qtyrange{1}{8}{\solarmass}) will survive expansion during the red giant (RGB) phase and remain bound to the resultant white dwarf.
-Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, however the tidal forces on planets that readily escape engulfment are negligible.
-During the asymptotic giant (AGB) phase, strong ionizing soft X-ray and UV emission will likely photoevaporate planetary atmospheres.
-In addition, the mass loss of the star will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
+Typical targets for imaging are nearby young stars; the close proximity decreases the projected separation of the inner working angle (IWA) of the instrument, allowing closer investigation, and younger exoplanets are hotter and therefore the contrast is reduced.
+Another way to reduce contrast would be to reduce the luminosity of the star, which is not possible during the main-sequence (MS) lifetime of a star but is possible in the latest stages of stellar evolution.
+When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) reach the end of their lifetimes, they become white dwarfs and begin cooling, which reduces their luminosity by a factor of $10^3-10^4$ compared to their progenitors.
+The faintness, broad spectral lines, and  expanded orbits, as we will discuss below, all make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
+However, the faintness reduces the contrast of planetary companions and the expanded separation greatly benefit imaging.
 
-If the planet has managed to survive through the RGB and AGB phases, stars below \qty{8}{\solarmass} will enter the white dwarf cooling sequence, which will lead to a reduction in luminosity by $10^3-10^4$.
-This means the contrast between a white dwarf and a companion will be 3-4 orders of magnitude lower than the equivalent main sequence system.
-The combination of expanded orbits and lower contrast are beneficial for imaging, due to the limited inner working angles and sensitivities of ground-based instrumentation.
-The transit photometry method is very insensitive to planets around white dwarfs because the probability of a transit decreases with increasing separation.
-Similarly, the radial velocity method is limited to very massive planets on larger separations in addition to the extremely broad spectral features of a white dwarf which greatly limit the precision of radial velocity measurements.
+White dwarfs do present challenges, and there is limited knowledge of planetary systems around evolved stars.
+\cite{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the red giant (RGB) phase.
+Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible.
+During the asymptotic giant (AGB) phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
+Overall, the probability of discovering a \textit{first-generation} planet around a white dwarf is low, but there are potential methods for \textit{second-generation} planets to exist after the violent RGB and AGB phases.
 
@@
 This excess could likely be attributed to circumstellar dust or gas discs, which are indicators of the planetary formation history.
-Of the $\sim$ 100 white dwarfs they studied, no companions were found.
+Of the $\sim$100 white dwarfs they studied, no companions were found.
 The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38.
@@
 
-The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a very wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}.
+To date, there has been no direct images of an exoplanet around a white dwarf.
+The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}.
 The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
 The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.
-Sirius B has also been imaged, which will be discussed later.
-To date, there has been no direct images of an exoplanet around a white dwarf.
 
-The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, an A1Vm star known for being the brightest in the night sky, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,collaboration_gaia_2018}.
-The proximity and brightness of the Sirius system make it one of the most well-studied systems throughout history \citep[see][]{wesemael_sirius_1982}.
+A particularly fascinating white dwarf is Sirius B, the closest and brightest white dwarf.
+The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}.
+As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging, and additionally it is a young system ($\sim$\qty{225}{\mega\year}), further reducing the predicted contrast necessary to image a planetary companion.
 
 The orbit of Sirius B was first studied by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
-\citet{bond_companion_1862} reported and confirmed visual evidence of Sirius B by Alvan G.
-Clark and his father.
-\citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be very similar to a main-sequence early A-type star despite the faintness, which we know know to be typical of white dwarf spectra.
+This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B.
+\citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.
 
 Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864}, with the first orbital solution including dynamic masses published by \citet{van_den_bos_orbit_1960}.
-\citet{gatewood_study_1978} improved upon the van den Bos orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary.
-\citet{bond_sirius_2017} greatly refine the orbit using a compilation of historical data and HST data, which gives dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+\citet{gatewood_study_1978} improved upon the \citeauthor{van_den_bos_orbit_1960} orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary.
+\citet{bond_sirius_2017} greatly refined the orbit using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 
 The precise dynamical masses are key for finding the age of Sirius; \citet{bond_sirius_2017} report a cooling age for Sirius B of \qty{126}{\mega\year} using isochrones.
-Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\solarmass}, which when combined with stellar evolution codes yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}.
+Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}.
 The precision of the system age is useful for constraining the mass of potential companions.
@@
 
-Some of the first modern studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}).
+Some of the first modern imaging studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}).
 \citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\jupitermass} at \ang{;;3} (\qty{7.9}{\au}).
@@
 \citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
-Very recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
-Because of the simultaneous observation, their contrast is split depending on which half of the FOV is being considered.
+Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
+Because of the simultaneous observation, their contrast depended on which region of the FOV was tested.
 Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.
@@
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
-The adaptive optics (AO) calibration failed when the extremely bright (-1.35 K-band magnitude) diffraction patterns would sweep into the field of view (FOV) of the wavefront sensor (WFS).
+The adaptive optics (AO) calibration failed when the -1.35 K-band magnitude diffraction patterns from Sirius A would sweep into the field of view (FOV) of the wavefront sensor (WFS).
 Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
-This is very similar to the issues reported by \citet[\S2]{vigan_high-contrast_2015} in their attempts to image Sirius B.
-In order to overcome these issues, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
+\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B.
+In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
 
@@
 
-During each observation, calibration frames were taken in the form of dark frames and sky flat frames.
+During each observation, we took calibration frames in the form of dark frames and sky flat frames.
 We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
@@
 For each epoch we applied a flat correction using calibration frames captured during observing.
-We also removed bad pixels using a combination of L.A.Cosmic \citep{dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
+We also removed bad pixels using a combination of L.A.Cosmic \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
 We removed sky background using a high-pass median filter with a box size of 31 pixels.
@@
 For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles have been made available on Zenodo \citep{lucas_nirc2_2021}.
+All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo \citep{lucas_nirc2_2021}.
 
@@
 The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}.
-The speckle pattern can be seen in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
+The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
     \label{fig:psf}
@@
 We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
-The collapsed residual frames along with the above metrics for each algorithm for each epoch can be found in \autoref{sec:adi-results}.
+The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \autoref{sec:adi-results}.
 
@@
 All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}.
-All of the code for the ADI processing in this paper, including the scripts for each figure produced can be found at the GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} in Jupyter notebooks and Julia scripts.
+All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} in Jupyter notebooks and Julia scripts.
 
@@
     \caption{The STIM maps for each epoch calculated from the residual cube.
-Note that the STIM probability has a typical cutoff threshold of 0.5 for significant detections.
+The STIM probability has a typical cutoff threshold of 0.5 for significant detections.
 The inner full-width at half-maximum (FWHM) is masked out for each map.}
@@
 It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
-Both of these algorithms have been shown to outperform traditional median and PCA subtraction for disk imaging.
+Both of these algorithms outperform traditional median and PCA subtraction for disk imaging.
 In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen.
-Due to the nature of high-contrast imaging, it is extremely difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no evidence for IR excess from a circumstellar disk.
+Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess.
 Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.
@@
 Then we use an age of \qty{226}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
-It is important to note how the precision of the system age (see \autoref{sec:intro}) leads to quite accurate interpolation on the evolutionary grids.
+It is important to note how the precision of the system age (see \autoref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids.
 The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the sky-background limited regime.
@@
 
-In this work we demonstrate the results of high-contrast images of Sirius B in the near-IR.
+In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR.
+While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets.
+In this work we present high-contrast images of Sirius B in the near-IR.
 Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au}.
@@
 
+In recent years improving contrast and inner working angle were the dominant parameters of interest.
+Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the sky background than the speckle noise.
+Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}.
+This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.
+
 We have published alongside this work the entire codebase used for pre-processing and reducing the data, and for generating every figure in this manuscript.
@@
 We hope that this improves the reproducibility of the work as well as providing data for exploring new and different ADI algorithms.
-
-In recent years improving contrast and inner working angle were the dominant parameters of interest.
-Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the background noise than the speckle noise.
-Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}.
-This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.
-
-In closing,
 
@@
     \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components.
-Each frame was been cropped to the inner \ang{;;0.25}.
-The inner FWHM has been masked out in each frame.
+Each frame was cropped to the inner \ang{;;0.25} and the inner FWHM has been masked out.
 The width of the circles represent the uncertainty.}

### 2021-07-31 paper/paper.tex
update paper

@@
 
-\title{A Search for Circumstellar Companions of Sirius B}
+\title{An Imaging Search for Circumstellar Companions of Sirius B}
 
+\shorttitle{An Imaging Search for Circumstellar Companions of Sirius B}
 \shortauthors{Lucas et al.}
@@
 We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging.
-We reach sub-Jupiter sensitivities at sub-AU separations, down to an ultimate sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}.
-Despite the high sensitivity of our observations, we do not detect any companions around Sirius B, which is consistent with previous studies.
-These observations showcase that for nearby faint targets direct imaging is ultimately limited by background noise more than contrast.
+We reach sub-Jupiter sensitivities and sub-AU separations, reaching $\sim$\qty{3.5}{\jupitermass} at $\sim$\qty{0.25}{\au} down to a sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}.
+We do not detect any companions around Sirius B, consistent with previous studies.
+Our observations are ultimately limited by the sky background more than contrast or separation, which is promising for future imaging studies of nearby faint targets.
 \end{abstract}
@@
 The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{-8}$, and for a Sun-Earth system are $\sim$$10^{-10}$ \citep{traub_direct_2010}.
-In addition, the close angular separation of planets makes it difficult to detect them over the diffraction pattern of the star and other noise sources.
-In order to make such a difficult detection it is imperative to minimize diffraction, scattering, and systematic noise.
+The infrared is where blackbody emission from exoplanets peaks, while simultaneously being well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible.
+In addition, the close angular separations of planets makes it difficult to detect them over the diffraction pattern of their host and other noise sources.
 
-Typical targets for imaging are nearby young stars; the close proximity decreases the projected separation of the inner working angle (IWA) of the instrument, allowing closer investigation, and younger exoplanets are hotter and therefore the contrast is reduced.
-Another way to reduce contrast would be to reduce the luminosity of the star, which is not possible during the main-sequence (MS) lifetime of a star but is possible in the latest stages of stellar evolution.
-When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) reach the end of their lifetimes, they become white dwarfs and begin cooling, which reduces their luminosity by a factor of $10^3-10^4$ compared to their progenitors.
-The faintness, broad spectral lines, and  expanded orbits, as we will discuss below, all make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
+Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a closer projected separation, allowing closer investigation, and younger exoplanets are hotter and therefore brighter, reducing the contrast.
+Another way to reduce contrast would be to make the star fainter, which is precisely what happens in the latest stages of stellar evolution during the white dwarf cooling sequence.
+When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) will eventually exit the main-sequence (MS) and expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase, potentially engulfing planets within the star's roche limit.
+Then, during the asymptotic giant branch (AGB) phase, mass loss will adiabatically expand any orbits.
+Once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor.
+The faintness broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
 However, the faintness reduces the contrast of planetary companions and the expanded separation greatly benefit imaging.
@@
 White dwarfs do present challenges, and there is limited knowledge of planetary systems around evolved stars.
-\cite{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the red giant (RGB) phase.
-Furthermore, \citet{nordhaus_orbits_2013} explain that close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible.
-During the asymptotic giant (AGB) phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
-Overall, the probability of discovering a \textit{first-generation} planet around a white dwarf is low, but there are potential methods for \textit{second-generation} planets to exist after the violent RGB and AGB phases.
+\citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase.
+Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}.
+During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
+In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to enter the system after the violent RGB and AGB phases \citep{perets_second_2010}.
 
-The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by looking for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
-This excess could likely be attributed to circumstellar dust or gas discs, which are indicators of the planetary formation history.
-Of the $\sim$100 white dwarfs they studied, no companions were found.
+The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by searching for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
+They found no companions around the $\sim$100 white dwarfs they studied.
 The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38.
-Eventually this excess was determined to be from a dust disc \citep{telesco_observations_1990}, with the current interpretation associating the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.
+Eventually this excess was determined to be from a dust disk \citep{telesco_observations_1990} which is indicative of the planetary formation history.
+The current interpretation associates the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.
 
-To date, there has been no direct images of an exoplanet around a white dwarf.
-The only planetary-mass object imaged around a single white dwarf (WD 0806-661B) was discovered using Spitzer with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit \citep{luhman_discovery_2011}.
+To date, there has been no direct images of an exoplanet around a white dwarf, although a planetary-mass brown dwarf with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit was imaged around a single white dwarf (WD 0806-661B) using Spitzer \citep{luhman_discovery_2011}.
 The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
@@
 
-Some of the first modern imaging studies searching for companions around Sirius B were \citet{schroeder_search_2000} and \citet{kuchner_search_2000}, who used the HST planetary camera and NICMOS cameras, respectively, looking for signal around \qty{1}{\micro\meter}, which combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \ang{;;2} (\qty{5.3}{\au}).
-\citet{bonnet-bidaud_adonis_2008} use the ground-based ESO/ADONIS instrument in JHKs to reach a sensitivty of $\sim$\qty{30}{\jupitermass} at \ang{;;3} (\qty{7.9}{\au}).
-\citet{skemer_sirius_2011} used mid-IR (out to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
-\citet{thalmann_piercing_2011} use Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
+The first modern imaging study searching for companions around Sirius B was \citet{schroeder_search_2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
+Around the same time \citet{kuchner_search_2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
+These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
+\citet{bonnet-bidaud_adonis_2008} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
+\citet{skemer_sirius_2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
+\citet{thalmann_piercing_2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
 Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
@@
 
-In this work we report our study of Sirius B using direct images from Keck/NIRC2.
+In this work we report direct images of Sirius B with Keck/NIRC2.
 \autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.
@@
 
-Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes which have to deal with extra scattering and diffraction from the atmosphere.
-
+Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
 We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
-The adaptive optics (AO) calibration failed when the -1.35 K-band magnitude diffraction patterns from Sirius A would sweep into the field of view (FOV) of the wavefront sensor (WFS).
+The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
 Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
@@
 The Keck AO system \citep{wizinowich_performance_2000} was not designed to accommodate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the WFS.
-We experimented with different filters in front of the WFS, settling on a narrow laser-line filter which attenuated Sirius B by $\sim$6 magnitudes.
+We experimented with different filters in front of the WFS, settling on a narrow laser-line filter which attenuated Sirius A by $\sim$6 magnitudes.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
@@
 At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}.
-Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF.
+Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to reach floating-point centroid accuracy.
+
 The co-registered frames are then shifted to the center of the FOV.
 Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch.
-With the pixel scale of \qty{10}{mas\per px} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
-We also measure the parallactic angle of each frame, including corrections for distortion effects following \cite{yelda_improving_2010}.
-For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo \citep{lucas_nirc2_2021}.
+With a pixel scale of \qty{10}{\milliarcsecond} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
+We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yelda_improving_2010}.
+For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
+All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo\footnote{\citealt{lucas_nirc2_2021}}.
 
@@
 
-A common problem when using subspace-driven ADI algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
+A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
+For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
+We chose 10 as the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components.
 In our analysis we employ the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
 The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
-A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without having to settle on the number of components ahead of time.
-For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
-We chose 10 as the max number of components because we saw a dramatic dropoff in contrast sensitivity after the first few components.
+A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
 The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms can be found in \autoref{sec:adi-results}.
@@
 The companion mass values are interpolated from the AMES-Cond grid.
-The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.}
+The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
+The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
     \label{fig:contrast}
@@
 We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
-For the first two epochs full-frame median subtraction had the best contrast at all separations.
+For the first two epochs full-frame median subtraction had the best contrast at almost all separations.
 For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
+The innermost annulus from this algorithm has greater than 1 contrast and is not shown.
 The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).
 
-In these images there is not \textit{consistent} or overwhelming evidence for a substellar companion.
+The reduced images do not show consistent or overwhelming evidence for a substellar companion.
 The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} from the center.
@@
 Both of these algorithms outperform traditional median and PCA subtraction for disk imaging.
-In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen.
+In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}.
 Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess.
@@
 In this work we present high-contrast images of Sirius B in the near-IR.
-Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au}.
+Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}.
 In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}.
 Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
+This non-detection is compelling for revising occurrence rates of second-generation planets and debris disks around white dwarfs.
 
@@
 Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}.
-This means we could potentially reach sub-Jupiter sensitivities for 10s-100s of targets without coronagraphy.
+This means potentially reach sub-Jupiter sensitivities around young systems ($\lesssim$\qty{300}{\mega\year}) and $<$\qty{10}{\jupitermass} sensitivities around moderate age systems ($\lesssim$\qty{7}{\giga\year}) for 10s-100s of targets without coronagraphy or extreme AO.
 
@@
 
-\input{sections/adi_results_full}
+\input{sections/adi_results}
 
@@
 
+We found multiple interesting blobs in the reduced data that were not statistically significant.
+Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions.
+We began by estimating the astrometry of the blobs by eye in reduced data (\autoref{tbl:astrometry}, \autoref{fig:prov-orbit}).
+We tried simulating $10^4$ orbits via rejection sampling with OFTI but failed to constrain all three points with any one orbit.
+Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.
+
 \begin{deluxetable}{ccc}[h!]
-    \tablecaption{Provisional astrometry for blobs of interesest from each epoch. The uncertainties are represented in parantheses and are derived from the FWHM of the PSF from each epoch.
+    \tablecaption{Provisional astrometry for blobs of interest from each epoch.
+The separation and offset are in relation to Sirius B.
+The uncertainties are derived from the FWHM of the PSF from each epoch.
     \label{tbl:astrometry}}
@@
     \centering
+    \figurenum{13}
     \plotone{orbit_frames}
@@
 The width of the circles represent the uncertainty.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \plotone{orbit_corner}
-    \caption{Corner plot of the marginal posteriors from the OFTI samples.}
+    \label{fig:prov-orbit}
 \end{figure}

### 2021-07-31 paper/sections/adi_results.tex
update paper

@@
+\begin{figure}[h!]
+    \centering
+    \epsscale{0.9}
+    \plotone{2020feb04_contrast_curves}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the first epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \epsscale{0.9}
+    \plotone{2020nov21_contrast_curves}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the second epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \epsscale{0.9}
+    \plotone{2020nov28_contrast_curves}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the third epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \figsetstart
-\figsetnum{6}
+\figsetnum{10}
 \figsettitle{ADI processing results}
 
+%%% first epoch
+
 \figsetgrpstart
-\figsetgrpnum{6.1}
+\figsetgrpnum{10.1}
 \figsetgrptitle{2020-02-04 median}
 \figsetplot{reports/2020feb04_median}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.2}
-\figsetgrptitle{2020-02-04 PCA(2)}
-\figsetplot{reports/2020feb04_pca-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.2}
+\figsetgrptitle{2020-02-04 PCA(1)}
+\figsetplot{reports/2020feb04_pca-1}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame PCA subtraction with 1 component.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.3}
-\figsetgrptitle{2020-02-04 NMF(2))}
-\figsetplot{reports/2020feb04_nmf-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.3}
+\figsetgrptitle{2020-02-04 NMF(1)}
+\figsetplot{reports/2020feb04_nmf-1}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame NMF subtraction with 1 component.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.4}
-\figsetgrptitle{2020-02-04 GreeDS(2)}
-\figsetplot{reports/2020feb04_greeds-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.4}
+\figsetgrptitle{2020-02-04 GreeDS(1)}
+\figsetplot{reports/2020feb04_greeds-1}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame GreeDS subtraction with 1 component.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.5}
+\figsetgrpnum{10.5}
 \figsetgrptitle{2020-02-04 annular median}
 \figsetplot{reports/2020feb04_annular_median}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnote{Post-processing results from the first epoch using annular median subtraction with a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.6}
-\figsetgrptitle{2020-02-04 annular PCA(2))}
-\figsetplot{reports/2020feb04_annular_pca-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.6}
+\figsetgrptitle{2020-02-04 annular PCA(1)}
+\figsetplot{reports/2020feb04_annular_pca-1}
+\figsetgrpnote{Post-processing results from the first epoch using annular PCA subtraction with 1 component and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.7}
-\figsetgrptitle{2020-02-04 annular NMF(2)}
-\figsetplot{reports/2020feb04_annular_nmf-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.7}
+\figsetgrptitle{2020-02-04 annular NMF(1)}
+\figsetplot{reports/2020feb04_annular_nmf-1}
+\figsetgrpnote{Post-processing results from the first epoch using annular NMF subtraction with 1 component and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+%%% second epoch
+
+\figsetgrpstart
+\figsetgrpnum{10.8}
+\figsetgrptitle{2020-11-21 median}
+\figsetplot{reports/2020nov21_median}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.8}
-\figsetgrptitle{2020-11-21 median subtraction.}
-\figsetplot{reports/2020nov21_median}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.9}
+\figsetgrptitle{2020-11-21 PCA(3)}
+\figsetplot{reports/2020nov21_pca-3}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame PCA subtraction with 3 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.9}
-\figsetgrptitle{2020-11-21 PCA subtraction with 2 components.}
-\figsetplot{reports/2020nov21_pca-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.10}
+\figsetgrptitle{2020-11-21 NMF(3)}
+\figsetplot{reports/2020nov21_nmf-3}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame NMF subtraction with 3 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.10}
-\figsetgrptitle{2020-11-21 NMF subtraction with 2 components.}
-\figsetplot{reports/2020nov21_nmf-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.11}
+\figsetgrptitle{2020-11-21 GreeDS(3)}
+\figsetplot{reports/2020nov21_greeds-3}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame GreeDS subtraction with 3 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.11}
-\figsetgrptitle{2020-11-21 GreeDS with 2 components.}
-\figsetplot{reports/2020nov21_greeds-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.12}
+\figsetgrptitle{2020-11-21 annular median}
+\figsetplot{reports/2020nov21_annular_median}
+\figsetgrpnote{Post-processing results from the second epoch using annular median subtraction with a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.12}
-\figsetgrptitle{2020-11-21 annular median subtraction with a rotation threshold of 0.5.}
-\figsetplot{reports/2020nov21_annular_median}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.13}
+\figsetgrptitle{2020-11-21 annular PCA(3)}
+\figsetplot{reports/2020nov21_annular_pca-3}
+\figsetgrpnote{Post-processing results from the second epoch using annular PCA subtraction with 3 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.13}
-\figsetgrptitle{2020-11-21 annular PCA subtraction with 2 components and a rotation threshold ofnov21 0.5.}
-\figsetplot{reports/2020nov21_annular_pca-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.14}
+\figsetgrptitle{2020-11-21 annular NMF(3)}
+\figsetplot{reports/2020nov21_annular_nmf-3}
+\figsetgrpnote{Post-processing results from the second epoch using annular NMF subtraction with 3 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+%%% third epoch
+
+\figsetgrpstart
+\figsetgrpnum{10.15}
+\figsetgrptitle{2020-11-28 median}
+\figsetplot{reports/2020nov28_median}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.14}
-\figsetgrptitle{2020-11-21 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
-\figsetplot{reports/2020nov21_annular_nmf-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.16}
+\figsetgrptitle{2020-11-28 PCA(2)}
+\figsetplot{reports/2020nov28_pca-2}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame PCA subtraction with 2 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.15}
-\figsetgrptitle{2020-11-28 median subtraction.}
-\figsetplot{reports/2020nov28_median}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.17}
+\figsetgrptitle{2020-11-28 NMF(2)}
+\figsetplot{reports/2020nov28_nmf-2}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame NMF subtraction with 2 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.16}
-\figsetgrptitle{2020-11-28 PCA subtraction with 2 components.}
-\figsetplot{reports/2020nov28_pca-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.18}
+\figsetgrptitle{2020-11-28 GreeDS(2)}
+\figsetplot{reports/2020nov28_greeds-2}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame GreeDS subtraction with 2 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.17}
-\figsetgrptitle{2020-11-28 NMF subtraction with 2 components.}
-\figsetplot{reports/2020nov28_nmf-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.19}
+\figsetgrptitle{2020-11-28 annular median}
+\figsetplot{reports/2020nov28_annular_median}
+\figsetgrpnote{Post-processing results from the third epoch using annular median subtraction with a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.18}
-\figsetgrptitle{2020-11-28 GreeDS with 2 components.}
-\figsetplot{reports/2020nov28_greeds-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnum{10.20}
+\figsetgrptitle{2020-11-28 annular PCA(2)}
+\figsetplot{reports/2020nov28_annular_pca-2}
+\figsetgrpnote{Post-processing results from the third epoch using annular PCA subtraction with 2 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 \figsetgrpstart
-\figsetgrpnum{6.19}
-\figsetgrptitle{2020-11-28 annular median subtraction with a rotation threshold of 0.5.}
-\figsetplot{reports/2020nov28_annular_median}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{6.20}
-\figsetgrptitle{2020-11-28 annular PCA subtraction with 2 components and a rotation threshold ofnov28 0.5.}
-\figsetplot{reports/2020nov28_annular_pca-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{6.21}
-\figsetgrptitle{2020-11-28 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
+\figsetgrpnum{10.21}
+\figsetgrptitle{2020-11-28 annular NMF(2)}
 \figsetplot{reports/2020nov28_annular_nmf-2}
-\figsetgrpnote{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
+\figsetgrpnote{Post-processing results from the third epoch using annular NMF subtraction with 2 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
 \figsetgrpend
@@
 
-\begin{figure*}
-\figurenum{6}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{10}
+    \epsscale{0.9}
     \plotone{reports/2020feb04_median}
-\caption{Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.}
-\end{figure*}
+    \caption{Post-processing results from the second epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.
+Outputs for other epochs and other algorithms (21 figures) are in the online figure set and the GitHub repository.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\figsetstart
+\figsetnum{11}
+\figsettitle{PCA, NMF, and GreeDS mosaics}
+
+%%% first epoch
+
+\figsetgrpstart
+\figsetgrpnum{11.1}
+\figsetgrptitle{2020-02-04 PCA mosaic}
+\figsetplot{reports/2020feb04_pca_mosaic}
+\figsetgrpnote{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.2}
+\figsetgrptitle{2020-02-04 NMF mosaic}
+\figsetplot{reports/2020feb04_nmf_mosaic}
+\figsetgrpnote{Collapsed residual frames from the first epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.3}
+\figsetgrptitle{2020-02-04 GreeDS mosaic}
+\figsetplot{reports/2020feb04_greeds_mosaic}
+\figsetgrpnote{Collapsed residual frames from the first epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+%%% second epoch
+
+\figsetgrpstart
+\figsetgrpnum{11.4}
+\figsetgrptitle{2020-11-21 PCA mosaic}
+\figsetplot{reports/2020nov21_pca_mosaic}
+\figsetgrpnote{Collapsed residual frames from the second epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.5}
+\figsetgrptitle{2020-11-21 NMF mosaic}
+\figsetplot{reports/2020nov21_nmf_mosaic}
+\figsetgrpnote{Collapsed residual frames from the second epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.6}
+\figsetgrptitle{2020-11-21 GreeDS mosaic}
+\figsetplot{reports/2020nov21_greeds_mosaic}
+\figsetgrpnote{Collapsed residual frames from the second epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+%%% third epoch
+
+\figsetgrpstart
+\figsetgrpnum{11.7}
+\figsetgrptitle{2020-11-28 PCA mosaic}
+\figsetplot{reports/2020nov28_pca_mosaic}
+\figsetgrpnote{Collapsed residual frames from the third epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.8}
+\figsetgrptitle{2020-11-28 NMF mosaic}
+\figsetplot{reports/2020nov28_nmf_mosaic}
+\figsetgrpnote{Collapsed residual frames from the third epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.9}
+\figsetgrptitle{2020-11-28 GreeDS mosaic}
+\figsetplot{reports/2020nov28_greeds_mosaic}
+\figsetgrpnote{Collapsed residual frames from the third epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetend
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{11}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_pca_mosaic}
+    \caption{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components.
+The figures share a common scale and the inner FWHM is masked out for all the frames.
+Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\figsetstart
+\figsetnum{12}
+\figsettitle{PCA, NMF, and GreeDS results}
+
+%%% first epoch
+
+\figsetgrpstart
+\figsetgrpnum{12.1}
+\figsetgrptitle{2020-02-04 PCA contrast}
+\figsetplot{reports/2020feb04_pca_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.2}
+\figsetgrptitle{2020-02-04 NMF contrast}
+\figsetplot{reports/2020feb04_nmf_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using NMF reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.3}
+\figsetgrptitle{2020-02-04 GreeDS contrast}
+\figsetplot{reports/2020feb04_greeds_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using GreeDS reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+%%% second epoch
+
+\figsetgrpstart
+\figsetgrpnum{12.4}
+\figsetgrptitle{2020-11-21 PCA contrast}
+\figsetplot{reports/2020nov21_pca_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.5}
+\figsetgrptitle{2020-11-21 NMF contrast}
+\figsetplot{reports/2020nov21_nmf_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using NMF reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.6}
+\figsetgrptitle{2020-11-21 GreeDS contrast}
+\figsetplot{reports/2020nov21_greeds_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using GreeDS reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+%%% third epoch
+
+\figsetgrpstart
+\figsetgrpnum{12.7}
+\figsetgrptitle{2020-11-28 PCA contrast}
+\figsetplot{reports/2020nov28_pca_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.8}
+\figsetgrptitle{2020-11-28 NMF contrast}
+\figsetplot{reports/2020nov28_nmf_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using NMF reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.9}
+\figsetgrptitle{2020-11-28 GreeDS contrast}
+\figsetplot{reports/2020nov28_greeds_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using GreeDS reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetend
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{12}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_pca_contrast_curves}
+    \caption{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.
+Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
+\end{figure}

### 2021-07-31 paper/figures/contrast.jl

@@ -66,7 +66,9 @@ axs.plot($(distances[3]), $(masses[3]), c="C5", label="  2020-11-28\nannular PCA
 axs.plot($(distances[3]), $(masses_corr[3]), c="C5", ls="--")
 
 ylims=axs.get_ylim()
-axs.vlines(1.5, *ylims, color="k", alpha=0.5, ls="-.", label="  dynamic limit")
+axs.vlines(1.5, *ylims, color="k", alpha=0.5, ls="-.")
+mid = (ylims[0] + ylims[1]) / 2
+axs.text(1.45, mid, "dynamic stability limit", color="k", alpha=0.5, va="center", ha="left", rotation="vertical")
 
 xlims = axs.get_xlim()
 axs.hlines(0.0005 * 1047.9, *xlims, color="k", alpha=0.3, linestyle=":", label="model mass limit")

### 2021-07-31 paper/figures/pca_nmf_greeds.jl

@@ -17,17 +17,32 @@ pxscale = 0.01 # arcsec / px
 auscale = pxscale / parallax # AU / px
 
 
+_label(a::Type{<:PCA}) = "PCA"
+_label(a::Type{<:NMF}) = "NMF"
+_label(a::Type{<:GreeDS}) = "GreeDS"
+
+_epochs = Dict(
+    "2020feb04" => "2020-02-04",
+    "2020nov21" => "2020-11-21",
+    "2020nov28" => "2020-11-28"
+)
+
 function plot_mosaic(res_cubes, angles; epoch, label, ncomps)
     py"""
     import proplot as pro
     fig, axs = pro.subplots(nrows=2, ncols=5, share=3, width="7.5in", space=0)
     """
     i = 0
-    for (n, res) in zip(res_cubes, ncomps)
+    flats = collapse.(res_cubes, Ref(angles))
+    vmax = mapreduce(maximum, max, flats)
+    vmin = mapreduce(minimum, min, flats)
+
+
+    for (n, flat) in zip(ncomps, flats)
         lab = "ncomp=$n"
-        flat = collapse(res, angles)
+        
         py"""
-        axs[$i].imshow($flat)
+        m = axs[$i].imshow($flat, vmin=$vmin, vmax=$vmax)
         axs[$i].text(6, 6, $lab, color="w")
         """
         i += 1
@@ -36,70 +51,70 @@ function plot_mosaic(res_cubes, angles; epoch, label, ncomps)
     ticks = range(40, 159, length=3)
     tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
 
+    figname = make_filename_friendly(figuredir("reports", "$(epoch)_$(label)_mosaic.pdf"))
     py"""
     axs.format(
         yticks=$ticks,
         yticklabels=$tick_labs,
-        ylabel="y [arcsec]"
+        ylabel="y [arcsec]",
         xticks=$ticks,
         xticklabels=$tick_labs,
         xlabel="x [arcsec]",
     )
-    fig.savefig($(figuredir(make_filename_friendly("$(epoch)_$(label)_mosaic") * ".pdf")))
+    fig.colorbar(m, loc="r")
+    fig.savefig($figname)
     """
 end
 
 function plot_results(res_cubes, angles, contrast_curves; epoch, label, fwhm)
     py"""
     import proplot as pro
[…]

### 2021-07-31 paper/figures/reports.jl

@@ -71,7 +71,7 @@ function plot_results(res_cube, angles, curve; fwhm, epoch, label)
         xlabel="x [arcsec]",
     )
 
-    axs[4].plot($arcsec, $(curve.contrast), label="Guassian", lw=1)
+    axs[4].plot($arcsec, $(curve.contrast), label="Gaussian", lw=1)
     axs[4].plot($arcsec, $(curve.contrast_corr), color="C0", ls="--", label="Student-t", lw=1)
     axs[4].fill_between($arcsec, $(curve.contrast), $(curve.contrast_corr), color="C0", alpha=0.2)
     axs[4].legend(ncol=1)
@@ -134,6 +134,11 @@ function plot_curves(contrast_curves; epoch)
     """
 end
 
+_ncomps = Dict(
+    "2020feb04" => 1,
+    "2020nov21" => 3,
+    "2020nov28" => 2
+)
 
 @progress name="epoch" for epoch in ["2020feb04", "2020nov21", "2020nov28"]
     cube = fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_cube_calib_registered_crop.fits"))
@@ -155,14 +160,15 @@ end
     mav_cube = MultiAnnulusView(cube .- minimum(cube), fwhm; inner=fwhm)
 
     # orient algorithms with appropriate data structures
+    ncomp = _ncomps[epoch]
     targets = [
         (Classic(), av_cube, "median"),
-        (PCA(2), av_cube, "PCA(2)"),
-        (NMF(2), av_cube, "NMF(2)"),
-        (GreeDS(2), av_cube, "GreeDS(2)"),
+        (PCA(ncomp), av_cube, "PCA($ncomp)"),
+        (NMF(ncomp), av_cube, "NMF($ncomp)"),
+        (GreeDS(ncomp), av_cube, "GreeDS($ncomp)"),
         (Framewise(Classic(), delta_rot=0.5), mav_cube, "annular median"),
-        (Framewise(PCA(2), delta_rot=0.5), mav_cube, "annular PCA(2)"),
-        (Framewise(NMF(2), delta_rot=0.5), mav_cube, "annular NMF(2)"),
+        (Framewise(PCA(ncomp), delta_rot=0.5), mav_cube, "annular PCA($ncomp)"),
+        (Framewise(NMF(ncomp), delta_rot=0.5), mav_cube, "annular NMF($ncomp)"),
     ]
 
     contrast_curves = Dict{String, Any}()

### 2021-07-31 src/SiriusB.jl

@@ -11,8 +11,6 @@ using PyCall
 export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir, load_or_produce,
        parallactic_angles, gaussian_fit, gaussian_fit_offset, center
 
-const PYFITS = pyimport("astropy.io.fits")
-
 # path configuration
 rootdir(args...) = joinpath(@__DIR__(), "..", args...)
 datadir(args...) = rootdir("data", args...)
@@ -52,7 +50,10 @@ function load_or_produce(func, filename; force=false)
 end
 
 
-load_fits(filename; kwargs...) = Array(PYFITS.getdata(filename; kwargs...))
+function load_fits(filename; kwargs...)
+    PYFITS = pyimport("astropy.io.fits")
+    Array(PYFITS.getdata(filename; kwargs...))
+end
 load_csv(filename; kwargs...) = DataFrame(CSV.File(filename; kwargs...))
 const LOADER = Dict(
     ".csv" => load_csv,
@@ -61,6 +62,7 @@ const LOADER = Dict(
 
 function save_fits(filename, data; kwargs...)
     mkpath(dirname(filename))
+    PYFITS = pyimport("astropy.io.fits")
     PYFITS.writeto(filename, Array(data); overwrite=true, kwargs...)
 end
 function save_csv(filename, data; kwargs...)

### 2021-07-31 paper/paper.tex
fix some formatting
update paper

@@
 
+\pagebreak
+
 \section{Analysis} \label{sec:analysis}
@@
 For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo\footnote{\citealt{lucas_nirc2_2021}}.
+All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo:\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}.
 
@@
 
-\begin{figure*}[t]
-    \centering
-    \epsscale{1}
-    \plotone{contrast_curves}
-    \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
-In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
-The companion mass values are interpolated from the AMES-Cond grid.
-The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
-The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
-    \label{fig:contrast}
-\end{figure*}
-
 We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
@@
 
+\begin{figure*}
+    \centering
+    \epsscale{1}
+    \plotone{contrast_curves}
+    \caption{The contrast curves for the best performing algorithm from each epoch.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
+The companion mass values are interpolated from the AMES-Cond grid.
+The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
+The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
+    \label{fig:contrast}
+\end{figure*}
+
+\pagebreak
 \section{Conclusions} \label{sec:conclusion}
@@
 \begin{acknowledgments}
+The data presented herein were obtained at the W.
+M.
+Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration.
+The Observatory was made possible by the generous financial support of the W.
+M.
+Keck Foundation.
+The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Maunakea has always had within the indigenous Hawaiian community.
+We are most fortunate to have the opportunity to conduct observations from this mountain.
+\end{acknowledgments}
 
-\end{acknowledgments}
+\facility{Keck:II (NIRC2)}
 

### 2021-08-04 paper/paper.tex
update paper

@@
 \author[0000-0001-6341-310X]{Miles Lucas}
-\affiliation{Institute for Astronomy, University of Hawai'i, USA}
+\affiliation{Institute for Astronomy, University of Hawaii at Manoa, 2680 Woodlawn Dr, Honolulu, HI 96822, USA}
 
 \author[0000-0003-1341-5531]{Michael Bottom}
-\affiliation{Institute for Astronomy, University of Hawai'i, USA}
+\affiliation{Institute for Astronomy, University of Hawaii at Hilo, 640 N Aohoku Pl, Hilo, HI 96720, USA}
 
 \author[0000-0003-4769-1665]{Garreth Ruane}
-\affiliation{Jet Propulsion Laboratory, California Institute of Technology, USA}
+\affiliation{Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr, Pasadena, CA 91109, USA}
 
 \author[0000-0002-0696-1780]{Sam Ragland}
-\affiliation{W.M. Keck Observatory, USA}
+\affiliation{W.M. Keck Observatory, 65-1120 Mamalahoa Hwy, Waimea, HI 96743, USA}
 
@@
 We present deep imaging of Sirius B, the closest and brightest white dwarf.
-We use Keck/NIRC2 in Lp band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging.
+We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging.
 We reach sub-Jupiter sensitivities and sub-AU separations, reaching $\sim$\qty{3.5}{\jupitermass} at $\sim$\qty{0.25}{\au} down to a sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}.
+The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the high-precision of the Sirius B system age.
 We do not detect any companions around Sirius B, consistent with previous studies.
-Our observations are ultimately limited by the sky background more than contrast or separation, which is promising for future imaging studies of nearby faint targets.
 \end{abstract}
@@
 The process required to image a planet is daunting, however.
-The typical astrophysical flux ratios for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{-8}$, and for a Sun-Earth system are $\sim$$10^{-10}$ \citep{traub_direct_2010}.
-The infrared is where blackbody emission from exoplanets peaks, while simultaneously being well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible.
+The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traub_direct_2010}.
+Blackbody emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet.
 In addition, the close angular separations of planets makes it difficult to detect them over the diffraction pattern of their host and other noise sources.
 
-Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a closer projected separation, allowing closer investigation, and younger exoplanets are hotter and therefore brighter, reducing the contrast.
+Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales.
+Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star.
 Another way to reduce contrast would be to make the star fainter, which is precisely what happens in the latest stages of stellar evolution during the white dwarf cooling sequence.
-When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) will eventually exit the main-sequence (MS) and expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase, potentially engulfing planets within the star's roche limit.
+When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase.
+This expansion will engulf planets within the star's Roche limit.
 Then, during the asymptotic giant branch (AGB) phase, mass loss will adiabatically expand any orbits.
-Once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor.
-The faintness broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
-However, the faintness reduces the contrast of planetary companions and the expanded separation greatly benefit imaging.
+Finally, once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor.
+The faintness, broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
+However, the reduced contrast due to the faintness of the star, and the expanded separation of planets both benefit imaging.
 
-White dwarfs do present challenges, and there is limited knowledge of planetary systems around evolved stars.
+\section{Post-MS Evolution}
+
+There is limited knowledge of planetary systems around evolved stars.
 \citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase.
@@
 During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
-In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to enter the system after the violent RGB and AGB phases \citep{perets_second_2010}.
+In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.
 
@@
 The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38.
-Eventually this excess was determined to be from a dust disk \citep{telesco_observations_1990} which is indicative of the planetary formation history.
-The current interpretation associates the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.
+Eventually this excess was determined to be from a dust disk \citep{telesco_observations_1990} and the current interpretation associates the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.
 
-To date, there has been no direct images of an exoplanet around a white dwarf, although a planetary-mass brown dwarf with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit was imaged around a single white dwarf (WD 0806-661B) using Spitzer \citep{luhman_discovery_2011}.
+To date, there has been no direct images of an exoplanet around a white dwarf, although a brown dwarf with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit was imaged around a single white dwarf (WD 0806-661B) using Spitzer \citep{luhman_discovery_2011}.
 The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
@@
 
-A particularly fascinating white dwarf is Sirius B, the closest and brightest white dwarf.
+\section{Sirius B and the Sirius System}
+
+A particularly fascinating such target is Sirius B, the closest and brightest white dwarf.
 The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}.
@@
 
-The orbit of Sirius B was first studied by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
+The age of the Sirius system is has much better precision than most stars ($\sim$1\% vs.
+$\sim$10\% or worse), which is paramount for estimating the mass of a companion from photometry.
+Because Sirius B is relatively young, the age uncertainty exponentially affects planet mass uncertainty due to the rapid cooling of young planets ($<$\qty{1}{\giga\year}) \citep{fortney_giant_2010}.
+The high system age precision is primarily derived from the well-defined dynamical masses of the binary.
+With well-known masses, isochrones and stellar evolution codes can be combined to pinpoint the age.
+The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
 This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B.
@@
 
-Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864}, with the first orbital solution including dynamic masses published by \citet{van_den_bos_orbit_1960}.
-\citet{gatewood_study_1978} improved upon the \citeauthor{van_den_bos_orbit_1960} orbital solution with over 300 more images, finding nearly the same dynamical masses for the binary.
-\citet{bond_sirius_2017} greatly refined the orbit using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864} for Sirius B.
+\citet{van_den_bos_orbit_1960,gatewood_study_1978} were the first to estimate dynamic masses using compilations of photographic plates from Lick and Yerkes observatories.
+\citet{bond_sirius_2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 
-The precise dynamical masses are key for finding the age of Sirius; \citet{bond_sirius_2017} report a cooling age for Sirius B of \qty{126}{\mega\year} using isochrones.
-Studies of the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} lead to estimates of the progenitor mass of Sirius B to be between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yield total ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about $\pm$\qty{10}{\mega\year} \citep{bond_sirius_2017}.
-The precision of the system age is useful for constraining the mass of potential companions.
+To find the total age of Sirius B, \citet{bond_sirius_2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first.
+Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}.
 
@@
 Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-We targeted Sirius B directly using Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
+We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
@@
 Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
-\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B.
+\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically.
 In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
 
-The Keck AO system \citep{wizinowich_performance_2000} was not designed to accommodate stars as bright as Sirius A, so we needed to attenuate the flux greatly to avoid saturating the WFS.
-We experimented with different filters in front of the WFS, settling on a narrow laser-line filter which attenuated Sirius A by $\sim$6 magnitudes.
+The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
@@
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
-We tried deploying the vortex coronagraph along with QACITS, but again the scattered light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
+We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
 
-During each observation, we took calibration frames in the form of dark frames and sky flat frames.
+During each observation, we took dark frames and sky flat frames for calibration.
 We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
-
-\begin{figure}
-    \centering
-    \epsscale{1.1}
-    \plotone{spike}
-    \caption{Calibrated science frame of Sirius b from 2020-02-04 epoch showing the strong scattered light effects from Sirius a.}
-    \label{fig:spike}
-\end{figure}
 
@@
 Observation time is based on the frames that were selected for processing.
+Seeing values are measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
+Seeing values, temperature, and water vapor measurements are all provided by the Maunakea weather center forecast archive.
     \label{tbl:obs}}
@@
     \startdata
-    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & &  &  \\
-    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & &  &  \\
-    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & &  &  \\
+    2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
+    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.75 & 3.5 \\
+    2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
     \enddata
@@
 
-\pagebreak
-
 \section{Analysis} \label{sec:analysis}
 
+\subsection{Pre-processing}
+
+The raw images from NIRC2 required pre-processing before analyzing them for companions.
 For each epoch we applied a flat correction using calibration frames captured during observing.
@@
 For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks at the following GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} and the pre-processed data cubes and parallactic angles are available on Zenodo:\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}.
+All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}) and the pre-processed data cubes and parallactic angles are available on Zenodo:\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}.
+
+\begin{figure}
+    \centering
+    \epsscale{1.1}
+    \plotone{spike}
+    \caption{A diffraction spike sweeping across a calibrated science frame of Sirius B from the first epoch.
+This shows the strong scattered light effects of Sirius A and how they affect the FOV of Sirius B \ang{;;11} away.}
+    \label{fig:spike}
+\end{figure}
+
+\subsection{Post-processing}
 
@@
     \plotone{psf}
-    \caption{The median frame from the 2020-11-21 epoch showing the instrumental PSF.
+    \caption{The median frame from the second epoch showing the instrumental PSF.
 The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}.
@@
 For this analysis we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation frame-by-frame, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
+The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
 
@@
 For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
-We chose 10 as the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components.
-In our analysis we employ the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
+We chose 10 as the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\autoref{fig:pca-contrast-curves}).
+In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
 The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
 A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
-The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms can be found in \autoref{sec:adi-results}.
+The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \autoref{sec:adi-results}.
 
 All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}.
-All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}} in Jupyter notebooks and Julia scripts.
+All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository in Jupyter notebooks and Julia scripts (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}).
 
@@
 
-We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
-For the first two epochs full-frame median subtraction had the best contrast at almost all separations.
-For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
-The innermost annulus from this algorithm has greater than 1 contrast and is not shown.
-The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).
-
-The reduced images do not show consistent or overwhelming evidence for a substellar companion.
-The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} from the center.
-The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star ($\sim$2 FWHM) all reduce the probability of these blobs being true companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
-We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}).
-We take this as direct evidence against the blobs being substellar companions of any kind.
-
-It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
-Both of these algorithms outperform traditional median and PCA subtraction for disk imaging.
-In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}.
-Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess.
-Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.
-
-The contrast maps from the best performing algorithm for each reduction are shown in \autoref{fig:contrast}.
-We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
-Then we use an age of \qty{226}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
-It is important to note how the precision of the system age (see \autoref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids.
-The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the sky-background limited regime.
-
-\begin{figure*}
+\begin{figure*}[t]
     \centering
@@
 The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar.
 In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
@@
 
-\pagebreak
+We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
+For the first two epochs full-frame median subtraction had the best contrast at almost all separations.
+For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
+The innermost annulus from this algorithm has invalid contrast ($>$1) and is not shown.
+The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).
+
+The reduced images do not show consistent or significant evidence for a substellar companion.
+The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} ($\sim$1.6 FWHM) from the center.
+The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
+Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
+We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}).
+We take this as direct evidence against the blobs being substellar companions of any kind.
+
+It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
+Both of these algorithms usually outperform traditional median and PCA subtraction for disk imaging.
+In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}.
+Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess.
+Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.
+
+The contrast maps from the best performing algorithm for each reduction are shown in \autoref{fig:contrast}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
+Then we use an age of \qty{225}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
+The high precision of the Sirius system's age (see \autoref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids.
+The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the background limited regime.
+
 \section{Conclusions} \label{sec:conclusion}
@@
 In this work we present high-contrast images of Sirius B in the near-IR.
-Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}.
-In the mid-IR previous works have only probed as close-in as $\sim$\qty{1}{\au}, where we reach a sensitivity of \qty{0.72}{\jupitermass}.
+Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits.
+Our observations also show how the high precision of the parameters of the Sirius system directly benefit the sensitivity to planets.
+Particularly, the low age uncertainty of Sirius B keeps our mass uncertainty below \qty{0.1}{\jupitermass}.
 Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
-This non-detection is compelling for revising occurrence rates of second-generation planets and debris disks around white dwarfs.
-
-In recent years improving contrast and inner working angle were the dominant parameters of interest.
-Our observations here show that for nearby faint targets (white dwarfs, M-dwarfs, etc.) we are limited more by the sky background than the speckle noise.
-Our sensitivities reach the background limit at $\sim$\ang{;;0.4}, which would correspond to projected separations of \qtyrange{1}{10}{\au} for stars at \qtyrange{2.7}{25}{\parsec}.
-This means potentially reach sub-Jupiter sensitivities around young systems ($\lesssim$\qty{300}{\mega\year}) and $<$\qty{10}{\jupitermass} sensitivities around moderate age systems ($\lesssim$\qty{7}{\giga\year}) for 10s-100s of targets without coronagraphy or extreme AO.
+This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{vigan_high-contrast_2015}.
 
@@
 We have also published our reduced datasets under an open license.
-We hope that this improves the reproducibility of the work as well as providing data for exploring new and different ADI algorithms.
+We hope that this improves the reproducibility of the work as well as providing data for testing new ADI algorithms.
 
-\begin{acknowledgments}
+\begin{acknowledgements}
 The data presented herein were obtained at the W.
@@
 We are most fortunate to have the opportunity to conduct observations from this mountain.
-\end{acknowledgments}
+\end{acknowledgements}
 

### 2021-08-04 paper/figures/contrast.jl

@@ -30,7 +30,7 @@ contrast_curves = [
 
 contrast_to_dmag(contrast) = -2.5 * log10(contrast)
 
-function dmag_to_mass(dmag)
+function dmag_to_mass(dmag, age)
     model.contrast_to_mass(
         deltaMag=dmag,
         age_Myr=age,
@@ -44,18 +44,26 @@ distances = [curve.distance .* auscale for curve in contrast_curves]
 
 masses = map(contrast_curves) do curve
     dmag = contrast_to_dmag.(curve.contrast)
-    dmag_to_mass.(dmag)
+    dmag_to_mass.(dmag, 225)
 end
 
 masses_corr = map(contrast_curves) do curve
     dmag = contrast_to_dmag.(curve.contrast_corr)
-    dmag_to_mass.(dmag)
+    dmag_to_mass.(dmag, 225)
+end
+
+average_error = mean(contrast_curves) do curve
+    dmag = contrast_to_dmag.(curve.contrast)
+    A = dmag_to_mass.(dmag, 225)
+    B = dmag_to_mass.(dmag, 250)
+    mean(abs.(A .- B))
 end
 
 py"""
 import proplot as pro
 fig, axs = pro.subplots(width="7.5in", height="4in")
 
+# curves
 axs.plot($(distances[1]), $(masses[1]), c="C0", label="  2020-02-04\n     median")
 axs.plot($(distances[1]), $(masses_corr[1]), c="C0", ls="--")
 
@@ -65,18 +73,24 @@ axs.plot($(distances[2]), $(masses_corr[2]), c="C1", ls="--")
 axs.plot($(distances[3]), $(masses[3]), c="C5", label="  2020-11-28\nannular PCA(2)")
 axs.plot($(distances[3]), $(masses_corr[3]), c="C5", ls="--")
 
+# error cross
+axs.scatter(0.7, 3, alpha=0, barcolor="k", capsize=2, bardata=$average_error)
+axs.text(0.73, 3, "mean uncertainty from age", fontsize=10, color="k", alpha=0.8, va="center")
+
+# stability limit
 ylims=axs.get_ylim()
-axs.vlines(1.5, *ylims, color="k", alpha=0.5, ls="-.")
+axs.vlines(1.5, *ylims, color="k", alpha=0.4, ls="-.")
 mid = (ylims[0] + ylims[1]) / 2
[…]

### 2021-08-04 paper/figures/psf.jl

@@ -23,8 +23,12 @@ function norm_psf(frame)
 end
 psf = norm_psf(flat)
 
-tick_locs = range(20, 179, length=5)
-tick_labs = @. string(round(0.01 * (tick_locs - 99.5), digits=1))
+parallax = 376.6801e-3 # arcseconds
+pxscale = 0.01 # arcsec / px
+auscale = pxscale / parallax # AU / px
+
+tick_locs = range(25, 174, length=5)
+tick_labs = @. string(round(auscale * (tick_locs - 99.5), digits=1))
 
 py"""
 import proplot as pro
@@ -42,8 +46,8 @@ axs.format(
     xticklabels=$tick_labs,
     yticks=$tick_locs,
     yticklabels=$tick_labs,
-    xlabel="x [arcsec]",
-    ylabel="y [arcsec]",
+    xlabel="x [AU]",
+    ylabel="y [AU]",
 )
 fig.save($(figuredir("psf.pdf")))
 """

### 2021-08-04 paper/figures/residuals.jl

@@ -39,20 +39,27 @@ flat_res = collapse.(res, angles)
 sigs = detectionmap.(significance, flat_res, fwhms)
 stims = stimmap.(res, angles)
 
-tick_locs = range(20, 179, length=5)
-tick_labs = @. string(round(0.01 * (tick_locs - 99.5), digits=1))
+parallax = 376.6801e-3 # arcseconds
+pxscale = 0.01 # arcsec / px
+auscale = pxscale / parallax # AU / px
+
+tick_locs = range(25, 174, length=5)
+tick_labs = @. string(round(auscale * (tick_locs - 99.5), digits=1))
 
 py"""
 import proplot as pro
+from matplotlib import patches
 fig, axs = pro.subplots(ncols=3, wspace="1em", figwidth="7.5in")
 
-axs[0].imshow($(flat_res[1]))#, colorbar="r", colorbar_kw=dict(space=0))
+axs[0].imshow($(flat_res[1]))
 axs[0].text(6, 6, "median", color="w")
 axs[0].format(title="Epoch 2020-02-04")
-axs[1].imshow($(flat_res[2]))#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
+
+axs[1].imshow($(flat_res[2]))
 axs[1].text(6, 6, "median", color="w")
 axs[1].format(title="Epoch 2020-11-21")
-axs[2].imshow($(flat_res[3]))#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
+
+axs[2].imshow($(flat_res[3]))
 axs[2].text(6, 6, "annular PCA(2)", color="w")
 axs[2].format(title="Epoch 2020-11-28")
 
@@ -61,8 +68,8 @@ axs.format(
     xticklabels=$tick_labs,
     yticks=$tick_locs,
     yticklabels=$tick_labs,
-    xlabel="x [arcsec]",
-    ylabel="y [arcsec]",
+    xlabel="x [AU]",
+    ylabel="y [AU]",
 )
 
 fig.save($(figuredir("residuals.pdf")))
@@ -88,8 +95,8 @@ axs.format(
     xticklabels=$tick_labs,
     yticks=$tick_locs,
     yticklabels=$tick_labs,
-    xlabel="x [arcsec]",
-    ylabel="y [arcsec]",
+    xlabel="x [AU]",
+    ylabel="y [AU]",
 )
 
 fig.save($(figuredir("sig.pdf")))
[…]

### 2021-08-04 paper/paper.tex
update paper

@@
 We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging.
-We reach sub-Jupiter sensitivities and sub-AU separations, reaching $\sim$\qty{3.5}{\jupitermass} at $\sim$\qty{0.25}{\au} down to a sensitivity of $\sim$\qty{0.6}{\jupitermass} at $\sim$\qty{1.5}{\au}.
+We reach sub-Jupiter sensitivities and sub-AU separations, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au} down to a sensitivity of \qty{0.6}{\jupitermass} at \qty{1.5}{\au}.
 The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the high-precision of the Sirius B system age.
@@
 There is limited knowledge of planetary systems around evolved stars.
-\citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggests exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase.
+\citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase.
 Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}.
@@
 
-Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
-Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
-The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
-Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
-\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically.
-In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
-
-The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS.
-While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
-From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \cite{bond_sirius_2017}.
-In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
-We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
-
-During each observation, we took dark frames and sky flat frames for calibration.
-We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
-
 \begin{deluxetable*}{ccccccccc}
@@
 
+\begin{figure}
+    \centering
+    \epsscale{1.1}
+    \plotone{spike}
+    \caption{A diffraction spike sweeping across a calibrated science frame of Sirius B from the first epoch.
+This shows the strong scattered light effects of Sirius A and how they affect the FOV of Sirius B \ang{;;11} away.}
+    \label{fig:spike}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \epsscale{1.1}
+    \plotone{psf}
+    \caption{The median frame from the second epoch showing the instrumental PSF.
+The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}.
+The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
+    \label{fig:psf}
+\end{figure}
+
+Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
+We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
+Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
+The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
+\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically.
+In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
+
+The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS.
+While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
+From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}.
+In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
+We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
+
+During each observation, we took dark frames and sky flat frames for calibration.
+We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
+
 \section{Analysis} \label{sec:analysis}
@@
 
-\begin{figure}
-    \centering
-    \epsscale{1.1}
-    \plotone{spike}
-    \caption{A diffraction spike sweeping across a calibrated science frame of Sirius B from the first epoch.
-This shows the strong scattered light effects of Sirius A and how they affect the FOV of Sirius B \ang{;;11} away.}
-    \label{fig:spike}
-\end{figure}
-
 \subsection{Post-processing}
-
-\begin{figure}
-    \centering
-    \epsscale{1.1}
-    \plotone{psf}
-    \caption{The median frame from the second epoch showing the instrumental PSF.
-The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}.
-The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
-    \label{fig:psf}
-\end{figure}
 

### 2021-08-04 paper/figures/contrast.jl

@@ -74,8 +74,8 @@ axs.plot($(distances[3]), $(masses[3]), c="C5", label="  2020-11-28\nannular PCA
 axs.plot($(distances[3]), $(masses_corr[3]), c="C5", ls="--")
 
 # error cross
-axs.scatter(0.7, 3, alpha=0, barcolor="k", capsize=2, bardata=$average_error)
-axs.text(0.73, 3, "mean uncertainty from age", fontsize=10, color="k", alpha=0.8, va="center")
+axs.scatter(0.7, 5, alpha=0, barcolor="k", capsize=2, bardata=$average_error)
+axs.text(0.73, 5, "mean uncertainty from age", fontsize=10, color="k", alpha=0.8, va="center")
 
 # stability limit
 ylims=axs.get_ylim()

### 2021-08-04 paper/figures/psf.jl

@@ -40,7 +40,7 @@ axs.imshow($psf,
     norm=LogNorm(vmin=3e-3, vmax=5e-2),
     colorbar="r",
 )
-axs.format(title="Epoch 2020-11-21")
+# axs.format(title="Epoch 2020-11-21")
 axs.format(
     xticks=$tick_locs,
     xticklabels=$tick_labs,

### 2021-08-04 paper/figures/psf.jl
update psf.jl script

@@ -34,7 +34,7 @@ py"""
 import proplot as pro
 from matplotlib.colors import LogNorm
 
-fig, axs = pro.subplots(figwidth="3.5in")
+fig, axs = pro.subplots(figwidth="4in")
 
 axs.imshow($psf, 
     norm=LogNorm(vmin=3e-3, vmax=5e-2),

### 2021-08-12 paper/paper.tex
update paper

@@
 Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star.
-Another way to reduce contrast would be to make the star fainter, which is precisely what happens in the latest stages of stellar evolution during the white dwarf cooling sequence.
+Another way to reduce contrast would be to image a faint star with bright companions, such as a young white dwarf (WD) star.
 When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase.
@@
 During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
-In addition to \textit{first-generation} planets there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.
+In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.
 
@@
 
-The age of the Sirius system is has much better precision than most stars ($\sim$1\% vs.
+The age of the Sirius system has much better precision than most stars ($\sim$1\% vs.
 $\sim$10\% or worse), which is paramount for estimating the mass of a companion from photometry.
@@
     2020-02-04 & 11.20 & 67.90 & 1.44 & 60.1 & 79.9 & 0.936 & 0.0 & 0.7 \\
-    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.75 & 3.5 \\
+    2020-11-21 & 11.27 & 66.42 & 2.91 & 91.4 & 76.4 & 0.871 & 0.8 & 3.5 \\
     2020-11-28 & 11.27 & 66.38 & 2.44 & 80.4 & 82.2 & 1.23 & -1.5 & 3.0 \\
@@
 Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 (\autoref{tbl:obs}).
+We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per px}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\autoref{tbl:obs}).
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
 The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
-Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, QACITS \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
 \citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically.
@@
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
-We tried deploying the vortex coronagraph along with QACITS, but the diffracted light from Sirius A made QACITS unstable, so we decided to forego any coronagraphy for the remaining observations.
+We tried deploying the vortex coronagraph along with \texttt{QACITS}, but the diffracted light from Sirius A made \texttt{QACITS} unstable, so we decided to forego any coronagraphy for the remaining observations.
 
 During each observation, we took dark frames and sky flat frames for calibration.
-We also disabled the field rotator, which caused the FOV to rotate throughout the night for angular differential imaging \citep[ADI;][]{marois_angular_2006}.
+All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.
 
 \section{Analysis} \label{sec:analysis}
+
+\begin{figure*}
+    \centering
+    \epsscale{1}
+    \plotone{contrast_curves}
+    \caption{The contrast curves for the best performing algorithm from each epoch.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar.
+In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
+The companion mass values are interpolated from the AMES-Cond grid.
+The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
+The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
+    \label{fig:contrast}
+\end{figure*}
 
@@
 For each epoch we applied a flat correction using calibration frames captured during observing.
-We also removed bad pixels using a combination of L.A.Cosmic \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
+We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
 We removed sky background using a high-pass median filter with a box size of 31 pixels.
@@
 \subsection{Post-processing}
-
-By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate.
-This reduces the probability of subtracting companion signal when we subtract the stellar PSF model.
-After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
-
-For this analysis we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
-
-We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve.
-The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
-The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
-We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
-The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \autoref{sec:adi-results}.
-
-A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
-For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
-We chose 10 as the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\autoref{fig:pca-contrast-curves}).
-In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
-The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
-A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
-The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \autoref{sec:adi-results}.
-
-All of the ADI algorithms and metrics are implemented in the open-source Julia package ADI.jl \citep{lucas_adijl_2020}.
-All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository in Jupyter notebooks and Julia scripts (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}).
-
-\section{Results} \label{sec:results}
 
@@
 
-\begin{figure*}[t]
-    \centering
-    \epsscale{1}
-    \plotone{contrast_curves}
-    \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
-The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar.
-In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
-The companion mass values are interpolated from the AMES-Cond grid.
-The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
-The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
-    \label{fig:contrast}
-\end{figure*}
+By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate.
+This reduces the probability of subtracting companion signal when we subtract the stellar PSF model.
+After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
+
+For this analysis we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
+
+We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve.
+The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
+The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
+We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
+The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \autoref{sec:adi-results}.
+
+A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
+For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
+We chose 10 for the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\autoref{fig:pca-contrast-curves}).
+In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
+The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
+A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
+The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \autoref{sec:adi-results}.
+
+All of the ADI algorithms and metrics are implemented in the open-source Julia package \texttt{ADI.jl} \citep{lucas_adijl_2020}.
+All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository in Jupyter notebooks and Julia scripts (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}).
+
+\section{Results} \label{sec:results}
 
@@
 The reduced images do not show consistent or significant evidence for a substellar companion.
-The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\ang{;;0.13} ($\sim$1.6 FWHM) from the center.
-The lack of evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
+The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\qty{0.3}{\au} (\ang{;;0.13}; 1.6 FWHM) from the center.
+The February epoch also shows a blob at a similar separation in the reduced image which does not appear in the STIM map.
+The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
 Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
@@
 Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess.
-Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/SPHERE) may be able to image such a disk.
+Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/ZIMPOL) may be able to image such a disk.
 
@@
 This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{vigan_high-contrast_2015}.
+
+For future work, we consider two potential improvements on our observations.
+As mentioned in \autoref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}.
+Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations.
+Furthermore, the polarimetric differential observation modes of both instruments allow for nearly diffraction-limited imaging, down to 10s of milliarcseconds.
+The other avenue for followup is space-based imaging, which is not to improve on the coronagraphic performance, which is still limited by the scattered light of Sirius A, but rather due to the increased zero-point sensitivity of the instruments.
+For example, using JWST/NIRCAM in long wavelength imaging mode has a limiting magnitude of $sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at $>$\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}.
+However, our ground-based observations are already quite close to the model limits, raising the concern of diminishing returns.
+Planetary atmosphere models must improve, first, before fully reaping the benefits of the additional sensitivity of space-based observations.
 
@@
     \startdata
-    2020-02-04 & $114\pm 40$ & $-115\pm 20$  \\
-    2020-11-21 & $121\pm 38$ & $-119\pm 18$  \\
-    2020-11-28 & $114\pm 41$ & $-113\pm 21$  \\
+    2020-02-04 & $123\pm 40$ & $-128\pm 20$  \\
+    2020-11-21 & $119\pm 38$ & $68\pm 18$  \\
+    2020-11-28 & $132\pm 41$ & $37\pm 21$  \\
     \enddata
@@
     \plotone{orbit_frames}
-    \caption{Provisional astrometry (white circles) displayed on STIM maps using the GreeDS algorithm with 2 components.
-Each frame was cropped to the inner \ang{;;0.25} and the inner FWHM has been masked out.
+    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch.
+Each frame was cropped to the inner $\sim$\qty{7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out.
 The width of the circles represent the uncertainty.}

### 2021-08-12 paper/sections/adi_results_full.tex
update paper

@@
-Results from processing each epoch of Sirius B data with various ADI algorithms.
-The top-left image is the subtracted, derotated, and collapsed image.
-The top-middle image is the Gaussian S/N map, the bottom-middle image is the Student-t S/N (significance) map, which typically requires a value of 5 to show a significant detection, and the bottom-left image is the STIM probability map, which typically requires a probability of 0.5 for significant detection.
-The right graph shows the 5$\sigma$ contrast, both the Gaussian and Student-t corrected curves.
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_median}
-    \caption{2020-02-04 median}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_pca-2}
-    \caption{2020-02-04 PCA(2)}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_nmf-2}
-    \caption{2020-02-04 NMF(2))}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_greeds-2}
-    \caption{2020-02-04 GreeDS(2)}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_annular_median}
-    \caption{2020-02-04 annular median}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_annular_pca-2}
-    \caption{2020-02-04 annular PCA(2))}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020feb04_annular_nmf-2}
-    \caption{2020-02-04 annular NMF(2)}
-\end{figure}
-
 \begin{figure}[h!]
@@
     \plotone{2020feb04_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-02-04 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_median}
-    \caption{2020-11-21 median subtraction.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_pca-2}
-    \caption{2020-11-21 PCA subtraction with 2 components.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_nmf-2}
-    \caption{2020-11-21 NMF subtraction with 2 components.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_greeds-2}    
-    \caption{2020-11-21 GreeDS with 2 components.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_annular_median}
-    \caption{2020-11-21 annular median subtraction with a rotation threshold of 0.5.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_annular_pca-2}
-    \caption{2020-11-21 annular PCA subtraction with 2 components and a rotation threshold ofnov21 0.5.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov21_annular_nmf-2}
-    \caption{2020-11-21 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the first epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
 \end{figure}
@@
     \plotone{2020nov21_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-21 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_median}
-    \caption{2020-11-28 median subtraction.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_pca-2}
-    \caption{2020-11-28 PCA subtraction with 2 components.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_nmf-2}
-    \caption{2020-11-28 NMF subtraction with 2 components.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_greeds-2}
-    \caption{2020-11-28 GreeDS with 2 components.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_annular_median}
-    \caption{2020-11-28 annular median subtraction with a rotation threshold of 0.5.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_annular_pca-2}
-    \caption{2020-11-28 annular PCA subtraction with 2 components and a rotation threshold ofnov28 0.5.}
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \epsscale{0.9}
-    \plotone{reports/2020nov28_annular_nmf-2}
-    \caption{2020-11-28 annular NMF subtraction with 2 components and a rotation threshold of 0.5.}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the second epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
 \end{figure}
@@
     \plotone{2020nov28_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-28 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the third epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\figsetstart
+\figsetnum{10}
+\figsettitle{ADI processing results}
+
+%%% first epoch
+
+\figsetgrpstart
+\figsetgrpnum{10.1}
+\figsetgrptitle{2020-02-04 median}
+\figsetplot{reports/2020feb04_median}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.2}
+\figsetgrptitle{2020-02-04 PCA(1)}
+\figsetplot{reports/2020feb04_pca-1}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame PCA subtraction with 1 component.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.3}
+\figsetgrptitle{2020-02-04 NMF(1)}
+\figsetplot{reports/2020feb04_nmf-1}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame NMF subtraction with 1 component.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.4}
+\figsetgrptitle{2020-02-04 GreeDS(1)}
+\figsetplot{reports/2020feb04_greeds-1}
+\figsetgrpnote{Post-processing results from the first epoch using full-frame GreeDS subtraction with 1 component.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.5}
+\figsetgrptitle{2020-02-04 annular median}
+\figsetplot{reports/2020feb04_annular_median}
+\figsetgrpnote{Post-processing results from the first epoch using annular median subtraction with a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.6}
+\figsetgrptitle{2020-02-04 annular PCA(1)}
+\figsetplot{reports/2020feb04_annular_pca-1}
+\figsetgrpnote{Post-processing results from the first epoch using annular PCA subtraction with 1 component and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.7}
+\figsetgrptitle{2020-02-04 annular NMF(1)}
+\figsetplot{reports/2020feb04_annular_nmf-1}
+\figsetgrpnote{Post-processing results from the first epoch using annular NMF subtraction with 1 component and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+%%% second epoch
+
+\figsetgrpstart
+\figsetgrpnum{10.8}
+\figsetgrptitle{2020-11-21 median}
+\figsetplot{reports/2020nov21_median}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.9}
+\figsetgrptitle{2020-11-21 PCA(3)}
+\figsetplot{reports/2020nov21_pca-3}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame PCA subtraction with 3 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.10}
+\figsetgrptitle{2020-11-21 NMF(3)}
+\figsetplot{reports/2020nov21_nmf-3}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame NMF subtraction with 3 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.11}
+\figsetgrptitle{2020-11-21 GreeDS(3)}
+\figsetplot{reports/2020nov21_greeds-3}
+\figsetgrpnote{Post-processing results from the second epoch using full-frame GreeDS subtraction with 3 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.12}
+\figsetgrptitle{2020-11-21 annular median}
+\figsetplot{reports/2020nov21_annular_median}
+\figsetgrpnote{Post-processing results from the second epoch using annular median subtraction with a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.13}
+\figsetgrptitle{2020-11-21 annular PCA(3)}
+\figsetplot{reports/2020nov21_annular_pca-3}
+\figsetgrpnote{Post-processing results from the second epoch using annular PCA subtraction with 3 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.14}
+\figsetgrptitle{2020-11-21 annular NMF(3)}
+\figsetplot{reports/2020nov21_annular_nmf-3}
+\figsetgrpnote{Post-processing results from the second epoch using annular NMF subtraction with 3 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+%%% third epoch
+
+\figsetgrpstart
+\figsetgrpnum{10.15}
+\figsetgrptitle{2020-11-28 median}
+\figsetplot{reports/2020nov28_median}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.16}
+\figsetgrptitle{2020-11-28 PCA(2)}
+\figsetplot{reports/2020nov28_pca-2}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame PCA subtraction with 2 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.17}
+\figsetgrptitle{2020-11-28 NMF(2)}
+\figsetplot{reports/2020nov28_nmf-2}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame NMF subtraction with 2 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.18}
+\figsetgrptitle{2020-11-28 GreeDS(2)}
+\figsetplot{reports/2020nov28_greeds-2}
+\figsetgrpnote{Post-processing results from the third epoch using full-frame GreeDS subtraction with 2 components.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.19}
+\figsetgrptitle{2020-11-28 annular median}
+\figsetplot{reports/2020nov28_annular_median}
+\figsetgrpnote{Post-processing results from the third epoch using annular median subtraction with a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.20}
+\figsetgrptitle{2020-11-28 annular PCA(2)}
+\figsetplot{reports/2020nov28_annular_pca-2}
+\figsetgrpnote{Post-processing results from the third epoch using annular PCA subtraction with 2 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{10.21}
+\figsetgrptitle{2020-11-28 annular NMF(2)}
+\figsetplot{reports/2020nov28_annular_nmf-2}
+\figsetgrpnote{Post-processing results from the third epoch using annular NMF subtraction with 2 components and a rotation threshold of 0.5 FWHM.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
+\figsetgrpend
+
+\figsetend
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{10}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_median}
+    \caption{Post-processing results from the second epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.
+Outputs for other epochs and other algorithms (21 figures) are in the online figure set and the GitHub repository.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\figsetstart
+\figsetnum{11}
+\figsettitle{PCA, NMF, and GreeDS mosaics}
+
+%%% first epoch
+
+\figsetgrpstart
+\figsetgrpnum{11.1}
+\figsetgrptitle{2020-02-04 PCA mosaic}
+\figsetplot{reports/2020feb04_pca_mosaic}
+\figsetgrpnote{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.2}
+\figsetgrptitle{2020-02-04 NMF mosaic}
+\figsetplot{reports/2020feb04_nmf_mosaic}
+\figsetgrpnote{Collapsed residual frames from the first epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.3}
+\figsetgrptitle{2020-02-04 GreeDS mosaic}
+\figsetplot{reports/2020feb04_greeds_mosaic}
+\figsetgrpnote{Collapsed residual frames from the first epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+%%% second epoch
+
+\figsetgrpstart
+\figsetgrpnum{11.4}
+\figsetgrptitle{2020-11-21 PCA mosaic}
+\figsetplot{reports/2020nov21_pca_mosaic}
+\figsetgrpnote{Collapsed residual frames from the second epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.5}
+\figsetgrptitle{2020-11-21 NMF mosaic}
+\figsetplot{reports/2020nov21_nmf_mosaic}
+\figsetgrpnote{Collapsed residual frames from the second epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.6}
+\figsetgrptitle{2020-11-21 GreeDS mosaic}
+\figsetplot{reports/2020nov21_greeds_mosaic}
+\figsetgrpnote{Collapsed residual frames from the second epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+%%% third epoch
+
+\figsetgrpstart
+\figsetgrpnum{11.7}
+\figsetgrptitle{2020-11-28 PCA mosaic}
+\figsetplot{reports/2020nov28_pca_mosaic}
+\figsetgrpnote{Collapsed residual frames from the third epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.8}
+\figsetgrptitle{2020-11-28 NMF mosaic}
+\figsetplot{reports/2020nov28_nmf_mosaic}
+\figsetgrpnote{Collapsed residual frames from the third epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{11.9}
+\figsetgrptitle{2020-11-28 GreeDS mosaic}
+\figsetplot{reports/2020nov28_greeds_mosaic}
+\figsetgrpnote{Collapsed residual frames from the third epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpend
+
+\figsetend
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{11}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_pca_mosaic}
+    \caption{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components.
+The figures share a common scale and the inner FWHM is masked out for all the frames.
+Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\figsetstart
+\figsetnum{12}
+\figsettitle{PCA, NMF, and GreeDS results}
+
+%%% first epoch
+
+\figsetgrpstart
+\figsetgrpnum{12.1}
+\figsetgrptitle{2020-02-04 PCA contrast}
+\figsetplot{reports/2020feb04_pca_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.2}
+\figsetgrptitle{2020-02-04 NMF contrast}
+\figsetplot{reports/2020feb04_nmf_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using NMF reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.3}
+\figsetgrptitle{2020-02-04 GreeDS contrast}
+\figsetplot{reports/2020feb04_greeds_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using GreeDS reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+%%% second epoch
+
+\figsetgrpstart
+\figsetgrpnum{12.4}
+\figsetgrptitle{2020-11-21 PCA contrast}
+\figsetplot{reports/2020nov21_pca_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.5}
+\figsetgrptitle{2020-11-21 NMF contrast}
+\figsetplot{reports/2020nov21_nmf_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using NMF reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.6}
+\figsetgrptitle{2020-11-21 GreeDS contrast}
+\figsetplot{reports/2020nov21_greeds_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using GreeDS reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+%%% third epoch
+
+\figsetgrpstart
+\figsetgrpnum{12.7}
+\figsetgrptitle{2020-11-28 PCA contrast}
+\figsetplot{reports/2020nov28_pca_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.8}
+\figsetgrptitle{2020-11-28 NMF contrast}
+\figsetplot{reports/2020nov28_nmf_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using NMF reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetgrpstart
+\figsetgrpnum{12.9}
+\figsetgrptitle{2020-11-28 GreeDS contrast}
+\figsetplot{reports/2020nov28_greeds_contrast_curves}
+\figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using GreeDS reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.}
+\figsetgrpend
+
+\figsetend
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{12}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_pca_contrast_curves}
+    \caption{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.
+Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
+    \label{fig:pca-contrast-curves}
+\end{figure}

### 2021-08-12 paper/figures/contrast.jl

@@ -1,7 +1,9 @@
 using CSV
 using DataFrames
+using Interpolations
 using PyCall
 using SiriusB
+using Statistics
 
 pro = pyimport("proplot")
 # rcParams
@@ -56,7 +58,7 @@ average_error = mean(contrast_curves) do curve
     dmag = contrast_to_dmag.(curve.contrast)
     A = dmag_to_mass.(dmag, 225)
     B = dmag_to_mass.(dmag, 250)
-    mean(abs.(A .- B))
+    mean(std([A B], dims=2))
 end
 
 py"""
@@ -74,33 +76,36 @@ axs.plot($(distances[3]), $(masses[3]), c="C5", label="  2020-11-28\nannular PCA
 axs.plot($(distances[3]), $(masses_corr[3]), c="C5", ls="--")
 
 # error cross
-axs.scatter(0.7, 5, alpha=0, barcolor="k", capsize=2, bardata=$average_error)
-axs.text(0.73, 5, "mean uncertainty from age", fontsize=10, color="k", alpha=0.8, va="center")
-
-# stability limit
-ylims=axs.get_ylim()
-axs.vlines(1.5, *ylims, color="k", alpha=0.4, ls="-.")
-mid = (ylims[0] + ylims[1]) / 2
-axs.text(1.45, mid, "dynamic stability limit", color="k", alpha=0.5, va="center", ha="left", rotation="vertical")
+axs.scatter(0.27, 0.73, alpha=0, barcolor="k", capsize=2, bardata=$average_error)
+axs.text(0.3, 0.73, "mean uncertainty from age", fontsize=10, color="k", alpha=0.8, va="center")
 
 # model mass limit
 xlims = axs.get_xlim()
 axs.hlines(0.0005 * 1047.9, *xlims, color="k", alpha=0.3, linestyle=":", label="model mass limit")
+axs.hlines($(1:2:13), *xlims, color="w", alpha=0.5, lw=0.75)
 
 # formatting
 axs.dualx(lambda x: x * $parallax, label="separation [arcsec]")
 axs.legend(ncol=1)
 axs.format(
+    yscale=pro.LogScale(base=2),
     xlabel="projected separation [AU]",
     ylabel="companion mass [M$_J$]",
     grid=True,
-    ylim=(0, ylims[1]),
     xlim=(xlims[0], 2),
     yticks="auto"
 )
 
[…]

### 2021-08-12 paper/figures/orbits.jl

@@ -17,27 +17,22 @@ pro.rc["image.origin"] = "lower"
 pro.rc["image.cmap"] = "inferno"
 pro.rc["grid"] = false
 
-epochs = [
-    "2020feb04",
-    "2020nov21",
-    "2020nov28"
-]
-cubes = [
-    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_cube_calib_registered_crop.fits"))
-    for epoch in epochs
+res_cubes = [
+    fits.getdata(datadir("epoch_2020feb04", "residuals", "2020feb04_sirius-b_residual_median.fits")),
+    fits.getdata(datadir("epoch_2020nov21", "residuals", "2020nov21_sirius-b_residual_median.fits")),
+    fits.getdata(datadir("epoch_2020nov28", "residuals", "2020nov28_sirius-b_residual_annular_pca-2.fits")),
 ]
 angles = [
-    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_pa.fits"))
-    for epoch in epochs
+    fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_pa.fits")),
+    fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_pa.fits")),
+    fits.getdata(datadir("epoch_2020nov28", "processed", "2020nov28_sirius-b_pa.fits")),
 ]
 fwhms = [
     7.985399074538929,
     7.644946278252633,
     8.216162087416189
 ]
-av_cubes = [AnnulusView(cube; inner=fwhm) for (cube, fwhm) in zip(cubes, fwhms)]
-res_cubes = [subtract(GreeDS(2), av_cube; angles=angle) for (av_cube, angle) in zip(av_cubes, angles)]
-stims = [stimmap(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
+# stims = [stimmap(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
 flat_res = [collapse(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
 
 parallax = 376.36801 # mas
@@ -48,9 +43,9 @@ errs = fwhms ./ 2
 
 # guesses from GreeDS outputs of three epochs
[…]

### 2021-08-13 paper/paper.tex
update paper

@@
 \documentclass[twocolumn]{aastex631}
-\usepackage{hyperref}
+\usepackage{cleveref}
 \let\tablenum\relax
@@
 
+% workaround for cleveref+AASTeX
+% https://github.com/AASJournals/AASTeX60/issues/69#issuecomment-685852891
+\makeatletter
+\usepackage{etoolbox}
+\patchcmd\H@refstepcounter{\protected@edef}{\protected@xdef}{}{}
+\makeatother
+
+% custom SI units
 \DeclareSIUnit\parsec{pc}
@@
 \DeclareSIUnit\year{yr}
+\DeclareSIUnit\pixel{px}
 \sisetup{
@@
 We present deep imaging of Sirius B, the closest and brightest white dwarf.
-We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across 3 epochs in 2020 using the technique of angular differential imaging.
+We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging.
 We reach sub-Jupiter sensitivities and sub-AU separations, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au} down to a sensitivity of \qty{0.6}{\jupitermass} at \qty{1.5}{\au}.
-The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the high-precision of the Sirius B system age.
-We do not detect any companions around Sirius B, consistent with previous studies.
+The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the precisely known Sirius B system age.
+Consistent with previous results, we do not detect any companions around Sirius B.
 \end{abstract}
@@
 High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets.
-Being able to probe the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory.
-The process required to image a planet is daunting, however.
+Probing the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory.
+Imaging a planet is challenging, however.
 The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traub_direct_2010}.
-Blackbody emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet.
-In addition, the close angular separations of planets makes it difficult to detect them over the diffraction pattern of their host and other noise sources.
+Thermal emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet.
+In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.
 
-Typical targets for imaging are nearby young stars; the close proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales.
+Typical targets for imaging are nearby young stars; the proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales.
 Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star.
 Another way to reduce contrast would be to image a faint star with bright companions, such as a young white dwarf (WD) star.
-When intermediate mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase.
-This expansion will engulf planets within the star's Roche limit.
-Then, during the asymptotic giant branch (AGB) phase, mass loss will adiabatically expand any orbits.
-Finally, once the star becomes a white dwarf it begins cooling, which reduces its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor.
-The faintness, broad spectral lines, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
+When intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase.
+This expansion engulfs planets within the star's Roche limit.
+If the planet survives this expansion, its orbital separation will gradually increase as the star loses mass during the asymptotic giant branch (AGB) phase.
+Finally, once the star becomes a white dwarf it begins cooling, which will reduce its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor.
+The faintness, lack of spectral features, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
 However, the reduced contrast due to the faintness of the star, and the expanded separation of planets both benefit imaging.
@@
 There is limited knowledge of planetary systems around evolved stars.
-\citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide ($>$\qty{5}{\au}) orbits around intermediate mass stars will survive expansion during the RGB phase.
-Close-in planets that escape the Roche limit of the expanding red giant can still be shredded by tidal forces, although the tidal forces on planets that readily escape engulfment are negligible \citep{nordhaus_orbits_2013}.
-During the AGB phase, stellar mass loss will adiabatically expand the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
+\citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
+Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhaus_orbits_2013}.
+During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
 In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.
 
-The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983} by searching for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
-They found no companions around the $\sim$100 white dwarfs they studied.
-The same method was applied by \citet{zuckerman_excess_1987} who found excess IR emission around white dwarf G29-38.
-Eventually this excess was determined to be from a dust disk \citep{telesco_observations_1990} and the current interpretation associates the dust with accretion onto the white dwarf, polluting the stellar atmosphere \citep{koester_metals_1997}.
+The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983}.
+They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
+The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet.
+They studied $\sim$100 white dwarfs but found no companions.
+The same method was applied by \citet{zuckerman_excess_1987}, who found excess IR emission around white dwarf G29-38.
+The emission was determined to be from a dust disk \citep{telesco_observations_1990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koester_metals_1997}.
+It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsor_pollution_2015}.
+\citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust therefore suppressing any IR excess.
 
-To date, there has been no direct images of an exoplanet around a white dwarf, although a brown dwarf with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit was imaged around a single white dwarf (WD 0806-661B) using Spitzer \citep{luhman_discovery_2011}.
+Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf.
+\citet{luhman_discovery_2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer.
 The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
@@
 The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}.
-As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging, and additionally it is a young system ($\sim$\qty{225}{\mega\year}), further reducing the predicted contrast necessary to image a planetary companion.
+As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging.
+Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortney_giant_2010}.
 
-The age of the Sirius system has much better precision than most stars ($\sim$1\% vs.
-$\sim$10\% or worse), which is paramount for estimating the mass of a companion from photometry.
-Because Sirius B is relatively young, the age uncertainty exponentially affects planet mass uncertainty due to the rapid cooling of young planets ($<$\qty{1}{\giga\year}) \citep{fortney_giant_2010}.
-The high system age precision is primarily derived from the well-defined dynamical masses of the binary.
-With well-known masses, isochrones and stellar evolution codes can be combined to pinpoint the age.
+A common problem in direct imaging is determining planetary masses from photometry using planetary atmosphere evolution grids.
+This method of interpolation depends on the stellar age, the stellar photometry, and the distance to the system.
+Determining stellar ages is quite difficult and sometimes impossible, and is often the largest source of uncertainty when interpolating planetary masses.
+Age uncertainty exponentially affects young systems (\textless\qty{1}{\giga\year}) due to the rapid cooling of giant planets.
+Sirius B avoids these pitfalls due to its unusually high age precision, primarily derived from accurate dynamical masses.
+
 The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
@@
 
-Initial astrometric perturbations suggested a 50 year orbital period \citep{auwers_orbit_1864} for Sirius B.
-\citet{van_den_bos_orbit_1960,gatewood_study_1978} were the first to estimate dynamic masses using compilations of photographic plates from Lick and Yerkes observatories.
+Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwers_orbit_1864}.
+\citet{van_den_bos_orbit_1960,gatewood_study_1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories.
 \citet{bond_sirius_2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holman_long-term_1999}.
+\citet{bond_sirius_2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
 
@@
 Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}.
-
-A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holman_long-term_1999}.
-\citet{bond_sirius_2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
+An age uncertainty of $\sim$1\% is execeptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
 
@@
 In this work we report direct images of Sirius B with Keck/NIRC2.
-\autoref{sec:obs} describes our target and observing strategy, \autoref{sec:analysis} describes the processing and analysis techniques used, \autoref{sec:results} describes our results and we conclude with \autoref{sec:conclusion}.
+The rest of the manuscript is organized as follows: \cref{sec:obs} describes our target and observing strategy, \cref{sec:analysis} describes the processing and analysis techniques used, and \cref{sec:results} describes our results.
 
@@
     \tablecaption{Observing parameters for the three epochs of data.
-All observations were carried out using the NIRC2 Lp-band filter.
+All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}).
 Observation time is based on the frames that were selected for processing.
-Seeing values are measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
-Seeing values, temperature, and water vapor measurements are all provided by the Maunakea weather center forecast archive.
+Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
+Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
     \label{tbl:obs}}
@@
 Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per px}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\autoref{tbl:obs}).
+We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\cref{tbl:obs}).
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
@@
 Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
-\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically.
+We did not try coronagraphy for the remaining observations.
+\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
 In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
 
-The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter to avoid saturating the WFS.
+The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
-From here, we slewed off-axis using the separations and position angles calculated in \autoref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}.
+From here, we slewed off-axis using the separations and position angles calculated in \cref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}.
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
-We tried deploying the vortex coronagraph along with \texttt{QACITS}, but the diffracted light from Sirius A made \texttt{QACITS} unstable, so we decided to forego any coronagraphy for the remaining observations.
 
@@
 The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
-The annular PCA curve is cut off because the contrast in the innermost annulus was greater than 1.}
+The annular PCA curve is cut off because the innermost annulus had greater than 1 contrast, which is invalid.}
     \label{fig:contrast}
@@
 For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter.
-At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \autoref{fig:spike}.
-Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to reach floating-point centroid accuracy.
+At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}.
+Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
 
-The co-registered frames are then shifted to the center of the FOV.
-Lastly the frames were cropped to the inner 200 pixels and stacked into data cubes for each epoch.
+The co-registered frames were shifted to the center of the FOV and cropped to the inner 200 pixels.
 With a pixel scale of \qty{10}{\milliarcsecond} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
+All the frames were stacked into data cubes for each epoch.
 We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yelda_improving_2010}.
-For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\autoref{fig:psf}).
+For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\cref{fig:psf}).
 All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}) and the pre-processed data cubes and parallactic angles are available on Zenodo:\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}.
@@
 
-We used three metrics for determining the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve.
+We used three metrics to determine the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve.
 The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
@@
 We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
-The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \autoref{sec:adi-results}.
+The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \cref{sec:adi-results}.
 
@@
 For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
-We chose 10 for the max number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\autoref{fig:pca-contrast-curves}).
+We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}).
 In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
@@
 A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
-The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \autoref{sec:adi-results}.
+The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \cref{sec:adi-results}.
 
@@
 
-We determined the best-performing algorithms for each epoch using the contrast curves described in \autoref{sec:analysis}.
+We determined the best-performing algorithms for each epoch using the contrast curves described in \cref{sec:analysis}.
 For the first two epochs full-frame median subtraction had the best contrast at almost all separations.
 For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
-The innermost annulus from this algorithm has invalid contrast ($>$1) and is not shown.
-The collapsed residual frames from each epoch are shown in \autoref{fig:residuals}, along with the Gaussian significance maps (\autoref{fig:sig}) and STIM maps (\autoref{fig:stim}).
+The innermost annulus from this algorithm has invalid contrast (\textgreater1) and is not shown.
+The collapsed residual frames from each epoch are shown in \cref{fig:residuals}, along with the Gaussian significance maps (\cref{fig:sig}) and STIM maps (\cref{fig:stim}).
 
@@
 The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\autoref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
-We generated $10^4$ orbits, none of which managed to contain the points from each epoch (\autoref{sec:orbits}).
+Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
+We generated $10^4$ orbits, none of which contained the points from each epoch (\cref{sec:orbits}).
 We take this as direct evidence against the blobs being substellar companions of any kind.
@@
 
-The contrast maps from the best performing algorithm for each reduction are shown in \autoref{fig:contrast}.
+The contrast maps from the best performing algorithm for each reduction are shown in \cref{fig:contrast}.
 We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
 Then we use an age of \qty{225}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
-The high precision of the Sirius system's age (see \autoref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids.
+The high precision of the Sirius system's age (see \cref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids.
+We also tested using the newer SONORA grid \citep{marley_mark_2018_1309035,marley_sonora_2021}, but the differences compared to AMES-Cond were less than the mean uncertainty from age.
 The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the background limited regime.
@@
 In this work we present high-contrast images of Sirius B in the near-IR.
-Our sensitivity limits are the best that have been reached for Sirius B, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits.
+Our sensitivity limits are the best that have been reached for Sirius B so far, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits.
 Our observations also show how the high precision of the parameters of the Sirius system directly benefit the sensitivity to planets.
@@
 For future work, we consider two potential improvements on our observations.
-As mentioned in \autoref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}.
+As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}.
 Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations.
 Furthermore, the polarimetric differential observation modes of both instruments allow for nearly diffraction-limited imaging, down to 10s of milliarcseconds.
-The other avenue for followup is space-based imaging, which is not to improve on the coronagraphic performance, which is still limited by the scattered light of Sirius A, but rather due to the increased zero-point sensitivity of the instruments.
-For example, using JWST/NIRCAM in long wavelength imaging mode has a limiting magnitude of $sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at $>$\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}.
-However, our ground-based observations are already quite close to the model limits, raising the concern of diminishing returns.
-Planetary atmosphere models must improve, first, before fully reaping the benefits of the additional sensitivity of space-based observations.
+
+Followup in the IR from space-based telescopes would increase the sensitivity of the observations due to the absence of background emission from Earth's atmosphere.
+For example, using JWST/NIRCAM in long wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}.
+The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) would still probe down to \qty{0.8}{\au}.
+Observations would be complicated by the scattered light from Sirius A, which could affect the fine-pointing control or worsen the background sensitivity.
+In the end, our ground-based observations are already quite close to the atmospheric model grid limits, raising the concern of diminishing returns.
+Planetary atmosphere models must improve, before fully reaping the benefits of the additional sensitivity of space-based observations.
 
@@
 Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions.
-We began by estimating the astrometry of the blobs by eye in reduced data (\autoref{tbl:astrometry}, \autoref{fig:prov-orbit}).
+We began by estimating the astrometry of the blobs by eye in reduced data (\cref{tbl:astrometry}, \cref{fig:prov-orbit}).
 We tried simulating $10^4$ orbits via rejection sampling with OFTI but failed to constrain all three points with any one orbit.
@@
 \begin{deluxetable}{ccc}[h!]
-    \tablecaption{Provisional astrometry for blobs of interest from each epoch.
+    \tablecaption{Provisional astrometry for a blob of interest from each epoch.
 The separation and offset are in relation to Sirius B.

### 2021-08-13 paper/figures/contrast_compare.jl

@@ -17,7 +17,11 @@ import sys
 sys.path.append($(srcdir()))
 """
 models = pyimport("mass_models")
-model = models.MassModel(srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt"))
+model_cond = models.MassModel(srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt"))
+model_sonora = models.SONORAModel(
+    srcdir("mass_models", "data", "tables_m+0.0_2018", "nc+0.0_co1.0_age"),
+    srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt")
+)
 
 parallax = 376.6801e-3 # arcseconds
 pxscale = 0.01 # arcseconds/px
@@ -32,7 +36,7 @@ contrast_curves = [
 
 contrast_to_dmag(contrast) = -2.5 * log10(contrast)
 
-function dmag_to_mass(dmag, age)
+function dmag_to_mass(dmag, age, model)
     model.contrast_to_mass(
         deltaMag=dmag,
         age_Myr=age,
@@ -46,18 +50,18 @@ distances = [curve.distance .* auscale for curve in contrast_curves]
 
 masses = map(contrast_curves) do curve
     dmag = contrast_to_dmag.(curve.contrast)
-    dmag_to_mass.(dmag, 225)
+    dmag_to_mass.(dmag, 225, model_cond)
 end
 
 masses_corr = map(contrast_curves) do curve
-    dmag = contrast_to_dmag.(curve.contrast_corr)
-    dmag_to_mass.(dmag, 225)
+    dmag = contrast_to_dmag.(curve.contrast)
+    dmag_to_mass.(dmag, 225, model_sonora)
 end
 
 average_error = mean(contrast_curves) do curve
     dmag = contrast_to_dmag.(curve.contrast)
-    A = dmag_to_mass.(dmag, 225)
-    B = dmag_to_mass.(dmag, 250)
+    A = dmag_to_mass.(dmag, 225, model_cond)
+    B = dmag_to_mass.(dmag, 250, model_cond)
     mean(std([A B], dims=2))
 end
 
@@ -106,6 +110,6 @@ axs.set_ylim(ylims)
 # ax2 = axs.alty(reverse=True, label="Δ mag")
[…]

### 2021-08-13 src/mass_models/read_model.py

@@ -7,9 +7,11 @@ import re
 import numpy as np
 from astropy.io import fits
 from astropy.table import Table
+import pandas as pd
 from scipy.interpolate import interp2d
 
-__all__ = ["MassModel"]
+__all__ = ["MassModel", "SONORAModel"]
+
 
 def Mj_to_solar(mass_MJ):
     return mass_MJ / 1047.9
@@ -97,14 +99,14 @@ class MassModel:
         self, prop_0=None, val_0=None, prop_1=None, val_1=None, prop_2=None
     ):
         """interpolate between any three properties.
-           prop0,val_0 -> dependent variable 0, with value val_0
-           prop1,val_1 -> dependent variable 1, with value val_1
-           prop2,      -> output variable.  for example:
-           m = MassModel('/Users/mbottom/Desktop/Coronagraphy/MassModels/model.BT-Settl.M-0.0.MKO.AB.txt')
-           m.interp_between(prop_0 = 'Age(Myr)', val_0 = 1000, prop_1 = "L'", val_1 = 7.091, prop_2 = 'M/Ms')
-           array([0.8])
-           says that at 1000 Myrs, for an L' value of 7.091, you would expect the mass to be 0.8 M*
-           """
+        prop0,val_0 -> dependent variable 0, with value val_0
+        prop1,val_1 -> dependent variable 1, with value val_1
+        prop2,      -> output variable.  for example:
+        m = MassModel('/Users/mbottom/Desktop/Coronagraphy/MassModels/model.BT-Settl.M-0.0.MKO.AB.txt')
+        m.interp_between(prop_0 = 'Age(Myr)', val_0 = 1000, prop_1 = "L'", val_1 = 7.091, prop_2 = 'M/Ms')
+        array([0.8])
+        says that at 1000 Myrs, for an L' value of 7.091, you would expect the mass to be 0.8 M*
+        """
 
         prop_0_below_table = self.get_below(prop_0, val_0)
         x0 = prop_0_below_table[prop_0].iloc[0]
@@ -200,3 +202,73 @@ class MassModel:
         return self.apparent_mag_to_mass(
             appmag=planet_app_mag, age_Myr=age_Myr, band=band, dist_pc=dist_pc
         )
+
+
+class SONORAModel(MassModel):
+    def __init__(self, filename, condgrid):
+        super().__init__(condgrid)
+        self.sonoragrid = pd.read_csv(
[…]

### 2021-08-13 paper/paper.tex
update paper with grammarly

@@
 It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsor_pollution_2015}.
-\citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust therefore suppressing any IR excess.
+\citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.
 
@@
 
-A particularly fascinating such target is Sirius B, the closest and brightest white dwarf.
+A particularly fascinating target is Sirius B, the closest and brightest white dwarf.
 The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}.
@@
 Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}.
-An age uncertainty of $\sim$1\% is execeptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
+An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
 
@@
 
-In this work we report direct images of Sirius B with Keck/NIRC2.
+In this work, we report direct images of Sirius B with Keck/NIRC2.
 The rest of the manuscript is organized as follows: \cref{sec:obs} describes our target and observing strategy, \cref{sec:analysis} describes the processing and analysis techniques used, and \cref{sec:results} describes our results.
@@
 
-During each observation, we took dark frames and sky flat frames for calibration.
+During each observation, we took dark frames and sky-flat frames for calibration.
 All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.
@@
 The raw images from NIRC2 required pre-processing before analyzing them for companions.
-For each epoch we applied a flat correction using calibration frames captured during observing.
+For each epoch, we applied a flat correction using calibration frames captured during observing.
 We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
@@
     \plotone{sig}
-    \caption{The \textit{significance} maps for each epoch accounting for small sample statistics \citep{mawet_fundamental_2014}.
+    \caption{The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawet_fundamental_2014}.
 Typically a critical value for detection is 5.
@@
     \plotone{stim}
-    \caption{The STIM maps for each epoch calculated from the residual cube.
+    \caption{The STIM maps for each epoch calculated from each residual cube.
 The STIM probability has a typical cutoff threshold of 0.5 for significant detections.
@@
 By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate.
-This reduces the probability of subtracting companion signal when we subtract the stellar PSF model.
+This reduces the probability of removing companion signal when we subtract the stellar PSF model.
 After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
 
-For this analysis we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames which have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
+For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
 
@@
 A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
-For PCA, NMF, and GreeDS algorithms, we created residual cubes for increasing number of components, from 1 to 10.
+For PCA, NMF, and GreeDS algorithms, we increased the number of components from 1 to 10, creating a residual cube for each iteration.
 We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}).
@@
 We determined the best-performing algorithms for each epoch using the contrast curves described in \cref{sec:analysis}.
-For the first two epochs full-frame median subtraction had the best contrast at almost all separations.
+For the first two epochs, full-frame median subtraction had the best contrast at almost all separations.
 For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
@@
 In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}.
-Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition there is no prior evidence for a circumstellar disk from IR excess.
+Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition, there is no prior evidence for a circumstellar disk from IR excess.
 Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/ZIMPOL) may be able to image such a disk.
@@
 We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
-Then we use an age of \qty{225}{\mega\year} to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
-The high precision of the Sirius system's age (see \cref{sec:intro}) reduces uncertainty when interpolating planetary mass from the evolutionary grids.
+Then we used \qty{225}{\mega\year} for the system age to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
+The high precision of the Sirius system's age reduces uncertainty when interpolating planetary mass from the evolutionary grids (see \cref{sec:intro}).
 We also tested using the newer SONORA grid \citep{marley_mark_2018_1309035,marley_sonora_2021}, but the differences compared to AMES-Cond were less than the mean uncertainty from age.
@@
 While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets.
-In this work we present high-contrast images of Sirius B in the near-IR.
+In this work, we present high-contrast images of Sirius B in the near-IR.
 Our sensitivity limits are the best that have been reached for Sirius B so far, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits.
-Our observations also show how the high precision of the parameters of the Sirius system directly benefit the sensitivity to planets.
+Our observations also show how the high precision of the parameters of the Sirius system directly benefits the sensitivity to planets.
 Particularly, the low age uncertainty of Sirius B keeps our mass uncertainty below \qty{0.1}{\jupitermass}.
@@
 
-For future work, we consider two potential improvements on our observations.
+For future work, we consider two avenues for followup.
 As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}.
@@
 Followup in the IR from space-based telescopes would increase the sensitivity of the observations due to the absence of background emission from Earth's atmosphere.
-For example, using JWST/NIRCAM in long wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}.
+For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}.
 The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) would still probe down to \qty{0.8}{\au}.
@@
 M.
-Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration.
+Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California, and the National Aeronautics and Space Administration.
 The Observatory was made possible by the generous financial support of the W.
@@
 We began by estimating the astrometry of the blobs by eye in reduced data (\cref{tbl:astrometry}, \cref{fig:prov-orbit}).
-We tried simulating $10^4$ orbits via rejection sampling with OFTI but failed to constrain all three points with any one orbit.
+We tried simulating $10^4$ orbits via rejection sampling with OFTI but no generated orbit was able to constrain all three points.
 Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.
@@
 Each frame was cropped to the inner $\sim$\qty{7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out.
-The width of the circles represent the uncertainty.}
+The width of the circles represents the uncertainty.}
     \label{fig:prov-orbit}

### 2021-09-20 notebooks/equillibrium_temp.jl
add pluto notebook for eq temp visualization

@@ -1,0 +1,261 @@
+### A Pluto.jl notebook ###
+# v0.15.1
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 7927ff00-1806-11ec-2787-4db3c2bd8448
+# imports
+begin
+	using Unitful, UnitfulAstro
+	using UnitfulRecipes
+	using Revise
+	using LinearAlgebra
+	using Pkg
+	Pkg.develop(path="/Users/miles/dev/julia/Transits")
+	using Transits
+	using Plots
+	using Markdown
+end
+
+# ╔═╡ 87591ebf-f36b-4643-bbf1-a961ed1825ff
+md"""
+# Equillibrium temperature in Sirius
+
+When considering a planet orbiting Sirius B, it is interesting to consider the irradiation from Sirius A. This is especially significant due to Sirius B's eccentric orbit (``e=0.6``), leading to an overall range of separations from 7.9-32 AU.
+
+The calculation for equilibrium temperature from a single star is
+```math
+T_\mathrm{eq} = \left[\frac{L(1 - A_B)}{16\sigma\pi a^2} \right]^{1/4}
+```
+
+we assume that adding an additional star will linearly add to the incident flux, so we can extend this to two stars with
+```math
+T_\mathrm{eq} = \sum_i{\left[\frac{L_i(1 - A_B)}{16\sigma\pi a_i^2} \right]^{1/4}}
+```
+
+This does not take into effect any reheating or geometric phase effects, which means this is likely an *upper limit*.
+"""
+
+# ╔═╡ b4375a6e-c669-4f64-aa9c-72375bf96868
+begin
+	plx = 0.3789 # arcsec
+	dist = inv(plx)u"pc" # parsec
+end
+
+# ╔═╡ 0bdbeded-0d6f-426b-80bd-0d20d058baf8
+# don't include i, Ω, or ω because we don't care about the 
+# line-of-sight rotation, only the relative position
+# orbital elements from Bond et al. 2017
[…]

### 2021-09-20 paper/figures/psf.jl
fix plotting bug which produced NAN values when normalizing

@@ -17,9 +17,8 @@ cube= fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_c
 flat = collapse(cube)
 
 function norm_psf(frame)
-    tmp = frame .- minimum(frame)
+    tmp = frame .- minimum(frame) .+ 1
     return tmp ./ maximum(tmp)
-    # return log10.(tmp ./ maximum(tmp))
 end
 psf = norm_psf(flat)
 

### 2021-09-20 paper/adi_results.tex
reorganize paper for easier submission

--- 2021-07-29 paper/sections/adi_results_full.tex
@@
     \plotone{2020nov28_contrast_curves}
-    \caption{5$\sigma$ contrast curves from various ADI algorithms for the 2020-11-28 epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown.}
+    \caption{5$\sigma$ contrast curves from every ADI algorithm for the third epoch. Both the Gaussian (solid lines) and Student-t corrected (dashed lines) contrast curves are shown. }
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{10}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_median}
+    \caption{Post-processing results from the second epoch using full-frame median subtraction.
+The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
+In each frame the inner FWHM is masked out.
+The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.
+Outputs for other epochs and other algorithms (21 figures) are in the online figure set and the GitHub repository.}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{11}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_pca_mosaic}
+    \caption{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components.
+The figures share a common scale and the inner FWHM is masked out for all the frames.
+Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[h!]
+    \centering
+    \figurenum{12}
+    \epsscale{0.9}
+    \plotone{reports/2020feb04_pca_contrast_curves}
+    \caption{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
+The left two figures are the average STIM probability map, and the SLIM detection map.
+For both of these maps, a typical cutoff value is 0.5.
+Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
+    \label{fig:pca-contrast-curves}
+\end{figure}

### 2021-09-20 paper/paper.tex
reorganize paper for easier submission

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn,linenumbers]{aastex631}
 \usepackage{cleveref}
@@
 We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
-The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \cref{sec:adi-results}.
+The collapsed residual frames along with the above metrics for each algorithm for each epoch are in section~\ref{sec:adi-results}.
 
@@
 A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
-The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \cref{sec:adi-results}.
+The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in section~\ref{sec:adi-results}.
 
@@
 Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
-We generated $10^4$ orbits, none of which contained the points from each epoch (\cref{sec:orbits}).
+We generated $10^4$ orbits, none of which contained the points from each epoch (section~\ref{sec:orbits}).
 We take this as direct evidence against the blobs being substellar companions of any kind.
@@
 
-\input{sections/adi_results}
+\input{adi_results_full}
 

### 2021-10-13 src/SiriusB.jl
add defaults and table interpolator to module source code

@@ -3,13 +3,23 @@ module SiriusB
 using CSV
 using DataFrames
 using Dates
+using DelimitedFiles
+using Dierckx
 using FITSIO
 import ImageTransformations: center
 using SkyCoords
 using PyCall
 
 export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir, load_or_produce,
-       parallactic_angles, gaussian_fit, gaussian_fit_offset, center
+       parallactic_angles, gaussian_fit, gaussian_fit_offset, center, table_interpolate, ATMO2020,
+       contrast_to_dmag, distance_modulus
+
+# constants associated with Sirius B
+const parallax = 374.48958852876103e-3 # arcsecond
+const distance = inv(parallax) # pc
+const pxscale = 0.01 # arcseconds/px
+const auscale = pxscale / parallax # AU/px
+const appmag = 9.01 # Ks band from Bonnet-Biduad 2008
 
 # path configuration
 rootdir(args...) = joinpath(@__DIR__(), "..", args...)
@@ -18,6 +28,10 @@ srcdir(args...) = rootdir("src", args...)
 notebookdir(args...) = rootdir("notebooks", args...)
 paperdir(args...) = rootdir("paper", args...)
 figuredir(args...) = paperdir("figures", args...)
+
+# simple calculations
+contrast_to_dmag(contrast) = -2.5log10(contrast)
+distance_modulus(distance) = 5log10(distance) - 5
 
 """
     load_or_produce(f, filename; force=false)
@@ -77,5 +91,6 @@ const SAVER = Dict(
 include("angles.jl")
 include("fitting.jl")
 include("badpix.jl")
+include("tables.jl")
 
 end

### 2021-10-13 src/tables.jl

@@ -1,0 +1,68 @@
+function get_below(subtable, arg)
+    _tab = Iterators.filter(r -> r[arg.first] ≤ arg.second, eachrow(subtable))
+    y = maximum(r -> r[arg.first], _tab)
+    return filter(r -> r[arg.first] ≈ y, subtable)
+end
+
+function get_above(subtable, arg)
+    _tab = Iterators.filter(r -> r[arg.first] > arg.second, eachrow(subtable))
+    y = minimum(r -> r[arg.first], _tab)
+    return filter(r -> r[arg.first] ≈ y, subtable)
+end
+
+
+function table_interpolate(table, arg1, arg2, arg3)
+    sub = copy(table)
+
+    sub0 = get_below(sub, arg1)
+    x0 = x1 = sub0[1, arg1.first]
+
+    tab0 = get_below(sub0, arg2)
+    y0 = tab0[1, arg2.first]
+    z0 = tab0[1, arg3]
+
+    tab1 = get_above(sub0, arg2)
+    y1 = tab1[1, arg2.first]
+    z1 = tab1[1, arg3]
+
+    sub1 = get_above(sub, arg1)
+    x2 = x3 = sub1[1, arg1.first]
+
+    tab2 = get_below(sub1, arg2)
+    y2 = tab2[1, arg2.first]
+    z2 = tab2[1, arg3]
+
+    tab3 = get_above(sub1, arg2)
+    y3 = tab3[1, arg2.first]
+    z3 = tab3[1, arg3]
+
+    xs = [x0, x1, x2, x3]
+    ys = [y0, y1, y2, y3]
+    zs = [z0, z1, z2, z3]
+    spl = Spline2D(xs, ys, zs, kx=1, ky=1)
+    return spl(arg1.second, arg2.second)
+end
+
+#################################################
+
+function read_ATMO2020_grid(dir)
+    filenames = filter(f -> endswith(f, "vega.txt"), readdir(dir))
+
+    header = ["Mass", "Age", "Teff", "Luminosity", "Radius", "Gravity", "MKO_Y", "MKO_J", "MKO_H", 
+              "MKO_K", "MKO_Lp", "MKO_Mp", "W1", "W2", "W3", "W4", "IRAC_CH1", "IRAC_CH2"]
+    
+    full_table = mapreduce(vcat, filenames) do filename
+        mat = readdlm(joinpath("MKO_WISE_IRAC", filename), skipstart=2)
+        # a bunch of magnitudes listed with 0, treat as NaN
[…]

### 2021-10-13 src/tables.jl
fix bug in directory parsing

@@ -52,7 +52,7 @@ function read_ATMO2020_grid(dir)
               "MKO_K", "MKO_Lp", "MKO_Mp", "W1", "W2", "W3", "W4", "IRAC_CH1", "IRAC_CH2"]
     
     full_table = mapreduce(vcat, filenames) do filename
-        mat = readdlm(joinpath("MKO_WISE_IRAC", filename), skipstart=2)
+        mat = readdlm(joinpath(dir, filename), skipstart=2)
         # a bunch of magnitudes listed with 0, treat as NaN
         @. mat[iszero(mat)] = NaN
         return DataFrame(mat, header)

### 2021-10-13 paper/figures/contrast_compare.jl
remove old code

@@ -1,115 +1,0 @@
-using CSV
-using DataFrames
-using Interpolations
-using PyCall
-using SiriusB
-using Statistics
-
-pro = pyimport("proplot")
-# rcParams
-pro.use_style("ggplot")
-pro.rc["image.origin"] = "lower"
-pro.rc["image.cmap"] = "inferno"
-pro.rc["grid"] = false
-
-py"""
-import sys
-sys.path.append($(srcdir()))
-"""
-models = pyimport("mass_models")
-model_cond = models.MassModel(srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt"))
-model_sonora = models.SONORAModel(
-    srcdir("mass_models", "data", "tables_m+0.0_2018", "nc+0.0_co1.0_age"),
-    srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt")
-)
-
-parallax = 376.6801e-3 # arcseconds
-pxscale = 0.01 # arcseconds/px
-auscale = pxscale / parallax # AU/px
-age = 226; # Myr
-
-contrast_curves = [
-    DataFrame(CSV.File(datadir("epoch_2020feb04", "residuals", "2020feb04_contrast-curve_median.csv"))),
-    DataFrame(CSV.File(datadir("epoch_2020nov21", "residuals", "2020nov21_contrast-curve_median.csv"))),
-    DataFrame(CSV.File(datadir("epoch_2020nov28", "residuals", "2020nov28_contrast-curve_annular-pca-2.csv"))),
-]
-
-contrast_to_dmag(contrast) = -2.5 * log10(contrast)
-
-function dmag_to_mass(dmag, age, model)
-    model.contrast_to_mass(
-        deltaMag=dmag,
-        age_Myr=age,
-        band="Lp",
-        dist_pc=1/parallax,
-        stellar_apparent_mag=9.1
-    )
-end
-
-distances = [curve.distance .* auscale for curve in contrast_curves]
-
-masses = map(contrast_curves) do curve
-    dmag = contrast_to_dmag.(curve.contrast)
-    dmag_to_mass.(dmag, 225, model_cond)
-end
-
-masses_corr = map(contrast_curves) do curve
-    dmag = contrast_to_dmag.(curve.contrast)
-    dmag_to_mass.(dmag, 225, model_sonora)
-end
-
[…]

### 2021-10-13 paper/figures/contrast.jl
update contrast curves

@@ -12,17 +12,6 @@ pro.rc["image.origin"] = "lower"
 pro.rc["image.cmap"] = "inferno"
 pro.rc["grid"] = false
 
-py"""
-import sys
-sys.path.append($(srcdir()))
-"""
-models = pyimport("mass_models")
-model = models.MassModel(srcdir("mass_models", "data", "model.AMES-Cond-2000.M-0.0.MKO.Vega.txt"))
-
-parallax = 376.6801e-3 # arcseconds
-pxscale = 0.01 # arcseconds/px
-auscale = pxscale / parallax # AU/px
-age = 226; # Myr
 
 contrast_curves = [
     DataFrame(CSV.File(datadir("epoch_2020feb04", "residuals", "2020feb04_contrast-curve_median.csv"))),
@@ -30,82 +19,114 @@ contrast_curves = [
     DataFrame(CSV.File(datadir("epoch_2020nov28", "residuals", "2020nov28_contrast-curve_annular-pca-2.csv"))),
 ]
 
-contrast_to_dmag(contrast) = -2.5 * log10(contrast)
+# convert distances from pixels to AU
+distances = [curve.distance .* SiriusB.auscale for curve in contrast_curves]
 
-function dmag_to_mass(dmag, age)
-    model.contrast_to_mass(
-        deltaMag=dmag,
-        age_Myr=age,
-        band="Lp",
-        dist_pc=1/parallax,
-        stellar_apparent_mag=9.1
-    )
+function contrast_to_absmag(y)
+    Δmag = contrast_to_dmag(y)
+    appmag = SiriusB.appmag + Δmag
+    return appmag - distance_modulus(SiriusB.distance)
 end
 
-distances = [curve.distance .* auscale for curve in contrast_curves]
-
-masses = map(contrast_curves) do curve
-    dmag = contrast_to_dmag.(curve.contrast)
-    dmag_to_mass.(dmag, 225)
-end
-
-masses_corr = map(contrast_curves) do curve
-    dmag = contrast_to_dmag.(curve.contrast_corr)
-    dmag_to_mass.(dmag, 225)
-end
-
-average_error = mean(contrast_curves) do curve
-    dmag = contrast_to_dmag.(curve.contrast)
-    A = dmag_to_mass.(dmag, 225)
-    B = dmag_to_mass.(dmag, 250)
-    mean(std([A B], dims=2))
-end
-
[…]

### 2021-10-13 paper/figures/residuals.jl
add extra plots with different clipping for detection maps

@@ -39,10 +39,6 @@ flat_res = collapse.(res, angles)
 sigs = detectionmap.(significance, flat_res, fwhms)
 stims = stimmap.(res, angles)
 
-parallax = 376.6801e-3 # arcseconds
-pxscale = 0.01 # arcsec / px
-auscale = pxscale / parallax # AU / px
-
 tick_locs = range(25, 174, length=5)
 tick_labs = @. string(round(auscale * (tick_locs - 99.5), digits=1))
 
@@ -100,6 +96,30 @@ axs.format(
 )
 
 fig.save($(figuredir("sig.pdf")))
+
+fig, axs = pro.subplots(ncols=3, wspace="1em", figwidth="7.5in")
+
+axs[0].imshow($(sigs[1]), vmin=3)#, colorbar="r", colorbar_kw=dict(space=0))
+axs[0].text(6, 6, "median", color="w")
+axs[0].format(title="Epoch 2020-02-04")
+axs[1].imshow($(sigs[2]), vmin=3)#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
+axs[1].text(6, 6, "median", color="w")
+axs[1].format(title="Epoch 2020-11-21")
+m= axs[2].imshow($(sigs[3]), vmin=3)#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
+axs[2].text(6, 6, "annular PCA(2)", color="w")
+axs[2].format(title="Epoch 2020-11-28")
+fig.colorbar(m, loc="r", label="significance")
+
+axs.format(
+    xticks=$tick_locs,
+    xticklabels=$tick_labs,
+    yticks=$tick_locs,
+    yticklabels=$tick_labs,
+    xlabel="x [AU]",
+    ylabel="y [AU]",
+)
+
+fig.save($(figuredir("sig_threshold.pdf")))
 """
 
 py"""
@@ -127,4 +147,28 @@ axs.format(
 )
 
 fig.save($(figuredir("stim.pdf")))
+
+fig, axs = pro.subplots(ncols=3, wspace="1em", figwidth="7.5in")
+
+axs[0].imshow($(stims[1]), vmin=0.5, vmax=1)#, colorbar="r", colorbar_kw=dict(space=0))
+axs[0].text(6, 6, "median", color="w")
+axs[0].format(title="Epoch 2020-02-04")
[…]

### 2021-10-13 paper/figures/orbits.jl
update figures to use SiriusB module constants and saved data

@@ -35,8 +35,8 @@ fwhms = [
 # stims = [stimmap(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
 flat_res = [collapse(res_cube, angle) for (res_cube, angle) in zip(res_cubes, angles)]
 
-parallax = 376.36801 # mas
-pxscale = 10 # mas/px
+parallax = SiriusB.parallax * 1e3 # mas
+pxscale = SiriusB.pxscale * 1e3 # mas/px
 
 
 errs = fwhms ./ 2
@@ -136,9 +136,9 @@ mydriver = driver.Driver(
     "OFTI",
     1, # number of bodies
     3.081, # total system mass M_sun https://iopscience.iop.org/article/10.3847/1538-4357/aa6af8/pdf
-    parallax, # parallax in mas https://iopscience.iop.org/article/10.3847/1538-4357/aa6af8/pdf
+    parallax, # parallax in mas (EDR3)
     mass_err = 0.034,
-    plx_err = 1.4
+    plx_err = 0.2313347
 )
 
 s = mydriver.sampler

### 2021-10-13 paper/figures/pca_nmf_greeds.jl

@@ -12,11 +12,6 @@ pro.rc["image.cmap"] = "inferno"
 pro.rc["image.origin"] = "lower"
 pro.rc["grid"] = false
 
-parallax = 376.6801e-3 # arcseconds
-pxscale = 0.01 # arcsec / px
-auscale = pxscale / parallax # AU / px
-
-
 _label(a::Type{<:PCA}) = "PCA"
 _label(a::Type{<:NMF}) = "NMF"
 _label(a::Type{<:GreeDS}) = "GreeDS"
@@ -49,7 +44,7 @@ function plot_mosaic(res_cubes, angles; epoch, label, ncomps)
     end
 
     ticks = range(40, 159, length=3)
-    tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
+    tick_labs = @. string(round(SiriusB.pxscale * (ticks - 99.5), digits=1))
 
     figname = make_filename_friendly(figuredir("reports", "$(epoch)_$(label)_mosaic.pdf"))
     py"""
@@ -75,7 +70,7 @@ function plot_results(res_cubes, angles, contrast_curves; epoch, label, fwhm)
     """
     # plot the average STIM map and SLIM probability map
     ticks = range(20, 179, length=5)
-    tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
+    tick_labs = @. string(round(SiriusB.pxscale * (ticks - 99.5), digits=1))
 
     stimmap, slimmask = slimmap(res_cubes, angles; N=ceil(Int, π/4 * fwhm^2))
     slimprob = stimmap .* slimmask
@@ -103,7 +98,7 @@ function plot_results(res_cubes, angles, contrast_curves; epoch, label, fwhm)
     """
     # now plot contrast curves
     for curve in contrast_curves
-        dist = curve.distance .* auscale
+        dist = curve.distance .* SiriusB.auscale
         py"""
         l = axs[2].plot($dist, $(curve.contrast), cycle=cycle)
         lines.extend(l)
@@ -113,7 +108,7 @@ function plot_results(res_cubes, angles, contrast_curves; epoch, label, fwhm)
     py"""
     axs[2].text(0.25, 5e-4, $(_epochs[epoch]), fontsize=14)
     fig.colorbar(lines, loc="r", label="ncomp", values=range(1, 11))
-    axs[2].dualx(lambda x: x * $parallax, label="separation [arcsec]")
[…]

### 2021-10-13 paper/figures/psf.jl

@@ -22,12 +22,8 @@ function norm_psf(frame)
 end
 psf = norm_psf(flat)
 
-parallax = 376.6801e-3 # arcseconds
-pxscale = 0.01 # arcsec / px
-auscale = pxscale / parallax # AU / px
-
 tick_locs = range(25, 174, length=5)
-tick_labs = @. string(round(auscale * (tick_locs - 99.5), digits=1))
+tick_labs = @. string(round(SiriusB.auscale * (tick_locs - 99.5), digits=1))
 
 py"""
 import proplot as pro

### 2021-10-13 paper/figures/reports.jl

@@ -12,10 +12,6 @@ pro.rc["image.cmap"] = "inferno"
 pro.rc["image.origin"] = "lower"
 pro.rc["grid"] = false
 
-parallax = 376.6801e-3 # arcseconds
-pxscale = 0.01 # arcsec / px
-auscale = pxscale / parallax # AU / px
-
 function plot_results(res_cube, angles, curve; fwhm, epoch, label)
     # produce images
     flat_res = collapse(res_cube, angles)
@@ -23,10 +19,10 @@ function plot_results(res_cube, angles, curve; fwhm, epoch, label)
     sig_map = detectionmap(significance, flat_res, fwhm)
     stim_map = stimmap(res_cube, angles)
 
-    arcsec = curve.distance .* pxscale
+    arcsec = curve.distance .* SiriusB.pxscale
 
     ticks = range(20, 179, length=5)
-    tick_labs = @. string(round(pxscale * (ticks - 99.5), digits=1))
+    tick_labs = @. string(round(SiriusB.pxscale * (ticks - 99.5), digits=1))
     # start plotting
     # NB: proplot does tricky things with the Axes class that doesn't play nicely
     # with PyCall.jl because it's treated as a Vector in Julia, so use Python
@@ -104,7 +100,7 @@ function plot_curves(contrast_curves; epoch)
     """
     i = 0
     for (label, curve) in contrast_curves
-        dist = curve.distance .* auscale
+        dist = curve.distance .* SiriusB.auscale
         color = "C$i"
         py"""
         axs.plot($dist, $(curve.contrast), color=$color, label=$label)
@@ -115,7 +111,7 @@ function plot_curves(contrast_curves; epoch)
     py"""
     axs.text(0.25, 5e-4, $(_epochs[epoch]), fontsize=14)
     axs.legend(ncol=2)
-    axs.dualx(lambda x: x * $parallax, label="separation [arcsec]")
+    axs.dualx(lambda x: x * $(SiriusB.parallax), label="separation [arcsec]")
     ax2 = axs.alty(
         yticks=[0.09, 0.31, 0.54, 0.77, 1],
         yticklabels=["8", "6", "4", "2", "0"],

### 2021-10-13 paper/figures/residuals.jl

@@ -16,9 +16,10 @@ epochs = [
     "2020nov21",
     "2020nov28"
 ]
-cubes = [
-    fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_cube_calib_registered_crop.fits"))
-    for epoch in epochs
+res = [
+    fits.getdata(datadir("epoch_2020feb04", "residuals", "2020feb04_sirius-b_residual_median.fits")),
+    fits.getdata(datadir("epoch_2020nov21", "residuals", "2020nov21_sirius-b_residual_median.fits")),
+    fits.getdata(datadir("epoch_2020nov28", "residuals", "2020nov28_sirius-b_residual_annular_pca-2.fits")),
 ]
 angles = [
     fits.getdata(datadir("epoch_$epoch", "processed", "$(epoch)_sirius-b_pa.fits"))
@@ -30,17 +31,12 @@ fwhms = [
     8.216162087416189
 ]
 
-res = [
-    subtract(Classic(), AnnulusView(cubes[1]; inner=fwhms[1])),
-    subtract(Classic(), AnnulusView(cubes[2]; inner=fwhms[2])),
-    subtract(Framewise(PCA(2), delta_rot=0.5), MultiAnnulusView(cubes[3], fwhms[3]; inner=fwhms[3]); angles=angles[3])
-]
 flat_res = collapse.(res, angles)
 sigs = detectionmap.(significance, flat_res, fwhms)
 stims = stimmap.(res, angles)
 
 tick_locs = range(25, 174, length=5)
-tick_labs = @. string(round(auscale * (tick_locs - 99.5), digits=1))
+tick_labs = @. string(round(SiriusB.auscale * (tick_locs - 99.5), digits=1))
 
 py"""
 import proplot as pro

### 2021-10-14 paper/paper.tex
update paper with references and new intro

@@
 Imaging a planet is challenging, however.
-The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traub_direct_2010}.
+The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
 Thermal emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet.
@@
 
-Typical targets for imaging are nearby young stars; the proximity means the same angular separation probes a smaller physical separation, allowing for studies closer to solar-system scales.
-Younger exoplanets are hotter and therefore brighter, reducing the flux ratio between the planet and its host star.
-Another way to reduce contrast would be to image a faint star with bright companions, such as a young white dwarf (WD) star.
-When intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) eventually exit the main-sequence (MS) they expand up to $\sim$100s of stellar radii during the red giant branch (RGB) phase.
-This expansion engulfs planets within the star's Roche limit.
-If the planet survives this expansion, its orbital separation will gradually increase as the star loses mass during the asymptotic giant branch (AGB) phase.
-Finally, once the star becomes a white dwarf it begins cooling, which will reduce its luminosity by 3 to 4 orders of magnitude compared to its MS progenitor.
-The faintness, lack of spectral features, and expanded orbits make white dwarfs exceptionally challenging for the transit photometry and radial velocity methods.
-However, the reduced contrast due to the faintness of the star, and the expanded separation of planets both benefit imaging.
+White dwarfs (WD) are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their main-sequence (MS) progenitors which reduces the contrast necessary to detect a companion.
+In addition, the relative lack of spectral features of WDs makes them imprecise targets for radial velocity analysis.
+The intrinsic faintness of WDs proves challenging for all detection methods; this is exacerbated on ground-based telescopes which require significant signal-to-noise (S/N) to operate their adaptive optics (AO) facilities.
+This implicitly limits searches of WDs to the $\sim$\qty{100}{\parsec} neighborhood.
+Little is known about post-MS planetary evolution, however, planets that are tenuous enough to survive the red giant and asymptotic giant phases of its host are interesting laboratories for planetary formation pathways as showcased by recent discoveries like giant planet candidate WD 1856+534b \citep{vanderburgGiantPlanetCandidate2020}.
 
-\section{Post-MS Evolution}
+In this work, we briefly review post-MS planetary formation theory (\cref{sec:post-ms}) and discuss the Sirius system, specifically bright WD Sirius B, as potential exoplanet hosts (\cref{sec:sirius}).
+In \cref{sec:obs}, \cref{sec:analysis}, and \cref{sec:results} we describe our observations of Sirius B in 2020, along with the subsequent analysis.
+Finally, in \cref{sec:conclusion} we discuss the implications of our observations for planetary formation theory and future work.
+
+\section{Post-MS Evolution} \label{sec:post-ms}
 
 There is limited knowledge of planetary systems around evolved stars.
-\citet{burleigh_imaging_2002,veras_post-main-sequence_2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
-Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhaus_orbits_2013}.
-During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeans_cosmogonic_1924}.
-In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{perets_second_2010}.
+\citet{burleighImagingPlanetsNearby2002a,verasPostmainsequencePlanetarySystem2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
+Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}.
+During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeansCosmogonicProblemsAssociated1924}.
+In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.
 
-The first search for substellar companions around white dwarfs was conducted by \citet{probst_infrared_1983}.
+The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}.
 They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
@@
 They studied $\sim$100 white dwarfs but found no companions.
-The same method was applied by \citet{zuckerman_excess_1987}, who found excess IR emission around white dwarf G29-38.
-The emission was determined to be from a dust disk \citep{telesco_observations_1990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koester_metals_1997}.
-It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsor_pollution_2015}.
-\citet{skemer_sirius_2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.
+The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38.
+The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}.
+It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}.
+\citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.
 
 Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf.
-\citet{luhman_discovery_2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer.
-The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hogan_dodo_2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
-The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xu_extreme-ao_2015}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.
+\citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer.
+The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
+The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.
 
-\section{Sirius B and the Sirius System}
+\section{Sirius B and the Sirius System} \label{sec:sirius}
 
 A particularly fascinating target is Sirius B, the closest and brightest white dwarf.
-The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{bond_sirius_2017,gaia_collaboration_gaia_2018}.
+The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}.
 As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging.
-Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortney_giant_2010}.
+Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.
 
@@
 
-The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{bessel_variations_1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
-This dark satellite was visually confirmed in \citet{bond_companion_1862} as Sirius B.
-\citet{adams_spectrum_1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.
+The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{besselVariationsProperMotions1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
+This dark satellite was visually confirmed in \citet{bondCompanionSiriusProf1862} as Sirius B.
+\citet{adamsSpectrumCompanionSirius1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.
 
-Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwers_orbit_1864}.
-\citet{van_den_bos_orbit_1960,gatewood_study_1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories.
-\citet{bond_sirius_2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
-A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holman_long-term_1999}.
-\citet{bond_sirius_2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
+Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}.
+\citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories.
+\citet{bondSiriusSystemIts2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}.
+\citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
 
-To find the total age of Sirius B, \citet{bond_sirius_2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first.
-Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummings_two_2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bond_sirius_2017}.
+To find the total age of Sirius B, \citet{bondSiriusSystemIts2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first.
+Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummingsTwoMassiveWhite2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bondSiriusSystemIts2017}.
 An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
 
-The first modern imaging study searching for companions around Sirius B was \citet{schroeder_search_2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
-Around the same time \citet{kuchner_search_2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
+The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
+Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
 These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
-\citet{bonnet-bidaud_adonis_2008} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
-\citet{skemer_sirius_2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
-\citet{thalmann_piercing_2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
-Recently, \citet{pathak_high_2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
+\citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
+\citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
+\citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
+Recently, \citet{pathakHighContrastImaging2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
 Because of the simultaneous observation, their contrast depended on which region of the FOV was tested.
@@
 \section{Observations} \label{sec:obs}
+\defcitealias{bonnet-bidaudADONISHighContrast2008a}{BB08}
+\defcitealias{bondSiriusSystemIts2017}{B17}
+\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
+\defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
+\begin{deluxetable}{cccc}
+    \tablecaption{Parameters of the Sirius system adopted in this study.\label{tbl:system}}
+    \tablehead{
+        \colhead{parameter} & \colhead{value} & \colhead{unit} & \colhead{ref.}
+    }
+    \startdata
+    $t_\mathrm{sys}$ & 226 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
+    $\pi$ & \num{374.5\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
+    $d$ & \num{2.67\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
+    \cutinhead{Sirius A}
+    $M_\star$ & \num{2.063\pm0.023} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
+    \cutinhead{Sirius B}
+    $M_\star$ & \num{1.018\pm0.011} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
+    $t_\mathrm{WD}$ & 125 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018}\\
+    $m^{Lp}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
+    $M^{Lp}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
+    \enddata
+\end{deluxetable}
 
-\begin{deluxetable*}{ccccccccc}
+\begin{deluxetable*}{ccccccccc}[t]
     \tabletypesize{\small}
@@
 
+% \begin{deluxetable}{ccccc}
+%     \tabletypesize{\small}
+%     \tablecaption{Observing parameters for the three epochs of data.
+All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}).
+Observation time is based on the frames that were selected for processing.
+Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
+Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
+%     \label{tbl:obs}}
+%     \tablehead{
+%         \colhead{Epoch} &
+%         \colhead{2020-02-4} &
+%         \colhead{2020-11-21} &
+%         \colhead{2020-11-28} &
+%         \colhead{}
+%     }
+%     \startdata
+%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
+%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
+%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
+%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
+%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
+%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
+%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
+%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
+%     \enddata
+% \end{deluxetable}
+
 \begin{figure}
@@
 The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
-Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabyn_w_2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{huby_w_2017}, performed erratically in the presence of the scattered light.
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of the scattered light.
 We did not try coronagraphy for the remaining observations.
-\citet[\S2]{vigan_high-contrast_2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
+\citet[\S2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
 In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
 
-The Keck AO system \citep{wizinowich_performance_2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
+The Keck AO system \citep{wizinowichPerformanceKeckObservatory2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
-From here, we slewed off-axis using the separations and position angles calculated in \cref{tbl:obs} from the orbital parameters in \citet{bond_sirius_2017}.
+From here, we slewed off-axis using the separations and position angles calculated in \cref{tbl:obs} from the orbital parameters in \citet{bondSiriusSystemIts2017}.
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
@@
 During each observation, we took dark frames and sky-flat frames for calibration.
-All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{marois_angular_2006}.
+All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
 
@@
 The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
-The mean uncertainty from the total system age ($\sim$\qty{10}{\mega\year}) is shown by a lone error bar.
-In addition, the expected upper limit for orbital separation of a stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
-The companion mass values are interpolated from the AMES-Cond grid.
-The lower mass limit (upper magnitude limit) of these models is plotted in a light-gray horizontal dashed line.
-The annular PCA curve is cut off because the innermost annulus had greater than 1 contrast, which is invalid.}
+The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
+The annular PCA curve is cut off because the innermost annulus has a contrast value greater than 1, which means even a 100 S/N companion would not be detectable with 5$\sigma$ significance.}
     \label{fig:contrast}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \epsscale{1}
+    \plotone{mass_curves}
+    \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the best contrast.
+The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits.
+The two ages represent the ages of the two potential formation pathways, one of which is the system age (\qty{226}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{125}{\mega\year}).
+The limits are calculated assuming an Lp apparant magnitude for Sirius B of \num{9.01} and converting contrast into absolute magnitudes.
+The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing.
+The lower mass limit of the ATMO2020 grid is plotted with a horizontal dashed line and the expected upper limit for dynamically stable orbits of \qty{1.5}{\au} is plotted with a vertical dashed line.}
+    \label{fig:mass}
 \end{figure*}
@@
 For each epoch, we applied a flat correction using calibration frames captured during observing.
-We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{van_dokkum_cosmic-ray_2001} and an adaptive sigma-clipping algorithm.
+We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{vandokkumCosmicRayRejectionLaplacian2001a} and an adaptive sigma-clipping algorithm.
 We removed sky background using a high-pass median filter with a box size of 31 pixels.
@@
 At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}.
-Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairos_efficient_2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
+Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
 
@@
 All the frames were stacked into data cubes for each epoch.
-We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yelda_improving_2010}.
+We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
 For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\cref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}) and the pre-processed data cubes and parallactic angles are available on Zenodo:\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}.
+All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\cref{sec:data}).
 
@@
 This reduces the probability of removing companion signal when we subtract the stellar PSF model.
-After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottom_noise-weighted_2017}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
+After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
 
-For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{marois_angular_2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummer_detection_2012}, non-negative matrix factorization \citep[NMF;][]{ren_non-negative_2018}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairet_reference-less_2019,pairet_mayonnaise_2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{marois_angular_2006}.
+For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{maroisAngularDifferentialImaging2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummerDetectionCharacterizationExoplanets2012a}, non-negative matrix factorization \citep[NMF;][]{renNonnegativeMatrixFactorization2018a}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{papairetReferencelessAlgorithmCircumstellar2019a,pairetMAYONNAISEMorphologicalComponents2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
+These algorithms are implemented in the open-source \texttt{ADI.jl} Julia package \citep{lucasADIJlJulia2020}.
 
-We used three metrics to determine the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve.
+We used three metrics available in \texttt{ADI.jl} to determine the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairetSTIMMapDetection2019}, and the contrast curve.
 The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
 The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
-We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}.
+We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
 The collapsed residual frames along with the above metrics for each algorithm for each epoch are in section~\ref{sec:adi-results}.
@@
 We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}).
-In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic.
+In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairetSignalProcessingMethods2020} as an ensemble statistic.
 The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
@@
 The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in section~\ref{sec:adi-results}.
-
-All of the ADI algorithms and metrics are implemented in the open-source Julia package \texttt{ADI.jl} \citep{lucas_adijl_2020}.
-All of the code for the ADI processing in this paper, including the scripts for each figure produced are in a GitHub repository in Jupyter notebooks and Julia scripts (\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}).
+All of the code used for this analysis is available in a GitHub respository (\cref{sec:data}).
 
@@
 For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
-The innermost annulus from this algorithm has invalid contrast (\textgreater1) and is not shown.
+The innermost annulus from this algorithm has greater than 1 contrast which implies a 100 S/N companion would not be detected with 5$\sigma$ significance.
+The contrast for this innermost annulus is therefore not plotted.
 The collapsed residual frames from each epoch are shown in \cref{fig:residuals}, along with the Gaussian significance maps (\cref{fig:sig}) and STIM maps (\cref{fig:stim}).
@@
 The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}.
+Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a}.
 We generated $10^4$ orbits, none of which contained the points from each epoch (section~\ref{sec:orbits}).
@@
 
-It is interesting to note the morphology of the innermost $\sim$\ang{;;0.4} in the frames produced by GreeDS and NMF.
-Both of these algorithms usually outperform traditional median and PCA subtraction for disk imaging.
-In the frames from each epoch, but particularly in the two November epochs, a symmetric ``barbell'' shape can be seen which is similar to other disk images \citep[e.g., fig.~7][]{norris_vampires_2014}.
-Due to the nature of high-contrast imaging, it is difficult to differentiate systematic noise from real signal in the speckle-limited regime, in addition, there is no prior evidence for a circumstellar disk from IR excess.
-Follow-up work in the visible (e.g., Subaru/VAMPIRES, VLT/ZIMPOL) may be able to image such a disk.
+\subsection{Companion Mass Detection Limits}
 
 The contrast maps from the best performing algorithm for each reduction are shown in \cref{fig:contrast}.
-We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bonnet-bidaud_adonis_2008}).
-Then we used \qty{225}{\mega\year} for the system age to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models \citep{allard_models_2012}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bidaudADONISHighContrast2008a}).
+Then we used \qty{225}{\mega\year} for the system age to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models .
 The high precision of the Sirius system's age reduces uncertainty when interpolating planetary mass from the evolutionary grids (see \cref{sec:intro}).
-We also tested using the newer SONORA grid \citep{marley_mark_2018_1309035,marley_sonora_2021}, but the differences compared to AMES-Cond were less than the mean uncertainty from age.
+We also tested using the newer SONORA grid , but the differences compared to AMES-Cond were less than the mean uncertainty from age.
 The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the background limited regime.
@@
 Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
-This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{vigan_high-contrast_2015}.
+This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{viganHighcontrastImagingSirius2015}.
 
 For future work, we consider two avenues for followup.
-As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES \citep{norris_vampires_2014} or VLT/ZIMPOL \citep{schmid_zimpol_2018}.
+As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES .
 Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations.
@@
 Followup in the IR from space-based telescopes would increase the sensitivity of the observations due to the absence of background emission from Earth's atmosphere.
-For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation \citep{pontoppidan_pandeia_2016}.
+For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation .
 The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) would still probe down to \qty{0.8}{\au}.
@@
 
-We have published alongside this work the entire codebase used for pre-processing and reducing the data, and for generating every figure in this manuscript.
-We have also published our reduced datasets under an open license.
-We hope that this improves the reproducibility of the work as well as providing data for testing new ADI algorithms.
+\subsection{Data and Code Availability} \label{sec:data}
+All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}}.
+This code includes all of the scripts for generating each figure in this manuscript.
+The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}}.
+We hope that this improves the reproducibility of the work as well as providing data for future investigations.
+Please reach out to the corresponding author for further inquiries regarding data and code availability.
 
@@
 \software{
-ADI.jl \citep{lucas_adijl_2020},
-astropy \citep{collaboration_astropy_2013,astropy_collaboration_astropy_2018},
-Julia \citep{bezanson_julia_2017},
-numpy \citep{harris_array_2020},
-scikit-image \citep{walt_scikit-image_2014},
+ADI.jl \citep{lucasADIJlJulia2020},
+astropy \citep{cocollaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
+Julia \citep{bezansonJuliaFreshApproach2017},
+numpy \citep{harrisArrayProgrammingNumPy2020},
+scikit-image \citep{waltScikitimageImageProcessing2014},
 }
@@
     \centering
-    \figurenum{13}
+    \figurenum{14}
     \plotone{orbit_frames}
     \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch.
-Each frame was cropped to the inner $\sim$\qty{7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out.
+Each frame was cropped to the inner $\sim$\qty{0.7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out.
 The width of the circles represents the uncertainty.}

### 2021-10-14 paper/figures/contrast.jl

@@ -45,7 +45,6 @@ axs.plot($(distances[3]), $(contrast_curves[3].contrast_corr), c="C5", ls="--")
 
 # formatting
 axs.dualx(lambda x: x * $(SiriusB.parallax), label="separation [arcsec]")
-axs.legend(ncol=1)
 axs.format(
     yscale="log",
     xlabel="projected separation [AU]",
@@ -55,6 +54,16 @@ axs.format(
     xlim=(None, 2),
 )
 
+# he's mad, he's gona and made a custom legend!
+from matplotlib.lines import Line2D
+leg1 = axs.legend(ncol=1, loc="ur")
+elements = [
+    Line2D([0], [0], color="k", alpha=0.6, label="Gaussian"),
+    Line2D([0], [0], color="k", alpha=0.6, ls="--", label="Student-t"),
+]
+axs.legend(handles=elements, queue=True, loc="uc")
+axs.add_artist(leg1)
+
 # stability limit
 ylims=axs.get_ylim()
 axs.vlines(1.5, *ylims, color="k", alpha=0.4, ls="-.")
@@ -63,7 +72,7 @@ mid = (ylims[0] + ylims[1]) / 40
 axs.text(1.45, mid, "dynamical stability limit", color="k", alpha=0.5, va="center", ha="left", rotation="vertical")
 axs.set_ylim(ylims)
 
-ax2 = axs.alty(reverse=True, label="abs. mag")
+ax2 = axs.alty(reverse=True, label="abs. mag [$M^{Lp}$]")
 ax2.plot($(distances[2]), $(contrast_to_absmag.(contrast_curves[2].contrast)), alpha=0)
 
 fig.savefig($(figuredir("contrast_curves.pdf")))
@@ -108,15 +117,23 @@ axs.hlines([1, 3, 5, 6, 7, 9, 10], *xlims, color="w", alpha=0.5, lw=0.75)
 
 # formatting
 axs.dualx(lambda x: x * $(SiriusB.parallax), label="separation [arcsec]")
-axs.legend(ncol=1)
 axs.format(
     yscale=pro.LogScale(base=2),
     xlabel="projected separation [AU]",
-    ylabel="mass [$M_J$] ",
+    ylabel="companion mass [$M_J$] ",
     grid=True,
     yformatter="auto",
     xlim=(None, 2),
 )
+
+# custom legend
+leg1 = axs.legend(ncol=1, loc="ur")
+elements = [
[…]

### 2021-11-03 paper/figures/residuals.jl
update to combine significance and stim detection map plots

@@ -69,18 +69,27 @@ fig.save($(figuredir("residuals.pdf")))
 
 py"""
 import proplot as pro
-fig, axs = pro.subplots(ncols=3, wspace="1em", figwidth="7.5in")
+fig, axs = pro.subplots(ncols=3, nrows=2, wspace="1em", figwidth="7.5in")
 
-axs[0].imshow($(sigs[1]), vmin=0, vmax=5)#, colorbar="r", colorbar_kw=dict(space=0))
-axs[0].text(6, 6, "median", color="w")
-axs[0].format(title="Epoch 2020-02-04")
-axs[1].imshow($(sigs[2]), vmin=0, vmax=5)#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
-axs[1].text(6, 6, "median", color="w")
-axs[1].format(title="Epoch 2020-11-21")
-m= axs[2].imshow($(sigs[3]), vmin=0, vmax=5)#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
-axs[2].text(6, 6, "annular PCA(2)", color="w")
-axs[2].format(title="Epoch 2020-11-28")
-fig.colorbar(m, loc="r", label="significance")
+axs[0, 0].imshow($(sigs[1]), vmin=0, vmax=5)#, colorbar="r", colorbar_kw=dict(space=0))
+axs[0, 0].text(6, 6, "median", color="w")
+axs[0, 0].format(title="Epoch 2020-02-04")
+axs[0, 1].imshow($(sigs[2]), vmin=0, vmax=5)#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
+axs[0, 1].text(6, 6, "median", color="w")
+axs[0, 1].format(title="Epoch 2020-11-21")
+m= axs[0, 2].imshow($(sigs[3]), vmin=0, vmax=5)#, colorbar="r", vmin=0, colorbar_kw=dict(space=0))
+axs[0, 2].text(6, 6, "annular PCA(2)", color="w")
+axs[0, 2].format(title="Epoch 2020-11-28")
+axs[0, 2].colorbar(m, loc="r", label="significance")
+
+
+axs[1, 0].imshow($(stims[1]), vmin=0, vmax=1)#, colorbar="r", colorbar_kw=dict(space=0))
+axs[1, 0].text(6, 6, "median", color="w")
[…]

### 2021-11-03 paper/figures/contrast.jl
update mass curves plots

@@ -50,7 +50,7 @@ axs.format(
     xlabel="projected separation [AU]",
     ylabel="contrast ",
     grid=True,
-    yformatter="sci",
+    yformatter="log",
     xlim=(None, 2),
 )
 
@@ -81,69 +81,133 @@ pro.close(fig)
 
 for curve in contrast_curves
     curve.absmags = contrast_to_absmag.(curve.contrast)
-    curve.masses_226 = map(curve.absmags) do absmag
-        table_interpolate(ATMO2020, :Age => 0.226, :MKO_Lp => absmag, :Mass_MJ)
+    curve.masses_225 = map(curve.absmags) do absmag
+        table_interpolate(ATMO2020, :Age => 0.225, :MKO_Lp => absmag, :Mass_MJ)
     end
-    curve.masses_125 = map(curve.absmags) do absmag
-        table_interpolate(ATMO2020, :Age => 0.125, :MKO_Lp => absmag, :Mass_MJ)
+    curve.masses_126 = map(curve.absmags) do absmag
+        table_interpolate(ATMO2020, :Age => 0.126, :MKO_Lp => absmag, :Mass_MJ)
     end
     curve.absmags_corr = contrast_to_absmag.(curve.contrast_corr)
-    curve.masses_corr_226 = map(curve.absmags_corr) do absmag
-        table_interpolate(ATMO2020, :Age => 0.226, :MKO_Lp => absmag, :Mass_MJ)
+    curve.masses_corr_225 = map(curve.absmags_corr) do absmag
+        table_interpolate(ATMO2020, :Age => 0.225, :MKO_Lp => absmag, :Mass_MJ)
     end
-    curve.masses_corr_125 = map(curve.absmags_corr) do absmag
-        table_interpolate(ATMO2020, :Age => 0.125, :MKO_Lp => absmag, :Mass_MJ)
+    curve.masses_corr_126 = map(curve.absmags_corr) do absmag
+        table_interpolate(ATMO2020, :Age => 0.126, :MKO_Lp => absmag, :Mass_MJ)
+    end
+    # these try catch curves are because Sonora grid bottoms out
+    curve.masses_225_SonoraSolar = map(curve.absmags) do absmag
+        try
+            table_interpolate(SonoraSolar, :age_Gyr => 0.225, :Keck_Lp => absmag, :M_Mjup)
+        catch
+            NaN
+        end
+    end
[…]

### 2021-11-03 paper/adi_results_full.tex
update paper with new intro and discussion

--- 2021-08-12 paper/sections/adi_results_full.tex
@@
     \centering
-    \epsscale{0.9}
     \plotone{2020feb04_contrast_curves}
@@
     \centering
-    \epsscale{0.9}
     \plotone{2020nov21_contrast_curves}
@@
     \centering
-    \epsscale{0.9}
     \plotone{2020nov28_contrast_curves}
@@
 The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
-In each frame the inner FWHM is masked out.
+In each frame the inner two FWHMs are masked out.
 The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
@@
     \figurenum{10}
-    \epsscale{0.9}
     \plotone{reports/2020feb04_median}
@@
 The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
-In each frame the inner FWHM is masked out.
+In each frame the inner two FWHMs are masked out.
 The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.
@@
 \figsetplot{reports/2020feb04_pca_mosaic}
-\figsetgrpnote{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020feb04_nmf_mosaic}
-\figsetgrpnote{Collapsed residual frames from the first epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the first epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020feb04_greeds_mosaic}
-\figsetgrpnote{Collapsed residual frames from the first epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the first epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020nov21_pca_mosaic}
-\figsetgrpnote{Collapsed residual frames from the second epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the second epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020nov21_nmf_mosaic}
-\figsetgrpnote{Collapsed residual frames from the second epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the second epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020nov21_greeds_mosaic}
-\figsetgrpnote{Collapsed residual frames from the second epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the second epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020nov28_pca_mosaic}
-\figsetgrpnote{Collapsed residual frames from the third epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the third epoch using PCA reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020nov28_nmf_mosaic}
-\figsetgrpnote{Collapsed residual frames from the third epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the third epoch using NMF reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
 \figsetplot{reports/2020nov28_greeds_mosaic}
-\figsetgrpnote{Collapsed residual frames from the third epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner FWHM is masked out for all the frames.}
+\figsetgrpnote{Collapsed residual frames from the third epoch using GreeDS reduction with 1-10 components. The figures share a common scale and the inner two FWHMs are masked out for all the frames.}
 \figsetgrpend
@@
     \figurenum{11}
-    \epsscale{0.9}
     \plotone{reports/2020feb04_pca_mosaic}
     \caption{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components.
-The figures share a common scale and the inner FWHM is masked out for all the frames.
+The figures share a common scale and the inner two FWHMs are masked out for all the frames.
 Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
@@
     \figurenum{12}
-    \epsscale{0.9}
     \plotone{reports/2020feb04_pca_contrast_curves}

### 2021-11-03 paper/paper.tex
update paper with new intro and discussion

@@
-\documentclass[twocolumn,linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 \usepackage{cleveref}
@@
 \newcommand\latex{La\TeX}
+\newcommand\Lp{$\mathrm{L}^\prime$}
 
@@
 
-\title{An Imaging Search for Circumstellar Companions of Sirius B}
+\title{An Imaging Search for Post-MS Companions of Sirius B}
 
-\shorttitle{An Imaging Search for Circumstellar Companions of Sirius B}
+\shorttitle{An Imaging Search for Post-MS Companions of Sirius B}
 \shortauthors{Lucas et al.}
@@
 \begin{abstract}
-We present deep imaging of Sirius B, the closest and brightest white dwarf.
-We use Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging.
-We reach sub-Jupiter sensitivities and sub-AU separations, reaching \qty{3.5}{\jupitermass} at \qty{0.25}{\au} down to a sensitivity of \qty{0.6}{\jupitermass} at \qty{1.5}{\au}.
-The uncertainty in mass sensitivity is below \qty{0.1}{\jupitermass} due to the precisely known Sirius B system age.
+Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.
+We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-MS planetary evolution in the Sirius system.
+We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging.
+Our observations are contrast limited out to \qty{1}{\au} and background limited beyond.
+The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.3} absolute magnitude.
+We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits using the ATMO2020 and Sonora Bobcat model grids.
+We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.7}{3}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.5}{\jupitermass} at \textgreater\qty{1}{\au}.
 Consistent with previous results, we do not detect any companions around Sirius B.
+Our excellent detection limits, even without coronagraphy, demonstrate the capabilities for modern high-contrast imaging studies of nearby (\textless\qty{25}{\parsec}) white dwarfs.
 \end{abstract}
@@
 
-High-contrast imaging (HCI) is a powerful technique for discovering and characterizing exoplanets.
-Probing the architecture, formation, and atmospheres of planets directly is necessary for advancing substellar companion formation and evolution theory.
-Imaging a planet is challenging, however.
-The typical astrophysical flux ratios (contrast) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
-Thermal emission from exoplanets peaks in the infrared and is well into the Rayleigh-Jeans limit of the star, decreasing contrast compared to the visible or ultraviolet.
-In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.
+\begin{itemize}
+    \item add Debes text
+    \item run through python scripts/grammarly
+    \item reorganize Zenodo sections
+    \item remove extra references
+    \item compile latex diff
+    \item add comments to latex diff referencing referee report
+\end{itemize}
 
-White dwarfs (WD) are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their main-sequence (MS) progenitors which reduces the contrast necessary to detect a companion.
-In addition, the relative lack of spectral features of WDs makes them imprecise targets for radial velocity analysis.
-The intrinsic faintness of WDs proves challenging for all detection methods; this is exacerbated on ground-based telescopes which require significant signal-to-noise (S/N) to operate their adaptive optics (AO) facilities.
-This implicitly limits searches of WDs to the $\sim$\qty{100}{\parsec} neighborhood.
-Little is known about post-MS planetary evolution, however, planets that are tenuous enough to survive the red giant and asymptotic giant phases of its host are interesting laboratories for planetary formation pathways as showcased by recent discoveries like giant planet candidate WD 1856+534b \citep{vanderburgGiantPlanetCandidate2020}.
+In recent decades astronomers have discovered thousands of exoplanets orbiting stars that will eventually evolve into giants and then white dwarfs \citep{akesonNASAExoplanetArchive2013}.
+The fate of planets around these stars beyond the main-sequence (MS) is uncertain due to the large expansion, stellar winds, and high irradiation encountered on the giant branch \citep{verasPostmainsequencePlanetarySystem2016}.
+Despite this, direct evidence from white dwarf (WD) pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
+Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.
 
-In this work, we briefly review post-MS planetary formation theory (\cref{sec:post-ms}) and discuss the Sirius system, specifically bright WD Sirius B, as potential exoplanet hosts (\cref{sec:sirius}).
-In \cref{sec:obs}, \cref{sec:analysis}, and \cref{sec:results} we describe our observations of Sirius B in 2020, along with the subsequent analysis.
-Finally, in \cref{sec:conclusion} we discuss the implications of our observations for planetary formation theory and future work.
-
-\section{Post-MS Evolution} \label{sec:post-ms}
+The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs.
+As the MS star runs out of Hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius.
+When Helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
+Eventually the star will run out of fuel and conclude its nuclear burning and become a WD.
+The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.
 
 There is limited knowledge of planetary systems around evolved stars.
-\citet{burleighImagingPlanetsNearby2002a,verasPostmainsequencePlanetarySystem2016} suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
+The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain.
+For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
+Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.
+The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.
+
+Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions.
+\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where in multi-star systems the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system).
+Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with ``hot-start'' planetary formation timescales \citep{spiegelSpectralPhotometricDiagnostics2012a}.
+A first-generation planet could act as a seed for planetesimal growth in these disks, too.
+Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies.
+\citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI).
+\citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted 3-body problem and concluded up to $\sim$10\% of all WD binaries might contain ``star-hopper'' planets which migrate between the stars.
+
+\textbf{John Debes work from 2000-2010 with Spitzer, HST}
+
+Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
+We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade.
+In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}).
+We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}).
+We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}).
+Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).
+
+\section{Directly imaging post-MS systems} \label{sec:imaging}
+
+High-contrast imaging is a powerful technique for discovering and characterizing exoplanets.
+Directly imaging a circumstellar companion is difficult, though.
+The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
+In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.
+Thermal emission from exoplanets peaks, well into in the infrared, on the Rayleigh-Jeans limit of the stellar spectrum.
+This makes infrared observations preferred over optical or ultraviolet observations due to the reduced contrast.
+
+WDs are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their MS progenitors which reduces the contrast necessary to detect a companion.
+The high effective temperatures of WD photospheres pushes the peak thermal emission even further into the optical and ultraviolet, reducing the intrinsic contrast between the star and the planet.
+In addition, the lack of spectral features of WDs \citep{schatzmanTheorieDebitEnergie1945} makes them imprecise targets for the radial velocity technique.
+The faintness of WDs proves challenging due to the high signal-to-noise ratio (S/N) required by modern adaptive optics (AO) instruments.
+This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing.
+This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13).
+Implicitly, this also limits searches to nearby WDs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
+
+% \section{Post-MS evolution} \label{sec:post-ms}
+
+% There is limited knowledge of planetary systems around evolved stars.
+The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain.
+The expansion of the stellar photosphere will engulf companions and cause tidal interactions, destroying planets or disrupting their orbits \citep{burleighImagingPlanetsNearby2002a, nordhausOrbitsLowmassCompanions2013}.
+Planets that escape engulfment will encounter stellar winds and strong irradiation, causing orbital expansion \citep{jeansCosmogonicProblemsAssociated1924}, enriching the circumstellar environment with metals and dust, and strongly heating planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.
+
+% The observational evidence for planets in post-MS systems is varied.
+WD atmospheres quickly separate heavy elements in their atmospheres due to their high surface gravity \citep{schatzmanTheorieDebitEnergie1945}, which causes the elements to sink and stratify.
+The time scale for this phenomena can be days to $\sim$\qty{1}{\mega\year}, significantly shorter than WD cooling ages, which means that most WD atmospheres are comprised of hydrogen, helium, and some carbon.
+However, metals heavier than carbon have been detected in WDs with cooling ages between \qtyrange{30}{500}{\mega\year}.
+A common explanation for the ``pollution'' of these WDs is the accretion of planetary material.
+This is backed up by the evidence of WD debris disks, although only a fraction of all polluted WDs are host to a disk \citep{koesterFrequencyPlanetaryDebris2014}.
+Chemical analysis shows the pollution is closer to planetary in origin rather than the interstellar medium.
+Most damning, though, is the correlation between the relative population of polluted WDs (25\% - 50\%) and the expected number of MS planet hosts \citep{koesterFrequencyPlanetaryDebris2014}.
+
+% suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
 Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}.
-During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet by a maximum factor of $M_{*,\mathrm{MS}}/M_{*,\mathrm{WD}}$ \citep{jeansCosmogonicProblemsAssociated1924}.
+During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet .
 In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.
 
-The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}.
+% The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}.
 They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
@@
 
-Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf.
+% Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf.
 \citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer.
@@
 
-\section{Sirius B and the Sirius System} \label{sec:sirius}
+\section{Sirius B and the Sirius system} \label{sec:sirius}
 
-A particularly fascinating target is Sirius B, the closest and brightest white dwarf.
-The Sirius system is the 7th closest to the sun at \qty{2.6}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1Vm star known for being the brightest, and Sirius B, a DA2 white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}.
-As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for imaging.
+One fascinating target for post-MS observations is Sirius B, the closest and brightest WD to our solar system.
+The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}.
+As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for direct imaging.
 Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.
 
-A common problem in direct imaging is determining planetary masses from photometry using planetary atmosphere evolution grids.
-This method of interpolation depends on the stellar age, the stellar photometry, and the distance to the system.
-Determining stellar ages is quite difficult and sometimes impossible, and is often the largest source of uncertainty when interpolating planetary masses.
-Age uncertainty exponentially affects young systems (\textless\qty{1}{\giga\year}) due to the rapid cooling of giant planets.
-Sirius B avoids these pitfalls due to its unusually high age precision, primarily derived from accurate dynamical masses.
-
-The dynamical masses are determined through astrometric studies; the first study of Sirius was performed by \citet{besselVariationsProperMotions1844}, who recognized wobbles in the proper motion of Sirius A caused by a ``dark satellite''.
-This dark satellite was visually confirmed in \citet{bondCompanionSiriusProf1862} as Sirius B.
-\citet{adamsSpectrumCompanionSirius1915} took the first spectral measurements of Sirius B and found it to be similar to a MS early A-type star, despite its faintness, which we now know to be typical of white dwarf spectra.
-
+Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment.
 Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}.
 \citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories.
-\citet{bondSiriusSystemIts2017} greatly refined the orbital solution using a compilation of historical data and Hubble Space Telescope (HST) data, which gave dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+\citet{bondSiriusSystemIts2017} used \textit{Hubble Space Telescope} (HST) data to compile the most precise orbital solution, to date, for Sirius.
+The dynamical masses were derived using this orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}.
@@
 
-To find the total age of Sirius B, \citet{bondSiriusSystemIts2017} used isochrones to constrain the cooling age (\qty{126}{\mega\year}), first.
-Applying the initial-final mass relation (IFMR) of white dwarfs \citep{cummingsTwoMassiveWhite2016} the estimated progenitor mass of Sirius B is between \qtyrange{5}{5.6}{\solarmass}, which, when combined with stellar evolution codes, yielded total system ages between \qtyrange{226}{228}{\mega\year} with an uncertainty of about \qty{+-10}{\mega\year} \citep{bondSiriusSystemIts2017}.
-An age uncertainty of $\sim$1\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
+The total age of Sirius B is the combination of its WD cooling age and the time from the zero-age MS (ZAMS) to the tip of the giant branch (TGB).
+We adapt the cooling age derived by \citet[sec.
+8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}.
+We use the updated WD initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.
 
+We adopt the system age derived in \citet{cummingsWhiteDwarfInitialFinal2018} using MIST isochrones of \qty{225}{\mega\year}, which implies a ZAMS to TGB age of \qty{99}{\mega\year}.
+These age determinations are limited both by the precision of the stellar parameters as well as the stellar evolution model.
+The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}.
+An age uncertainty of $\sim$4\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
+These values are compiled in \Cref{tbl:system}.
+
+One of the peculiarities of the Sirius system is its large eccentricity of 0.59 \citep{bondSiriusSystemIts2017}.
+If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
+\begin{equation}
+    a_i = a_f \frac{M_{B,f} + M_{A,f}}{M_{B,i} + M_{A,i}}
+\end{equation}
+where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states.
+The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}.
+If the orbit expansion was indeed adiabatic, the eccentricity would be the same before and after evolution.
+In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}.
+\citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}.
+This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage.
+Mass transfer and tidal circularization would be expected, however the present-day eccentricity provide contrary evidence.
+
+\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping'', but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which we would expect to increase with mass transfer to conserve total angular momentum in the binary.
+\citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}.
+\citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components.
+We extrapolate their Figure 7 using the parameters for Sirius to estimate a $\sim$70\% collision probability for an initial companion of Sirius B if it is chaotically ejected.
+When combined, these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
+
+We also consider adiabatic orbit expansion of a substellar companion
+\begin{equation}
+a_i = a_f \frac{M_{f}}{M_{i}}
+\end{equation}
+where $a$ is the semi-major axis, and $M$ is the stellar mass of Sirius B.
+Using the maximum stellar radius of \qty{5.104\pm0.075}{\au} and assuming an extra 20\% separation to escape tidal shredding \citep{nordhausOrbitsLowmassCompanions2013} would create a forbidden region within \qty{31\pm6}{\au} around present Sirius B.
+In combination with the dynamical stability limits of \qty{1.5}{\au}, we can readily rule out the plausibility of detecting a first-generation companion of Sirius B.
+
+There have been many attempts to find planets in the Sirius system, but so far no planets have been detected.
+\citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond}, but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric uncertainty down to $\sim$\qty{10}{\milliarcsecond}.
 The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
 Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
-These studies combined had a sensitivity down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
-\citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reached a sensitivty of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
-\citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs which ruled out evidence for any infrared excess around Sirius B.
-\citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reaching detection sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
-Recently, \citet{pathakHighContrastImaging2021} took simultaneous mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A (through a coronagraph) and B.
-Because of the simultaneous observation, their contrast depended on which region of the FOV was tested.
-Their average sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.
-
-In this work, we report direct images of Sirius B with Keck/NIRC2.
-The rest of the manuscript is organized as follows: \cref{sec:obs} describes our target and observing strategy, \cref{sec:analysis} describes the processing and analysis techniques used, and \cref{sec:results} describes our results.
+A planetary atmosphere and evolution model needs to be chosen in order to derive mass sensitivity limits from imaging.
+Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}) biasing direct comparisons of mass limits.
+These studies combined reported sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
+\citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reported a sensitivity of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
+\citet{skemerSiriusImagedMidinfrared2011} used mid-IR (up to \qty{10}{\micro\meter}) observations from Gemini/T-ReCs, which ruled out evidence for significant infrared excess from massive disks around Sirius B.
+\citet{thalmannPiercingGlareDirect2011} used Subaru/IRCS at \qty{4.05}{\micro\meter} reporting sensitivities of \qtyrange{6}{12}{\jupitermass} at \ang{;;1}.
+Recently, \citet{pathakHighContrastImaging2021} took coronagraphic mid-IR observations (\qty{10}{\micro\meter}) at VLT/VISIR of Sirius A which contained Sirius B in the FOV.
+Because of the simultaneous observation, their contrast had an azimuthal dependence.
+Their average reported sensitivity is $\sim$\qty{2.5}{\jupitermass} at \qty{1}{\au}, and their best sensitivity (from the ``inner'' region) is $\sim$\qty{1.5}{\jupitermass} at \qty{1}{\au}.
 
@@
     \startdata
-    $t_\mathrm{sys}$ & 226 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
-    $\pi$ & \num{374.5\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
-    $d$ & \num{2.67\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
+    $t_\mathrm{sys}$ & 225 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
+    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
+    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
+    $a$ & \num{20.016\pm0.014} & \unit{\au} & \citetalias{bondSiriusSystemIts2017} \\
     \cutinhead{Sirius A}
@@
     $M_\star$ & \num{1.018\pm0.011} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017} \\
-    $t_\mathrm{WD}$ & 125 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018}\\
-    $m^{Lp}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
-    $M^{Lp}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
+    $M_\mathrm{MS}$ & \num{5.1\pm1.1} & \unit{\solarmass} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
+    $t_\mathrm{WD}$ & 126 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017}\\
+    $m^{\mathrm{L}^\prime}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
+    $M^{\mathrm{L}^\prime}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
     \enddata
@@
     \tablecaption{Observing parameters for the three epochs of data.
-All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}).
+All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in \Lp-band (\qty{3.776}{\micro\meter}).
 Observation time is based on the frames that were selected for processing.
-Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
-Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
+Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor and averaged over the observing session.
+Seeing values, temperature, and water vapor measurements were all retrieved from the Maunakea weather center forecast archive.
     \label{tbl:obs}}
@@
 %     \tablecaption{Observing parameters for the three epochs of data.
-All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in Lp-band (\qty{3.776}{\micro\meter}).
+All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in \Lp-band (\qty{3.776}{\micro\meter}).
 Observation time is based on the frames that were selected for processing.
@@
     \plotone{spike}
-    \caption{A diffraction spike sweeping across a calibrated science frame of Sirius B from the first epoch.
-This shows the strong scattered light effects of Sirius A and how they affect the FOV of Sirius B \ang{;;11} away.}
+    \caption{Scattered light from Sirius A is present in our FOV around Sirius B as shown by this diffraction spike  sweeping across a calibrated science frame of Sirius B from the first epoch.
+Despite Sirius B's separation of \ang{;;11}, the overwhelming brightness of Sirius A impedes observations of Sirius B.}
     \label{fig:spike}
@@
     \caption{The median frame from the second epoch showing the instrumental PSF.
-The inner core has a FWHM of $\sim$\qty{76}{\milliarcsecond}.
-The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry corresponding to the hexagonal shape of the primary mirror.}
+The inner core has a Gaussian FWHM of $\sim$\qty{76}{\milliarcsecond}.
+The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry coinciding with the hexagonal shape of the primary mirror.}
     \label{fig:psf}
@@
 
+We directly imaged Sirius B with Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\Cref{tbl:obs}).
 Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-We directly imaged Sirius B with Keck/NIRC2 in Lp-band (\qty{3.776}{\micro\meter}) using the narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) across three epochs in 2020 (\cref{tbl:obs}).
 Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
@@
 \citet[\S2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
-In order to overcome these obstacles, we decided to try using Sirius A as the AO guide star and off-axis guiding to Sirius B.
+In order to overcome these obstacles, we decided to used Sirius A as the AO guide star and off-axis guided on Sirius B.
 
-The Keck AO system \citep{wizinowichPerformanceKeckObservatory2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
+The Keck facility AO system \citep{wizinowichPerformanceKeckObservatory2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
-From here, we slewed off-axis using the separations and position angles calculated in \cref{tbl:obs} from the orbital parameters in \citet{bondSiriusSystemIts2017}.
+From here, we slewed off-axis using the separations and position angles calculated in \Cref{tbl:obs} from the orbital solution of \citet{bondSiriusSystemIts2017}.
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
@@
 During each observation, we took dark frames and sky-flat frames for calibration.
-All observations were taken with the telescope's field rotator set to track the telescope pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
+All observations were taken with the large hexagonal pupil maskand with the telescope's field rotator set to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
+In order to avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.
 
 \section{Analysis} \label{sec:analysis}
-
-\begin{figure*}
-    \centering
-    \epsscale{1}
-    \plotone{contrast_curves}
-    \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
-The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
-The annular PCA curve is cut off because the innermost annulus has a contrast value greater than 1, which means even a 100 S/N companion would not be detectable with 5$\sigma$ significance.}
-    \label{fig:contrast}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \epsscale{1}
-    \plotone{mass_curves}
-    \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the best contrast.
-The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits.
-The two ages represent the ages of the two potential formation pathways, one of which is the system age (\qty{226}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{125}{\mega\year}).
-The limits are calculated assuming an Lp apparant magnitude for Sirius B of \num{9.01} and converting contrast into absolute magnitudes.
-The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing.
-The lower mass limit of the ATMO2020 grid is plotted with a horizontal dashed line and the expected upper limit for dynamically stable orbits of \qty{1.5}{\au} is plotted with a vertical dashed line.}
-    \label{fig:mass}
-\end{figure*}
 
@@
 For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter.
-At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \cref{fig:spike}.
-Then, each good frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
+At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
+Then, each selected frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
 
 The co-registered frames were shifted to the center of the FOV and cropped to the inner 200 pixels.
-With a pixel scale of \qty{10}{\milliarcsecond} the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
+With a pixel scale of \qty{10}{\milliarcsecond}, the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
 All the frames were stacked into data cubes for each epoch.
 We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
-For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\cref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\cref{sec:data}).
+For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
+All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\Cref{sec:data}).
 
@@
     \centering
-    \epsscale{0.95}
+    % \epsscale{0.95}
     \plotone{residuals}
-    \caption{The flat residuals of each epoch after PSF subtraction, derotating, and collapsing. The inner full-width at half-maximum (FWHM) is masked out for each frame.}
+    \caption{The flat residuals of each epoch after PSF subtraction, derotating, and collapsing. The inner two FWHMs are masked out for each frame.}
     \label{fig:residuals}
@@
     \centering
-    \epsscale{0.95}
-    \plotone{sig}
-    \caption{The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawet_fundamental_2014}.
+    % \epsscale{0.95}
+    \plotone{detection_maps}
+    \caption{\textbf{top row:} The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawetFundamentalLimitationsHigh2014}.
 Typically a critical value for detection is 5.
-The inner full-width at half-maximum (FWHM) is masked out for each map.}
-    \label{fig:sig}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \epsscale{0.95}
-    \plotone{stim}
-    \caption{The STIM maps for each epoch calculated from each residual cube.
+\textbf{bottom row:} The STIM maps for each epoch calculated from each residual cube.
 The STIM probability has a typical cutoff threshold of 0.5 for significant detections.
-The inner full-width at half-maximum (FWHM) is masked out for each map.}
-    \label{fig:stim}
+The inner two FWHMs are masked out for each map.}
+    \label{fig:detection}
 \end{figure*}
@@
 
-For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{maroisAngularDifferentialImaging2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummerDetectionCharacterizationExoplanets2012a}, non-negative matrix factorization \citep[NMF;][]{renNonnegativeMatrixFactorization2018a}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{papairetReferencelessAlgorithmCircumstellar2019a,pairetMAYONNAISEMorphologicalComponents2020}.
+For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{maroisAngularDifferentialImaging2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummerDetectionCharacterizationExoplanets2012a}, non-negative matrix factorization \citep[NMF;][]{renNonnegativeMatrixFactorization2018a}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairetReferencelessAlgorithmCircumstellar2019a,pairetMAYONNAISEMorphologicalComponents2020}.
 The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
@@
 
-We used three metrics available in \texttt{ADI.jl} to determine the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairetSTIMMapDetection2019}, and the contrast curve.
-The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics.
-The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above.
+We determined the best performing PSF subtraction algorithm by measuring the throughput of companion signal through repeated injection and recovery.
+By using a known, fixed S/N for injection, the 5$\sigma$ detection limits can be measured at various positions within the FOV and are azimuthally averaged to produce a \textit{contrast curve}.
 We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
-The collapsed residual frames along with the above metrics for each algorithm for each epoch are in section~\ref{sec:adi-results}.
+We employed two different detection metrics to search for companions in the residual data: the Gaussian significance map \citep{mawetFundamentalLimitationsHigh2014} and the standardized trajectory intensity mean map \citep[STIM map;][]{pairetSTIMMapDetection2019}.
+These maps assign the likelihood of a companion to each pixel using different assumptions of the residual statistics.
+These three metrics are calculated using the methods available in \texttt{ADI.jl}.
+The collapsed residual frames along with the above metrics for each algorithm and epoch are in Appendix~\ref{sec:adi-results}.
 
 A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
-For PCA, NMF, and GreeDS algorithms, we increased the number of components from 1 to 10, creating a residual cube for each iteration.
-We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}).
+For PCA, NMF, and GreeDS algorithms, we varied the number of components from 1 to 10, creating a residual cube for each iteration.
+We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\Cref{fig:pca-contrast-curves}).
 In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairetSignalProcessingMethods2020} as an ensemble statistic.
@@
 A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
-The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in section~\ref{sec:adi-results}.
-All of the code used for this analysis is available in a GitHub respository (\cref{sec:data}).
+The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in Appendix~\ref{sec:adi-results}.
+All of the code used for this analysis is available in a GitHub repository (\Cref{sec:data}).
 
@@
 
-We determined the best-performing algorithms for each epoch using the contrast curves described in \cref{sec:analysis}.
+\begin{figure*}
+    \centering
+    \plotone{contrast_curves}
+    \caption{The contrast curves for the best performing algorithm from each epoch.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
+The annular PCA curve is cut off because the innermost annulus was not able to detect a 100 S/N companion with 5$\sigma$ significance.}
+    \label{fig:contrast}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \plotone{mass_curves}
+    \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the most sensitive contrast.
+The limits are calculated assuming an \Lp absolute magnitude for Sirius B of \num{11.9}.
+Both curves are truncated at \qty{1.5}{\au} due to the dynamical stability limit.
+\textbf{(a)} The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing.
+The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits.
+The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{126}{\mega\year}).
+The relative difference between the ages comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}.
+\textbf{(b)} The absolute magnitudes are converted to masses using the Sonora Bobcat grid with solar metallicity (solid lines) and with +\qty{0.5}{dex} metallicity (dotted lines).
+For clarity, only the Gaussian contrast curves are shown in this panel.
+The two isochrone ages are shown as well, although the Sonora grid cuts off below \qty{200}{\kelvin}, which causes the cutoffs around \qty{1}{\jupitermass}.
+The relative difference due to the metallicity is $\sim$\qty{0.1}{\jupitermass}.}
+    \label{fig:mass-curves}
+\end{figure*}
+
+We determined the best-performing algorithms for each epoch using the contrast curves described in \Cref{sec:analysis}.
 For the first two epochs, full-frame median subtraction had the best contrast at almost all separations.
 For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
-The innermost annulus from this algorithm has greater than 1 contrast which implies a 100 S/N companion would not be detected with 5$\sigma$ significance.
+This algorithm was unable to detect a 100 S/N companion injected into the innermost annulus with 5$\sigma$ significance.
 The contrast for this innermost annulus is therefore not plotted.
-The collapsed residual frames from each epoch are shown in \cref{fig:residuals}, along with the Gaussian significance maps (\cref{fig:sig}) and STIM maps (\cref{fig:stim}).
+The collapsed residual frames from each epoch are shown in \Cref{fig:residuals}, along with the Gaussian significance maps and STIM maps (\Cref{fig:detection}).
+
+The contrast maps from the best performing algorithm for each reduction are shown in \Cref{fig:contrast}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.01 (adapted from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}.
+We divide \Cref{fig:contrast} into two regimes: speckle-limited and background-limited.
+The speckle-limited regime exists from \qtyrange{0.2}{1}{\au} characterized by the increasing sensitivity with separation.
+Here we reach a median 5$\sigma$ detection limit of $\sim$19 magnitude (\Lp).
+This regime is constrained by the quality of the AO correction and the PSF subtraction method, mainly.
+The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily constrained by the sky brightness.
+In this region, we reach 20.3 magnitude (\Lp) in the 2020-11-21 epoch.
+Our data is background-limited due to the relative brightness of the sky in \Lp (\qty{2.91}{mag\per sq.
+arcsec}\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc2/sensitivity.html}}) compared to the pixel-to-pixel noise sources (e.g., read noise).
+
+\subsection{Companions around Sirius B}
 
@@
 The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a}.
-We generated $10^4$ orbits, none of which contained the points from each epoch (section~\ref{sec:orbits}).
-We take this as direct evidence against the blobs being substellar companions of any kind.
+Nonetheless, we estimated astrometry for blobs from each epoch (\Cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a}.
+We generated $10^4$ orbits, none of which constrained the points from each epoch (Appendix~\ref{sec:orbits}).
+This implies non-Keplerian motion and we take this as direct evidence against the blobs being substellar companions of any kind.
+The signal can be simply explained as residual starlight not removed during PSF subtraction.
 
-\subsection{Companion Mass Detection Limits}
+\subsection{Mass detection limits}
 
-The contrast maps from the best performing algorithm for each reduction are shown in \cref{fig:contrast}.
-We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited magnitude using an Lp-band magnitude for Sirius B of 9.1 (adapted from \citealp{bidaudADONISHighContrast2008a}).
-Then we used \qty{225}{\mega\year} for the system age to interpolate the planetary mass using the AMES-Cond evolutionary grid and atmosphere models .
-The high precision of the Sirius system's age reduces uncertainty when interpolating planetary mass from the evolutionary grids (see \cref{sec:intro}).
-We also tested using the newer SONORA grid , but the differences compared to AMES-Cond were less than the mean uncertainty from age.
-The best performing epoch was on the night of 2020-11-21, which managed to reach an exceptional sensitivity of \qty{3.5}{\jupitermass} at \qty{0.25}{\au} (\ang{;;0.09}) in the speckle limited regime and ultimately \qty{0.6}{\jupitermass} at \qty{1.5}{\au} (\ang{;;0.38}) in the background limited regime.
+In order to convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid.
+This is not a trivial task, as the effects of post-MS stellar evolution on planets are highly uncertain and not readily modeled in the currently available grids.
+In particular, we want to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds.
+We start with the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} for our solar metallicity model.
+Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which have been shown to better model very cool objects than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}.
+The ATMO2020 models are not available for non-solar metallicities, yet, so we also employ the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicity.
 
-\section{Conclusions} \label{sec:conclusion}
+To determine the correct isochrone for the grids, we consider two formation scenarios.
+If a first-generation planet survives the giant phase of Sirius B through star hopping, it would have an age closer to the system age of \qty{225}{\mega\year}.
+If the planet formed in a disk of stellar ejecta during the AGB phase, the age would be closer to the WD cooling age of \qty{126}{\mega\year}.
+If the planet formed in such a disk, or if it accreted some of the material, it would almost certainly have peculiar chemistry, although it is uncertain exactly how the relative abundances would change.
 
-In closing, the Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR.
+\Cref{fig:mass-curves} shows our most sensitive contrast curve converted to mass limits under the different models.
+The first panel uses the ATMO2020 models to show how the choice of isochrone age leads to a $\sim$\qty{0.3}{\jupitermass} difference in the background-limited regime.
+The second panel uses the Sonora models to demonstrate the relatively minor effects ($\sim$\qty{0.1}{\jupitermass}) +\qty{0.5}{dex} has on the mass limits.
+We could not fully utilize the Sonora grid, though, because there are no atmospheric models tabulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models we need for the background-limited regimes.
+Overall, we constrain our detection limits to \qtyrange{1.7}{2.5}{\jupitermass} at \qty{0.5}{\au} (\ang{;;0.19}) in the speckle-limited regime and ultimately \qtyrange{0.6}{1.1}{\jupitermass} at \textgreater\qty{1}{\au} (\ang{;;0.38}) in the background-limited regime.
+
+\section{Discussion \& Conclusions} \label{sec:conclusion}
+
+Post-MS planetary evolution has historically been limited to theoretical work.
+Recently, though increasingly strong and diverse observational constraints have invigorated the field.
+We set out in this work to study the nearby Sirius system for post-MS companions around Sirius B.
+The Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR.
 While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets.
-In this work, we present high-contrast images of Sirius B in the near-IR.
-Our sensitivity limits are the best that have been reached for Sirius B so far, reaching \qty{0.6}{\jupitermass} at \qty{1.5}{\au}, the outer limit for dynamically stable orbits.
+In this work, we presented high-contrast images of Sirius B in the near-IR.
+Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, reaching \num{20.3} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
+We consider multiple planetary formation pathways yielding ages between \qtyrange{126}{225}{\mega\year} and explore the effects of enriched metallicity.
+We translate our sensitivity limits using the ATMO2020 and Sonora Bobcat grids to constrain our mass detection limits to \qtyrange{0.7}{1.5}{\jupitermass} at \textgreater\qty{1}{\au}.
 Our observations also show how the high precision of the parameters of the Sirius system directly benefits the sensitivity to planets.
-Particularly, the low age uncertainty of Sirius B keeps our mass uncertainty below \qty{0.1}{\jupitermass}.
-Despite the high sensitivity of this study, we found no appreciable evidence for a companion around Sirius B, consistent with previous results.
-This non-detection furthers evidence against a second-generation planet migrating or forming within the Sirius system \citep{viganHighcontrastImagingSirius2015}.
+For example, the $\sim$4\% relative uncertainty of Sirius B's age translates to mass detection limit uncertainty below \qty{0.1}{\jupitermass}.
+Despite the high sensitivity of this study, we found no significant evidence for a companion around Sirius B, consistent with previous results.
 
-For future work, we consider two avenues for followup.
-As mentioned in \cref{sec:results}, optical observations using an instrument like Subaru/VAMPIRES .
-Optical observations can look for disks in the Rayleigh-scattering regime, which is not readily probed by IR observations.
-Furthermore, the polarimetric differential observation modes of both instruments allow for nearly diffraction-limited imaging, down to 10s of milliarcseconds.
+Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach exceptional detection limits.
+We took the WD sample from \citet{holberg25ParsecLocal2016} and look at binary systems.
+The median distance of this subset is \qty{20}{\parsec}.
+In this work, our inner working angle due to the stellar PSF was $\sim$\qty{80}{\milliarcsecond}, which would be a projected separation of \qty{1.6}{\au} at \qty{20}{\parsec}.
+The median R magnitude is $\sim$\num{15.2}, though, which may prove challenging for natural guide star AO.
+However, with laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude increases significantly ($m^R\lesssim$ \num{19}).
+We suspect future work using LGS AO is capable of studying WD systems at the sub-AU and sub-Jupiter-mass scales.
+Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the MS.
 
-Followup in the IR from space-based telescopes would increase the sensitivity of the observations due to the absence of background emission from Earth's atmosphere.
-For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter, which would easily reach the model mass sensitivity limits at \textgreater\ang{;;0.3} without saturation .
-The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) would still probe down to \qty{0.8}{\au}.
-Observations would be complicated by the scattered light from Sirius A, which could affect the fine-pointing control or worsen the background sensitivity.
-In the end, our ground-based observations are already quite close to the atmospheric model grid limits, raising the concern of diminishing returns.
-Planetary atmosphere models must improve, before fully reaping the benefits of the additional sensitivity of space-based observations.
+We also consider future space-based observations with the \textit{James Webb Space Telescope} (JWST), eliminating the effects of atmospheric seeing and the bright sky background.
+For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter.
+The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby WDs, depending on the contrast-limited performance of NIRCAM.
+Unfortunately, Sirius B is far too bright and too close to Sirius A to observe with JWST without severe saturation.
 
-\subsection{Data and Code Availability} \label{sec:data}
-All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository\footnote{\href{https://github.com/mileslucas/sirius-b}{https://github.com/mileslucas/sirius-b}}.
+\section{Data and code availability} \label{sec:data}
+All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository\footnote{\url{https://github.com/mileslucas/sirius-b}}.
 This code includes all of the scripts for generating each figure in this manuscript.
@@
 \begin{acknowledgements}
+We thank the anonymous referee for their helpful comments.
+We thank Michael Liu and Mark Phillips for their expertise and advice on the ATMO2020 model grid.
+We thank Mark Marley and Didier Saumon for their assistance with the Sonora Bobcat model grid.
 The data presented herein were obtained at the W.
@@
 ADI.jl \citep{lucasADIJlJulia2020},
-astropy \citep{cocollaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
+astropy \citep{collaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
 Julia \citep{bezansonJuliaFreshApproach2017},
@@
 
-\section{ADI Processing Results} \label{sec:adi-results}
+\section{ADI processing results} \label{sec:adi-results}
 
@@
 \clearpage
-\section{Provisional Orbit Fitting} \label{sec:orbits}
+\section{Provisional orbit fitting} \label{sec:orbits}
 
@@
 Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions.
-We began by estimating the astrometry of the blobs by eye in reduced data (\cref{tbl:astrometry}, \cref{fig:prov-orbit}).
+We began by estimating the astrometry of the blobs by eye in reduced data (\Cref{tbl:astrometry}, \Cref{fig:prov-orbit}).
 We tried simulating $10^4$ orbits via rejection sampling with OFTI but no generated orbit was able to constrain all three points.
@@
     \centering
-    \figurenum{14}
+    \figurenum{13}
     \plotone{orbit_frames}
     \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch.
-Each frame was cropped to the inner $\sim$\qty{0.7}{\au} (\ang{;;0.25}) and the inner FWHM has been masked out.
-The width of the circles represents the uncertainty.}
+Each frame was cropped to the inner $\sim$\qty{0.7}{\au} (\ang{;;0.25}) and the inner two FWHMs have been masked out.
+The width of the circles represents the measurement uncertainty.}
     \label{fig:prov-orbit}

### 2021-11-03 src/SiriusB.jl
add Sonora tables to module

@@ -7,12 +7,13 @@ using DelimitedFiles
 using Dierckx
 using FITSIO
 import ImageTransformations: center
-using SkyCoords
+using Printf
 using PyCall
+using SkyCoords
 
 export rootdir, datadir, srcdir, notebookdir, paperdir, figuredir, load_or_produce,
        parallactic_angles, gaussian_fit, gaussian_fit_offset, center, table_interpolate, ATMO2020,
-       contrast_to_dmag, distance_modulus
+       contrast_to_dmag, distance_modulus, SonoraSolar, SonoraMetalRich
 
 # constants associated with Sirius B
 const parallax = 374.48958852876103e-3 # arcsecond

### 2021-11-03 src/tables.jl

@@ -1,12 +1,24 @@
 function get_below(subtable, arg)
     _tab = Iterators.filter(r -> r[arg.first] ≤ arg.second, eachrow(subtable))
-    y = maximum(r -> r[arg.first], _tab)
+    local y
+    try
+        y = maximum(r -> r[arg.first], _tab)
+    catch e
+        @debug "out of bounds" subtable arg
+        throw(e)
+    end
     return filter(r -> r[arg.first] ≈ y, subtable)
 end
 
 function get_above(subtable, arg)
     _tab = Iterators.filter(r -> r[arg.first] > arg.second, eachrow(subtable))
-    y = minimum(r -> r[arg.first], _tab)
+    local y
+    try
+        y = minimum(r -> r[arg.first], _tab)
+    catch e
+        @debug "out of bounds" subtable arg
+        throw(e)
+    end
     return filter(r -> r[arg.first] ≈ y, subtable)
 end
 
@@ -66,3 +78,64 @@ const ATMO2020 = read_ATMO2020_grid(srcdir("mass_models", "ATMO2020_NEQ_weak"))
 #################################################
 
 
+function read_Sonora_grid(dir; metallicity=0, CO_ratio=1.0)
+    # prepare file names
+    if CO_ratio ≈ 1
+        dex_token = @sprintf "%+02.1f" metallicity
+        CO_token = ""
+    else
+        dex_token = @sprintf "_m%+02.1f" metallicity
+        CO_token = @sprintf "_co%02.1f" CO_ratio
+    end
+    evo_path = joinpath(dir, "evolution_tables", @sprintf("evo_tables%+02.1f", metallicity), @sprintf("nc%+02.1f_co%02.1f_age", metallicity, CO_ratio))
+    mag_path = joinpath(dir, "photometry_tables", @sprintf("mag_table%s%s", dex_token, CO_token))
+
+    # read evolution_table
+    evo_header = ["age_Gyr", "M_Msun", "logL", "Teff", "logg", "R_Rsun"]
+    evo_mat = open(evo_path, "r") do fh
+        # skip first (header) row
+        readline(fh)
+        # iterate over rows
+        rows = map(readlines(fh)) do row
+            tokens = split(replace(row, "\n" => ""))
+            if length(tokens) == 1
+                nothing
+            else
+                parse.(Float64, tokens)
[…]

### 2021-11-03 notebooks/star_hoppers.jl
add star-hoppers derivation notebook

@@ -1,0 +1,173 @@
+### A Pluto.jl notebook ###
+# v0.16.0
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 03688332-bcc4-4c84-8924-7f1610db077e
+# imports
+begin
+	using Dierckx
+	using Markdown
+	using Measurements
+	using Unitful
+	using UnitfulAngles
+	using UnitfulAstro
+end
+
+# ╔═╡ b1450a24-3120-11ec-2c56-d7b2f96fdf46
+md"""
+# Star Hoppers
+
+This notebook will follow along with some derivations of [Kratter & Perets (2012)](https://ui.adsabs.harvard.edu/abs/2012ApJ...753...91K).
+"""
+
+# ╔═╡ 2dbe3b2b-f33b-46f3-98f3-869c539451db
+M_A = (2.063 ± 0.023)u"Msun"
+
+# ╔═╡ 6eef835d-49b3-4ffe-bc3a-dc7d5938fe5b
+M_B_WD = (1.018 ± 0.011)u"Msun"
+
+# ╔═╡ c79b9551-4ccc-4ea4-8e41-1c56cd5e4c72
+md"white dwarf initial-final mass relation (IFMR) from [Cummings et al. (eqn. 6; 2018)](https://ui.adsabs.harvard.edu/abs/2018ApJ...866...21C)"
+
+# ╔═╡ 6062c398-de6a-457f-a7c5-e8ce13d7bd3e
+function MIST_highmass_IFMR(M_WD)
+	b = (0.471 ± 0.077)u"Msun"
+	m = (0.107 ± 0.016)
+	return (M_WD - b) / m
+end
+
+# ╔═╡ eb6f04d6-596f-497e-93ab-fdcde0e92d8d
+M_B_MS = MIST_highmass_IFMR(M_B_WD)
+
+# ╔═╡ df958bae-32e7-47b6-8e9f-95698151113c
+md"""
+Adiabatic expansion factor
+
+```math
+f = \frac{a_f}{a_i} = \frac{M_\mathrm{MS}}{M_\mathrm{WD}}
+```
+"""
+
+# ╔═╡ f6d29ca4-b536-49a9-9391-81b44d3e7413
+f = M_B_MS / M_B_WD
+
[…]

### 2021-11-03 paper/paper.tex
remove unused references

@@
 For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
-Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.
+Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
 The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.
@@
 Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}.
-\citet{vandenbosOrbitSiriusADS1960,gatewoodStudySirius1978} were the first to estimate dynamical masses using compilations of photographic plates from Lick and Yerkes observatories.
-\citet{bondSiriusSystemIts2017} used \textit{Hubble Space Telescope} (HST) data to compile the most precise orbital solution, to date, for Sirius.
-The dynamical masses were derived using this orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius, to date.
+They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}.
@@
 
-We also consider future space-based observations with the \textit{James Webb Space Telescope} (JWST), eliminating the effects of atmospheric seeing and the bright sky background.
+We also consider future space-based observations with the James Webb Space Telescope (JWST), eliminating the effects of atmospheric seeing and the bright sky background.
 For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter.

### 2021-11-03 paper/paper.tex
add debes ref and small grammar fixes

@@
 
-\section{Introduction} \label{sec:intro}
-
-\begin{itemize}
-    \item add Debes text
-    \item run through python scripts/grammarly
-    \item reorganize Zenodo sections
-    \item remove extra references
-    \item compile latex diff
-    \item add comments to latex diff referencing referee report
-\end{itemize}
+\section{Introduction}\label{sec:intro}
 
@@
 The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs.
-As the MS star runs out of Hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius.
-When Helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
+As the MS star runs out of hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius.
+When helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
 Eventually the star will run out of fuel and conclude its nuclear burning and become a WD.
@@
 
-\textbf{John Debes work from 2000-2010 with Spitzer, HST}
-
-Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
+Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
 We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade.
@@
 
-\section{Directly imaging post-MS systems} \label{sec:imaging}
+\section{Directly imaging post-MS systems}\label{sec:imaging}
 
@@
 
-% \section{Post-MS evolution} \label{sec:post-ms}
+% \section{Post-MS evolution}\label{sec:post-ms}
 
@@
 
-\section{Sirius B and the Sirius system} \label{sec:sirius}
+\section{Sirius B and the Sirius system}\label{sec:sirius}
 
@@
 Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
-A planetary atmosphere and evolution model needs to be chosen in order to derive mass sensitivity limits from imaging.
+A planetary atmosphere and evolution model are needed in order to derive mass sensitivity limits from imaging.
 Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}) biasing direct comparisons of mass limits.
@@
 
-\section{Observations} \label{sec:obs}
+\section{Observations}\label{sec:obs}
 \defcitealias{bonnet-bidaudADONISHighContrast2008a}{BB08}
@@
 The inner core has a Gaussian FWHM of $\sim$\qty{76}{\milliarcsecond}.
-The speckle pattern is shown in the blobs surrounding the first ring, with roughly 6-way radial symmetry coinciding with the hexagonal shape of the primary mirror.}
+The blobs surrounding the first ring are the speckles, with roughly 6-way radial symmetry coinciding with the hexagonal shape of the primary mirror.}
     \label{fig:psf}
@@
 During each observation, we took dark frames and sky-flat frames for calibration.
-All observations were taken with the large hexagonal pupil maskand with the telescope's field rotator set to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
+All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
 In order to avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.
 
-\section{Analysis} \label{sec:analysis}
+\section{Analysis}\label{sec:analysis}
 
@@
 
-\section{Results} \label{sec:results}
+\section{Results}\label{sec:results}
 
@@
 The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
-The annular PCA curve is cut off because the innermost annulus was not able to detect a 100 S/N companion with 5$\sigma$ significance.}
+The annular PCA curve cuts off because the innermost annulus was not able to detect a 100 S/N companion with 5$\sigma$ significance.}
     \label{fig:contrast}
@@
 \textbf{(b)} The absolute magnitudes are converted to masses using the Sonora Bobcat grid with solar metallicity (solid lines) and with +\qty{0.5}{dex} metallicity (dotted lines).
-For clarity, only the Gaussian contrast curves are shown in this panel.
-The two isochrone ages are shown as well, although the Sonora grid cuts off below \qty{200}{\kelvin}, which causes the cutoffs around \qty{1}{\jupitermass}.
+For clarity, we only show the Gaussian contrast curves in this panel.
+The Sonora grid does not have atmospheric spectra for $T_\mathrm{eff}$ \textless \qty{200}{\kelvin}, which causes the cutoffs around \qty{1}{\jupitermass}.
 The relative difference due to the metallicity is $\sim$\qty{0.1}{\jupitermass}.}
@@
 The contrast for this innermost annulus is therefore not plotted.
-The collapsed residual frames from each epoch are shown in \Cref{fig:residuals}, along with the Gaussian significance maps and STIM maps (\Cref{fig:detection}).
+\Crefrange{fig:residuals}{fig:detection} show the collapsed residual frames from each epoch, along with the Gaussian significance maps and STIM maps.
 
-The contrast maps from the best performing algorithm for each reduction are shown in \Cref{fig:contrast}.
+We show the contrast curves from the best performing algorithm for each reduction in \Cref{fig:contrast}.
 We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.01 (adapted from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}.
@@
 We start with the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} for our solar metallicity model.
-Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which have been shown to better model very cool objects than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}.
+Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which model very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}.
 The ATMO2020 models are not available for non-solar metallicities, yet, so we also employ the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicity.
@@
 
-\section{Discussion \& Conclusions} \label{sec:conclusion}
+\section{Discussion \& Conclusions}\label{sec:conclusion}
 
@@
 Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach exceptional detection limits.
-We took the WD sample from \citet{holberg25ParsecLocal2016} and look at binary systems.
+We took the WD sample from \citet{holberg25ParsecLocal2016} and analyzed the 7 binary systems.
 The median distance of this subset is \qty{20}{\parsec}.
@@
 
-\section{Data and code availability} \label{sec:data}
-All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository\footnote{\url{https://github.com/mileslucas/sirius-b}}.
-This code includes all of the scripts for generating each figure in this manuscript.
-The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}}.
-We hope that this improves the reproducibility of the work as well as providing data for future investigations.
+\section{Data and code availability}\label{sec:data}
+
+All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
+The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}} We hope that this improves the reproducibility of the work as well as providing data for future investigations.
 Please reach out to the corresponding author for further inquiries regarding data and code availability.
@@
 
-\section{ADI processing results} \label{sec:adi-results}
+\section{ADI processing results}\label{sec:adi-results}
 
@@
 \clearpage
-\section{Provisional orbit fitting} \label{sec:orbits}
+\section{Provisional orbit fitting}\label{sec:orbits}
 

### 2021-11-04 paper/paper.tex
revise contrast curves using 9.1 for apparant mag

@@
 Our observations are contrast limited out to \qty{1}{\au} and background limited beyond.
-The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.3} absolute magnitude.
+The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} absolute magnitude.
 We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits using the ATMO2020 and Sonora Bobcat model grids.
-We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.7}{3}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.5}{\jupitermass} at \textgreater\qty{1}{\au}.
+We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}.
 Consistent with previous results, we do not detect any companions around Sirius B.
@@
     $t_\mathrm{WD}$ & 126 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017}\\
-    $m^{\mathrm{L}^\prime}$ & \num{9.01\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
-    $M^{\mathrm{L}^\prime}$ & \num{11.88\pm0.16} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
+    $m^{\mathrm{L}^\prime}$ & \num{9.1\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
+    $M^{\mathrm{L}^\prime}$ & \num{11.97\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
     \enddata
@@
     \centering
-    % \epsscale{0.95}
+    \epsscale{0.95}
     \plotone{residuals}
@@
     \centering
-    % \epsscale{0.95}
     \plotone{detection_maps}
@@
 The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+The absolute magnitude are calculated using an absolute magnitude for Sirius B of 11.97.
 The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
@@
     \caption{Mass sensitivity curves derived from the 2020-11-21 epoch, which has the most sensitive contrast.
-The limits are calculated assuming an \Lp absolute magnitude for Sirius B of \num{11.9}.
+The limits are calculated from the absolute magnitude derived in the contrast curves.
 Both curves are truncated at \qty{1.5}{\au} due to the dynamical stability limit.
@@
 We show the contrast curves from the best performing algorithm for each reduction in \Cref{fig:contrast}.
-We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.01 (adapted from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.1 (adapted from Ks-band magnitude from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}.
 We divide \Cref{fig:contrast} into two regimes: speckle-limited and background-limited.
@@
 The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily constrained by the sky brightness.
-In this region, we reach 20.3 magnitude (\Lp) in the 2020-11-21 epoch.
+In this region, we reach 20.4 magnitude (\Lp) in the 2020-11-21 epoch.
 Our data is background-limited due to the relative brightness of the sky in \Lp (\qty{2.91}{mag\per sq.
@@
 The first panel uses the ATMO2020 models to show how the choice of isochrone age leads to a $\sim$\qty{0.3}{\jupitermass} difference in the background-limited regime.
-The second panel uses the Sonora models to demonstrate the relatively minor effects ($\sim$\qty{0.1}{\jupitermass}) +\qty{0.5}{dex} has on the mass limits.
+The second panel uses the Sonora models to demonstrate the relatively minor effects ($\sim$\qty{0.1}{\jupitermass}) the increased metallicity has on the mass limits.
 We could not fully utilize the Sonora grid, though, because there are no atmospheric models tabulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models we need for the background-limited regimes.
-Overall, we constrain our detection limits to \qtyrange{1.7}{2.5}{\jupitermass} at \qty{0.5}{\au} (\ang{;;0.19}) in the speckle-limited regime and ultimately \qtyrange{0.6}{1.1}{\jupitermass} at \textgreater\qty{1}{\au} (\ang{;;0.38}) in the background-limited regime.
+Overall, we constrain our detection limits to \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} (\ang{;;0.19}) in the speckle-limited regime and ultimately \qtyrange{0.7}{1.1}{\jupitermass} at \textgreater\qty{1}{\au} (\ang{;;0.38}) in the background-limited regime.
 
@@
 In this work, we presented high-contrast images of Sirius B in the near-IR.
-Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, reaching \num{20.3} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
+Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, reaching \num{20.4} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
 We consider multiple planetary formation pathways yielding ages between \qtyrange{126}{225}{\mega\year} and explore the effects of enriched metallicity.
-We translate our sensitivity limits using the ATMO2020 and Sonora Bobcat grids to constrain our mass detection limits to \qtyrange{0.7}{1.5}{\jupitermass} at \textgreater\qty{1}{\au}.
+We translate our sensitivity limits using the ATMO2020 and Sonora Bobcat grids to constrain our mass detection limits to \qtyrange{0.7}{1.1}{\jupitermass} at \textgreater\qty{1}{\au}.
 Our observations also show how the high precision of the parameters of the Sirius system directly benefits the sensitivity to planets.

### 2021-11-04 paper/figures/contrast.jl

@@ -72,7 +72,7 @@ mid = (ylims[0] + ylims[1]) / 40
 axs.text(1.45, mid, "dynamical stability limit", color="k", alpha=0.5, va="center", ha="left", rotation="vertical")
 axs.set_ylim(ylims)
 
-ax2 = axs.alty(reverse=True, label="abs. mag [$M^{Lp}$]")
+ax2 = axs.alty(reverse=True, label="abs. mag [$\mathrm{L^\prime}$]")
 ax2.plot($(distances[2]), $(contrast_to_absmag.(contrast_curves[2].contrast)), alpha=0)
 
 fig.savefig($(figuredir("contrast_curves.pdf")))
@@ -96,61 +96,29 @@ for curve in contrast_curves
     end
     # these try catch curves are because Sonora grid bottoms out
     curve.masses_225_SonoraSolar = map(curve.absmags) do absmag
-        try
-            table_interpolate(SonoraSolar, :age_Gyr => 0.225, :Keck_Lp => absmag, :M_Mjup)
-        catch
-            NaN
-        end
+        table_interpolate(SonoraSolar, :age_Gyr => 0.225, :Keck_Lp => absmag, :M_Mjup)
     end
     curve.masses_126_SonoraSolar = map(curve.absmags) do absmag
-        try
-            table_interpolate(SonoraSolar, :age_Gyr => 0.126, :Keck_Lp => absmag, :M_Mjup)
-        catch
-            NaN
-        end
+        table_interpolate(SonoraSolar, :age_Gyr => 0.126, :Keck_Lp => absmag, :M_Mjup)
     end
     curve.masses_corr_225_SonoraSolar = map(curve.absmags_corr) do absmag
-        try
-            table_interpolate(SonoraSolar, :age_Gyr => 0.225, :Keck_Lp => absmag, :M_Mjup)
-        catch
-            NaN
-        end
+        table_interpolate(SonoraSolar, :age_Gyr => 0.225, :Keck_Lp => absmag, :M_Mjup)
     end
     curve.masses_corr_126_SonoraSolar = map(curve.absmags_corr) do absmag
-        try
-            table_interpolate(SonoraSolar, :age_Gyr => 0.126, :Keck_Lp => absmag, :M_Mjup)
-        catch
-            NaN
-        end
+        table_interpolate(SonoraSolar, :age_Gyr => 0.126, :Keck_Lp => absmag, :M_Mjup)
     end
     # metalrich
[…]

### 2021-11-04 src/SiriusB.jl

@@ -20,7 +20,7 @@ const parallax = 374.48958852876103e-3 # arcsecond
 const distance = inv(parallax) # pc
 const pxscale = 0.01 # arcseconds/px
 const auscale = pxscale / parallax # AU/px
-const appmag = 9.01 # Ks band from Bonnet-Biduad 2008
+const appmag = 9.1 # Lp band from Bonnet-Biduad 2008
 
 # path configuration
 rootdir(args...) = joinpath(@__DIR__(), "..", args...)

### 2021-11-04 src/tables.jl

@@ -1,58 +1,64 @@
 function get_below(subtable, arg)
     _tab = Iterators.filter(r -> r[arg.first] ≤ arg.second, eachrow(subtable))
-    local y
-    try
-        y = maximum(r -> r[arg.first], _tab)
-    catch e
-        @debug "out of bounds" subtable arg
-        throw(e)
-    end
+    y = maximum(r -> r[arg.first], _tab)
     return filter(r -> r[arg.first] ≈ y, subtable)
 end
 
 function get_above(subtable, arg)
     _tab = Iterators.filter(r -> r[arg.first] > arg.second, eachrow(subtable))
-    local y
-    try
-        y = minimum(r -> r[arg.first], _tab)
-    catch e
-        @debug "out of bounds" subtable arg
-        throw(e)
-    end
+    y = minimum(r -> r[arg.first], _tab)
     return filter(r -> r[arg.first] ≈ y, subtable)
 end
 
 
 function table_interpolate(table, arg1, arg2, arg3)
     sub = copy(table)
+    try
+        sub0 = get_below(sub, arg1)
+        # isempty(sub0) == 0 && return NaN
+        x0 = x1 = sub0[1, arg1.first]
 
-    sub0 = get_below(sub, arg1)
-    x0 = x1 = sub0[1, arg1.first]
+        # check bounds
+        # bounds2 = extrema(sub0[!, arg2.first])
+        # if  arg2.second < bounds2[1] || arg2.second > bounds2[2]
+        #     @debug "out of bounds" sub0 arg2
+        #     return NaN
+        # end
 
-    tab0 = get_below(sub0, arg2)
-    y0 = tab0[1, arg2.first]
-    z0 = tab0[1, arg3]
+        tab0 = get_below(sub0, arg2)
+        y0 = tab0[1, arg2.first]
+        z0 = tab0[1, arg3]
 
-    tab1 = get_above(sub0, arg2)
-    y1 = tab1[1, arg2.first]
-    z1 = tab1[1, arg3]
+        tab1 = get_above(sub0, arg2)
+        y1 = tab1[1, arg2.first]
+        z1 = tab1[1, arg3]
 
-    sub1 = get_above(sub, arg1)
-    x2 = x3 = sub1[1, arg1.first]
+        sub1 = get_above(sub, arg1)
+        # isempty(sub1) == 0 && return NaN
+        x2 = x3 = sub1[1, arg1.first]
[…]

### 2021-11-04 paper/paper.tex
update paper

@@
 For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
-Surviving planets are subject to adiabatic orbit expansion \citep{jeansCosmogonicProblemsAssociated1924}, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
+Surviving planets are subject to adiabatic orbit expansion, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
 The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.
@@
 In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.
-Thermal emission from exoplanets peaks, well into in the infrared, on the Rayleigh-Jeans limit of the stellar spectrum.
+Thermal emission from exoplanets peaks well into the infrared, on the Rayleigh-Jeans limit of the stellar spectrum.
 This makes infrared observations preferred over optical or ultraviolet observations due to the reduced contrast.
@@
 In addition, the lack of spectral features of WDs \citep{schatzmanTheorieDebitEnergie1945} makes them imprecise targets for the radial velocity technique.
+The small stellar radii of WDs lowers the transit probability significantly, although detections of substellar companions around WDs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}.
 The faintness of WDs proves challenging due to the high signal-to-noise ratio (S/N) required by modern adaptive optics (AO) instruments.
@@
 \end{equation}
-where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states.
+where $a$ is the system semi-major axis, $M_A$ and $M_B$ are the respective stellar masses, and subscripts $i$ and $f$ correspond to the initial (MS) versus final (post-MS) states \citep{jeansCosmogonicProblemsAssociated1924}.
 The current semi-major axis of the binary is \qty{20}{\au}, and assuming negligible mass transfer between the two stars, the initial semi-major axis would be \qty{8.6\pm1.3}{\au}.
@@
     $a$ & \num{20.016\pm0.014} & \unit{\au} & \citetalias{bondSiriusSystemIts2017} \\
+    $e$ & \num{0.59142\pm0.00037} &  & \citetalias{bondSiriusSystemIts2017} \\
     \cutinhead{Sirius A}

### 2021-11-10 paper/paper.tex
update paper from revisions

@@
     list-units=single,
-    separate-uncertainty
+    separate-uncertainty,
+    separate-uncertainty-units=single,
 }
@@
 
-\title{An Imaging Search for Post-MS Companions of Sirius B}
+\title{An Imaging Search for Post-Main-Sequence Planets of Sirius B}
 
-\shorttitle{An Imaging Search for Post-MS Companions of Sirius B}
+\shorttitle{An Imaging Search for Post-MS Planets of Sirius B}
 \shortauthors{Lucas et al.}
@@
 \begin{abstract}
-Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.
-We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-MS planetary evolution in the Sirius system.
+Discovery and characterization of post-main-sequence planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution.
+We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-main-sequence planetary evolution in the Sirius system.
 We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging.
-Our observations are contrast limited out to \qty{1}{\au} and background limited beyond.
-The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} absolute magnitude.
-We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits using the ATMO2020 and Sonora Bobcat model grids.
-We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}.
+Our observations are speckle-limited out to \qty{1}{\au} and background-limited beyond.
+The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} \Lp absolute magnitude.
+We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits, and achieve sub-Jupiter sensitivities at sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}.
 Consistent with previous results, we do not detect any companions around Sirius B.
-Our excellent detection limits, even without coronagraphy, demonstrate the capabilities for modern high-contrast imaging studies of nearby (\textless\qty{25}{\parsec}) white dwarfs.
+Our strong detection limits demonstrate the potential of using high-contrast imaging to characterize nearby white dwarfs.
 \end{abstract}
@@
 
-In recent decades astronomers have discovered thousands of exoplanets orbiting stars that will eventually evolve into giants and then white dwarfs \citep{akesonNASAExoplanetArchive2013}.
-The fate of planets around these stars beyond the main-sequence (MS) is uncertain due to the large expansion, stellar winds, and high irradiation encountered on the giant branch \citep{verasPostmainsequencePlanetarySystem2016}.
-Despite this, direct evidence from white dwarf (WD) pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
-Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.
+In recent decades thousands of exoplanets have been discovered orbiting stars that will eventually leave the stability of the main-sequence (MS) \citep{akesonNASAExoplanetArchive2013}.
+The fate of planets around these stars beyond the MS is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}.
+Despite this, direct evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
+Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution.
 
-The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs.
-As the MS star runs out of hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius.
-When helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
-Eventually the star will run out of fuel and conclude its nuclear burning and become a WD.
-The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.
+The evolution of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs.
+As the MS star runs out of hydrogen to burn in its core, it expands to 100s of times its size, engulfing any companions within the stellar radius.
+When helium fusion ignites the giant star becomes three to four orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
+Eventually the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf.
+The white dwarf begins cooling, becoming three to four orders of magnitude dimmer than its MS progenitor.
 
 There is limited knowledge of planetary systems around evolved stars.
-The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain.
-For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
-Surviving planets are subject to adiabatic orbit expansion, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
-The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.
+The pathway for a \textit{first-generation} planet to survive around a post-MS host is violent and uncertain.
+During giant branch evolution, the planet needs to escape engulfment as well as tidal shredding from its inflated host \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
+Planets which survive their hosts' inflation are subject to stellar winds and high luminosity, which causes adiabatic orbit expansion (with the potential for destabilizing the orbit), chemical enrichment of the circumstellar environment with metals and dust, and strong irradiation \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
+Numerical simulations suggest that a giant planet needs to be $\gtrsim$\qty{5}{\au} from a solar-like host to escape expansion and tidal effects \citep{spiegelJupiterWillBecome2012,nordhausOrbitsLowmassCompanions2013}.
+When combined with adiabtatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.
 
 Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions.
-\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where in multi-star systems the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system).
-Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with ``hot-start'' planetary formation timescales \citep{spiegelSpectralPhotometricDiagnostics2012a}.
-A first-generation planet could act as a seed for planetesimal growth in these disks, too.
+\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system).
+These disks serve as reservoirs of material and energy for planet formation, and new planets could form from a first-generation planet acting as a seed.
+Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both ``hot'' and ``cold''-start planetary formation timescales \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}.
 Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies.
 \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI).
-\citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted 3-body problem and concluded up to $\sim$10\% of all WD binaries might contain ``star-hopper'' planets which migrate between the stars.
+\citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted three-body problem and concluded up to $\sim$10\% of all white dwarf binaries might contain ``star-hopper'' planets which migrate between the stars.
 
 Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
-We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade.
+Recent evidence and theories, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets.
+These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.
+
 In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}).
-We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}).
-We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}).
-Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).
+We will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}).
+We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Crefrange{sec:obs}{sec:analysis}).
+Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).
 
@@
 
-High-contrast imaging is a powerful technique for discovering and characterizing exoplanets.
-Directly imaging a circumstellar companion is difficult, though.
+High-contrast imaging is a powerful, but challenging, technique for discovering and characterizing exoplanets.
+Giant exoplanets are most easily detected by their thermal emission, which peaks in the infrared and decreases exponentially as the planet ages \citep{fortneyGiantPlanetInterior2010}.
 The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
-In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.
-Thermal emission from exoplanets peaks well into the infrared, on the Rayleigh-Jeans limit of the stellar spectrum.
-This makes infrared observations preferred over optical or ultraviolet observations due to the reduced contrast.
+The close angular separations of exoplanets make it difficult to disentangle planet-light from the stellar diffraction pattern.
+This problem is exacerbated on the ground as the effects of atmospheric seeing further degrade the sensitivity to exoplanets.
+High-contrast imaging typically comprises large-aperture telescopes, adaptive optics (AO), coronagraphy, high-gain, low-read-noise detectors, observational techniques, and post-processing techniques to overcome the challenges in detecting the faint exoplanet signal.
 
-WDs are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their MS progenitors which reduces the contrast necessary to detect a companion.
-The high effective temperatures of WD photospheres pushes the peak thermal emission even further into the optical and ultraviolet, reducing the intrinsic contrast between the star and the planet.
-In addition, the lack of spectral features of WDs \citep{schatzmanTheorieDebitEnergie1945} makes them imprecise targets for the radial velocity technique.
-The small stellar radii of WDs lowers the transit probability significantly, although detections of substellar companions around WDs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}.
-The faintness of WDs proves challenging due to the high signal-to-noise ratio (S/N) required by modern adaptive optics (AO) instruments.
+ Using large-aperture telescopes provides greater collecting power and angular resolution.
+AO corrects, to an extent, the effects of atmospheric seeing and instrumental noise (speckles) by measuring wavefront errors and cancelling them out with dynamical optics, like a deformable mirror.
+Wavefront errors are measured from a wavefront sensor which typically is illuminated by the target itself.
+The high loop rates of AO, especially on the ground ($\sim$\qty{100}{\hertz} to \qty{1}{\kilo\hertz}), makes Poisson photon noise the limiting factor for AO, which limits the efficacy of faint imaging targets.
+AO correction is necessary for maintaining the necessary angular resolution and sensitivity for exoplanet imaging, as well as keeping the stellar point-spread-function (PSF) centered on a coronagraph, if present.
+
+Coronagraphs are designed to control and attenuate the diffraction of starlight through the telescope while allowing off-axis exoplanet light to pass unperturbed.
+Coronagraphs are extremely sensitive to wavefront errors, particularly tip-tilt pointing errors, necessitating high-quality AO correction.
+Coronagraphs have an inner working angle, the separation where stellar throughput is halved, which is analagous to the full-width at half-maximum (FWHM) of a non-coronagraphic PSF.
+The inner working angle determines how close we can probe to the stars, and it fundamentally limits imaging searches to nearby systems, whose projected separations are closer to solar-system scales.
+
+Exoplanets are faint enough that only a few photons per second reach the detector \citep{traubDirectImagingExoplanets2010}, which makes High-gain, low-read-noise detectors paramount for direct imaging.
+Observational techniques, like angular differential imaging \citep{maroisAngularDifferentialImaging2006}, spatially decorrelate speckles to improve the noise attenuation of long observations.
+Post-processing techniques like PSF subtraction remove the stellar diffraction pattern, but at the risk of removing exoplanet signal.
+Altogether, these techniques have proven sufficient for ground-based telescopes to image giant planets outside our solar system.
+
+White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion.
+The lack of spectral features of white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique.
+The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}.
+The faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by the AO.
 This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing.
 This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13).
-Implicitly, this also limits searches to nearby WDs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
-
-% \section{Post-MS evolution}\label{sec:post-ms}
-
-% There is limited knowledge of planetary systems around evolved stars.
-The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain.
-The expansion of the stellar photosphere will engulf companions and cause tidal interactions, destroying planets or disrupting their orbits \citep{burleighImagingPlanetsNearby2002a, nordhausOrbitsLowmassCompanions2013}.
-Planets that escape engulfment will encounter stellar winds and strong irradiation, causing orbital expansion \citep{jeansCosmogonicProblemsAssociated1924}, enriching the circumstellar environment with metals and dust, and strongly heating planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.
-
-% The observational evidence for planets in post-MS systems is varied.
-WD atmospheres quickly separate heavy elements in their atmospheres due to their high surface gravity \citep{schatzmanTheorieDebitEnergie1945}, which causes the elements to sink and stratify.
-The time scale for this phenomena can be days to $\sim$\qty{1}{\mega\year}, significantly shorter than WD cooling ages, which means that most WD atmospheres are comprised of hydrogen, helium, and some carbon.
-However, metals heavier than carbon have been detected in WDs with cooling ages between \qtyrange{30}{500}{\mega\year}.
-A common explanation for the ``pollution'' of these WDs is the accretion of planetary material.
-This is backed up by the evidence of WD debris disks, although only a fraction of all polluted WDs are host to a disk \citep{koesterFrequencyPlanetaryDebris2014}.
-Chemical analysis shows the pollution is closer to planetary in origin rather than the interstellar medium.
-Most damning, though, is the correlation between the relative population of polluted WDs (25\% - 50\%) and the expected number of MS planet hosts \citep{koesterFrequencyPlanetaryDebris2014}.
-
-% suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
-Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}.
-During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet .
-In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.
-
-% The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}.
-They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
-The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet.
-They studied $\sim$100 white dwarfs but found no companions.
-The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38.
-The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}.
-It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}.
-\citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.
-
-% Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf.
-\citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer.
-The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
-The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.
+Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
 
@@
 
-One fascinating target for post-MS observations is Sirius B, the closest and brightest WD to our solar system.
-The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}.
-As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for direct imaging.
+One fascinating target for post-MS observations is Sirius B, the closest and brightest white dwarf to the sun.
+The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}.
+As mentioned previously, the proximity and intrinsic faintness of Sirius B (compared to a MS star) make it compelling for direct imaging.
 Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.
@@
 Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}.
-Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius, to date.
+Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius to date.
 They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
@@
 
-The total age of Sirius B is the combination of its WD cooling age and the time from the zero-age MS (ZAMS) to the tip of the giant branch (TGB).
-We adapt the cooling age derived by \citet[sec.
-8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}.
-We use the updated WD initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.
+The total age of Sirius B is the combination of its white dwarf cooling age and the time from the zero-age main sequence (ZAMS) to the tip of the giant branch (TGB).
+We adapt the cooling age derived by \citet[Sec.~8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}.
+We use the updated white dwarf initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.
 
@@
 The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}.
-An age uncertainty of $\sim$4\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
-These values are compiled in \Cref{tbl:system}.
+Determining stellar ages is not trivial, and for many systems an accurate age is impossible to constrain.
+This age uncertainty of $\sim$4\% is exceptional, even compared to the $\sim$10\% uncertainty of stars found in young moving groups.
+The values for our adapted and derived parameters values are compiled in \Cref{tbl:system}.
 
-One of the peculiarities of the Sirius system is its large eccentricity of 0.59 \citep{bondSiriusSystemIts2017}.
+One of the peculiarities of the Sirius system is its large eccentricity, $e\sim0.6$ \citep{bondSiriusSystemIts2017}.
 If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
@@
 
-\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping'', but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which we would expect to increase with mass transfer to conserve total angular momentum in the binary.
+\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping,'' but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which would be expected to increase with mass transfer to conserve total angular momentum in the binary.
 \citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}.
 \citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components.
-We extrapolate their Figure 7 using the parameters for Sirius to estimate a $\sim$70\% collision probability for an initial companion of Sirius B if it is chaotically ejected.
-When combined, these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
+If Sirius B ejected a first-generation companion during its giant branch evolution, we estimate a $\sim$70\% probability of the planet colliding with Sirius A \citep[Fig.
+7]{kratterStarHoppersPlanet2012}, although this is far from disqualifying the potential for orbital capture.
+This is an interesting explanation for the chemical peculiarities of Sirius A's atmosphere \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}.
+The variety in these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
 
@@
 There have been many attempts to find planets in the Sirius system, but so far no planets have been detected.
-\citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond}, but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric uncertainty down to $\sim$\qty{10}{\milliarcsecond}.
+\citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond} ($\sim$\qty{200}{\jupitermass}), but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric limits down to \qty{10}{\milliarcsecond} ($\sim$\qty{20}{\jupitermass}).
 The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
 Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
-A planetary atmosphere and evolution model are needed in order to derive mass sensitivity limits from imaging.
-Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}) biasing direct comparisons of mass limits.
-These studies combined reported sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
+These studies reported\footnote{A planetary atmosphere and evolution model are needed in order to derive mass sensitivity limits from imaging.
+Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}), biasing direct comparisons of mass limits.} sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
 \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reported a sensitivity of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
@@
 \defcitealias{bondSiriusSystemIts2017}{B17}
-\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
+\defcitealias{gaiacollaborationGaiaEarlyData2021}{G21a}
 \defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
@@
     $t_\mathrm{sys}$ & 225 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
-    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
-    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
+    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{gaiacollaborationGaiaEarlyData2021} \\
+    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{gaiacollaborationGaiaEarlyData2021} \\
     $a$ & \num{20.016\pm0.014} & \unit{\au} & \citetalias{bondSiriusSystemIts2017} \\
@@
     $m^{\mathrm{L}^\prime}$ & \num{9.1\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
-    $M^{\mathrm{L}^\prime}$ & \num{11.97\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
+    $M^{\mathrm{L}^\prime}$ & \num{11.97\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,gaiacollaborationGaiaEarlyData2021} \\
     \enddata
@@
 Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
-The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
-Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of the scattered light.
+Our first attempt to observe Sirius B failed due to the light from Sirius A scattering into the FOV of the wavefront sensor (WFS).
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of various diffracted light features.
 We did not try coronagraphy for the remaining observations.
-\citet[\S2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
-In order to overcome these obstacles, we decided to used Sirius A as the AO guide star and off-axis guided on Sirius B.
+\citet[Sec.~2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
+In order to overcome these obstacles, we decided to use Sirius A as the AO guide star and off-axis guide to Sirius B.
 
-The Keck facility AO system \citep{wizinowichPerformanceKeckObservatory2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
+Sirius A saturated the WFS of the Keck facility AO system \citep{wizinowichPerformanceKeckObservatory2000}, so we attenuated the flux using a narrow laser-line filter.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
@@
 
-During each observation, we took dark frames and sky-flat frames for calibration.
+During each observation, we took dark frames, dome-flat frames, and sky-flat frames for calibration.
 All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
@@
 
-\subsection{Pre-processing}
+\subsection{Pre-processing}\label{sec:pre-processing}
 
 The raw images from NIRC2 required pre-processing before analyzing them for companions.
-For each epoch, we applied a flat correction using calibration frames captured during observing.
+For each epoch, we applied a flat correction using the sky-flat frames captured during observing.
+We determined the sky-flats had better flat correction than the dome-flats.
 We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{vandokkumCosmicRayRejectionLaplacian2001a} and an adaptive sigma-clipping algorithm.
-We removed sky background using a high-pass median filter with a box size of 31 pixels.
+We removed sky background using a high-pass median filter.
 For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter.
-At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
-Then, each selected frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
+At this point we manually discarded bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
+Then, we co-registered each frame with sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
 
-The co-registered frames were shifted to the center of the FOV and cropped to the inner 200 pixels.
+We centered the co-registered frames in the FOV and cropped to the inner 200 pixels.
 With a pixel scale of \qty{10}{\milliarcsecond}, the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
-All the frames were stacked into data cubes for each epoch.
-We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
-For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
+We stacked the frames into data cubes for each epoch.
+We also measured the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
+For each epoch, we measured the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
 All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\Cref{sec:data}).
@@
 
-By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate.
-This reduces the probability of removing companion signal when we subtract the stellar PSF model.
-After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
+By taking data with the field rotator disabled (ADI), the stellar PSF will not appear to rotate but the FOV will appear to rotate.
+This allows for effective separation of companion light from the PSF by spatial decorrelating speckles.
+After PSF subtraction, we derotated the frames according to their parallactic angle and collapse dthe residuals with a weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
 
 For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{maroisAngularDifferentialImaging2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummerDetectionCharacterizationExoplanets2012a}, non-negative matrix factorization \citep[NMF;][]{renNonnegativeMatrixFactorization2018a}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairetReferencelessAlgorithmCircumstellar2019a,pairetMAYONNAISEMorphologicalComponents2020}.
-The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
-These algorithms are implemented in the open-source \texttt{ADI.jl} Julia package \citep{lucasADIJlJulia2020}.
+We also applied he median subtraction and PCA algorithms in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
+We used the open-source \texttt{ADI.jl} Julia package for implementations of the above algorithms \citep{lucasADIJlJulia2020}.
 
-We determined the best performing PSF subtraction algorithm by measuring the throughput of companion signal through repeated injection and recovery.
-By using a known, fixed S/N for injection, the 5$\sigma$ detection limits can be measured at various positions within the FOV and are azimuthally averaged to produce a \textit{contrast curve}.
-We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
+We determined the best performing PSF subtraction algorithm by measuring the sensitivity to companion signal through repeated injection and recovery of a model PSF.
+We used a known, fixed S/N for injection to derive the 5$\sigma$ detection limits at various positions within the FOV and azimuthally averaged the results to produce a \textit{contrast curve}.
+We calculated both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
 We employed two different detection metrics to search for companions in the residual data: the Gaussian significance map \citep{mawetFundamentalLimitationsHigh2014} and the standardized trajectory intensity mean map \citep[STIM map;][]{pairetSTIMMapDetection2019}.
 These maps assign the likelihood of a companion to each pixel using different assumptions of the residual statistics.
-These three metrics are calculated using the methods available in \texttt{ADI.jl}.
+We used \texttt{ADI.jl} for calculating these metrics.
 The collapsed residual frames along with the above metrics for each algorithm and epoch are in Appendix~\ref{sec:adi-results}.
@@
 A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
-For PCA, NMF, and GreeDS algorithms, we varied the number of components from 1 to 10, creating a residual cube for each iteration.
+For PCA, NMF, and GreeDS algorithms, we created sets of residual cubes, varying the number of components from 1 to 10.
 We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\Cref{fig:pca-contrast-curves}).
@@
 The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
-A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
+We expect a real companion to be present in many different residual cubes from the same dataset, so this ensemble statistic gives us a probability map without determining the number of components \textit{a priori}.
 The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in Appendix~\ref{sec:adi-results}.
-All of the code used for this analysis is available in a GitHub repository (\Cref{sec:data}).
+All of the code and data used for this analysis is available in a GitHub repository (\Cref{sec:data}).
 
@@
 The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits.
-The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{126}{\mega\year}).
-The relative difference between the ages comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}.
+The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the white dwarf cooling age of Sirius B (\qty{126}{\mega\year}).
+The relative difference between the ages (first-generation vs.
+second-generation) comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}.
 \textbf{(b)} The absolute magnitudes are converted to masses using the Sonora Bobcat grid with solar metallicity (solid lines) and with +\qty{0.5}{dex} metallicity (dotted lines).
@@
 We show the contrast curves from the best performing algorithm for each reduction in \Cref{fig:contrast}.
-We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.1 (adapted from Ks-band magnitude from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.1 (adapted from Ks-band magnitude from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{gaiacollaborationGaiaEarlyData2021}.
 We divide \Cref{fig:contrast} into two regimes: speckle-limited and background-limited.
@@
 Here we reach a median 5$\sigma$ detection limit of $\sim$19 magnitude (\Lp).
-This regime is constrained by the quality of the AO correction and the PSF subtraction method, mainly.
-The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily constrained by the sky brightness.
+This regime is mainly constrained by the quality of the AO correction and the PSF subtraction method.
+The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily limited by the sky brightness.
 In this region, we reach 20.4 magnitude (\Lp) in the 2020-11-21 epoch.
@@
 This implies non-Keplerian motion and we take this as direct evidence against the blobs being substellar companions of any kind.
-The signal can be simply explained as residual starlight not removed during PSF subtraction.
+We considered the possibility that the blobs are scattered light from a circumstellar debris disk, but this is highly unlikely given the brightness of the blob and the lack of IR excess that such a massive disk would radiate \citep{skemerSiriusImagedMidinfrared2011}.
+The signal can simply be explained as residual starlight not removed during PSF subtraction.
 
@@
 This is not a trivial task, as the effects of post-MS stellar evolution on planets are highly uncertain and not readily modeled in the currently available grids.
-In particular, we want to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds.
-We start with the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} for our solar metallicity model.
-Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which model very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}.
-The ATMO2020 models are not available for non-solar metallicities, yet, so we also employ the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicity.
+In particular, we would like to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds.
+We used the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} with non-equilibrium chemistry due to weak vertical mixing for our solar metallicity model, following \citet{pathakHighContrastImaging2021}.
+The ATMO2020 grid models very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}, but are not available for non-solar metallicities.
+To explore metal enrichment, we employed the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicities.
 
 To determine the correct isochrone for the grids, we consider two formation scenarios.
-If a first-generation planet survives the giant phase of Sirius B through star hopping, it would have an age closer to the system age of \qty{225}{\mega\year}.
-If the planet formed in a disk of stellar ejecta during the AGB phase, the age would be closer to the WD cooling age of \qty{126}{\mega\year}.
+If a first-generation planet survived the giant phase of Sirius B through star hopping, it would have an age closer to the system age of \qty{225}{\mega\year}.
+If the planet formed in a disk of stellar ejecta during the giant branch evolution, the age would be closer to the white dwarf cooling age of \qty{126}{\mega\year}.
 If the planet formed in such a disk, or if it accreted some of the material, it would almost certainly have peculiar chemistry, although it is uncertain exactly how the relative abundances would change.
@@
 The second panel uses the Sonora models to demonstrate the relatively minor effects ($\sim$\qty{0.1}{\jupitermass}) the increased metallicity has on the mass limits.
-We could not fully utilize the Sonora grid, though, because there are no atmospheric models tabulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models we need for the background-limited regimes.
+We could not fully utilize the Sonora grid because there are no atmospheric models simulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models we need for the background-limited regimes.
 Overall, we constrain our detection limits to \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} (\ang{;;0.19}) in the speckle-limited regime and ultimately \qtyrange{0.7}{1.1}{\jupitermass} at \textgreater\qty{1}{\au} (\ang{;;0.38}) in the background-limited regime.
@@
 Post-MS planetary evolution has historically been limited to theoretical work.
-Recently, though increasingly strong and diverse observational constraints have invigorated the field.
+Recently, though increasingly strong and diverse observational constraints, including direct detections, have invigorated the field.
 We set out in this work to study the nearby Sirius system for post-MS companions around Sirius B.
 The Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR.
-While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets.
+It is highly unlikely a first-generation planet survived post-MS evolution, but no previous imaging efforts have directly addressed post-MS formation pathways in their analyses.
 In this work, we presented high-contrast images of Sirius B in the near-IR.
@@
 
-Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach exceptional detection limits.
-We took the WD sample from \citet{holberg25ParsecLocal2016} and analyzed the 7 binary systems.
-The median distance of this subset is \qty{20}{\parsec}.
-In this work, our inner working angle due to the stellar PSF was $\sim$\qty{80}{\milliarcsecond}, which would be a projected separation of \qty{1.6}{\au} at \qty{20}{\parsec}.
-The median R magnitude is $\sim$\num{15.2}, though, which may prove challenging for natural guide star AO.
-However, with laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude increases significantly ($m^R\lesssim$ \num{19}).
-We suspect future work using LGS AO is capable of studying WD systems at the sub-AU and sub-Jupiter-mass scales.
+Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach strong detection limits.
+Our strong detection limits benefit directly from the precise stellar characterization of the Sirius system, as well as the proximity and brightness of Sirius B.
+With laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude for sufficient AO performances, increases significantly ($m^R\lesssim$ \num{19}).
+We suspect future work using LGS AO is capable of studying white dwarf systems and white dwarf binaries at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
 Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the MS.
@@
 For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter.
-The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby WDs, depending on the contrast-limited performance of NIRCAM.
+The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby white dwarfs, depending on the contrast-limited performance of NIRCAM.
 Unfortunately, Sirius B is far too bright and too close to Sirius A to observe with JWST without severe saturation.
@@
 All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
-The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}} We hope that this improves the reproducibility of the work as well as providing data for future investigations.
-Please reach out to the corresponding author for further inquiries regarding data and code availability.
+The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}}.
+Inquiries regarding data and code are welcome.
 
@@
 ADI.jl \citep{lucasADIJlJulia2020},
-astropy \citep{collaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
+astropy \citep{astropycollaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
 Julia \citep{bezansonJuliaFreshApproach2017},

### 2021-11-10 paper/paper.tex
more papepr revisions and bib fixes

@@
 The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\Cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a}.
+Nonetheless, we estimated astrometry for blobs from each epoch (\Cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a} using the open-source \texttt{orbitize} Python package \citep{bluntOrbitizeComprehensiveOrbitfitting2020}.
 We generated $10^4$ orbits, none of which constrained the points from each epoch (Appendix~\ref{sec:orbits}).
@@
 Post-MS planetary evolution has historically been limited to theoretical work.
-Recently, though increasingly strong and diverse observational constraints, including direct detections, have invigorated the field.
+Recently, though, increasingly strong and diverse observational constraints, including new detections, have invigorated the field.
 We set out in this work to study the nearby Sirius system for post-MS companions around Sirius B.
@@
 Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach strong detection limits.
-Our strong detection limits benefit directly from the precise stellar characterization of the Sirius system, as well as the proximity and brightness of Sirius B.
+Our detection limits benefit directly from the precise stellar characterization of the Sirius system, as well as the proximity and brightness of Sirius B.
 With laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude for sufficient AO performances, increases significantly ($m^R\lesssim$ \num{19}).
-We suspect future work using LGS AO is capable of studying white dwarf systems and white dwarf binaries at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
-Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the MS.
+We suspect future work using LGS AO is capable of studying nearby white dwarf systems at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
+Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the main sequence.
 
@@
 numpy \citep{harrisArrayProgrammingNumPy2020},
+orbitize \citep{bluntOrbitizeComprehensiveOrbitfitting2020},
 scikit-image \citep{waltScikitimageImageProcessing2014},
@@
 We found multiple interesting blobs in the reduced data that were not statistically significant.
-Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions.
-We began by estimating the astrometry of the blobs by eye in reduced data (\Cref{tbl:astrometry}, \Cref{fig:prov-orbit}).
-We tried simulating $10^4$ orbits via rejection sampling with OFTI but no generated orbit was able to constrain all three points.
-Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.
+Nonetheless, we tried fitting Keplerian orbits using OFTI \citep{bluntOrbitsImpatientBayesian2017a} to determine the feasibility of the blobs being astrophysical companions.
+We began by estimating the astrometry of the blobs by eye in the reduced data (\Cref{tbl:astrometry}, \Cref{fig:prov-orbit}).
+We tried simulating $10^4$ orbits via rejection sampling with OFTI, but none of the generated orbits contained all three points in their solution.
+Overall we determined these blobs are not companions and are most likely systematic noise from the stellar PSF.
 
@@
 The separation and offset are in relation to Sirius B.
-The uncertainties are derived from the FWHM of the PSF from each epoch.
+The uncertainties were derived from the FWHM of the PSF from each epoch.
     \label{tbl:astrometry}}
@@
     \plotone{orbit_frames}
-    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch.
+    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residual frames from each epoch.
 Each frame was cropped to the inner $\sim$\qty{0.7}{\au} (\ang{;;0.25}) and the inner two FWHMs have been masked out.

### 2021-11-17 paper/figures/spike.jl
update spike figure

@@ -10,12 +10,12 @@ pro.rc["image.origin"] = "lower"
 pro.rc["image.cmap"] = "inferno"
 pro.rc["grid"] = false
 
-data_cube = fits.getdata(datadir("epoch_2020feb04", "processed", "2020feb04_sirius-b_cube_calib.fits"))
-frame = data_cube[88, :, :]
+data_cube = fits.getdata(datadir("epoch_2020nov21", "processed", "2020nov21_sirius-b_cube_calib.fits"))
+frame = Float32.(data_cube[169, :, :])
 
-fig, axs = pro.subplots(figwidth="3.5in")
+fig, axs = pro.subplots(figwidth="4in")
 ax = first(axs)
 vmin, vmax = zscale(frame)
 ax.imshow(frame; vmin, vmax, colorbar="r")
-ax.format(xlabel="x", ylabel="y")
+ax.format(xlabel="x [px]", ylabel="y [px]")
 fig.save(figuredir("spike.pdf"))

### 2021-11-17 src/mass_models/__init__.py
remove old code

@@ -1,1 +1,0 @@
-from .read_model import *

### 2021-11-17 src/mass_models/read_model.py

@@ -1,274 +1,0 @@
-# code from Mike that interpolates over tables of photometric models
-# such as AMES-COND, BT-SETTI, SONORA, and the like, allowing us to
-# estimate planetary masses from a given contrast
-
-import re
-
-import numpy as np
-from astropy.io import fits
-from astropy.table import Table
-import pandas as pd
-from scipy.interpolate import interp2d
-
-__all__ = ["MassModel", "SONORAModel"]
-
-
-def Mj_to_solar(mass_MJ):
-    return mass_MJ / 1047.9
-
-
-def solar_to_Mj(mass_ms):
-    return mass_ms * 1047.9
-
-
-def distance_modulus(dist_pc):
-    return 5.0 * np.log10(dist_pc) - 5
-
-
-def extract_first_number_from_string(stringy):
-    allnums = re.findall(r"-?\d+\.?\d*", stringy)
-    firstnum = float(allnums[0])
-    return firstnum
-
-
-def get_headers(headerline):
-    # return the line column labels
-    # unfucking the M/MsTeff thing
-    return list(filter(None, headerline.replace("Teff", " Teff").split(" ")))
-
-
-def split_row(row):
-    bb = filter(None, row.split(" "))
-    return bb
-
-
-def parse_allard_file(fname):
-    with open(fname) as f:
-        content = f.readlines()
-        content = [x.strip() for x in content]
-
-    output = []
-    age = None
-    for line in content:
-        if "Gyr" in line:
-            age = extract_first_number_from_string(line)
-            continue
-        if "M/Ms" in line:
-            headers = get_headers(line)
-        else:
-            # split the row by spaces
-            row = split_row(line)
-            try:
-                numrow = [float(x) for x in row]
-                # if not empty
-                if numrow:
-                    output.append([1000 * age] + numrow)
-            except:
-                pass
-    tab = Table(np.array(output), names=["Age(Myr)"] + headers)
-    return tab.to_pandas()
-
-
-class MassModel:
-    def __init__(self, filename):
-        self.table = parse_allard_file(filename)
-
-    def get_below(self, item, amt, subtable=None):
-        # returns a subtable
-        # eg get_below('Age(Myr)', 1000) will return
[…]

### 2021-11-19 paper/adi_results_full.tex
update paper with fresh revisions

@@
 The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
-In each frame the inner two FWHMs are masked out.
+In each frame, the inner two FWHMs are masked out.
 The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.}
@@
 The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
-In each frame the inner two FWHMs are masked out.
+In each frame, the inner two FWHMs are masked out.
 The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.
@@
 The figures share a common scale and the inner two FWHMs are masked out for all the frames.
-Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
+Outputs for the other epochs and the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
 \end{figure}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using NMF reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the first epoch using GreeDS reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using PCA reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using NMF reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the second epoch using GreeDS reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using PCA reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using NMF reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
 \figsetgrpnote{5$\sigma$ Gaussian contrast curves for the third epoch using GreeDS reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.}
@@
     \caption{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.
-Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
+Outputs for the other epochs and the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
     \label{fig:pca-contrast-curves}

### 2021-11-19 paper/paper.tex
update paper with fresh revisions

@@
 
+\received{August 13, 2021}
+\revised{\today}
+
 \begin{document}
@@
 \begin{abstract}
-Discovery and characterization of post-main-sequence planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution.
-We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-main-sequence planetary evolution in the Sirius system.
+We present deep imaging of Sirius B, the closest and brightest white dwarf, to constrain post-main-sequence planetary evolution in the Sirius system.
 We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging.
@@
 In recent decades thousands of exoplanets have been discovered orbiting stars that will eventually leave the stability of the main-sequence (MS) \citep{akesonNASAExoplanetArchive2013}.
-The fate of planets around these stars beyond the MS is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}.
+The eventual fate of planets around these stars is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}.
 Despite this, direct evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
@@
 The evolution of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs.
-As the MS star runs out of hydrogen to burn in its core, it expands to 100s of times its size, engulfing any companions within the stellar radius.
-When helium fusion ignites the giant star becomes three to four orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
-Eventually the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf.
+As the main-sequence star runs out of hydrogen to burn in its core, it expands to 100s of times its size, engulfing any companions within the stellar radius.
+When helium fusion ignites, the giant star becomes three to four orders of magnitude brighter, causing stellar winds and strong irradiation.
+Eventually, the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf.
 The white dwarf begins cooling, becoming three to four orders of magnitude dimmer than its MS progenitor.
@@
 During giant branch evolution, the planet needs to escape engulfment as well as tidal shredding from its inflated host \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
-Planets which survive their hosts' inflation are subject to stellar winds and high luminosity, which causes adiabatic orbit expansion (with the potential for destabilizing the orbit), chemical enrichment of the circumstellar environment with metals and dust, and strong irradiation \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
+Planets which survive their hosts' inflation are privy to the effects of stellar winds and the high luminosities of asymptotic giant stars \citep{mustillForetellingsRagnarokWorldengulfing2012,mustillMainsequenceProgenitorConfigurations2013,verasPostmainsequencePlanetarySystem2016}.
+The stellar winds will chemically enrich the circumstellar environment with metals and dust, and the high luminosity and proximity to the stellar surface will cause strong irradiation, and therefore heating \citep{spiegelJupiterWillBecome2012}.
+The mass-loss from the stellar winds can adiabatically expand a planet's orbit \citep{jeansCosmogonicProblemsAssociated1924}, potentially destabilizing the orbit and chaotically ejecting the planet \citep{kratterStarHoppersPlanet2012}.
 Numerical simulations suggest that a giant planet needs to be $\gtrsim$\qty{5}{\au} from a solar-like host to escape expansion and tidal effects \citep{spiegelJupiterWillBecome2012,nordhausOrbitsLowmassCompanions2013}.
-When combined with adiabtatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.
+When combined with adiabatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.
 
 Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions.
-\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system).
-These disks serve as reservoirs of material and energy for planet formation, and new planets could form from a first-generation planet acting as a seed.
-Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both ``hot'' and ``cold''-start planetary formation timescales \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}.
+\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around another star (or, in fact, the whole system).
+These disks serve as reservoirs of material and energy for planet formation, which could be kick-started by a first-generation planet acting as a seed.
+Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both gravitational-instability (``hot start'') and core-accretion (``cold start'') formation theories \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}.
 Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies.
@@
 Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
-Recent evidence and theories, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets.
+Recent evidence and theoretical works, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets.
 These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.
 
-In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}).
-We will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}).
+Direct imaging is well-suited for finding planets around white dwarfs due to the intrinsic faintness of the host (compared to a MS star) and lack of spectral features for radial velocity studies \citep{burleighImagingPlanetsNearby2002a}.
+With direct imaging, exoplanets can be detected and characterized independently from the orbital period of the planet, the stellar radius, or stellar spectrum, which makes it powerful compared to broadband photometric analysis or transit photometry methods.
+High-contrast imaging pushes direct imaging to its limits using large-aperture telescopes, adaptive optics, coronagraphy, low-noise detectors, image-processing, and observational techniques.
+Despite the power of high-contrast imaging, very few observations have been carried out for white dwarfs (a recent example is \citealt{pathakHighContrastImaging2021}).
+
+Exoplanets are faint enough that only a few photons per second reach the detector.
+The host stars are many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$) and have close angular separations, which means planets are easily washed out by the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}.
+In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-random perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}).
+Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation.
+AO is also paramount for enabling coronagraphy, which attenuates on-axis starlight while transmitting off-axis signal, up to some inner working angle.
+
+Typical high-contrast targets are nearby young objects observed in the near-infrared.
+Younger planets are brighter, thanks to their latent formation heat \citep{fortneyGiantPlanetInterior2010}, which reduces the star-planet contrast, and observing them in the near-infrared corresponds with their peak blackbody emission.
+Nearby targets have larger angular separations between potential planets and their hosts, which makes it easier to separate the signals.
+Nearby targets are also intrinsically brighter, enabling effective AO control.
+White dwarfs are atypical high-contrast targets due to their age and sparsity, but their relative faintness is compelling for the reduced contrast.
+In addition, a post-MS planet would be much younger than the system age of a white dwarf and would therefore still retain a large portion of its latent heat, further motivating high-contrast searches of nearby white dwarfs.
+
+We set out in this work to perform high-contrast observations of Sirius B for post-MS planets.
+In the rest of this report, we will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}).
 We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Crefrange{sec:obs}{sec:analysis}).
-Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).
+Lastly, we will discuss our results within the context of Sirius and post-MS systems, as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).
 
-\section{Directly imaging post-MS systems}\label{sec:imaging}
+% High-contrast imaging is a powerful, but challenging, technique for discovering and characterizing exoplanets.
+Giant exoplanets are most easily detected by the thermal emission of their latent formation heat, which peaks in the infrared and decreases as the planet ages \citep{fortneyGiantPlanetInterior2010}.
+The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
+The close angular separations of exoplanets from their host stars make it difficult to disentangle planet-light from the stellar diffraction pattern.
+This problem is exacerbated on the ground as the effects of atmospheric seeing further degrade the sensitivity to exoplanets.
+High-contrast imaging typically comprises large-aperture telescopes, adaptive optics (AO), coronagraphy, low-noise detectors, observational techniques, and image-processing to overcome the challenges in detecting the faint exoplanet signal.
 
-High-contrast imaging is a powerful, but challenging, technique for discovering and characterizing exoplanets.
-Giant exoplanets are most easily detected by their thermal emission, which peaks in the infrared and decreases exponentially as the planet ages \citep{fortneyGiantPlanetInterior2010}.
-The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
-The close angular separations of exoplanets make it difficult to disentangle planet-light from the stellar diffraction pattern.
-This problem is exacerbated on the ground as the effects of atmospheric seeing further degrade the sensitivity to exoplanets.
-High-contrast imaging typically comprises large-aperture telescopes, adaptive optics (AO), coronagraphy, high-gain, low-read-noise detectors, observational techniques, and post-processing techniques to overcome the challenges in detecting the faint exoplanet signal.
-
- Using large-aperture telescopes provides greater collecting power and angular resolution.
+% Using large-aperture telescopes provides greater collecting power and angular resolution.
 AO corrects, to an extent, the effects of atmospheric seeing and instrumental noise (speckles) by measuring wavefront errors and cancelling them out with dynamical optics, like a deformable mirror.
 Wavefront errors are measured from a wavefront sensor which typically is illuminated by the target itself.
-The high loop rates of AO, especially on the ground ($\sim$\qty{100}{\hertz} to \qty{1}{\kilo\hertz}), makes Poisson photon noise the limiting factor for AO, which limits the efficacy of faint imaging targets.
+The high loop rates of AO, especially on the ground ($\sim$\qty{100}{\hertz} to \qty{1}{\kilo\hertz}), makes Poisson photon noise the limiting factor for AO, which limits the efficacy of faint imaging targets \citep{guyonExtremeAdaptiveOptics2018}.
 AO correction is necessary for maintaining the necessary angular resolution and sensitivity for exoplanet imaging, as well as keeping the stellar point-spread-function (PSF) centered on a coronagraph, if present.
 
-Coronagraphs are designed to control and attenuate the diffraction of starlight through the telescope while allowing off-axis exoplanet light to pass unperturbed.
+% Coronagraphs are designed to control and attenuate the diffraction of starlight through the telescope while allowing off-axis exoplanet light to pass unperturbed.
 Coronagraphs are extremely sensitive to wavefront errors, particularly tip-tilt pointing errors, necessitating high-quality AO correction.
-Coronagraphs have an inner working angle, the separation where stellar throughput is halved, which is analagous to the full-width at half-maximum (FWHM) of a non-coronagraphic PSF.
+Coronagraphs have an inner working angle, the separation where stellar throughput is halved, which is analogous to the full-width at half-maximum (FWHM) of a non-coronagraphic PSF.
 The inner working angle determines how close we can probe to the stars, and it fundamentally limits imaging searches to nearby systems, whose projected separations are closer to solar-system scales.
 
-Exoplanets are faint enough that only a few photons per second reach the detector \citep{traubDirectImagingExoplanets2010}, which makes High-gain, low-read-noise detectors paramount for direct imaging.
+% Exoplanets are faint enough that only a few photons per second reach the detector \citep{traubDirectImagingExoplanets2010}, which makes high-gain, low-read-noise detectors paramount for direct imaging.
 Observational techniques, like angular differential imaging \citep{maroisAngularDifferentialImaging2006}, spatially decorrelate speckles to improve the noise attenuation of long observations.
@@
 
-White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion.
-The lack of spectral features of white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique.
+% White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion.
+The lack of spectral features in white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique.
 The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}.
-The faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by the AO.
+The intrinsic faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by AO.
 This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing.
@@
 One fascinating target for post-MS observations is Sirius B, the closest and brightest white dwarf to the sun.
-The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}.
+The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a $J=$-1.36 magnitude A1V star, and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}.
 As mentioned previously, the proximity and intrinsic faintness of Sirius B (compared to a MS star) make it compelling for direct imaging.
@@
 Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment.
-Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}.
 Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius to date.
-They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+Their astrometric uncertainties are over an order of magnitude improved from the visual orbit derived by \citet{vandenbosOrbitSiriusADS1960}.
+Following the procedure of \citet{gatewoodStudySirius1978}, \citet{bondSiriusSystemIts2017} derived dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}.
-\citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
+\citet{bondSiriusSystemIts2017} calculated the longest stable companion period around Sirius B to be \qty{1.8}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
 
@@
 The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}.
-Determining stellar ages is not trivial, and for many systems an accurate age is impossible to constrain.
-This age uncertainty of $\sim$4\% is exceptional, even compared to the $\sim$10\% uncertainty of stars found in young moving groups.
-The values for our adapted and derived parameters values are compiled in \Cref{tbl:system}.
+Determining stellar ages is challenging, and our age uncertainty of $\sim$4\% is exceptional compared to those typically obtained by dynamical analysis of young moving groups ($\sim$10\%) or gyrochronology ($\sim$15\%).
+The values for our adapted and derived parameters are compiled in \Cref{tbl:system}.
 
@@
 In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}.
-\citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}.
+\citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate-mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}.
 This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage.
-Mass transfer and tidal circularization would be expected, however the present-day eccentricity provide contrary evidence.
+Mass transfer and tidal circularization would be expected; however, the present-day eccentricity provides contrary evidence.
 
 \citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping,'' but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which would be expected to increase with mass transfer to conserve total angular momentum in the binary.
-\citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}.
-\citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components.
+\citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of a third body between \qtyrange{0.6}{5.5}{\solarmass}.
+\citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is a collision with one of the binary components.
 If Sirius B ejected a first-generation companion during its giant branch evolution, we estimate a $\sim$70\% probability of the planet colliding with Sirius A \citep[Fig.
 7]{kratterStarHoppersPlanet2012}, although this is far from disqualifying the potential for orbital capture.
-This is an interesting explanation for the chemical peculiarities of Sirius A's atmosphere \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}.
-The variety in these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
+This is an interesting, although uncertain, explanation for the peculiar surface chemical abundances found on Sirius A \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}.
+The variety in these studies shows the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
 
@@
 
-There have been many attempts to find planets in the Sirius system, but so far no planets have been detected.
+There have been many attempts to find planets in the Sirius system, but, so far, no planets have been detected.
 \citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond} ($\sim$\qty{200}{\jupitermass}), but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric limits down to \qty{10}{\milliarcsecond} ($\sim$\qty{20}{\jupitermass}).
 The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
-Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
-These studies reported\footnote{A planetary atmosphere and evolution model are needed in order to derive mass sensitivity limits from imaging.
-Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}), biasing direct comparisons of mass limits.} sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
+Around the same time, \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
+These studies reported\footnote{A planetary atmosphere and evolution model are needed to derive mass sensitivity limits from imaging.
+Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:mass-limits}), biasing direct comparisons of mass limits.} sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
 \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reported a sensitivity of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
@@
 
-% \begin{deluxetable}{ccccc}
-%     \tabletypesize{\small}
-%     \tablecaption{Observing parameters for the three epochs of data.
-All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in \Lp-band (\qty{3.776}{\micro\meter}).
-Observation time is based on the frames that were selected for processing.
-Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
-Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
-%     \label{tbl:obs}}
-%     \tablehead{
-%         \colhead{Epoch} &
-%         \colhead{2020-02-4} &
-%         \colhead{2020-11-21} &
-%         \colhead{2020-11-28} &
-%         \colhead{}
-%     }
-%     \startdata
-%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
-%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
-%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
-%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
-%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
-%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
-%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
-%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
-%     \enddata
-% \end{deluxetable}
-
 \begin{figure}
     \centering
-    \epsscale{1.1}
+    \epsscale{1.2}
     \plotone{spike}
@@
 Our first attempt to observe Sirius B failed due to the light from Sirius A scattering into the FOV of the wavefront sensor (WFS).
-Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of various diffracted light features.
-We did not try coronagraphy for the remaining observations.
 \citet[Sec.~2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
-In order to overcome these obstacles, we decided to use Sirius A as the AO guide star and off-axis guide to Sirius B.
+To overcome these obstacles, we decided to use Sirius A as the AO guide star and off-axis guide to Sirius B.
 
@@
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
+We tried to use the vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} but gave up when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of various diffracted light features.
+This rendered the coronagraph ineffective, especially with the large amounts of drift.
+We did not try coronagraphy for the remaining observations.
 
 During each observation, we took dark frames, dome-flat frames, and sky-flat frames for calibration.
-All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
-In order to avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.
+All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
+To avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.
 
@@
 We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{vandokkumCosmicRayRejectionLaplacian2001a} and an adaptive sigma-clipping algorithm.
-We removed sky background using a high-pass median filter.
-For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter.
-At this point we manually discarded bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
+We removed the sky background using a high-pass median filter.
+For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions to simplify background subtraction, but this ended up performing worse than the high-pass filter.
+At this point, we manually discarded bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
 Then, we co-registered each frame with sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
 
-We centered the co-registered frames in the FOV and cropped to the inner 200 pixels.
+We centered the co-registered frames in the FOV and cropped them to the inner 200 pixels.
 With a pixel scale of \qty{10}{\milliarcsecond}, the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
@@
 We also measured the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
-For each epoch, we measured the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
-All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\Cref{sec:data}).
+For each epoch, we measured the full width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
+All the pre-processing code is available in Jupyter notebooks in a GitHub repository (\Cref{sec:data}).
 
@@
     \caption{\textbf{top row:} The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawetFundamentalLimitationsHigh2014}.
-Typically a critical value for detection is 5.
+Typically, a critical value for detection is 5.
 \textbf{bottom row:} The STIM maps for each epoch calculated from each residual cube.
@@
 By taking data with the field rotator disabled (ADI), the stellar PSF will not appear to rotate but the FOV will appear to rotate.
-This allows for effective separation of companion light from the PSF by spatial decorrelating speckles.
-After PSF subtraction, we derotated the frames according to their parallactic angle and collapse dthe residuals with a weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
+This allows for the effective separation of companion light from the PSF by spatial decorrelating speckles.
+After PSF subtraction, we derotated the frames according to their parallactic angle and collapsed the residuals with a variance-weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
 
 For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{maroisAngularDifferentialImaging2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummerDetectionCharacterizationExoplanets2012a}, non-negative matrix factorization \citep[NMF;][]{renNonnegativeMatrixFactorization2018a}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairetReferencelessAlgorithmCircumstellar2019a,pairetMAYONNAISEMorphologicalComponents2020}.
-We also applied he median subtraction and PCA algorithms in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
+We also applied the median subtraction and PCA algorithms in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
 We used the open-source \texttt{ADI.jl} Julia package for implementations of the above algorithms \citep{lucasADIJlJulia2020}.
@@
 We determined the best performing PSF subtraction algorithm by measuring the sensitivity to companion signal through repeated injection and recovery of a model PSF.
-We used a known, fixed S/N for injection to derive the 5$\sigma$ detection limits at various positions within the FOV and azimuthally averaged the results to produce a \textit{contrast curve}.
+We used a known, fixed S/N for injection to derive the 5$\sigma$ detection limits at various positions within the FOV and azimuthally averaged the results to produce a contrast curve.
 We calculated both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
@@
 We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\Cref{fig:pca-contrast-curves}).
-In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairetSignalProcessingMethods2020} as an ensemble statistic.
+In our analysis, we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairetSignalProcessingMethods2020} as an ensemble statistic.
 The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
@@
 The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in Appendix~\ref{sec:adi-results}.
-All of the code and data used for this analysis is available in a GitHub repository (\Cref{sec:data}).
+All the code and data used for this analysis is available in a GitHub repository (\Cref{sec:data}).
 
@@
     \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
-The absolute magnitude are calculated using an absolute magnitude for Sirius B of 11.97.
+The solid lines are the Gaussian 5$\sigma$ contrast curves, and the dashed lines are the Student-t corrected curves.
+The absolute magnitude is calculated using an absolute magnitude for Sirius B of 11.97.
 The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
@@
 \textbf{(a)} The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing.
-The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits.
+The solid lines are the Gaussian 5$\sigma$ detection limits, and the dashed lines are the Student-t corrected limits.
 The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the white dwarf cooling age of Sirius B (\qty{126}{\mega\year}).
@@
 For the first two epochs, full-frame median subtraction had the best contrast at almost all separations.
-For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
+For the last epoch, annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
 This algorithm was unable to detect a 100 S/N companion injected into the innermost annulus with 5$\sigma$ significance.
@@
 
-We show the contrast curves from the best performing algorithm for each reduction in \Cref{fig:contrast}.
+We show the contrast curves from the best-performing algorithm for each reduction in \Cref{fig:contrast}.
 We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.1 (adapted from Ks-band magnitude from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{gaiacollaborationGaiaEarlyData2021}.
@@
 This regime is mainly constrained by the quality of the AO correction and the PSF subtraction method.
-The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily limited by the sky brightness.
+The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves and is primarily limited by the sky brightness.
 In this region, we reach 20.4 magnitude (\Lp) in the 2020-11-21 epoch.
@@
 
-\subsection{Mass detection limits}
+\subsection{Mass detection limits}\label{sec:mass-limits}
 
-In order to convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid.
+To convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid.
 This is not a trivial task, as the effects of post-MS stellar evolution on planets are highly uncertain and not readily modeled in the currently available grids.
@@
 We used the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} with non-equilibrium chemistry due to weak vertical mixing for our solar metallicity model, following \citet{pathakHighContrastImaging2021}.
-The ATMO2020 grid models very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}, but are not available for non-solar metallicities.
+ATMO2020 models very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012} but are not available for non-solar metallicities.
 To explore metal enrichment, we employed the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicities.
@@
 To determine the correct isochrone for the grids, we consider two formation scenarios.
-If a first-generation planet survived the giant phase of Sirius B through star hopping, it would have an age closer to the system age of \qty{225}{\mega\year}.
+If a first-generation planet survived the giant phase of Sirius B through star hopping, it would have an age close to the system age of \qty{225}{\mega\year}.
 If the planet formed in a disk of stellar ejecta during the giant branch evolution, the age would be closer to the white dwarf cooling age of \qty{126}{\mega\year}.
@@
 The second panel uses the Sonora models to demonstrate the relatively minor effects ($\sim$\qty{0.1}{\jupitermass}) the increased metallicity has on the mass limits.
-We could not fully utilize the Sonora grid because there are no atmospheric models simulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models we need for the background-limited regimes.
+We could not fully utilize the Sonora grid because there are no atmospheric models simulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models needed for the background-limited regimes.
 Overall, we constrain our detection limits to \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} (\ang{;;0.19}) in the speckle-limited regime and ultimately \qtyrange{0.7}{1.1}{\jupitermass} at \textgreater\qty{1}{\au} (\ang{;;0.38}) in the background-limited regime.
@@
 Recently, though, increasingly strong and diverse observational constraints, including new detections, have invigorated the field.
-We set out in this work to study the nearby Sirius system for post-MS companions around Sirius B.
-The Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR.
-It is highly unlikely a first-generation planet survived post-MS evolution, but no previous imaging efforts have directly addressed post-MS formation pathways in their analyses.
+We set out in this work to search nearby white dwarf Sirius B for post-MS planets.
+The Sirius system is one of the most well studied in history, and its precise characterization improves our systematic uncertainties.
+It is highly unlikely a first-generation planet survived Sirius B's giant branch evolution, but no previous imaging efforts have directly addressed post-MS formation in their analyses.
+
 In this work, we presented high-contrast images of Sirius B in the near-IR.
@@
 Our observations also show how the high precision of the parameters of the Sirius system directly benefits the sensitivity to planets.
-For example, the $\sim$4\% relative uncertainty of Sirius B's age translates to mass detection limit uncertainty below \qty{0.1}{\jupitermass}.
+For example, the $\sim$4\% relative age uncertainty (\Cref{sec:sirius}) translates to a mass uncertainty below \qty{0.1}{\jupitermass}.
 Despite the high sensitivity of this study, we found no significant evidence for a companion around Sirius B, consistent with previous results.
@@
 With laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude for sufficient AO performances, increases significantly ($m^R\lesssim$ \num{19}).
-We suspect future work using LGS AO is capable of studying nearby white dwarf systems at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
+We suspect future work using LGS AO will be capable of studying nearby white dwarf systems at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
 Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the main sequence.
 
-We also consider future space-based observations with the James Webb Space Telescope (JWST), eliminating the effects of atmospheric seeing and the bright sky background.
+Future space-based observations with the James Webb Space Telescope (JWST) will avoid the effects of atmospheric seeing and the bright sky background.
 For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter.
@@
 
-All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
+All the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
 The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}}.
@@
     \tablecaption{Provisional astrometry for a blob of interest from each epoch.
-The separation and offset are in relation to Sirius B.
+The separation and offset are relative to Sirius B.
 The uncertainties were derived from the FWHM of the PSF from each epoch.

### 2021-11-19 paper/paper.tex
add back pagenumbers
updat elanguage

@@
 Exoplanets are faint enough that only a few photons per second reach the detector.
-The host stars are many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$) and have close angular separations, which means planets are easily washed out by the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}.
+Host stars are typically many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$), and planets have very small angular separations from their hosts, which makes it difficult to disentangle the planet-light from the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}.
 In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-random perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}).
@@
 Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
+\pagebreak
 

### 2021-11-23 paper/paper.tex
remove commented text
gary/mike revisions

@@
 The eventual fate of planets around these stars is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}.
-Despite this, direct evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
-Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interactions during the most critical phases of stellar evolution.
+Despite this, evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
+Discovery and characterization of post-MS planets is essential to study how they transform and how they interact with their hosts during the most critical phases of stellar evolution.
 
-The evolution of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs.
-As the main-sequence star runs out of hydrogen to burn in its core, it expands to 100s of times its size, engulfing any companions within the stellar radius.
+The post-MS lifetimes of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs.
+As the main-sequence star runs out of hydrogen to burn in its core, it expands to hundreds of times its size, engulfing any companions within the stellar radius.
 When helium fusion ignites, the giant star becomes three to four orders of magnitude brighter, causing stellar winds and strong irradiation.
@@
 Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
-Recent evidence and theoretical works, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets.
+Recent evidence and theoretical works \citep[e.g.,][]{xuSpitzerObservationsWhite2012,koesterFrequencyPlanetaryDebris2014,verasPostmainsequencePlanetarySystem2016,vanderburgGiantPlanetCandidate2020}, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets.
 These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.
@@
 Direct imaging is well-suited for finding planets around white dwarfs due to the intrinsic faintness of the host (compared to a MS star) and lack of spectral features for radial velocity studies \citep{burleighImagingPlanetsNearby2002a}.
-With direct imaging, exoplanets can be detected and characterized independently from the orbital period of the planet, the stellar radius, or stellar spectrum, which makes it powerful compared to broadband photometric analysis or transit photometry methods.
+With direct imaging, exoplanets can be detected and characterized independently from the orbital period of the planet, the stellar radius, or stellar spectrum, which makes it powerful compared to broadband spectral-energy distribution analysis or transit photometry methods.
 High-contrast imaging pushes direct imaging to its limits using large-aperture telescopes, adaptive optics, coronagraphy, low-noise detectors, image-processing, and observational techniques.
@@
 
-Exoplanets are faint enough that only a few photons per second reach the detector.
+Exoplanets are faint enough that in certain cases only a few photons per second reach the detector.
 Host stars are typically many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$), and planets have very small angular separations from their hosts, which makes it difficult to disentangle the planet-light from the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}.
-In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-random perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}).
+In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-static perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}).
 Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation.
@@
 Typical high-contrast targets are nearby young objects observed in the near-infrared.
-Younger planets are brighter, thanks to their latent formation heat \citep{fortneyGiantPlanetInterior2010}, which reduces the star-planet contrast, and observing them in the near-infrared corresponds with their peak blackbody emission.
-Nearby targets have larger angular separations between potential planets and their hosts, which makes it easier to separate the signals.
+Younger planets are brighter, thanks to their latent formation heat \citep{fortneyGiantPlanetInterior2010} and observing them in the near-infrared corresponds with their peak blackbody emission.
+Nearby targets have larger angular separations between potential planets and their hosts, which makes it easier to separate the planet from the star.
 Nearby targets are also intrinsically brighter, enabling effective AO control.
-White dwarfs are atypical high-contrast targets due to their age and sparsity, but their relative faintness is compelling for the reduced contrast.
+White dwarfs are atypical high-contrast targets due to their age and sparsity, but their relative faintness is compelling for the reduced star-planet flux ratio.
 In addition, a post-MS planet would be much younger than the system age of a white dwarf and would therefore still retain a large portion of its latent heat, further motivating high-contrast searches of nearby white dwarfs.
 
-We set out in this work to perform high-contrast observations of Sirius B for post-MS planets.
+In this work we set out to perform high-contrast observations of Sirius B to search for post-MS planets.
 In the rest of this report, we will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}).
@@
 
-% High-contrast imaging is a powerful, but challenging, technique for discovering and characterizing exoplanets.
-Giant exoplanets are most easily detected by the thermal emission of their latent formation heat, which peaks in the infrared and decreases as the planet ages \citep{fortneyGiantPlanetInterior2010}.
-The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
-The close angular separations of exoplanets from their host stars make it difficult to disentangle planet-light from the stellar diffraction pattern.
-This problem is exacerbated on the ground as the effects of atmospheric seeing further degrade the sensitivity to exoplanets.
-High-contrast imaging typically comprises large-aperture telescopes, adaptive optics (AO), coronagraphy, low-noise detectors, observational techniques, and image-processing to overcome the challenges in detecting the faint exoplanet signal.
-
-% Using large-aperture telescopes provides greater collecting power and angular resolution.
-AO corrects, to an extent, the effects of atmospheric seeing and instrumental noise (speckles) by measuring wavefront errors and cancelling them out with dynamical optics, like a deformable mirror.
-Wavefront errors are measured from a wavefront sensor which typically is illuminated by the target itself.
-The high loop rates of AO, especially on the ground ($\sim$\qty{100}{\hertz} to \qty{1}{\kilo\hertz}), makes Poisson photon noise the limiting factor for AO, which limits the efficacy of faint imaging targets \citep{guyonExtremeAdaptiveOptics2018}.
-AO correction is necessary for maintaining the necessary angular resolution and sensitivity for exoplanet imaging, as well as keeping the stellar point-spread-function (PSF) centered on a coronagraph, if present.
-
-% Coronagraphs are designed to control and attenuate the diffraction of starlight through the telescope while allowing off-axis exoplanet light to pass unperturbed.
-Coronagraphs are extremely sensitive to wavefront errors, particularly tip-tilt pointing errors, necessitating high-quality AO correction.
-Coronagraphs have an inner working angle, the separation where stellar throughput is halved, which is analogous to the full-width at half-maximum (FWHM) of a non-coronagraphic PSF.
-The inner working angle determines how close we can probe to the stars, and it fundamentally limits imaging searches to nearby systems, whose projected separations are closer to solar-system scales.
-
-% Exoplanets are faint enough that only a few photons per second reach the detector \citep{traubDirectImagingExoplanets2010}, which makes high-gain, low-read-noise detectors paramount for direct imaging.
-Observational techniques, like angular differential imaging \citep{maroisAngularDifferentialImaging2006}, spatially decorrelate speckles to improve the noise attenuation of long observations.
-Post-processing techniques like PSF subtraction remove the stellar diffraction pattern, but at the risk of removing exoplanet signal.
-Altogether, these techniques have proven sufficient for ground-based telescopes to image giant planets outside our solar system.
-
-% White dwarfs are interesting targets for direct imaging- they are three to four orders of magnitude fainter than their MS progenitors, reducing the contrast necessary to detect a companion.
-The lack of spectral features in white dwarfs \citep{schatzmanTheorieDebitEnergie1945} makes them difficult targets for the radial velocity technique.
-The small stellar radii of white dwarfs lowers the transit probability significantly, although detections of substellar companions around white dwarfs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}.
-The intrinsic faintness of white dwarfs proves challenging due to the high signal-to-noise ratio (S/N) required by AO.
-This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing.
-This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13).
-Implicitly, this also limits searches to nearby white dwarfs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
-\pagebreak
-
 \section{Sirius B and the Sirius system}\label{sec:sirius}
 
-One fascinating target for post-MS observations is Sirius B, the closest and brightest white dwarf to the sun.
 The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a $J=$-1.36 magnitude A1V star, and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}.
@@
 The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}.
-Determining stellar ages is challenging, and our age uncertainty of $\sim$4\% is exceptional compared to those typically obtained by dynamical analysis of young moving groups ($\sim$10\%) or gyrochronology ($\sim$15\%).
+Determining stellar ages is challenging, and the age uncertainty of $\sim$4\% is exceptional compared to those typically obtained by dynamical analysis of young moving groups ($\sim$10\%) or gyrochronology ($\sim$15\%).
 The values for our adapted and derived parameters are compiled in \Cref{tbl:system}.
@@
 By taking data with the field rotator disabled (ADI), the stellar PSF will not appear to rotate but the FOV will appear to rotate.
-This allows for the effective separation of companion light from the PSF by spatial decorrelating speckles.
+This allows for the effective separation of companion light from the PSF by spatially decorrelating speckles.
 After PSF subtraction, we derotated the frames according to their parallactic angle and collapsed the residuals with a variance-weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
@@
 For the last epoch, annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
-This algorithm was unable to detect a 100 S/N companion injected into the innermost annulus with 5$\sigma$ significance.
-The contrast for this innermost annulus is therefore not plotted.
+When processed with this algorithm, we were unable to retrieve a 100 S/N injected companion with 5$\sigma$ significance in the innermost annulus.
+The contrast in this region is ill-determined and therefore not plotted.
 \Crefrange{fig:residuals}{fig:detection} show the collapsed residual frames from each epoch, along with the Gaussian significance maps and STIM maps.
@@
 In this work, we presented high-contrast images of Sirius B in the near-IR.
-Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, reaching \num{20.4} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
+Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, down to \num{20.4} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
 We consider multiple planetary formation pathways yielding ages between \qtyrange{126}{225}{\mega\year} and explore the effects of enriched metallicity.
@@
 Our detection limits benefit directly from the precise stellar characterization of the Sirius system, as well as the proximity and brightness of Sirius B.
-With laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude for sufficient AO performances, increases significantly ($m^R\lesssim$ \num{19}).
-We suspect future work using LGS AO will be capable of studying nearby white dwarf systems at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
+With laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018} the limiting magnitude for sufficient AO performance is improved ($m^R\lesssim$ \num{19}).
+Future extremely large telescopes will benefit from increased collecting areas and smaller inner working angles due to the larger aperture diameters.
+The Thirty Meter Telescope (TMT), for example, will have LGS AO in its first-generation instrument suite (NFIRAOS), which will significantly improve the faintness limits of its high-contrast instrumentation.
+We suspect future work using LGS AO on current and next-generation telescopes will be capable of studying nearby white dwarf systems at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
 Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the main sequence.
@@
 
-All the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
-The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}}.
-Inquiries regarding data and code are welcome.
+All the code used for pre-processing and reducing the data is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
+The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}} Inquiries regarding data and code are welcome.
 

### 2021-12-07 paper/paper.tex
tidy tex
Updates from Overleaf

@@
     list-units=single,
-    separate-uncertainty,
-    separate-uncertainty-units=single,
+    separate-uncertainty
 }
@@
 
-\received{August 13, 2021}
-\revised{\today}
-
 \begin{document}
 
-\title{An Imaging Search for Post-Main-Sequence Planets of Sirius B}
+\title{An Imaging Search for Post-MS Companions of Sirius B}
 
-\shorttitle{An Imaging Search for Post-MS Planets of Sirius B}
+\shorttitle{An Imaging Search for Post-MS Companions of Sirius B}
 \shortauthors{Lucas et al.}
@@
 \begin{abstract}
-We present deep imaging of Sirius B, the closest and brightest white dwarf, to constrain post-main-sequence planetary evolution in the Sirius system.
+Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.
+We present deep imaging of Sirius B, the closest and brightest white dwarf, in order to constrain post-MS planetary evolution in the Sirius system.
 We use Keck/NIRC2 in \Lp-band (\qty{3.776}{\micro\meter}) across three epochs in 2020 using the technique of angular differential imaging.
-Our observations are speckle-limited out to \qty{1}{\au} and background-limited beyond.
-The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} \Lp absolute magnitude.
-We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits, and achieve sub-Jupiter sensitivities at sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}.
+Our observations are contrast limited out to \qty{1}{\au} and background limited beyond.
+The 5$\sigma$ detection limits from our best performing epoch are \numrange{17}{20.4} absolute magnitude.
+We consider multiple planetary formation pathways in the context of Sirius B's evolution to derive mass sensitivity limits using the ATMO2020 and Sonora Bobcat model grids.
+We achieve sub-Jupiter sensitivities and sub-AU separations, reaching \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} down to a sensitivity of \qtyrange{0.7}{1.2}{\jupitermass} at \textgreater\qty{1}{\au}.
 Consistent with previous results, we do not detect any companions around Sirius B.
-Our strong detection limits demonstrate the potential of using high-contrast imaging to characterize nearby white dwarfs.
+Our excellent detection limits, even without coronagraphy, demonstrate the capabilities for modern high-contrast imaging studies of nearby (\textless\qty{25}{\parsec}) white dwarfs.
 \end{abstract}
@@
 
-In recent decades thousands of exoplanets have been discovered orbiting stars that will eventually leave the stability of the main-sequence (MS) \citep{akesonNASAExoplanetArchive2013}.
-The eventual fate of planets around these stars is uncertain due to the large expansion, stellar winds, and high irradiation encountered during giant branch evolution \citep{verasPostmainsequencePlanetarySystem2016}.
-Despite this, evidence from white dwarf pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
-Discovery and characterization of post-MS planets is essential to study how they transform and how they interact with their hosts during the most critical phases of stellar evolution.
+In recent decades astronomers have discovered thousands of exoplanets orbiting stars that will eventually evolve into giants and then white dwarfs \citep{akesonNASAExoplanetArchive2013}.
+The fate of planets around these stars beyond the main-sequence (MS) is uncertain due to the large expansion, stellar winds, and high irradiation encountered on the giant branch \citep{verasPostmainsequencePlanetarySystem2016}.
+Despite this, direct evidence from white dwarf (WD) pollution \citep{juraExternallyPollutedWhite2007,xuSpitzerObservationsWhite2012}, debris disks \citep{deruyterKeplerianDiscsPostAGB2006,zuckermanAncientPlanetarySystems2010,koesterFrequencyPlanetaryDebris2014}, and substellar companions \citep[e.g.,][]{luhmanDiscoveryCandidateCoolest2011,vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} culminate to suggest planetary systems beyond the MS are more common than previously thought.
+Discovery and characterization of post-MS planets is essential to study planetary system evolution and planet-star interaction during the most critical phases of stellar evolution.
 
-The post-MS lifetimes of intermediate-mass stars (\qtyrange{1}{8}{\solarmass}) comprises a relatively brief period of giant branch evolution before all nuclear fusion ends and the stars become white dwarfs.
-As the main-sequence star runs out of hydrogen to burn in its core, it expands to hundreds of times its size, engulfing any companions within the stellar radius.
-When helium fusion ignites, the giant star becomes three to four orders of magnitude brighter, causing stellar winds and strong irradiation.
-Eventually, the star runs out of fuel and concludes its nuclear burning, becoming a white dwarf.
-The white dwarf begins cooling, becoming three to four orders of magnitude dimmer than its MS progenitor.
+The evolution of intermediate mass stars (\qtyrange{1}{8}{\solarmass}) comprises a violent and relatively brief giant branch evolution before all nuclear fusion ends and the stars become WDs.
+As the MS star runs out of hydrogen to burn in its core, it will expand to 100s of times its size, engulfing any companions within the stellar radius.
+When helium fusion ignites the giant star becomes \numrange{3}{4} orders of magnitude brighter than its MS progenitor, causing stellar winds and strong irradiation.
+Eventually the star will run out of fuel and conclude its nuclear burning and become a WD.
+The WD begins cooling, becoming \numrange{3}{4} orders of magnitude dimmer than its MS progenitor.
 
 There is limited knowledge of planetary systems around evolved stars.
-The pathway for a \textit{first-generation} planet to survive around a post-MS host is violent and uncertain.
-During giant branch evolution, the planet needs to escape engulfment as well as tidal shredding from its inflated host \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
-Planets which survive their hosts' inflation are privy to the effects of stellar winds and the high luminosities of asymptotic giant stars \citep{mustillForetellingsRagnarokWorldengulfing2012,mustillMainsequenceProgenitorConfigurations2013,verasPostmainsequencePlanetarySystem2016}.
-The stellar winds will chemically enrich the circumstellar environment with metals and dust, and the high luminosity and proximity to the stellar surface will cause strong irradiation, and therefore heating \citep{spiegelJupiterWillBecome2012}.
-The mass-loss from the stellar winds can adiabatically expand a planet's orbit \citep{jeansCosmogonicProblemsAssociated1924}, potentially destabilizing the orbit and chaotically ejecting the planet \citep{kratterStarHoppersPlanet2012}.
-Numerical simulations suggest that a giant planet needs to be $\gtrsim$\qty{5}{\au} from a solar-like host to escape expansion and tidal effects \citep{spiegelJupiterWillBecome2012,nordhausOrbitsLowmassCompanions2013}.
-When combined with adiabatic orbit expansion, this creates a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{10}{\au}.
+The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain.
+For a planet to survive the giant branch evolution, it first needs to escape engulfment as well as tidal shredding \citep{burleighImagingPlanetsNearby2002a,nordhausOrbitsLowmassCompanions2013}.
+Surviving planets are subject to adiabatic orbit expansion, which can potentially de-stabilize multi-object systems, stellar winds, and high irradiation which enriches the circumstellar environment with metals and dust, and strongly heats planets close to the giant star \citep{mustillForetellingsRagnarokWorldengulfing2012,verasPostmainsequencePlanetarySystem2016}.
+The expansion and tidal effects on the circumstellar environment create a ``forbidden'' region of exoplanet phase space for orbital separations closer than $\sim$\qty{5}{\au}.
 
 Recent discoveries of exoplanets in ``forbidden'' formation regions \citep{vanderburgGiantPlanetCandidate2020,blackmanJovianAnalogueOrbiting2021} suggest evidence for a class of \textit{second-generation} companions.
-\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where, in multi-star systems, the stellar ejecta from an evolving giant star forms a protoplanetary disk around another star (or, in fact, the whole system).
-These disks serve as reservoirs of material and energy for planet formation, which could be kick-started by a first-generation planet acting as a seed.
-Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with both gravitational-instability (``hot start'') and core-accretion (``cold start'') formation theories \citep{marleyLuminosityYoungJupiters2007,spiegelSpectralPhotometricDiagnostics2012a}.
+\citet{peretsSecondGenerationPlanets2010,peretsPlanetsEvolvedBinary2011} describe a planetary formation pathway where in multi-star systems the stellar ejecta from an evolving giant star forms a protoplanetary disk around a separate star (or, in fact, the whole system).
+Such disks would have lifetimes of \qtyrange{1}{100}{\mega\year} which is commensurate with ``hot-start'' planetary formation timescales \citep{spiegelSpectralPhotometricDiagnostics2012a}.
+A first-generation planet could act as a seed for planetesimal growth in these disks, too.
 Another formation pathway considers the chaotic evolution of companion orbits due to stellar mass loss in the presence of multiple bodies.
 \citet{peretsTripleEvolutionDynamical2012} describe this interaction for triplet systems in detail (the ``triple evolution dynamical interaction'', or TEDI).
-\citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted three-body problem and concluded up to $\sim$10\% of all white dwarf binaries might contain ``star-hopper'' planets which migrate between the stars.
+\citet{kratterStarHoppersPlanet2012} explore similar dynamical interactions in the restricted 3-body problem and concluded up to $\sim$10\% of all WD binaries might contain ``star-hopper'' planets which migrate between the stars.
 
 Previous searches for substellar companions around white dwarfs \citep[e.g.,][]{debesAreThereUnstable2002,hoganDODOSurveyII2009,luhmanDiscoveryCandidateCoolest2011,xuExtremeAOSearchGiant2015a} have primarily focused on detecting wide-orbit planets which survived the giant branch evolution of their hosts.
-Recent evidence and theoretical works \citep[e.g.,][]{xuSpitzerObservationsWhite2012,koesterFrequencyPlanetaryDebris2014,verasPostmainsequencePlanetarySystem2016,vanderburgGiantPlanetCandidate2020}, though, suggest ``forbidden'' regions of planetary evolution are worth investigating for exotic post-MS planets.
-These planets would provide crucial insight into planetary system evolution and planet-star interactions during giant branch evolution.
+We posit that previously ``forbidden'' regions of planetary evolution are worth investigating by utilizing the modern high-contrast instrumentation that has come to fruition in the recent decade.
+In the rest of this report, we will discuss high-contrast imaging as a detection technique for post-MS systems (\Cref{sec:imaging}).
+We will introduce the Sirius system as a potential candidate for post-MS companions, along with previous studies of WD Sirius B (\Cref{sec:sirius}).
+We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Cref{sec:obs}, \Cref{sec:analysis}).
+Lastly, we will discuss our results within the context of Sirius and post-MS systems as well as future directions for post-MS imaging (\Cref{sec:results}, \Cref{sec:conclusion}).
 
-Direct imaging is well-suited for finding planets around white dwarfs due to the intrinsic faintness of the host (compared to a MS star) and lack of spectral features for radial velocity studies \citep{burleighImagingPlanetsNearby2002a}.
-With direct imaging, exoplanets can be detected and characterized independently from the orbital period of the planet, the stellar radius, or stellar spectrum, which makes it powerful compared to broadband spectral-energy distribution analysis or transit photometry methods.
-High-contrast imaging pushes direct imaging to its limits using large-aperture telescopes, adaptive optics, coronagraphy, low-noise detectors, image-processing, and observational techniques.
-Despite the power of high-contrast imaging, very few observations have been carried out for white dwarfs (a recent example is \citealt{pathakHighContrastImaging2021}).
+\section{Directly imaging post-MS systems}\label{sec:imaging}
 
-Exoplanets are faint enough that in certain cases only a few photons per second reach the detector.
-Host stars are typically many orders of magnitude brighter than the thermal emission of giant planets ($\sim10^{\text{-}8}$), and planets have very small angular separations from their hosts, which makes it difficult to disentangle the planet-light from the stellar diffraction pattern \citep{traubDirectImagingExoplanets2010}.
-In addition, atmospheric seeing and instrumental aberrations greatly reduce the sensitivity to exoplanets due to the manifestation of quasi-static perturbations of the instrumental point-spread function (speckles, see \citealp{guyonExtremeAdaptiveOptics2018}).
-Adaptive optics (AO) corrects a large percentage of the effects of speckles but has decreasing efficacy for dim targets due to the photon-limited nature of modern AO instrumentation.
-AO is also paramount for enabling coronagraphy, which attenuates on-axis starlight while transmitting off-axis signal, up to some inner working angle.
+High-contrast imaging is a powerful technique for discovering and characterizing exoplanets.
+Directly imaging a circumstellar companion is difficult, though.
+The typical astrophysical flux ratios (contrasts) for a Sun-Jupiter analog in the near-infrared (NIR) are $\sim$$10^{\text{-}8}$, and for a Sun-Earth system are $\sim$$10^{\text{-}10}$ \citep{traubDirectImagingExoplanets2010}.
+In addition, the close angular separations of planets make it difficult to detect them over the diffraction pattern of their host and other noise sources.
+Thermal emission from exoplanets peaks well into the infrared, on the Rayleigh-Jeans limit of the stellar spectrum.
+This makes infrared observations preferred over optical or ultraviolet observations due to the reduced contrast.
 
-Typical high-contrast targets are nearby young objects observed in the near-infrared.
-Younger planets are brighter, thanks to their latent formation heat \citep{fortneyGiantPlanetInterior2010} and observing them in the near-infrared corresponds with their peak blackbody emission.
-Nearby targets have larger angular separations between potential planets and their hosts, which makes it easier to separate the planet from the star.
-Nearby targets are also intrinsically brighter, enabling effective AO control.
-White dwarfs are atypical high-contrast targets due to their age and sparsity, but their relative faintness is compelling for the reduced star-planet flux ratio.
-In addition, a post-MS planet would be much younger than the system age of a white dwarf and would therefore still retain a large portion of its latent heat, further motivating high-contrast searches of nearby white dwarfs.
+WDs are interesting targets for direct imaging- they are \numrange{3}{4} orders of magnitude fainter than their MS progenitors which reduces the contrast necessary to detect a companion.
+The high effective temperatures of WD photospheres pushes the peak thermal emission even further into the optical and ultraviolet, reducing the intrinsic contrast between the star and the planet.
+In addition, the lack of spectral features of WDs \citep{schatzmanTheorieDebitEnergie1945} makes them imprecise targets for the radial velocity technique.
+The small stellar radii of WDs lowers the transit probability significantly, although detections of substellar companions around WDs have been made \citep[e.g.,][]{vanderburgGiantPlanetCandidate2020}.
+The faintness of WDs proves challenging due to the high signal-to-noise ratio (S/N) required by modern adaptive optics (AO) instruments.
+This is exacerbated on ground-based telescopes which require extreme AO to counteract the effects of atmospheric seeing.
+This constrains potential companion searches to relatively bright targets ($m^R\lesssim$ 13).
+Implicitly, this also limits searches to nearby WDs ($d\sim$\qty{25}{\parsec}, \citealp{holberg25ParsecLocal2016}), which is beneficial for imaging because the limited inner working angle of the instrumentation will project to closer separations around closer stars.
 
-In this work we set out to perform high-contrast observations of Sirius B to search for post-MS planets.
-In the rest of this report, we will introduce the Sirius system as a potential candidate for post-MS planets, along with previous studies of white dwarf Sirius B (\Cref{sec:sirius}).
-We will detail our 2020 near-infrared observations of Sirius B with Keck/NIRC2, as well as our processing steps and statistical analysis for companion detection (\Crefrange{sec:obs}{sec:analysis}).
-Lastly, we will discuss our results within the context of Sirius and post-MS systems, as well as future directions for post-MS imaging (\Crefrange{sec:results}{sec:conclusion}).
+% \section{Post-MS evolution}\label{sec:post-ms}
+
+% There is limited knowledge of planetary systems around evolved stars.
+The pathway for a \textit{first-generation} planet around a post-MS host is violent and uncertain.
+The expansion of the stellar photosphere will engulf companions and cause tidal interactions, destroying planets or disrupting their orbits \citep{burleighImagingPlanetsNearby2002a, nordhausOrbitsLowmassCompanions2013}.
+Planets that escape engulfment will encounter stellar winds and strong irradiation, causing orbital expansion \citep{jeansCosmogonicProblemsAssociated1924}, enriching the circumstellar environment with metals and dust, and strongly heating planets close to the giant star \citep{verasPostmainsequencePlanetarySystem2016}.
+
+% The observational evidence for planets in post-MS systems is varied.
+WD atmospheres quickly separate heavy elements in their atmospheres due to their high surface gravity \citep{schatzmanTheorieDebitEnergie1945}, which causes the elements to sink and stratify.
+The time scale for this phenomena can be days to $\sim$\qty{1}{\mega\year}, significantly shorter than WD cooling ages, which means that most WD atmospheres are comprised of hydrogen, helium, and some carbon.
+However, metals heavier than carbon have been detected in WDs with cooling ages between \qtyrange{30}{500}{\mega\year}.
+A common explanation for the ``pollution'' of these WDs is the accretion of planetary material.
+This is backed up by the evidence of WD debris disks, although only a fraction of all polluted WDs are host to a disk \citep{koesterFrequencyPlanetaryDebris2014}.
+Chemical analysis shows the pollution is closer to planetary in origin rather than the interstellar medium.
+Most damning, though, is the correlation between the relative population of polluted WDs (25\% - 50\%) and the expected number of MS planet hosts \citep{koesterFrequencyPlanetaryDebris2014}.
+
+% suggest exoplanets on initially wide (\textgreater\qty{5}{\au}) orbits around intermediate-mass stars will survive expansion during the RGB phase.
+Planets very close to the Roche limit of the expanding red giant can still be shredded by tidal forces despite escaping engulfment, although the tidal forces are negligible on planets that are far from the Roche limit (and readily escape engulfment) \citep{nordhausOrbitsLowmassCompanions2013}.
+During the AGB phase, stellar mass loss adiabatically expands the orbit of the planet .
+In addition to \textit{first-generation} planets, there are potential methods for \textit{second-generation} planets to form after the violent RGB and AGB phases \citep{peretsSecondGenerationPlanets2010}.
+
+% The first search for substellar companions around white dwarfs was conducted by \citet{probstInfraredSearchVery1983}.
+They searched for infrared (IR) excess in their spectral energy distributions (SED) using broadband photometry.
+The IR excess would be indicative of thermal emission of faint material around the star, such as a circumstellar disk or giant planet.
+They studied $\sim$100 white dwarfs but found no companions.
+The same method was applied by \citet{zuckermanAncientPlanetarySystems2010}, who found excess IR emission around white dwarf G29-38.
+The emission was determined to be from a dust disk \citep{telescoObservationsG29381990}, which was associated with accretion onto the white dwarf's surface, polluting the stellar atmosphere \citep{koesterMetalsVariableG29381997}.
+It is estimated that while a third of white dwarfs are polluted, only a few percent have IR excesses \citep{bonsorInfraredObservationsWhite2017}.
+\citet{skemerSiriusImagedMidinfrared2011} suggested stellar radiation from stars hotter than \qty{15,000}{\kelvin} would sublimate dust, therefore, suppressing any IR excess.
+
+% Imaging is well-suited for studying evolved planetary systems, yet to date, only one planet has been imaged around a white dwarf.
+\citet{luhmanDiscoveryCandidateCoolest2011} discovered a companion around WD 0806-661B with a mass of \qty{7}{\jupitermass} on a wide \qty{2500}{\au} orbit using Spitzer.
+The ``Degenerate Objects around Degenerate Objects'' survey \citep[DODO;][]{hoganDODOSurveyII2009} observed 29 white dwarfs with Gemini/NIRI and VLT/ISAAC, reaching an average upper limit around $\sim$\qty{8}{\jupitermass} beyond \qty{35}{\au}.
+The young white dwarf GD 50 was observed using the extreme AO instrument SPHERE at the VLT \citep{xuExtremeAOSearchGiant2015a}, reaching sensitivity limits of \qty{4}{\jupitermass} at \qty{6.2}{\au}.
 
@@
 
-The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a $J=$-1.36 magnitude A1V star, and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{gaiacollaborationGaiaMission2016,bondSiriusSystemIts2017,gaiacollaborationGaiaEarlyData2021}.
-As mentioned previously, the proximity and intrinsic faintness of Sirius B (compared to a MS star) make it compelling for direct imaging.
+One fascinating target for post-MS observations is Sirius B, the closest and brightest WD to our solar system.
+The Sirius system is the 7th closest to the sun at \qty{2.7}{\parsec}, consisting of Sirius A, a -1.35 magnitude A1V star and Sirius B, a DA white dwarf with a \qty{50}{\year} orbit \citep{collaborationGaiaMission2016, bondSiriusSystemIts2017,collaborationGaiaEarlyData2021a}.
+As mentioned previously, the proximity and faintness of Sirius B (compared to a MS star) make it compelling for direct imaging.
 Additionally, the young system age ($\sim$\qty{225}{\mega\year}) means any giant planets would still retain much of their latent formation heat, increasing their luminosity in the IR \citep{fortneyGiantPlanetInterior2010}.
@@
 Sirius is one of the oldest studied star systems; the breadth and depth of knowledge about the binary gives exceptional precision for characterizing the circumstellar environment.
-Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius to date.
-Their astrometric uncertainties are over an order of magnitude improved from the visual orbit derived by \citet{vandenbosOrbitSiriusADS1960}.
-Following the procedure of \citet{gatewoodStudySirius1978}, \citet{bondSiriusSystemIts2017} derived dynamical masses of \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
+Initial astrometric measurements suggested a 50 year orbital period for Sirius B \citep{auwersOrbitSirius1864}.
+Most recently, \citet{bondSiriusSystemIts2017} used Hubble Space Telescope (HST) along with old photographic plates to compile the most precise orbital solution for Sirius, to date.
+They derived dynamical masses using their orbital solution and Hipparcos parallaxes: \qty{2.063+-0.023}{\solarmass} and \qty{1.018+-0.011}{\solarmass} for A and B, respectively.
 A companion around Sirius B would be affected by the orbit of Sirius A, and this constrained three-body system has been studied numerically \citep{holmanLongTermStabilityPlanets1999}.
-\citet{bondSiriusSystemIts2017} calculated the longest stable companion period around Sirius B to be \qty{1.8}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
+\citet{bondSiriusSystemIts2017} calculate the longest period stable companion around Sirius B is \qty{1.79}{\year}, which corresponds to a \qty{1.5}{\au} circular orbit.
 
-The total age of Sirius B is the combination of its white dwarf cooling age and the time from the zero-age main sequence (ZAMS) to the tip of the giant branch (TGB).
-We adapt the cooling age derived by \citet[Sec.~8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}.
-We use the updated white dwarf initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.
+The total age of Sirius B is the combination of its WD cooling age and the time from the zero-age MS (ZAMS) to the tip of the giant branch (TGB).
+We adapt the cooling age derived by \citet[sec.
+8]{bondSiriusSystemIts2017} of \qty{126}{\mega\year}.
+We use the updated WD initial-final mass relation (IFMR) of \citet{cummingsWhiteDwarfInitialFinal2018} to estimate the Sirius B progenitor mass of \qty{5.1\pm1.1}{\solarmass}.
 
@@
 The spread of ages derived by \citet{cummingsWhiteDwarfInitialFinal2018} from different models is $\sim$\qty{10}{\mega\year}.
-Determining stellar ages is challenging, and the age uncertainty of $\sim$4\% is exceptional compared to those typically obtained by dynamical analysis of young moving groups ($\sim$10\%) or gyrochronology ($\sim$15\%).
-The values for our adapted and derived parameters are compiled in \Cref{tbl:system}.
+An age uncertainty of $\sim$4\% is exceptional compared to the $\sim$10\% or worse of stars found in young moving groups, not to mention many stars cannot be precisely dated at all.
+These values are compiled in \Cref{tbl:system}.
 
-One of the peculiarities of the Sirius system is its large eccentricity, $e\sim0.6$ \citep{bondSiriusSystemIts2017}.
+One of the peculiarities of the Sirius system is its large eccentricity of 0.59 \citep{bondSiriusSystemIts2017}.
 If we assume the orbital expansion due to Sirius B's evolution was adiabatic, we can calculate the initial semi-major axis of the binary
@@
 In this case, the periastron of Sirius A and B would be \qty{3.52\pm0.52}{\au}.
-\citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate-mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}.
+\citet{verasPostmainsequencePlanetarySystem2016} tabulated the maximum stellar radius of intermediate mass stars during their giant evolution, from which we interpolate a maximum radius for Sirius B of \qty{5.104\pm0.075}{\au}.
 This means Sirius A certainly interacted with Sirius B and may have had a common envelope stage.
-Mass transfer and tidal circularization would be expected; however, the present-day eccentricity provides contrary evidence.
+Mass transfer and tidal circularization would be expected, however the present-day eccentricity provide contrary evidence.
 
-\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping,'' but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which would be expected to increase with mass transfer to conserve total angular momentum in the binary.
-\citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of a third body between \qtyrange{0.6}{5.5}{\solarmass}.
-\citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is a collision with one of the binary components.
-If Sirius B ejected a first-generation companion during its giant branch evolution, we estimate a $\sim$70\% probability of the planet colliding with Sirius A \citep[Fig.
-7]{kratterStarHoppersPlanet2012}, although this is far from disqualifying the potential for orbital capture.
-This is an interesting, although uncertain, explanation for the peculiar surface chemical abundances found on Sirius A \citep{landstreetAbundancesElementsHe2011a,takedaRotationalVelocitySirius2020a}.
-The variety in these studies shows the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
+\citet{bonacicmarinovicOrbitalEccentricitiesBinary2008} propose an explanation for the lack of tidal circularization called ``tidal-pumping'', but neglect to address the observed slow rotation speed of Sirius A \citep{grayPreciseRotationRates2014,takedaRotationalVelocitySirius2020a}, which we would expect to increase with mass transfer to conserve total angular momentum in the binary.
+\citet{peretsTripleEvolutionDynamical2012} suggest the present eccentricity could be due to the chaotic expulsion of third body between \qtyrange{0.6}{5.5}{\solarmass}.
+\citet{kratterStarHoppersPlanet2012} point out, though, that the most probable outcome of a planetary-mass companion in a chaotic orbital evolution is collision with one of the binary components.
+We extrapolate their Figure 7 using the parameters for Sirius to estimate a $\sim$70\% collision probability for an initial companion of Sirius B if it is chaotically ejected.
+When combined, these studies show the necessity to consider multiple, potentially exotic formation pathways for planetary candidates.
 
@@
 
-There have been many attempts to find planets in the Sirius system, but, so far, no planets have been detected.
-\citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond} ($\sim$\qty{200}{\jupitermass}), but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric limits down to \qty{10}{\milliarcsecond} ($\sim$\qty{20}{\jupitermass}).
+There have been many attempts to find planets in the Sirius system, but so far no planets have been detected.
+\citet{benestSiriusTripleStar1995} suggested the presence of a third body with astrometric perturbations of \qty{100}{\milliarcsecond}, but this has so far been unrealized, with \citet{bondSiriusSystemIts2017} reducing astrometric uncertainty down to $\sim$\qty{10}{\milliarcsecond}.
 The first modern imaging study searching for companions around Sirius B was \citet{schroederSearchFaintCompanions2000} who used the HST wide-field planetary camera (WFPC) at \qty{1}{\micro\meter}.
-Around the same time, \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
-These studies reported\footnote{A planetary atmosphere and evolution model are needed to derive mass sensitivity limits from imaging.
-Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:mass-limits}), biasing direct comparisons of mass limits.} sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
+Around the same time \citet{kuchnerSearchExozodiacalDust2000} searched in a narrower field of view (FOV) with HST/NICMOS at \qty{1}{\micro\meter}.
+A planetary atmosphere and evolution model are needed in order to derive mass sensitivity limits from imaging.
+Prior works to our own do not necessarily make the same model choices that we do (\Cref{sec:results}) biasing direct comparisons of mass limits.
+These studies combined reported sensitivities down to $\sim$\qty{10}{\jupitermass} at \qty{5.3}{\au} (\ang{;;2}).
 \citet{bonnet-bidaudADONISHighContrast2008a} used the ground-based ESO/ADONIS instrument in J, H, and Ks-band and reported a sensitivity of $\sim$\qty{30}{\jupitermass} at \qty{7.9}{\au} (\ang{;;3}).
@@
 \defcitealias{bondSiriusSystemIts2017}{B17}
-\defcitealias{gaiacollaborationGaiaEarlyData2021}{G21a}
+\defcitealias{collaborationGaiaEarlyData2021a}{G21a}
 \defcitealias{cummingsWhiteDwarfInitialFinal2018}{C18}
@@
     $t_\mathrm{sys}$ & 225 & \unit{\mega\year} & \citetalias{bondSiriusSystemIts2017,cummingsWhiteDwarfInitialFinal2018} \\
-    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{gaiacollaborationGaiaEarlyData2021} \\
-    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{gaiacollaborationGaiaEarlyData2021} \\
+    $\pi$ & \num{374.49\pm0.23} & mas & \citetalias{collaborationGaiaEarlyData2021a} \\
+    $d$ & \num{2.6702\pm.0016} & pc & \citetalias{collaborationGaiaEarlyData2021a} \\
     $a$ & \num{20.016\pm0.014} & \unit{\au} & \citetalias{bondSiriusSystemIts2017} \\
@@
     $m^{\mathrm{L}^\prime}$ & \num{9.1\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a} \\
-    $M^{\mathrm{L}^\prime}$ & \num{11.97\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,gaiacollaborationGaiaEarlyData2021} \\
+    $M^{\mathrm{L}^\prime}$ & \num{11.97\pm0.2} & & \citetalias{bonnet-bidaudADONISHighContrast2008a,collaborationGaiaEarlyData2021a} \\
     \enddata
@@
 
+% \begin{deluxetable}{ccccc}
+%     \tabletypesize{\small}
+%     \tablecaption{Observing parameters for the three epochs of data.
+All observations were carried out using the NIRC2 narrow camera (\qty{10}{\milliarcsecond\per\pixel}; \ang{;;2.5}$\times$\ang{;;2.5}) in \Lp-band (\qty{3.776}{\micro\meter}).
+Observation time is based on the frames that were selected for processing.
+Seeing values were measured at \qty{0.5}{\micro\meter} using a differential image motion monitor (DIMM) and averaged over the observing session.
+Seeing values, temperature, and water vapor measurements were all taken from the Maunakea weather center forecast archive.
+%     \label{tbl:obs}}
+%     \tablehead{
+%         \colhead{Epoch} &
+%         \colhead{2020-02-4} &
+%         \colhead{2020-11-21} &
+%         \colhead{2020-11-28} &
+%         \colhead{}
+%     }
+%     \startdata
+%     Sirius B offset & 11.20 & 11.27 & 11.27 & \unit{\arcsecond}  \\
+%     Sirius B PA & 67.90 & 66.42 & 66.38 & \unit{\degree} \\
+%     Obs. time & 1.44 & 2.91 & 2.44 & hr \\
+%     FOV rotation & 60.1 & 91.4 & 80.4 & \unit{\degree} \\
+%     FWHM & 79.9 & 76.4 & 82.2 & \unit{\milliarcsecond} \\
+%     Seeing & 0.936 & 0.871 & 1.23 & \unit{\arcsecond} \\
+%     Temp & 0.0 & 0.8 & -1.5 & \unit{\celsius} \\
+%     PWV & 0.7 & 3.5 & 3.0 & \unit{\milli\meter}
+%     \enddata
+% \end{deluxetable}
+
 \begin{figure}
     \centering
-    \epsscale{1.2}
+    \epsscale{1.1}
     \plotone{spike}
@@
 Despite Sirius B being the brightest white dwarf in the sky, it is still 10 magnitudes fainter than Sirius A, making it a technically challenging target, especially on ground-based telescopes.
-Our first attempt to observe Sirius B failed due to the light from Sirius A scattering into the FOV of the wavefront sensor (WFS).
-\citet[Sec.~2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
-To overcome these obstacles, we decided to use Sirius A as the AO guide star and off-axis guide to Sirius B.
+Our first attempt to observe Sirius B failed due to the strong scattered light from Sirius A.
+The adaptive optics (AO) calibration failed when the scattered light from Sirius A would sweep into the FOV of the wavefront sensor (WFS).
+Similarly, trying to deploy the focal-plane vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} failed when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of the scattered light.
+We did not try coronagraphy for the remaining observations.
+\citet[\S2]{viganHighcontrastImagingSirius2015} reported similar issues in their attempts to image Sirius B coronagraphically using VLT/SPHERE.
+In order to overcome these obstacles, we decided to used Sirius A as the AO guide star and off-axis guided on Sirius B.
 
-Sirius A saturated the WFS of the Keck facility AO system \citep{wizinowichPerformanceKeckObservatory2000}, so we attenuated the flux using a narrow laser-line filter.
+The Keck facility AO system \citep{wizinowichPerformanceKeckObservatory2000} was saturated by Sirius A, so we attenuated the flux using a narrow laser-line filter in the WFS.
 While still bright (appearing like a $\sim$5 magnitude star on the WFS), this was enough attenuation to close the AO loop.
@@
 In this mode, we noticed higher than usual drift in the focal plane, requiring manually recentering the target every 5 or 10 minutes.
-We tried to use the vortex coronagraph \citep{serabynKeckObservatoryInfrared2017} but gave up when the coronagraphic pointing control algorithm, \texttt{QACITS} \citep{hubyOnskyPerformanceQACITS2017a}, performed erratically in the presence of various diffracted light features.
-This rendered the coronagraph ineffective, especially with the large amounts of drift.
-We did not try coronagraphy for the remaining observations.
 
-During each observation, we took dark frames, dome-flat frames, and sky-flat frames for calibration.
-All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
-To avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.
+During each observation, we took dark frames and sky-flat frames for calibration.
+All observations used the large hexagonal pupil mask and set the telescope's field rotator to track the pupil in order to exploit the natural rotation of the sky via angular differential imaging \citep[ADI;][]{maroisAngularDifferentialImaging2006}.
+In order to avoid saturation from the sky background, we used \qty{0.4}{\second} integration times and coadded every \num{75} acquisitions, resulting in $\sim$\qty{30}{\second} per frame in the final images.
 
@@
 
-\subsection{Pre-processing}\label{sec:pre-processing}
+\subsection{Pre-processing}
 
 The raw images from NIRC2 required pre-processing before analyzing them for companions.
-For each epoch, we applied a flat correction using the sky-flat frames captured during observing.
-We determined the sky-flats had better flat correction than the dome-flats.
+For each epoch, we applied a flat correction using calibration frames captured during observing.
 We also removed bad pixels using a combination of \texttt{L.A.Cosmic} \citep{vandokkumCosmicRayRejectionLaplacian2001a} and an adaptive sigma-clipping algorithm.
-We removed the sky background using a high-pass median filter.
-For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions to simplify background subtraction, but this ended up performing worse than the high-pass filter.
-At this point, we manually discarded bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
-Then, we co-registered each frame with sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
+We removed sky background using a high-pass median filter with a box size of 31 pixels.
+For both the November epochs we tried exploiting the large focal plane drifts by dithering between two positions in order to simplify background subtraction, but this ended up performing worse than the high-pass filter.
+At this point frames were manually selected to remove bad frames, especially those with diffraction spikes from Sirius A within a few hundred pixels, like in \Cref{fig:spike}.
+Then, each selected frame was co-registered to sub-pixel accuracy using the algorithm presented in \citet{guizar-sicairosEfficientSubpixelImage2008}, followed by fitting each frame with a Gaussian PSF to further increase centroid accuracy.
 
-We centered the co-registered frames in the FOV and cropped them to the inner 200 pixels.
+The co-registered frames were shifted to the center of the FOV and cropped to the inner 200 pixels.
 With a pixel scale of \qty{10}{\milliarcsecond}, the crop corresponds to a maximum separation of \ang{;;1} or a projected separation of \qty{2.7}{\au}.
-We stacked the frames into data cubes for each epoch.
-We also measured the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
-For each epoch, we measured the full width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
-All the pre-processing code is available in Jupyter notebooks in a GitHub repository (\Cref{sec:data}).
+All the frames were stacked into data cubes for each epoch.
+We also measure the parallactic angle of each frame, including corrections for distortion effects following \citet{yeldaImprovingGalacticCenter2010}.
+For each epoch, we measure the full-width at half-maximum (FWHM) of the stellar PSF for use in post-processing by fitting a bivariate Gaussian model to the median frame from each data cube (\Cref{fig:psf}).
+All of the pre-processing code is available in Jupyter notebooks in a GitHub repository (\Cref{sec:data}).
 
@@
     \caption{\textbf{top row:} The \textit{significance} maps for each epoch accounting for small-sample statistics \citep{mawetFundamentalLimitationsHigh2014}.
-Typically, a critical value for detection is 5.
+Typically a critical value for detection is 5.
 \textbf{bottom row:} The STIM maps for each epoch calculated from each residual cube.
@@
 
-By taking data with the field rotator disabled (ADI), the stellar PSF will not appear to rotate but the FOV will appear to rotate.
-This allows for the effective separation of companion light from the PSF by spatially decorrelating speckles.
-After PSF subtraction, we derotated the frames according to their parallactic angle and collapsed the residuals with a variance-weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
+By taking data with the field rotator disabled (ADI), the point-spread function (PSF) will not appear to rotate while any potential companion will appear to rotate.
+This reduces the probability of removing companion signal when we subtract the stellar PSF model.
+After subtraction, the frames are derotated by their parallactic angle and combined with a weighted sum \citep{bottomNoiseweightedAngularDifferential2017a}, which reduces the pixel-to-pixel noise as the number of frames in the data cube increases.
 
 For this analysis, we used four ADI algorithms for modeling and subtracting the stellar PSF: median subtraction \citep{maroisAngularDifferentialImaging2006}, principal component analysis \citep[PCA, also referred to as KLIP;][]{soummerDetectionCharacterizationExoplanets2012a}, non-negative matrix factorization \citep[NMF;][]{renNonnegativeMatrixFactorization2018a}, and fixed-point greedy disk subtraction \citep[GreeDS;][]{pairetReferencelessAlgorithmCircumstellar2019a,pairetMAYONNAISEMorphologicalComponents2020}.
-We also applied the median subtraction and PCA algorithms in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
-We used the open-source \texttt{ADI.jl} Julia package for implementations of the above algorithms \citep{lucasADIJlJulia2020}.
+The median subtraction and PCA methods were also applied in an annular method, where we modeled the PSF in annuli of increasing separation, discarding frames that have not rotated at least 0.5 FWHM \citep{maroisAngularDifferentialImaging2006}.
+These algorithms are implemented in the open-source \texttt{ADI.jl} Julia package \citep{lucasADIJlJulia2020}.
 
-We determined the best performing PSF subtraction algorithm by measuring the sensitivity to companion signal through repeated injection and recovery of a model PSF.
-We used a known, fixed S/N for injection to derive the 5$\sigma$ detection limits at various positions within the FOV and azimuthally averaged the results to produce a contrast curve.
-We calculated both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
+We determined the best performing PSF subtraction algorithm by measuring the throughput of companion signal through repeated injection and recovery.
+By using a known, fixed S/N for injection, the 5$\sigma$ detection limits can be measured at various positions within the FOV and are azimuthally averaged to produce a \textit{contrast curve}.
+We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawetFundamentalLimitationsHigh2014}.
 We employed two different detection metrics to search for companions in the residual data: the Gaussian significance map \citep{mawetFundamentalLimitationsHigh2014} and the standardized trajectory intensity mean map \citep[STIM map;][]{pairetSTIMMapDetection2019}.
 These maps assign the likelihood of a companion to each pixel using different assumptions of the residual statistics.
-We used \texttt{ADI.jl} for calculating these metrics.
+These three metrics are calculated using the methods available in \texttt{ADI.jl}.
 The collapsed residual frames along with the above metrics for each algorithm and epoch are in Appendix~\ref{sec:adi-results}.
@@
 A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components).
-For PCA, NMF, and GreeDS algorithms, we created sets of residual cubes, varying the number of components from 1 to 10.
+For PCA, NMF, and GreeDS algorithms, we varied the number of components from 1 to 10, creating a residual cube for each iteration.
 We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\Cref{fig:pca-contrast-curves}).
-In our analysis, we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairetSignalProcessingMethods2020} as an ensemble statistic.
+In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairetSignalProcessingMethods2020} as an ensemble statistic.
 The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map.
-We expect a real companion to be present in many different residual cubes from the same dataset, so this ensemble statistic gives us a probability map without determining the number of components \textit{a priori}.
+A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components.
 The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in Appendix~\ref{sec:adi-results}.
-All the code and data used for this analysis is available in a GitHub repository (\Cref{sec:data}).
+All of the code used for this analysis is available in a GitHub repository (\Cref{sec:data}).
 
@@
     \caption{The contrast curves for the best performing algorithm from each epoch.
-The solid lines are the Gaussian 5$\sigma$ contrast curves, and the dashed lines are the Student-t corrected curves.
-The absolute magnitude is calculated using an absolute magnitude for Sirius B of 11.97.
+The solid lines are the Gaussian 5$\sigma$ contrast curves and the dashed lines are the Student-t corrected curves.
+The absolute magnitude are calculated using an absolute magnitude for Sirius B of 11.97.
 The expected upper limit for a dynamically stable orbit of \qty{1.5}{\au} is plotted as a vertical dashed line.
@@
 \textbf{(a)} The absolute magnitudes are converted to masses using the ATMO2020 isochrone grid with non-equilibrium chemistry and weak convective mixing.
-The solid lines are the Gaussian 5$\sigma$ detection limits, and the dashed lines are the Student-t corrected limits.
-The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the white dwarf cooling age of Sirius B (\qty{126}{\mega\year}).
-The relative difference between the ages (first-generation vs.
-second-generation) comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}.
+The solid lines are the Gaussian 5$\sigma$ detection limits and the dashed lines are the Student-t corrected limits.
+The two ages represent the ages of two potential formation pathways, one of which is the system age (\qty{225}{\mega\year}), the other is the WD cooling age of Sirius B (\qty{126}{\mega\year}).
+The relative difference between the ages comes out to $\sim$\qty{0.3}{\jupitermass} at \qty{1}{\au}.
 \textbf{(b)} The absolute magnitudes are converted to masses using the Sonora Bobcat grid with solar metallicity (solid lines) and with +\qty{0.5}{dex} metallicity (dotted lines).
@@
 For the first two epochs, full-frame median subtraction had the best contrast at almost all separations.
-For the last epoch, annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
-When processed with this algorithm, we were unable to retrieve a 100 S/N injected companion with 5$\sigma$ significance in the innermost annulus.
-The contrast in this region is ill-determined and therefore not plotted.
+For the last epoch annular PCA subtraction with 2 principal components and a rotation threshold of 0.5 FWHM produced the best contrast at close separations (\qtyrange{0.2}{0.4}{\arcsecond}) and had similar performance to other algorithms beyond \ang{;;0.4}.
+This algorithm was unable to detect a 100 S/N companion injected into the innermost annulus with 5$\sigma$ significance.
+The contrast for this innermost annulus is therefore not plotted.
 \Crefrange{fig:residuals}{fig:detection} show the collapsed residual frames from each epoch, along with the Gaussian significance maps and STIM maps.
 
-We show the contrast curves from the best-performing algorithm for each reduction in \Cref{fig:contrast}.
-We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.1 (adapted from Ks-band magnitude from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{gaiacollaborationGaiaEarlyData2021}.
+We show the contrast curves from the best performing algorithm for each reduction in \Cref{fig:contrast}.
+We determine the limiting sensitivities in terms of the planetary mass by first calculating the contrast-limited absolute magnitude using an \Lp-band magnitude for Sirius B of 9.1 (adapted from Ks-band magnitude from \citealp{bonnet-bidaudADONISHighContrast2008a}) and a distance modulus of \num{-2.87} \citep{collaborationGaiaEarlyData2021a}.
 We divide \Cref{fig:contrast} into two regimes: speckle-limited and background-limited.
@@
 Here we reach a median 5$\sigma$ detection limit of $\sim$19 magnitude (\Lp).
-This regime is mainly constrained by the quality of the AO correction and the PSF subtraction method.
-The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves and is primarily limited by the sky brightness.
+This regime is constrained by the quality of the AO correction and the PSF subtraction method, mainly.
+The background-limited regime (\textgreater\qty{1}{\au}) is characterized by the flattening of the contrast curves, and is primarily constrained by the sky brightness.
 In this region, we reach 20.4 magnitude (\Lp) in the 2020-11-21 epoch.
@@
 The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions.
-Nonetheless, we estimated astrometry for blobs from each epoch (\Cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a} using the open-source \texttt{orbitize} Python package \citep{bluntOrbitizeComprehensiveOrbitfitting2020}.
+Nonetheless, we estimated astrometry for blobs from each epoch (\Cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{bluntOrbitsImpatientBayesian2017a}.
 We generated $10^4$ orbits, none of which constrained the points from each epoch (Appendix~\ref{sec:orbits}).
 This implies non-Keplerian motion and we take this as direct evidence against the blobs being substellar companions of any kind.
-We considered the possibility that the blobs are scattered light from a circumstellar debris disk, but this is highly unlikely given the brightness of the blob and the lack of IR excess that such a massive disk would radiate \citep{skemerSiriusImagedMidinfrared2011}.
-The signal can simply be explained as residual starlight not removed during PSF subtraction.
+The signal can be simply explained as residual starlight not removed during PSF subtraction.
 
-\subsection{Mass detection limits}\label{sec:mass-limits}
+\subsection{Mass detection limits}
 
-To convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid.
+In order to convert our photometric detection limits to mass limits we must employ an appropriate planetary atmosphere model and evolution grid.
 This is not a trivial task, as the effects of post-MS stellar evolution on planets are highly uncertain and not readily modeled in the currently available grids.
-In particular, we would like to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds.
-We used the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} with non-equilibrium chemistry due to weak vertical mixing for our solar metallicity model, following \citet{pathakHighContrastImaging2021}.
-ATMO2020 models very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012} but are not available for non-solar metallicities.
-To explore metal enrichment, we employed the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicities.
+In particular, we want to study the effects of metal and dust enrichment of the circumstellar environment from stellar winds.
+We start with the ATMO2020 model grid \citep{phillipsNewSetAtmosphere2020a} for our solar metallicity model.
+Following \citet{pathakHighContrastImaging2021}, we use the non-equilibrium chemistry models with weak vertical mixing, which model very cool objects better than previous grids such as AMES-Cond \citep{allardModelsVerylowmassStars2012}.
+The ATMO2020 models are not available for non-solar metallicities, yet, so we also employ the Sonora Bobcat grid \citep{marleySonoraBobcatCloudfree2021,marleySonoraBrownDwarf2021} at both solar and +\qty{0.5}{dex} metallicity.
 
 To determine the correct isochrone for the grids, we consider two formation scenarios.
-If a first-generation planet survived the giant phase of Sirius B through star hopping, it would have an age close to the system age of \qty{225}{\mega\year}.
-If the planet formed in a disk of stellar ejecta during the giant branch evolution, the age would be closer to the white dwarf cooling age of \qty{126}{\mega\year}.
+If a first-generation planet survives the giant phase of Sirius B through star hopping, it would have an age closer to the system age of \qty{225}{\mega\year}.
+If the planet formed in a disk of stellar ejecta during the AGB phase, the age would be closer to the WD cooling age of \qty{126}{\mega\year}.
 If the planet formed in such a disk, or if it accreted some of the material, it would almost certainly have peculiar chemistry, although it is uncertain exactly how the relative abundances would change.
@@
 The second panel uses the Sonora models to demonstrate the relatively minor effects ($\sim$\qty{0.1}{\jupitermass}) the increased metallicity has on the mass limits.
-We could not fully utilize the Sonora grid because there are no atmospheric models simulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models needed for the background-limited regimes.
+We could not fully utilize the Sonora grid, though, because there are no atmospheric models tabulated for effective temperatures below \qty{200}{\kelvin}, which are precisely the models we need for the background-limited regimes.
 Overall, we constrain our detection limits to \qtyrange{1.6}{2.4}{\jupitermass} at \qty{0.5}{\au} (\ang{;;0.19}) in the speckle-limited regime and ultimately \qtyrange{0.7}{1.1}{\jupitermass} at \textgreater\qty{1}{\au} (\ang{;;0.38}) in the background-limited regime.
@@
 Post-MS planetary evolution has historically been limited to theoretical work.
-Recently, though, increasingly strong and diverse observational constraints, including new detections, have invigorated the field.
-We set out in this work to search nearby white dwarf Sirius B for post-MS planets.
-The Sirius system is one of the most well studied in history, and its precise characterization improves our systematic uncertainties.
-It is highly unlikely a first-generation planet survived Sirius B's giant branch evolution, but no previous imaging efforts have directly addressed post-MS formation in their analyses.
-
+Recently, though increasingly strong and diverse observational constraints have invigorated the field.
+We set out in this work to study the nearby Sirius system for post-MS companions around Sirius B.
+The Sirius system is one of the most well studied in history, with Sirius B being the target of companion searches from the visible to the IR.
+While it is highly unlikely a first-generation planet survived post-MS evolution, imaging efforts have gradually increased the sensitivity to second-generation planets.
 In this work, we presented high-contrast images of Sirius B in the near-IR.
-Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, down to \num{20.4} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
+Our 5$\sigma$ sensitivity limits are the best that have been reached for Sirius B so far, reaching \num{20.4} \Lp absolute magnitude at \textgreater\qty{1}{\au}.
 We consider multiple planetary formation pathways yielding ages between \qtyrange{126}{225}{\mega\year} and explore the effects of enriched metallicity.
@@
 Our observations also show how the high precision of the parameters of the Sirius system directly benefits the sensitivity to planets.
-For example, the $\sim$4\% relative age uncertainty (\Cref{sec:sirius}) translates to a mass uncertainty below \qty{0.1}{\jupitermass}.
+For example, the $\sim$4\% relative uncertainty of Sirius B's age translates to mass detection limit uncertainty below \qty{0.1}{\jupitermass}.
 Despite the high sensitivity of this study, we found no significant evidence for a companion around Sirius B, consistent with previous results.
 
-Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach strong detection limits.
-Our detection limits benefit directly from the precise stellar characterization of the Sirius system, as well as the proximity and brightness of Sirius B.
-With laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018} the limiting magnitude for sufficient AO performance is improved ($m^R\lesssim$ \num{19}).
-Future extremely large telescopes will benefit from increased collecting areas and smaller inner working angles due to the larger aperture diameters.
-The Thirty Meter Telescope (TMT), for example, will have LGS AO in its first-generation instrument suite (NFIRAOS), which will significantly improve the faintness limits of its high-contrast instrumentation.
-We suspect future work using LGS AO on current and next-generation telescopes will be capable of studying nearby white dwarf systems at the sub-AU and sub-Jupiter-mass scales \citep{holberg25ParsecLocal2016}.
-Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the main sequence.
+Although our observations yield no detections, we illustrate the capability of modern high-contrast instrumentation, even without coronagraphy, to reach exceptional detection limits.
+We took the WD sample from \citet{holberg25ParsecLocal2016} and analyzed the 7 binary systems.
+The median distance of this subset is \qty{20}{\parsec}.
+In this work, our inner working angle due to the stellar PSF was $\sim$\qty{80}{\milliarcsecond}, which would be a projected separation of \qty{1.6}{\au} at \qty{20}{\parsec}.
+The median R magnitude is $\sim$\num{15.2}, though, which may prove challenging for natural guide star AO.
+However, with laser guide stars \citep[LGS; e.g.,][]{vandamKeckObservatoryLaser2006,baranecRoboAO2FacilityRapid2018}, the limiting magnitude increases significantly ($m^R\lesssim$ \num{19}).
+We suspect future work using LGS AO is capable of studying WD systems at the sub-AU and sub-Jupiter-mass scales.
+Such observations could significantly improve our theories of planetary formation and stellar evolution beyond the MS.
 
-Future space-based observations with the James Webb Space Telescope (JWST) will avoid the effects of atmospheric seeing and the bright sky background.
+We also consider future space-based observations with the James Webb Space Telescope (JWST), eliminating the effects of atmospheric seeing and the bright sky background.
 For example, using JWST/NIRCAM in long-wavelength imaging mode has a limiting magnitude of $\sim$25 in the F480M filter.
-The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby white dwarfs, depending on the contrast-limited performance of NIRCAM.
+The pixel scale (\qty{0.06}{\arcsecond\per\pixel}) and PSF size ($\sim$\ang{;;0.3}) are adequate for sub-AU observations of nearby WDs, depending on the contrast-limited performance of NIRCAM.
 Unfortunately, Sirius B is far too bright and too close to Sirius A to observe with JWST without severe saturation.
@@
 
-All the code used for pre-processing and reducing the data is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
-The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}} Inquiries regarding data and code are welcome.
+All of the code used for pre-processing data, reducing data, and generating the figures is available under an open-source license in a GitHub repository.\footnote{\url{https://github.com/mileslucas/sirius-b}} This code includes all of the scripts for generating each figure in this manuscript.
+The pre-processed data cubes and parallactic angles are available on Zenodo under an open-source license.\footnote{\dataset[10.5281/zenodo.5115225]{\doi{10.5281/zenodo.5115225}}} We hope that this improves the reproducibility of the work as well as providing data for future investigations.
+Please reach out to the corresponding author for further inquiries regarding data and code availability.
 
@@
 ADI.jl \citep{lucasADIJlJulia2020},
-astropy \citep{astropycollaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
+astropy \citep{collaborationAstropyCommunityPython2013,astropycollaborationAstropyProjectBuilding2018},
 Julia \citep{bezansonJuliaFreshApproach2017},
 numpy \citep{harrisArrayProgrammingNumPy2020},
-orbitize \citep{bluntOrbitizeComprehensiveOrbitfitting2020},
 scikit-image \citep{waltScikitimageImageProcessing2014},
@@
 We found multiple interesting blobs in the reduced data that were not statistically significant.
-Nonetheless, we tried fitting Keplerian orbits using OFTI \citep{bluntOrbitsImpatientBayesian2017a} to determine the feasibility of the blobs being astrophysical companions.
-We began by estimating the astrometry of the blobs by eye in the reduced data (\Cref{tbl:astrometry}, \Cref{fig:prov-orbit}).
-We tried simulating $10^4$ orbits via rejection sampling with OFTI, but none of the generated orbits contained all three points in their solution.
-Overall we determined these blobs are not companions and are most likely systematic noise from the stellar PSF.
+Nonetheless, we tried fitting Keplerian orbits using OFTI to determine the feasibility of the blobs being real companions.
+We began by estimating the astrometry of the blobs by eye in reduced data (\Cref{tbl:astrometry}, \Cref{fig:prov-orbit}).
+We tried simulating $10^4$ orbits via rejection sampling with OFTI but no generated orbit was able to constrain all three points.
+Overall we determine these blobs are not real companions and are most likely systematic noise in the stellar PSF.
 
@@
     \tablecaption{Provisional astrometry for a blob of interest from each epoch.
-The separation and offset are relative to Sirius B.
-The uncertainties were derived from the FWHM of the PSF from each epoch.
+The separation and offset are in relation to Sirius B.
+The uncertainties are derived from the FWHM of the PSF from each epoch.
     \label{tbl:astrometry}}
@@
     \plotone{orbit_frames}
-    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residual frames from each epoch.
+    \caption{Provisional astrometry (white circles) displayed on collapsed and derotated residuals from each epoch.
 Each frame was cropped to the inner $\sim$\qty{0.7}{\au} (\ang{;;0.25}) and the inner two FWHMs have been masked out.

### 2021-12-07 paper/adi_results.tex
update non-figureset appendix plots

@@
 The top-left frame is the collapsed residual frame, the top-right is the Gaussian S/N map, the bottom-left is the STIM probability map, and the bottom-right is the Student-t corrected significance map.
-In each frame the inner FWHM is masked out.
+In each frame, the inner two FWHMs are masked out.
 The right figure show the Gaussian (solid line) and Student-t corrected (dashed curve) 5$\sigma$ contrast curve.
@@
     \figurenum{11}
-    \epsscale{0.9}
     \plotone{reports/2020feb04_pca_mosaic}
     \caption{Collapsed residual frames from the first epoch using PCA reduction with 1-10 components.
-The figures share a common scale and the inner FWHM is masked out for all the frames.
-Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
+The figures share a common scale and the inner two FWHMs are masked out for all the frames.
+Outputs for the other epochs and the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository}
 \end{figure}
@@
     \figurenum{12}
-    \epsscale{0.9}
     \plotone{reports/2020feb04_pca_contrast_curves}
     \caption{5$\sigma$ Gaussian contrast curves for the first epoch using PCA reduction with 1-10 components.
-The left two figures are the average STIM probability map, and the SLIM detection map.
+The left two figures are the STIM probability map and the SLIM detection map.
 For both of these maps, a typical cutoff value is 0.5.
-Outputs for the other epochs and for the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
+Outputs for the other epochs and the NMF and GreeDS algorithms (9 figures) are in the online figure set and the GitHub repository.}
     \label{fig:pca-contrast-curves}
